### 2017-11-13 Writing/Proposal/tex/paper.tex
Add ressources.

\documentclass[12pt]{scrartcl}

\usepackage[american]{babel}

\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{paralist}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{geometry}
% \geometry{a4paper,body={5.8in,9in}}
\geometry{a4paper}

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{placeins}
\usepackage{subcaption}

\usepackage{setspace}

\setlength{\parindent}{0pt}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ab hier steht der eigentliche Text:
\begin{document}
\title{Thesis Title}
\subtitle{Bachelor Thesis Proposal \& Work Plan}
% bei Masterarbeit ggf. ändern
\author{First Name + Name\\ \small{matriculation number: xxxxxxx}\\ \small{mail-address}}
\date{\today}
\maketitle

\section{Motivation}\label{sec:motivation}

\section{Task Objectives}\label{sec:task-objectives}

\section{Task Description}\label{sec:task-description}

\section{Time-Schedule and Subtasks}\label{sec:schedule-and-subtasks}

% % %
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.9\textwidth]{timeschedule}
	\caption{Sketch of the time schedule for the work on the thesis}
	\label{fig:time-schedule}
\end{figure}
% % %
\section{Initial Document Structure}\label{sec:doc-structure}
\begin{enumerate}
	\item Introduction
	\item ...
\end{enumerate}
\newpage
\bibliography{literature}
\bibliographystyle{myalphadin}

\vspace{6cm}

\begin{center}
     \begin{tabular}{l p{0.1\textwidth} r}
       \cline{1-1} \cline{3-3}
       \begin{minipage}[t]{0.4\textwidth}
         \centering
         Supervisor)\\(Titel Vorname Nachname)
         \end{minipage}
&
         \begin{minipage}[t]{0.2\textwidth}
         \end{minipage}
&
         \begin{minipage}[t]{0.4\textwidth}
           \centering
           Student(in)\\(Vorname Nachname)
         \end{minipage}
     \end{tabular}
\end{center}

\end{document}

### 2017-11-20 Writing/Proposal/tex/paper.tex
Added updated proposal kickoff talk and proposal.
Worked on Proposal.

@@
 \usepackage{lmodern}
+\usepackage[marginal]{footmisc}
+\usepackage{hyperref}
 
@@
 \begin{document}
-\title{Thesis Title}
-\subtitle{Bachelor Thesis Proposal \& Work Plan}
-% bei Masterarbeit ggf. ändern
-\author{First Name + Name\\ \small{matriculation number: xxxxxxx}\\ \small{mail-address}}
+
+\title{Automatic Ranking of Classification Algorithms}
+\subtitle{A Comparison of Regression-Based Ranking and Preference Models
+\\\vspace{2em}Bachelor Thesis Proposal \& Work Plan}
+
+\author{Helena Graf\\ 
+\small{matriculation number: 7011643}\\ 
+\small{hgraf@mail.upb.de}}
 \date{\today}
+
 \maketitle
+\vspace{2em}
+
+\begin{center}
+\small{Supervisors:}\\
+\large{Prof. Dr. Eyke H\"ullermeier}\\
+\large{Prof. Dr. Axel-Cyrille Ngonga Ngomo}
+\end{center}
+
+\newpage
+\tableofcontents
+\newpage
 
 \section{Motivation}\label{sec:motivation}
+Selecting a fitting classifier for a new problem is difficult, since algorithm performances can vary substantially among datasets, and it is not feasible to simply apply a large number of them to empirically to find a good match.
+For example, on a dataset about the electricity prices in the Australian state New South Wales, %TODO cite
+ the predictive accuracy for the Multilayer Perceptron\footnote{Hyperparameters: L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a.} is 0.7887 %TODO cite
+. The predictive accuracy of the Random Forests\footnote{Hyperparameters: P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1.} algorithm on the same data set is 0.9236, a much higher value. %TODO cite
+On a different data set, with the topic of vehicle silhouetes, %TODO cite
+ we get a predictive accuracy of 0.7979 %TODO cite
+ for the Multilayer Perceptron, and 0.7518 %TODO cite
+ for Random Forests, showing an advantage of the former on this dataset\footnote{Hyperparameters as above.}.
+So in each case, one would have picked a different algorithm in order to achieve the best results.
+\\
 
-\section{Task Objectives}\label{sec:task-objectives}
+Due to the fact that algorithm selection is a common problem in machine learning, one would generally like to automate that process.
+This approach is based on the idea, that one can predict a good classifier by generalizing from the algorithm's past performances.
+Hence, we attempt this by applying machine learning, regression models and preference learning, to be precise, to performance measures.
+Therefore, the same task would ideally not have to be solved repetitively by independent people, but instead, the insight gained about the learning process would be re-used.\\
+
+Furthermore, the idea of selecting one single algorithm for a given problem can be relaxed in the context of this thesis.
+Since the prediction will most likely not be correct in all cases, and the performance of an algorithm is also dependent on the hyperparameter-tuning, returning a ranking of classifiers is sensible.
+This ranking could then be used in another framework to inspect top-rated algorithms closer, in order to return a better algorithm to the user.
+\\
+
+\section{Related Work}\label{sec:related_work}
+\subsection{Evolutionary Algorithms}
+\subsection{Runtime Predictions}
+
+\section{Goals}\label{sec:goals}
+The overall goal of this thesis is to test the assumption that one can predict an accuracy-based ranking of classification algorithms for a new dataset given past performances of the classifiers.
+In this context, this will be done by implementing two different methods for generating a ranking, regression-based and preference based ranking, and comparing the results.
+\subsection{Required Goals}\label{subsec:required_goals}
+Implementation in Java to be done in two phases\\
+Using jpl for rankers, ml-plan for regression, data from openML, based on weka, 
+Evaluation procedure via Kindall\\
+Evaluate against??
+\subsection{Optional Goals}\label{subsec:optional_goals}
+Adding another layer to search by including hyperparameters, possibly by means of iterative requests to tool.
+
+Is succesful, add runtime and / or complexity and make combined predictions
 
 \section{Task Description}\label{sec:task-description}
+Section might be obsolete - approach described under 'goals'? Or need more details?
+\newpage
 
-\section{Time-Schedule and Subtasks}\label{sec:schedule-and-subtasks}
+\section{Preliminary Document Structure}\label{sec:doc-structure}
+\begin{enumerate}
+	\item Introduction
+	\begin{enumerate}[1.1]
+		\item Solution Approach
+		\item Structure
+	\end{enumerate}
+	\item Fundamentals
+	\begin{enumerate}[2.1]
+		\item ML-Plan
+		\item JPL
+	\end{enumerate}
+	\item Implementation
+	\begin{enumerate} [3.1]
+		\item Regression-based Ranking
+		\begin{enumerate}[3.1.1]
+			\item Preliminary Regression Algorithm
+			\item Automatic Algorithm Selection
+		\end{enumerate}
+		\item Preference Models
+		\begin{enumerate}
+			\item Preliminary Ranking Algorithm
+			\item Automatic Algorithm Selection
+		\end{enumerate}
+	\end{enumerate}
+	\item Evaluation
+	\begin{enumerate}[4.1]
+		\item Computing the Accuracy of the Results
+		\item Assessment of the Accuracy
+	\end{enumerate}
+	\item Related Work
+	\begin{enumerate}[5.1]
+		\item Evolutionary Algorithms
+		\item Runtime Predictions
+	\end{enumerate}
+	\item Conclusion
+	\item Literature
+	\item Appendix
+\end{enumerate}
+
+\newpage
+
+\section{Schedule}\label{sec:schedule}
 
@@
 	\centering
-	\includegraphics[width=.9\textwidth]{timeschedule}
+	\includegraphics[angle=-90,width=.8\textwidth]{Gantt_BA_Helena}
 	\caption{Sketch of the time schedule for the work on the thesis}
@@
 % % %
-\section{Initial Document Structure}\label{sec:doc-structure}
-\begin{enumerate}
-	\item Introduction
-	\item ...
-\end{enumerate}
+
 \newpage
+
 \bibliography{literature}
@@
          \centering
-         Supervisor)\\(Titel Vorname Nachname)
+         Supervisor\\(Prof. Dr. Eyke H\"ullermeier)
          \end{minipage}
@@
            \centering
-           Student(in)\\(Vorname Nachname)
+           Student\\(Helena Graf)
          \end{minipage}

### 2017-11-27 Writing/Proposal/Tex/paper.tex
Cleanup of Proposal folder; preliminary version of proposal.

\documentclass[12pt]{scrartcl}

\usepackage[american]{babel}

\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{paralist}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage[marginal]{footmisc}
\usepackage{hyperref}
\usepackage{pgfgantt}
\usepackage{float}
\usepackage[backend=biber,style=numeric-comp]{biblatex}
\addbibresource{literature3.bib}

\usepackage{geometry}
% \geometry{a4paper,body={5.8in,9in}}
\geometry{a4paper}

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{placeins}
\usepackage{subcaption}

\usepackage{setspace}

\setlength{\parindent}{0pt}

\renewcommand{\labelenumi}{\arabic{enumi}.} 
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumii}}

\begin{document}

\title{Automatic Ranking of Classification Algorithms}
\subtitle{A Comparison of Regression-Based Ranking and Preference Models
\\\vspace{2em}Bachelor Thesis Proposal \& Work Plan}

\author{Helena Graf\\ 
\small{matriculation number: 7011643}\\ 
\small{hgraf@mail.upb.de}}
\date{\today}

\maketitle
\vspace{2em}

\begin{center}
\small{Supervisors:}\\
\large{Prof. Dr. Eyke H\"ullermeier}\\
\large{Prof. Dr. Axel-Cyrille Ngonga Ngomo}
\end{center}

\newpage
\tableofcontents
\newpage

\section{Motivation}\label{sec:motivation}
%start with why ML is becoming more important
As the potential of big data is evident, an increasing amount of data is collected and available for analyzation - but this potential is not utilized. In a white paper, the international data corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data, only 3\% where tagged as to enable further processing, and only 0.5\% where analyzed. While the claim of a follow-up paper in 2017 projects that in 2025, 15\% of the then estimated 163ZB of global data will be tagged, and approximately 3\% analyzed, is more optimistic, it still shows that there is a huge amount of data that could potentially be useful, but this is not exploited. This shows that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process, in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.[citations will follow]\\ %TODO sources!!

Often, the problem at hand is classification: Assigning an instance a certain class, for example deciding if a client of a bank will be given a credit, based on factors like other existing credits or the  job of the client. But selecting a fitting classifier for a new dataset is difficult, since algorithm performances can vary substantially among datasets, and it is not feasible to simply apply a large number of them to empirically to find a good match. For example, on a dataset about the electricity prices in the Australian state New South Wales, %TODO cite
 the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 %TODO cite
. The predictive accuracy of the Random Forests\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236, a much higher value. %TODO cite
On a different data set, with the topic of vehicle silhouettes, %TODO cite
 we get a predictive accuracy of 0.7979 %TODO cite
 for the Multilayer Perceptron, and 0.7518 %TODO cite
 for Random Forests, showing an advantage of the former on this dataset\footnote{Hyperparameters as above.}. So in each case, one would have picked a different algorithm in order to achieve the best results. In general, this means that for a different dataset, a different algorithm might yield the best performance.[citations will follow]\\

Since there is no one best classifier for all datasets, it is likely that how well a classifier performs on a given dataset is to at least some degree dependent on properties of the dataset. Combined with the need for automatic machine learning, this calls for an approach that takes past performances of classifiers, dependent on properties of datasets, in consideration to automatically make suggestions for classifiers for a given dataset.

\section{Related Work}\label{sec:related_work}
The demand for aid in the process of selecting an algorithm has already lead to the development of tools that automate machine-learning (Auto-ML). In the following paragraphs, The way that three of those tools work is outlined briefly.\\

Auto-WEKA is an Auto-ML tool that both selects a machine learning algorithm and sets its hyperparameters by using Bayesian optimization \cite{thornton2013auto}. It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka} to assist the large number of novice users of the software in selecting parameterized algorithms for their problems. The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}. In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution. An input dataset is first preprocessed by means of feature selection. Then, Sequential Model-Based Optimization is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}. In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is integrated into the model. This cycle is then repeated until the allocated time has run out. While Auto-WEKA works reasonably well, it does not use meta-knowledge, that is the algorithms performance regarding properties of the datasets, to make its decisions. \\

% SK-learn
AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an Auto-ML tool which is based on scikit-learn \cite{feurer2015efficient}. It works very similar to Auto-ML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian Optimization and automatically constructing ensembles during optimization. During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of datasets. Then, for each dataset, the algorithm which shows the best empirical performance is noted for each dataset. Then, certain meta-features are calculated for each dataset. For a new dataset, at first, its meta-features are computed. Then, the Manhattan distance to the other datasets is determined according to the meta-features, and the algorithms that are associated with the k-nearest datasets are used as a starting point for further optimization. The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust way. Their results show that Meta-Learning can be used to improve the overall Auto-ML process.\\

% ML-Plan
ML-Plan is an Auto-ML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline [Reference will follow]. This is achieved by viewing machine-learning as a task, building a hierarchical task network out of those tasks, and then searching for a solution in the induced tree structure. In the tree, the root node is a complex task, middle nodes represent incomplete pipelines, and leaf nodes are complete pipelines. An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'. The first of these tasks would then further be decomposed down the tree and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all so-called primitive tasks that do not need to be further decomposed. A best-first search algorithms in a modified variant is then used to find the good solutions in this pipeline. While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\

\section{Goals}\label{sec:goals}
The aim of this thesis is to test the assumption that given a new dataset, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods. It is derived from the need for Auto-ML tools and the fact that related solutions so far have not exploited Meta-Learning in this way. If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how Meta-Learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process. The aim presented consists of multiple goals, which can be divided into required and optional goals.

\subsection{Required Goals}\label{subsec:required_goals}
Based on the general objective of the thesis, several goals should be achieved:

\begin{enumerate}
	\item Implementing a tool with the following functionality:
	\begin{enumerate}
		\item A pre-processing phase in which the performances of the available set of classifiers is calculated for a set of datasets, a regression model is fit to each of the classifiers, and a preference-ranker is fit to the ranks of the algorithms which can be deduced from their performance values.
		\item A method where the tool is given a dataset and returns a ranking of classifiers for this dataset.
		\item The possibility to choose between regression-based and preference-based ranking.
	\end{enumerate}
	\item Evaluate the performance of both the regression and preference-ranking variant of the implementation by comparing them against each other, an oracle, and a baseline.
\end{enumerate}

\subsection{Optional Goals}\label{subsec:optional_goals}
If the required goals have been met in less time than originally allocated, addressing additional goals may be considered. The following list suggests possible optional goals. However, they may be replaced if while working on the thesis it becomes clear that more appropriate expansions exists.

\begin{enumerate}
	\item Extend the evaluation to compare the tool with other Auto-ML solutions.
	\item Extend the evaluation to compare with a more intelligent baseline.
	\item Adding another layer to search by including hyperparameters, possibly by means of iterative requests to tool.
	\item If the accuracy prediction is succesful, add runtime and / or complexity predictions and make combined predictions
\end{enumerate}

\section{Approach}\label{sec:approach}
As described in chapter \ref{sec:goals}, the goal is to implement an Auto-ML tool that returns a ranking of classification algorithms for a given dataset based on past performances of the classifiers by using regression and preference-ranking, and comparing and evaluating the results.

% what about meta classifiers / ensemble methods or just base classifiers
The implementation of the tool will be done in Java 8, and will consist of two phases. In the first phase, a basic functionality is going to be ensured, but placeholder regression and preference-ranking models are going to be used. The first step of this phase is to implement the first preprocessing phase, which consist of computing the performances of classifiers on datasets. For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included. The datasets will be fetched from OpenML.org, which is an open-source project where users can contribute datasets, implementations for machine learning algorithms, and run said algorithms on the datasets. Since the results of the runs are available publicly on the website, not all of the required base data will be needed to be computed, but can be extracted instead. OpenML.org provides the datasets in .ARFF format, and supplies a plugin that works from WEKA, which should ensure that these libraries work together smoothly. The second step of the first phase is to add the functionality to fit a preliminary regression model and preference ranker to the performance data, based on properties of the datasets. This step also includes providing a method that can be given a dataset and returns a ranking, based on the choice of ranking method.\\

In the second phase of the implementation, the preliminary algorithms used in the first phase will be replaced. The regression models are going to be customized for each classifier by using ML-Plan (described in section \ref{sec:related_work}) and configuring it to work with regression models. To do this, the configuration file of ML-Plan has to be manipulated. The ranking model is going to be optimized in this phase as well, using the jPL framework [citation will follow]. The project provides a framework for the evaluation of preference learners, including label ranking, which is the problem at hand.\\

For the evaluation, it is necessary to generate a baseline and an oracle. Both can be obtained from the data of the preprocessing phase. Since due to all performances of classifiers being recorded on all sets, one can obtain a best ranking of classifiers for each dataset from the same table. The baseline which is going to be used is the best algorithm, which performs best on the largest number of datasets. This can be obtained from the table by counting the number of times each algorithm performes the best. The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall Rank Correlation Coefficient.

\newpage
\section{Preliminary Document Structure}\label{sec:doc-structure}
The following structure will serve as an orientation during the writing process. While the chapters should remain the same, subsections may be added, removed or moved.

\begin{enumerate}
	\item Introduction
	\item Fundamentals
	\begin{enumerate}
		\item Meta-Learning
		\item Kendall Rank Correclation Coefficient
		\item JPL
		\item WEKA
	\end{enumerate}
	\item Approach
	\item Implementation
	\begin{enumerate} 
		\item Regression-based Ranking
		\begin{enumerate}
			\item Preliminary Regression Algorithm
			\item Automatic Algorithm Selection
		\end{enumerate}
		\item Preference Models
		\begin{enumerate}
			\item Preliminary Ranking Algorithm
			\item Automatic Algorithm Selection
		\end{enumerate}
	\end{enumerate}
	\item Evaluation
	\begin{enumerate}
		\item Computing the Accuracy of the Results
		\item Assessment of the Accuracy
	\end{enumerate}
	\item Related Work
		% Include RECIPE in final work also
		%Auto-WEKA
		%Auto-sklearn
		% ML-Plan
	\item Conclusion
	\item Literature
	\item Appendix
\end{enumerate}

\newpage
\section{Schedule}\label{sec:schedule}
The working time is going to be structured according to the schedule shown in figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.

\begin{figure}[H]
% Colour Definitions for Gantt Chart
\definecolor{uniblue}{RGB}{000,032,091}
\definecolor{unigrey}{RGB}{199,201,199}
\definecolor{uniaccentblue}{RGB}{000,163,224}

% Gantt Chart of Schedule
\begin{ganttchart}[
%% Style Definitions %%
% Canvas %
x unit=0.6cm,
y unit chart = 0.65cm,
canvas/.append style={fill=none, draw=unigrey},
hgrid style/.style={draw=black!25, line width=.75pt},
vgrid={*1{draw=unigrey, line width=.75pt}},
title/.style={draw=none, fill=none},
% Title %
title label font=\bfseries,
title label node/.append style={below=0pt},
include title in canvas=false,
% Bar %
bar height=.5,
bar label node/.append style={align=left,text width=14em},
bar/.append style={draw=none, fill=uniblue},
% Group %
group height=.2,
   group peaks tip position=0,
group label node/.append style={align=left,text width=15em},
group/.append style={fill=black,opacity=0}
]{1}{16}

%% Chart %%
% Title %
\gantttitle[title label node/.append style={below left=0pt and -7pt}]{WEEK:\quad1}{1}
\gantttitlelist{2,...,16}{1} \\

% Elements %
\ganttgroup[]{Implementation}{1}{10} \\
\ganttbar{Phase 1}{1}{2} \\
\ganttbar[]{Phase 2}{3}{4} \\
\ganttbar[]{Evaluation}{6}{7} \\
\ganttbar[bar/.append style={fill=unigrey}]{Buffer}{5}{5} \\

\ganttgroup[]{Writing\footnotemark}{1}{13} \\
\ganttbar[]{Related \& Fundamentals}{1}{3} \\
\ganttbar[]{Approach \& Implementation}{4}{7} \\
\ganttbar[]{Evaluation \& Conclusion}{8}{10} \\
\ganttbar[bar/.append style={fill=unigrey}]{Buffer, Proofreading}{11}{13} \\
\ganttbar[]{Corrections}{14}{15} \\

\ganttgroup[]{Other}{5}{16} \\
\ganttbar[]{Presentation Preparation}{15}{16} \\

\end{ganttchart}

\caption{Sketch of the Work Schedule for the thesis.}
\label{fig:schedule}
\end{figure}

\footnotetext{The chapter 'Introduction' is not included since it will be written in parallel to other chapters, in small bits according to the progress of the thesis.}

\newpage
\printbibliography

\newpage
% Signatures and Delcaration %
Hereby supervisor and student confirm that this proposal is the basis for the topic assignment of the described work. The timetable and topic description are accepted by both sides as laid out in this proposal.

\vspace{6cm}

\begin{center}
     \begin{tabular}{l p{0.1\textwidth} r}
       \cline{1-1} \cline{3-3}
       \begin{minipage}[t]{0.4\textwidth}
         \centering
         Supervisor\\(Prof. Dr. Eyke H\"ullermeier)
         \end{minipage}
&
         \begin{minipage}[t]{0.2\textwidth}
         \end{minipage}
&
         \begin{minipage}[t]{0.4\textwidth}
           \centering
           Student\\(Helena Graf)
         \end{minipage}
     \end{tabular}
\end{center}

\end{document}

### 2017-11-30 Writing/Proposal/Tex/paper.tex
Proposal latest version, added correction discussed on monday.

@@
 \subtitle{A Comparison of Regression-Based Ranking and Preference Models
-\\\vspace{2em}Bachelor Thesis Proposal \& Work Plan}
+\\\vspace{2em}Bachelor's Thesis Proposal \& Work Plan}
 
@@
 \newpage
-\tableofcontents
-\newpage
 
@@
 %start with why ML is becoming more important
-As the potential of big data is evident, an increasing amount of data is collected and available for analyzation - but this potential is not utilized.
-In a white paper, the international data corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data, only 3\% where tagged as to enable further processing, and only 0.5\% where analyzed.
-While the claim of a follow-up paper in 2017 projects that in 2025, 15\% of the then estimated 163ZB of global data will be tagged, and approximately 3\% analyzed, is more optimistic, it still shows that there is a huge amount of data that could potentially be useful, but this is not exploited.
-This shows that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process, in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.[citations will follow]\\ %TODO sources!!
+The potential of big data is evident, and an increasing amount of information is collected and available for analysis - but this potential is not utilized.
+In a white paper, the International Data Corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data only 3\% were tagged as to enable further processing, and only 0.5\% were analyzed \cite{gantz2012the}.
+A follow-up paper in 2017 projects that in 2025, 15\% of the estimated 163ZB of global data will be tagged, and approximately 3\% analyzed \cite{gantz2017data}.
+While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available.
+This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.\\
 
-Often, the problem at hand is classification: Assigning an instance a certain class, for example deciding if a client of a bank will be given a credit, based on factors like other existing credits or the  job of the client.
-But selecting a fitting classifier for a new dataset is difficult, since algorithm performances can vary substantially among datasets, and it is not feasible to simply apply a large number of them to empirically to find a good match.
-For example, on a dataset about the electricity prices in the Australian state New South Wales, %TODO cite
- the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 %TODO cite
-.
-The predictive accuracy of the Random Forests\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236, a much higher value.
-%TODO cite
-On a different data set, with the topic of vehicle silhouettes, %TODO cite
- we get a predictive accuracy of 0.7979 %TODO cite
- for the Multilayer Perceptron, and 0.7518 %TODO cite
- for Random Forests, showing an advantage of the former on this dataset\footnote{Hyperparameters as above.}.
+One of the most prominent machine learning tasks is classification: A class is assigned to an instance, for example clients of a bank may be either deemed creditworthy or not, based on factors like other existing credits or the job of the client.
+But selecting a fitting classifier for a new dataset is difficult, since algorithm performances can vary substantially among datasets, and it is not feasible to simply apply a large number of them to empirically find a good match.
+For example, on a dataset about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
+The predictive accuracy of the Random Forests\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
+On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this dataset\footnote{Hyperparameters as above.}.
 So in each case, one would have picked a different algorithm in order to achieve the best results.
-In general, this means that for a different dataset, a different algorithm might yield the best performance.[citations will follow]\\
+In general, this means that for a different dataset, a different algorithm might yield the best performance.\\
 
-Since there is no one best classifier for all datasets, it is likely that how well a classifier performs on a given dataset is to at least some degree dependent on properties of the dataset.
-Combined with the need for automatic machine learning, this calls for an approach that takes past performances of classifiers, dependent on properties of datasets, in consideration to automatically make suggestions for classifiers for a given dataset.
+Since there is no one best classifier for all datasets, it is likely that how well a classifier performs on a given dataset is dependent on properties of the dataset, at least to some degree.
+Combined with the need for automated machine learning, this calls for an approach that considers past performances of classifiers for datasets in relation to properties of these datasets to automatically suggest well-performing classifiers for a new problem.
 
 \section{Related Work}\label{sec:related_work}
-The demand for aid in the process of selecting an algorithm has already lead to the development of tools that automate machine-learning (Auto-ML).
-In the following paragraphs, The way that three of those tools work is outlined briefly.\\
+The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (Auto-ML).
+In the following paragraphs, three of those tools work qre outlined briefly.\\
 
-Auto-WEKA is an Auto-ML tool that both selects a machine learning algorithm and sets its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
+Auto-WEKA is an Auto-ML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
 It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka} to assist the large number of novice users of the software in selecting parameterized algorithms for their problems.
@@
 An input dataset is first preprocessed by means of feature selection.
-Then, Sequential Model-Based Optimization is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}.
-In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is integrated into the model.
+Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}.
+In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model.
 This cycle is then repeated until the allocated time has run out.
-While Auto-WEKA works reasonably well, it does not use meta-knowledge, that is the algorithms performance regarding properties of the datasets, to make its decisions.
+Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forests, which perform well on a large number of datasets, first.
 \\
@@
 % SK-learn
-AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an Auto-ML tool which is based on scikit-learn \cite{feurer2015efficient}.
+AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an Auto-ML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}.
 It works very similar to Auto-ML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian Optimization and automatically constructing ensembles during optimization.
 During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of datasets.
-Then, for each dataset, the algorithm which shows the best empirical performance is noted for each dataset.
+For each dataset, the algorithm which shows the best empirical performance is noted.
 Then, certain meta-features are calculated for each dataset.
-For a new dataset, at first, its meta-features are computed.
+The first step of the tool when given a new problem is to calculate meta-features of the dataset.
 Then, the Manhattan distance to the other datasets is determined according to the meta-features, and the algorithms that are associated with the k-nearest datasets are used as a starting point for further optimization.
-The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust way.
+The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust application.
 Their results show that Meta-Learning can be used to improve the overall Auto-ML process.\\
@@
 % ML-Plan
-ML-Plan is an Auto-ML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline [Reference will follow].
+ML-Plan is an Auto-ML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}.
 This is achieved by viewing machine-learning as a task, building a hierarchical task network out of those tasks, and then searching for a solution in the induced tree structure.
-In the tree, the root node is a complex task, middle nodes represent incomplete pipelines, and leaf nodes are complete pipelines.
+In the tree, the root node is a complex task, inner nodes represent incomplete pipelines, and leaf nodes are complete pipelines.
 An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'.
 The first of these tasks would then further be decomposed down the tree and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all so-called primitive tasks that do not need to be further decomposed.
-A best-first search algorithms in a modified variant is then used to find the good solutions in this pipeline.
+A best-first search algorithms in a modified variant is then used to find good solutions in this task network.
 While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\
@@
 
+\newpage
 \subsection{Required Goals}\label{subsec:required_goals}
@@
 	\end{enumerate}
-	\item Evaluate the performance of both the regression and preference-ranking variant of the implementation by comparing them against each other, an oracle, and a baseline.
+	\item Evaluate the predictions of both the regression and preference-ranking variant of the implementation by comparing them against each other, an oracle that represents the best ranking according to actual algorithms performances, and a best-algorithm baseline.
 \end{enumerate}
@@
 \subsection{Optional Goals}\label{subsec:optional_goals}
-If the required goals have been met in less time than originally allocated, addressing additional goals may be considered.
+If the required goals have been met in less time than originally allocated, and the initial results are promising, addressing additional goals may be considered.
 The following list suggests possible optional goals.
@@
 \begin{enumerate}
-	\item Extend the evaluation to compare the tool with other Auto-ML solutions.
-	\item Extend the evaluation to compare with a more intelligent baseline.
-	\item Adding another layer to search by including hyperparameters, possibly by means of iterative requests to tool.
-	\item If the accuracy prediction is succesful, add runtime and / or complexity predictions and make combined predictions
+	\item Adding automatic optimization of regression and ranking models with the help of ML-Plan and jPl \footnotemark  respectively \cite{intelligent2017jpl}.
+	\item Extend the evaluation by comparing the tool with other Auto-ML solutions.
+	\item Extend the evaluation by evaluating against a more intelligent baseline.
+	\item Adding another layer to the search by including hyperparameters, possibly by means of iterative requests to the tool.
+	\item Adding runtime and/ or complexity prediciton to allow for combined predictions.
 \end{enumerate}
+\footnotetext{A framework for the evaluation of preference learners.}
 
 \section{Approach}\label{sec:approach}
-As described in chapter \ref{sec:goals}, the goal is to implement an Auto-ML tool that returns a ranking of classification algorithms for a given dataset based on past performances of the classifiers by using regression and preference-ranking, and comparing and evaluating the results.
+As described in chapter \ref{sec:goals}, the goal is to implement an Auto-ML tool that returns a ranking of classification algorithms for a given dataset based on past performances of the classifiers by using regression and ranking models and evaluating the results.
+The implementation of this tool will be done in Java 8.
+Since the aim is to ensure a basic functionality, preliminary algorithms are going to be use both for regression and ranking models.\\
 
-% what about meta classifiers / ensemble methods or just base classifiers
-The implementation of the tool will be done in Java 8, and will consist of two phases.
-In the first phase, a basic functionality is going to be ensured, but placeholder regression and preference-ranking models are going to be used.
-The first step of this phase is to implement the first preprocessing phase, which consist of computing the performances of classifiers on datasets.
-For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included.
+The first step therefore is to implement the preprocessing phase, which consist of computing the performances of classifiers on datasets.
+For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark.
 The datasets will be fetched from OpenML.org, which is an open-source project where users can contribute datasets, implementations for machine learning algorithms, and run said algorithms on the datasets.
-Since the results of the runs are available publicly on the website, not all of the required base data will be needed to be computed, but can be extracted instead.
-OpenML.org provides the datasets in .ARFF format, and supplies a plugin that works from WEKA, which should ensure that these libraries work together smoothly.
-The second step of the first phase is to add the functionality to fit a preliminary regression model and preference ranker to the performance data, based on properties of the datasets.
-This step also includes providing a method that can be given a dataset and returns a ranking, based on the choice of ranking method.\\
+Since the results of the runs are available publicly on the website, not all of the required base data will be needed to be computed, but some may be extracted instead.
+OpenML.org provides the datasets in .ARFF format, and supplies a WEKA plugin, which should ensure that these libraries work together smoothly.
+\\
 
-In the second phase of the implementation, the preliminary algorithms used in the first phase will be replaced.
-The regression models are going to be customized for each classifier by using ML-Plan (described in section \ref{sec:related_work}) and configuring it to work with regression models.
-To do this, the configuration file of ML-Plan has to be manipulated.
-The ranking model is going to be optimized in this phase as well, using the jPL framework [citation will follow].
-The project provides a framework for the evaluation of preference learners, including label ranking, which is the problem at hand.\\
+The next step is to add the functionality to fit preliminary regression models and a preference ranker to the performance data, based on properties of the datasets.
+This step also includes providing a method that can be given a dataset and returns a ranking, based on the choice of ranking method either based on regression or a preference model.
+This method first needs to compute properties of the new dataset.
+Then, for regression, it is going to use the preliminary regression model of each algorithm to get a predicted performance of each classifier for the new dataset.
+These predictions are turned into a ranking.
+For the ranking model, the computed properties of the new dataset can be fed to the model directly.\\
+
+% Optional
+%In the second phase of the implementation, the preliminary algorithms used in the first phase will be replaced.
+The regression models are going to be customized by using ML-Plan (described in section \ref{sec:related_work}) and configuring it to work with regression models.
+For this, the configuration file of ML-Plan will have to be manipulated.
+The ranking model is going to be optimized in this phase as well, using the jPL framework \cite{intelligent2017jpl}.
+The project provides a framework for the evaluation of preference learners, including label ranking, which is the problem in this case.\\
 
 For the evaluation, it is necessary to generate a baseline and an oracle.
-Both can be obtained from the data of the preprocessing phase.
-Since due to all performances of classifiers being recorded on all sets, one can obtain a best ranking of classifiers for each dataset from the same table.
-The baseline which is going to be used is the best algorithm, which performs best on the largest number of datasets.
-This can be obtained from the table by counting the number of times each algorithm performes the best.
+Both can be obtained from the data of the pre-processing phase.
+Due to all performances of classifiers being recorded on all datasets, one can obtain an optimal ranking of classifiers for each dataset from that same table.
+The baseline which is going to be used is the best algorithm, that is the algorithm which performs best on the largest number of datasets.
+This can be obtained from the table of the pre-processing phase as well by counting the number of times each algorithm performs the best.
 The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall Rank Correlation Coefficient.
+
+\footnotetext{Meta-Classifiers and Ensemble-Classifiers will not be supported.}
 

### 2017-12-01 Writing/Proposal/Tex/paper.tex
Further corrections in proposal.

@@
 \usepackage[backend=biber,style=numeric-comp]{biblatex}
+\usepackage{tikz}
+\usepackage{xcolor}
+
+% Colour Definitions
+\definecolor{uniblue}{RGB}{000,032,091}
+\definecolor{unigrey}{RGB}{199,201,199}
+\definecolor{uniaccentblue}{RGB}{000,163,224}
+
 \addbibresource{literature3.bib}
@@
 One of the most prominent machine learning tasks is classification: A class is assigned to an instance, for example clients of a bank may be either deemed creditworthy or not, based on factors like other existing credits or the job of the client.
-But selecting a fitting classifier for a new dataset is difficult, since algorithm performances can vary substantially among datasets, and it is not feasible to simply apply a large number of them to empirically find a good match.
-For example, on a dataset about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
-The predictive accuracy of the Random Forests\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
-On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this dataset\footnote{Hyperparameters as above.}.
+But selecting a fitting classifier for a new data set is difficult, since algorithm performances can vary substantially among data sets, and it is not feasible to simply apply a large number of them to empirically find a good match.
+For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
+The predictive accuracy of the Random Forest\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
+On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}.
 So in each case, one would have picked a different algorithm in order to achieve the best results.
-In general, this means that for a different dataset, a different algorithm might yield the best performance.\\
+In general, this means that for a different data set, a different algorithm might yield the best performance.\\
 
-Since there is no one best classifier for all datasets, it is likely that how well a classifier performs on a given dataset is dependent on properties of the dataset, at least to some degree.
-Combined with the need for automated machine learning, this calls for an approach that considers past performances of classifiers for datasets in relation to properties of these datasets to automatically suggest well-performing classifiers for a new problem.
+Since there is no one best classifier for all data sets, it is likely that how well a classifier performs on a given data set is dependent on properties of the data set, at least to some degree.
+Combined with the need for automated machine learning, this calls for an approach that considers past performances of classifiers for data sets in relation to properties of these data sets to automatically suggest well-performing classifiers for a new problem.
 
 \section{Related Work}\label{sec:related_work}
-The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (Auto-ML).
-In the following paragraphs, three of those tools work qre outlined briefly.\\
+The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML).
+In the following paragraphs, three of those tools work are outlined briefly.\\
 
-Auto-WEKA is an Auto-ML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
+Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
 It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka} to assist the large number of novice users of the software in selecting parameterized algorithms for their problems.
@@
 In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution.
-An input dataset is first preprocessed by means of feature selection.
+An input data set is first preprocessed by means of feature selection.
 Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}.
@@
 This cycle is then repeated until the allocated time has run out.
-Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forests, which perform well on a large number of datasets, first.
+Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forests, which perform well on a large number of data sets, first.
 \\
@@
 % SK-learn
-AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an Auto-ML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}.
-It works very similar to Auto-ML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian Optimization and automatically constructing ensembles during optimization.
-During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of datasets.
-For each dataset, the algorithm which shows the best empirical performance is noted.
-Then, certain meta-features are calculated for each dataset.
-The first step of the tool when given a new problem is to calculate meta-features of the dataset.
-Then, the Manhattan distance to the other datasets is determined according to the meta-features, and the algorithms that are associated with the k-nearest datasets are used as a starting point for further optimization.
+AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an AutoML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}.
+It works very similar to AutoML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian Optimization and automatically constructing ensembles during optimization.
+During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of data sets.
+For each data set, the algorithm which shows the best empirical performance is noted.
+Then, certain meta-features are calculated for each data set.
+The first step of the tool when given a new problem is to calculate meta-features of the data set.
+Then, the Manhattan distance to the other data sets is determined according to the meta-features, and the algorithms that are associated with the k-nearest data sets are used as a starting point for further optimization.
 The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust application.
-Their results show that Meta-Learning can be used to improve the overall Auto-ML process.\\
+Their results show that Meta-Learning can be used to improve the overall AutoML process.\\
 
 % ML-Plan
-ML-Plan is an Auto-ML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}.
+ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}.
 This is achieved by viewing machine-learning as a task, building a hierarchical task network out of those tasks, and then searching for a solution in the induced tree structure.
-In the tree, the root node is a complex task, inner nodes represent incomplete pipelines, and leaf nodes are complete pipelines.
+In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks.
 An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'.
-The first of these tasks would then further be decomposed down the tree and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all so-called primitive tasks that do not need to be further decomposed.
-A best-first search algorithms in a modified variant is then used to find good solutions in this task network.
+The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed.
+A best-first search algorithm in a modified variant is then used to find good solutions in this task network.
 While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\
 
+\begin{figure}
+\tikzset{edge from parent/.style={draw,->}}
+\begin{tikzpicture}[sibling distance=10em,
+  every node/.style = {shape=rectangle, rounded corners,
+    draw, align=center}]]
+  \node {\textcolor{uniblue}{classify}}
+    child { node {...} }
+    child { node {\textcolor{uniblue}{classifyWithNN}}
+    child { node {...} }
+      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
+        child { node {...} }
+        child { node {...} 
+          child { node {...}  }
+          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } } } }
+    };
+\end{tikzpicture}
+\caption{An example for how the complex task 'classify' might be broken down by ML-Plan.
+The figure is loosely adapted from \cite{wever2017automatic}.
+Nodes containing '...' represent an undefined amount of subtrees.
+\textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
+\label{fig:mltree}
+\end{figure}
+
 \section{Goals}\label{sec:goals}
-The aim of this thesis is to test the assumption that given a new dataset, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods.
-It is derived from the need for Auto-ML tools and the fact that related solutions so far have not exploited Meta-Learning in this way.
+The aim of this thesis is to test the assumption that given a new data set, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods.
+It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited Meta-Learning in this way.
 If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how Meta-Learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process.
@@
 
-\newpage
 \subsection{Required Goals}\label{subsec:required_goals}
@@
 	\begin{enumerate}
-		\item A pre-processing phase in which the performances of the available set of classifiers is calculated for a set of datasets, a regression model is fit to each of the classifiers, and a preference-ranker is fit to the ranks of the algorithms which can be deduced from their performance values.
-		\item A method where the tool is given a dataset and returns a ranking of classifiers for this dataset.
+		\item A pre-processing phase in which the performances of the available set of classifiers is calculated for a set of data sets, a regression model is fit to each of the classifiers, and a preference-ranker is fit to the ranks of the algorithms which can be deduced from their performance values.
+		\item A method where the tool is given a data set and returns a ranking of classifiers for this data set.
 		\item The possibility to choose between regression-based and preference-based ranking.
@@
 
+\newpage
 \subsection{Optional Goals}\label{subsec:optional_goals}
@@
 The following list suggests possible optional goals.
-However, they may be replaced if while working on the thesis it becomes clear that more appropriate expansions exists.
+However, they may be replaced if while working on the thesis it becomes clear that more appropriate expansions exist.
 
 \begin{enumerate}
-	\item Adding automatic optimization of regression and ranking models with the help of ML-Plan and jPl \footnotemark  respectively \cite{intelligent2017jpl}.
-	\item Extend the evaluation by comparing the tool with other Auto-ML solutions.
+	\item Adding automatic optimization of regression and ranking models with the help of ML-Plan and jPL\footnotemark{ } respectively \cite{intelligent2017jpl}.
+	\item Extend the evaluation by comparing the tool with other AutoML solutions.
 	\item Extend the evaluation by evaluating against a more intelligent baseline.
@@
 \section{Approach}\label{sec:approach}
-As described in chapter \ref{sec:goals}, the goal is to implement an Auto-ML tool that returns a ranking of classification algorithms for a given dataset based on past performances of the classifiers by using regression and ranking models and evaluating the results.
+As described in Chapter \ref{sec:goals}, the goal is to implement an AutoML tool that returns a ranking of classification algorithms for a given data set based on past performances of the classifiers by using regression and ranking models and evaluating the results.
 The implementation of this tool will be done in Java 8.
-Since the aim is to ensure a basic functionality, preliminary algorithms are going to be use both for regression and ranking models.\\
+Since the aim is to ensure a basic functionality, preliminary algorithms are going to be used both for regression and ranking models.\\
 
-The first step therefore is to implement the preprocessing phase, which consist of computing the performances of classifiers on datasets.
+The first step therefore is to implement the pre-processing phase, which consist of computing the performances of classifiers on data sets.
 For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark.
-The datasets will be fetched from OpenML.org, which is an open-source project where users can contribute datasets, implementations for machine learning algorithms, and run said algorithms on the datasets.
-Since the results of the runs are available publicly on the website, not all of the required base data will be needed to be computed, but some may be extracted instead.
-OpenML.org provides the datasets in .ARFF format, and supplies a WEKA plugin, which should ensure that these libraries work together smoothly.
+The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and run algorithm runs.
+Since the results of the runs are available publicly on the website, some of the required data may be extracted instead of computed.
+OpenML.org provides the data sets in .ARFF format, and supplies a WEKA plug-in, which should ensure that these libraries work together smoothly.
 \\
 
-The next step is to add the functionality to fit preliminary regression models and a preference ranker to the performance data, based on properties of the datasets.
-This step also includes providing a method that can be given a dataset and returns a ranking, based on the choice of ranking method either based on regression or a preference model.
-This method first needs to compute properties of the new dataset.
-Then, for regression, it is going to use the preliminary regression model of each algorithm to get a predicted performance of each classifier for the new dataset.
+\footnotetext{Meta-Classifiers and Ensemble-Classifiers will not be supported.}
+
+The next step is to add the functionality to fit preliminary regression models and a preference ranker to the performance data, based on properties of the data sets.
+This step also includes providing a method that can be given a data set and returns a ranking, based on the choice of ranking method either based on regression or a preference model.
+This method first needs to compute properties of the new data set.
+Then, for regression, it is going to use the preliminary regression model of each algorithm to get a predicted performance of each classifier for the new data set.
 These predictions are turned into a ranking.
-For the ranking model, the computed properties of the new dataset can be fed to the model directly.\\
-
-% Optional
-%In the second phase of the implementation, the preliminary algorithms used in the first phase will be replaced.
-The regression models are going to be customized by using ML-Plan (described in section \ref{sec:related_work}) and configuring it to work with regression models.
-For this, the configuration file of ML-Plan will have to be manipulated.
-The ranking model is going to be optimized in this phase as well, using the jPL framework \cite{intelligent2017jpl}.
-The project provides a framework for the evaluation of preference learners, including label ranking, which is the problem in this case.\\
+For the ranking model, the computed properties of the new data set can be fed to the model directly.\\
 
@@
 Both can be obtained from the data of the pre-processing phase.
-Due to all performances of classifiers being recorded on all datasets, one can obtain an optimal ranking of classifiers for each dataset from that same table.
-The baseline which is going to be used is the best algorithm, that is the algorithm which performs best on the largest number of datasets.
-This can be obtained from the table of the pre-processing phase as well by counting the number of times each algorithm performs the best.
+Due to all performances of classifiers being recorded on all data sets, one can obtain an optimal ranking of classifiers for each data set from that same table.
+The baseline which is going to be used is counting the number of data sets for which a classifier is the best option, and then ranking them from overall best performance (best choice for most data sets) to worst.
+This can be obtained from the table of the pre-processing phase as well.
 The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall Rank Correlation Coefficient.
-
-\footnotetext{Meta-Classifiers and Ensemble-Classifiers will not be supported.}
 
@@
 		\item Meta-Learning
-		\item Kendall Rank Correclation Coefficient
+		\item Kendall Rank Correlation Coefficient
 		\item JPL
@@
 \begin{figure}[H]
-% Colour Definitions for Gantt Chart
-\definecolor{uniblue}{RGB}{000,032,091}
-\definecolor{unigrey}{RGB}{199,201,199}
-\definecolor{uniaccentblue}{RGB}{000,163,224}
-
 % Gantt Chart of Schedule

### 2017-12-06 Writing/Proposal/Tex/paper.tex
Cleanup of proposal presentation and tex files.
Further minor corrections in proposal + title change.

@@
 \usepackage{graphicx}
-\graphicspath{{images/}}
 
@@
 
-\title{Automatic Ranking of Classification Algorithms}
+\title{Ranking of Classification Algorithms in AutoML}
 \subtitle{A Comparison of Regression-Based Ranking and Preference Models
@@
 The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML).
-In the following paragraphs, three of those tools work are outlined briefly.\\
+In the following paragraphs, three of such tools are outlined briefly.\\
 
@@
 AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an AutoML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}.
-It works very similar to AutoML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian Optimization and automatically constructing ensembles during optimization.
+It works very similar to AutoML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian optimization and automatically constructing ensembles during optimization.
 During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of data sets.
@@
 The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust application.
-Their results show that Meta-Learning can be used to improve the overall AutoML process.\\
+Their results show that meta-learning can be used to improve the overall AutoML process.\\
 
@@
 The aim of this thesis is to test the assumption that given a new data set, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods.
-It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited Meta-Learning in this way.
-If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how Meta-Learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process.
+It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited meta-learning in this way.
+If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how meta-learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process.
 The aim presented consists of multiple goals, which can be divided into required and optional goals.
@@
 For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark.
-The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and run algorithm runs.
+The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and algorithm runs.
 Since the results of the runs are available publicly on the website, some of the required data may be extracted instead of computed.
@@
 
-\footnotetext{Meta-Classifiers and Ensemble-Classifiers will not be supported.}
+\footnotetext{Meta-classifiers and ensemble-classifiers will not be supported.}
 
@@
 This can be obtained from the table of the pre-processing phase as well.
-The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall Rank Correlation Coefficient.
+The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall rank correlation coefficient.
 
@@
 \section{Schedule}\label{sec:schedule}
-The working time is going to be structured according to the schedule shown in figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.
+The working time is going to be structured according to the schedule shown in Figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.
 

### 2018-01-07 Writing/Thesis/content/abstract.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
\pdfbookmark[0]{Abstract}{Abstract}
\chapter*{Abstract}
\label{sec:abstract}
\vspace*{-10mm}

Should abstract be included?

\vspace*{20mm}

{\usekomafont{chapter}Abstract (different language)}\label{sec:abstract-diff} \\

Und falls ja, dann zweisprachig?

### 2018-01-07 Writing/Thesis/content/chapter-appendix.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
\chapter{Example Appendix}
\label{sec:appendix}

\section{Appendix Section 1}
\label{sec:appendix:sec1}

\begin{table}[h]
	\begin{tabularx}{\textwidth}{X | X | X}
		%\hline
		Alpha		& Beta			& Gamma			\\ \hline
		0			& 1				& 2				\\ \hline
		3			& 4				& 5				\\ %\hline
	\end{tabularx}
	\label{tab:table1}
	\caption{This is a caption text.}
\end{table}

### 2018-01-07 Writing/Thesis/content/chapter-approach.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
\chapter{Approach}
\label{sec:approach}

\section{System Section 1}
\label{sec:approach:sec1}

\begin{figure}[htb]
	\includegraphics[width=\textwidth]{gfx/Clean-Thesis-Figure}
	\caption{Figure example: \textit{(a)} example part one, \textit{(c)} example part two; \textit{(c)} example part three}
	\label{fig:system:example1}
\end{figure}

### 2018-01-07 Writing/Thesis/content/chapter-conclusion.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
\chapter{Conclusion}
\label{sec:conclusion}

\section{Future Work}
\label{sec:conclusion:future}

### 2018-01-07 Writing/Thesis/content/chapter-fundamentals.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
\chapter{Fundamentals}
\label{sec:fundamentals}

This chapter lays out the fundamentals for Firstly,the

\section{Machine Learning}
In this section, the aspects of the field of machine learning which are relevant for this thesis are going to be introduced briefly. The core of machine learning are learning algorithms, which are used to induce a general model from a set of data samples. The concept of machine learning will be explained here with the help of an example. % Further what happens exactly here

Suppose an aspiring gardener wants to learn how to distinguish between different species of iris plants, a genus of ornamental plants with colorful flowers. More specifically, the focus lies on the three species iris versicolor, virginica and setosa. In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species. The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered the three) an unknown iris plant is. The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation. They observe that all iris setosa plants from his sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species. The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants. While this model will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.

\begin{table}[h]
	\begin{tabularx}{\textwidth}{X X X X X X}
		%\hline
		Feature	& Sepal length	& Sepal width	& Petal length	& Petal width 	& Species			\\ \hline
				& 5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				& 5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				& 5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				& 5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				& 6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				& 5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				& 7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				& 5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				& 6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\label{tab:iris}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
\end{table}

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ that represents an ideal way of identifying iris species. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. He then chooses a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.

%TODO include picture of the models etc + table + decision tree that is built

\subsection{Supervised Learning}
The problem described above has some additional properties besides being a machine learning problem in general. Firstly, it falls in the category of supervised machine learning. Supervised learning is one of the three main learning paradigms of machine learning, together with reinforcement learning and unsupervised learning. In the context of this thesis, the latter will be neglected as only supervised learning is used. It is characterized by the fact that the learning algorithm is provided with a set of inputs \textit{together} with the outputs, which could be viewed as a kind of teacher, or supervisor, explaining expected results to the learner. In the other cases, no such detailed feedback is provided to the learner.

\subsection{Classification and Regression}
In addition to falling into the category of supervised learning, the problem is a classification problem. The nature of the prediction is to assign one of the three classes, or labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant. Formally, this means that the output space $Y$ of the target function consist of a finite set of labels $(y_1,\dots,y_n)$, so in this case $Y=('iris-setosa','iris virginica', 'iris versicolor')$.

Apart from classification, another important category of machine learning problems is regression problems. In the case of regression, the output space of the target function is no longer finite, but instead consist of real numbers. To reconsider the gardening example, the gardener could want to predict the height of a plant on the basis of the same features as used above. Likewise, they would have to observe a number of plants to gather feature values together with the expected target value, which instead of the species would then be the height of the plant in centimeters, that is $Y=\mathbb{R}$.

\subsection{Preference Learning}
% Why is label ranking relevant? -> for prediction based on preference
% Preference learning
Preference Learning is a relatively new subfield of machine learning\cite{DBLP:books/daglib/0025729}. It is dedicated to the problem of learning how to rank, the precise definition of what this encompasses being defined by which specific task one is engaged in. Out of the three main tasks of preference learning, namely label ranking, instance ranking and object ranking, label ranking is the relevant one in the context of this thesis. But before going into to details of label ranking, it first has to be explained what is meant with a ranking in this context and how it is distinguished from the concept of an ordering.

\subsubsection{Ranking and Ordering}

% Gardener example ranking his favourite plants

\begin{table}[h]
\centering
	\begin{tabularx}{.8\textwidth}{>{\hsize=0.9\hsize}X | >{\hsize=.1\hsize}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash} >{\hsize=.1\hsize}X}
		%\hline
		Species		& 	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris virginica}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris versicolor}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris setosa}	& 	\\ \hline
		Labels		& [ & 1,									& 2,										& 3 									& ] \\
		Scores		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
		Ranking		& [ & 2,									& 3,										& 1 									& ] \\ 
		Ordering		& [ & 3,									& 1,										& 2 									& ] \\ 		
	\end{tabularx}
	\label{tab:ranking_vs_ordering}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
\end{table}

The values in table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.

\subsubsection{Label Ranking}
% could be seen as a generalisation of classification
Similar to classification, in label ranking there is a finite set of labels $Y=(y_1,\dots,y_n)$, but it is not the output space. Instead, the output space consists of rankings of these labels

\subsection{Meta Learning}
% Context is meta learning -> what does that mean and what are the consequence

\section{Evaluation}

\subsection{Classifier Evaluation}

\subsection{Kendall Rank Correlation Coefficient}
% We need to evaluate the ranker quality somehow, ranker predicts rank, so need a 
To evaluate the quality of the prediction that the ranker will make, a statistic is needed to compare a predicted ranking with other rankings like a baseline or an optimal ranking.

% Definition of Kendall
The Kendall Rank Correlation Coefficient is a measure of association between two rankings of the same items also known as Kendall's tau. For two independent variables $X$ and $Y$ and and observations of values $(x_1,...,x_m)$ for $X$ and $(y_1,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations. If for two pairs $(x_i,y_i)$ and $(x_j,y_j)$ both $x_i < x_j$ and $y_i < y_j$ (or the opposite) holds, they are viewed as concordant. If $x_i < x_j$ but $y_i > y_j$ (or the opposite), they are viewed as discordant. Other cases are not considered. The simplest version of the statistic, called $T_A$ is then defined as

$$T_A = \frac{n_c - n_d}{n_0},$$
with \\
$n_c$, the number of concordant pairs, \\
$n_d$, the number of discordant pairs, and \\
$n_0 = n * (n + 1) / 2$.

As we have seen in example above, can also have same rank for items. In order to account for this, a second statistic, $T_B$ has been defined as

$$T_A = \frac{n_c - n_d}{\sqrt{(n_0 - n_1 )(n_0 - n_2 )}},$$
with \\
$n_c$, $n_d$, $n_0$ as above, \\
$n_1=\sum_i{t_i(t_i-1)/2}$, \\
$n_1=\sum_j{t_j(t_j-1)/2}$, \\
$t_i,$ the number of ties observed for X in the ith position of the ranking \\
$u_j,$ the number of ties observed for Y in the ith position of the ranking

% In theory explanation for Kendall's Tau B because ranking could be tied but not as a result of Label Ranking and unlikely for regression the implementation that is used calculates Tau b!
\section{Implementation}
\subsection{jPL}

\subsection{WEKA}

### 2018-01-07 Writing/Thesis/content/chapter-implementation.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
\chapter{Implementation}
\label{sec:implementation}

### 2018-01-07 Writing/Thesis/content/chapter-introduction.tex
Add introduction, related + fundamentals parts

--- 2017-12-06 Writing/Proposal/Tex/paper.tex
@@
-\documentclass[12pt]{scrartcl}
+% !TEX root = ../my-thesis.tex
+%
+\chapter{Introduction}
+\label{sec:intro}
 
-\usepackage[american]{babel}
-
-\usepackage{graphicx}
-
-\usepackage{paralist}
-\usepackage{csquotes}
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
-
-\usepackage[marginal]{footmisc}
-\usepackage{hyperref}
-\usepackage{pgfgantt}
-\usepackage{float}
-\usepackage[backend=biber,style=numeric-comp]{biblatex}
-\usepackage{tikz}
-\usepackage{xcolor}
-
-% Colour Definitions
-\definecolor{uniblue}{RGB}{000,032,091}
-\definecolor{unigrey}{RGB}{199,201,199}
-\definecolor{uniaccentblue}{RGB}{000,163,224}
-
-\addbibresource{literature3.bib}
-
-\usepackage{geometry}
-% \geometry{a4paper,body={5.8in,9in}}
-\geometry{a4paper}
-
-\usepackage{amsmath, amsfonts, amssymb}
-\usepackage{placeins}
-\usepackage{subcaption}
-
-\usepackage{setspace}
-
-\setlength{\parindent}{0pt}
-
-\renewcommand{\labelenumi}{\arabic{enumi}.} 
-\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
-\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumii}}
-
-\begin{document}
-
-\title{Ranking of Classification Algorithms in AutoML}
-\subtitle{A Comparison of Regression-Based Ranking and Preference Models
-\\\vspace{2em}Bachelor's Thesis Proposal \& Work Plan}
-
-\author{Helena Graf\\ 
-\small{matriculation number: 7011643}\\ 
-\small{hgraf@mail.upb.de}}
-\date{\today}
-
-\maketitle
-\vspace{2em}
-
-\begin{center}
-\small{Supervisors:}\\
-\large{Prof. Dr. Eyke H\"ullermeier}\\
-\large{Prof. Dr. Axel-Cyrille Ngonga Ngomo}
-\end{center}
-
-\newpage
-
-\section{Motivation}\label{sec:motivation}
-%start with why ML is becoming more important
+\section{Motivation and Problem Statement}
+\label{sec:intro:motivation}
 The potential of big data is evident, and an increasing amount of information is collected and available for analysis - but this potential is not utilized.
@@
 While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available.
-This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.\\
+This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.
 
@@
 So in each case, one would have picked a different algorithm in order to achieve the best results.
-In general, this means that for a different data set, a different algorithm might yield the best performance.\\
+In general, this means that for a different data set, a different algorithm might yield the best performance.
 
@@
 
-\section{Related Work}\label{sec:related_work}
-The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML).
-In the following paragraphs, three of such tools are outlined briefly.\\
+\section{Results}
+\label{sec:intro:results}
 
-Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
-It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka} to assist the large number of novice users of the software in selecting parameterized algorithms for their problems.
-The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}.
-In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution.
-An input data set is first preprocessed by means of feature selection.
-Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}.
-In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model.
-This cycle is then repeated until the allocated time has run out.
-Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forests, which perform well on a large number of data sets, first.
-\\
+\section{Thesis Structure}
+\label{sec:intro:structure}
 
-% SK-learn
-AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an AutoML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}.
-It works very similar to AutoML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian optimization and automatically constructing ensembles during optimization.
-During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of data sets.
-For each data set, the algorithm which shows the best empirical performance is noted.
-Then, certain meta-features are calculated for each data set.
-The first step of the tool when given a new problem is to calculate meta-features of the data set.
-Then, the Manhattan distance to the other data sets is determined according to the meta-features, and the algorithms that are associated with the k-nearest data sets are used as a starting point for further optimization.
-The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust application.
-Their results show that meta-learning can be used to improve the overall AutoML process.\\
-
-% ML-Plan
-ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}.
-This is achieved by viewing machine-learning as a task, building a hierarchical task network out of those tasks, and then searching for a solution in the induced tree structure.
-In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks.
-An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'.
-The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed.
-A best-first search algorithm in a modified variant is then used to find good solutions in this task network.
-While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\
-
-\begin{figure}
-\tikzset{edge from parent/.style={draw,->}}
-\begin{tikzpicture}[sibling distance=10em,
-  every node/.style = {shape=rectangle, rounded corners,
-    draw, align=center}]]
-  \node {\textcolor{uniblue}{classify}}
-    child { node {...} }
-    child { node {\textcolor{uniblue}{classifyWithNN}}
-    child { node {...} }
-      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
-        child { node {...} }
-        child { node {...} 
-          child { node {...}  }
-          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } } } }
-    };
-\end{tikzpicture}
-\caption{An example for how the complex task 'classify' might be broken down by ML-Plan.
-The figure is loosely adapted from \cite{wever2017automatic}.
-Nodes containing '...' represent an undefined amount of subtrees.
-\textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
-\label{fig:mltree}
-\end{figure}
-
-\section{Goals}\label{sec:goals}
-The aim of this thesis is to test the assumption that given a new data set, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods.
-It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited meta-learning in this way.
-If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how meta-learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process.
-The aim presented consists of multiple goals, which can be divided into required and optional goals.
-
-\subsection{Required Goals}\label{subsec:required_goals}
-Based on the general objective of the thesis, several goals should be achieved:
-
-\begin{enumerate}
-	\item Implementing a tool with the following functionality:
-	\begin{enumerate}
-		\item A pre-processing phase in which the performances of the available set of classifiers is calculated for a set of data sets, a regression model is fit to each of the classifiers, and a preference-ranker is fit to the ranks of the algorithms which can be deduced from their performance values.
-		\item A method where the tool is given a data set and returns a ranking of classifiers for this data set.
-		\item The possibility to choose between regression-based and preference-based ranking.
-	\end{enumerate}
-	\item Evaluate the predictions of both the regression and preference-ranking variant of the implementation by comparing them against each other, an oracle that represents the best ranking according to actual algorithms performances, and a best-algorithm baseline.
-\end{enumerate}
-
-\newpage
-\subsection{Optional Goals}\label{subsec:optional_goals}
-If the required goals have been met in less time than originally allocated, and the initial results are promising, addressing additional goals may be considered.
-The following list suggests possible optional goals.
-However, they may be replaced if while working on the thesis it becomes clear that more appropriate expansions exist.
-
-\begin{enumerate}
-	\item Adding automatic optimization of regression and ranking models with the help of ML-Plan and jPL\footnotemark{ } respectively \cite{intelligent2017jpl}.
-	\item Extend the evaluation by comparing the tool with other AutoML solutions.
-	\item Extend the evaluation by evaluating against a more intelligent baseline.
-	\item Adding another layer to the search by including hyperparameters, possibly by means of iterative requests to the tool.
-	\item Adding runtime and/ or complexity prediciton to allow for combined predictions.
-\end{enumerate}
-\footnotetext{A framework for the evaluation of preference learners.}
-
-\section{Approach}\label{sec:approach}
-As described in Chapter \ref{sec:goals}, the goal is to implement an AutoML tool that returns a ranking of classification algorithms for a given data set based on past performances of the classifiers by using regression and ranking models and evaluating the results.
-The implementation of this tool will be done in Java 8.
-Since the aim is to ensure a basic functionality, preliminary algorithms are going to be used both for regression and ranking models.\\
-
-The first step therefore is to implement the pre-processing phase, which consist of computing the performances of classifiers on data sets.
-For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark.
-The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and algorithm runs.
-Since the results of the runs are available publicly on the website, some of the required data may be extracted instead of computed.
-OpenML.org provides the data sets in .ARFF format, and supplies a WEKA plug-in, which should ensure that these libraries work together smoothly.
-\\
-
-\footnotetext{Meta-classifiers and ensemble-classifiers will not be supported.}
-
-The next step is to add the functionality to fit preliminary regression models and a preference ranker to the performance data, based on properties of the data sets.
-This step also includes providing a method that can be given a data set and returns a ranking, based on the choice of ranking method either based on regression or a preference model.
-This method first needs to compute properties of the new data set.
-Then, for regression, it is going to use the preliminary regression model of each algorithm to get a predicted performance of each classifier for the new data set.
-These predictions are turned into a ranking.
-For the ranking model, the computed properties of the new data set can be fed to the model directly.\\
-
-For the evaluation, it is necessary to generate a baseline and an oracle.
-Both can be obtained from the data of the pre-processing phase.
-Due to all performances of classifiers being recorded on all data sets, one can obtain an optimal ranking of classifiers for each data set from that same table.
-The baseline which is going to be used is counting the number of data sets for which a classifier is the best option, and then ranking them from overall best performance (best choice for most data sets) to worst.
-This can be obtained from the table of the pre-processing phase as well.
-The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall rank correlation coefficient.
-
-\newpage
-\section{Preliminary Document Structure}\label{sec:doc-structure}
-The following structure will serve as an orientation during the writing process. While the chapters should remain the same, subsections may be added, removed or moved.
-
-\begin{enumerate}
-	\item Introduction
-	\item Fundamentals
-	\begin{enumerate}
-		\item Meta-Learning
-		\item Kendall Rank Correlation Coefficient
-		\item JPL
-		\item WEKA
-	\end{enumerate}
-	\item Approach
-	\item Implementation
-	\begin{enumerate} 
-		\item Regression-based Ranking
-		\begin{enumerate}
-			\item Preliminary Regression Algorithm
-			\item Automatic Algorithm Selection
-		\end{enumerate}
-		\item Preference Models
-		\begin{enumerate}
-			\item Preliminary Ranking Algorithm
-			\item Automatic Algorithm Selection
-		\end{enumerate}
-	\end{enumerate}
-	\item Evaluation
-	\begin{enumerate}
-		\item Computing the Accuracy of the Results
-		\item Assessment of the Accuracy
-	\end{enumerate}
-	\item Related Work
-		% Include RECIPE in final work also
-		%Auto-WEKA
-		%Auto-sklearn
-		% ML-Plan
-	\item Conclusion
-	\item Literature
-	\item Appendix
-\end{enumerate}
-
-\newpage
-\section{Schedule}\label{sec:schedule}
-The working time is going to be structured according to the schedule shown in Figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.
-
-\begin{figure}[H]
-% Gantt Chart of Schedule
-\begin{ganttchart}[
-%% Style Definitions %%
-% Canvas %
-x unit=0.6cm,
-y unit chart = 0.65cm,
-canvas/.append style={fill=none, draw=unigrey},
-hgrid style/.style={draw=black!25, line width=.75pt},
-vgrid={*1{draw=unigrey, line width=.75pt}},
-title/.style={draw=none, fill=none},
-% Title %
-title label font=\bfseries,
-title label node/.append style={below=0pt},
-include title in canvas=false,
-% Bar %
-bar height=.5,
-bar label node/.append style={align=left,text width=14em},
-bar/.append style={draw=none, fill=uniblue},
-% Group %
-group height=.2,
-   group peaks tip position=0,
-group label node/.append style={align=left,text width=15em},
-group/.append style={fill=black,opacity=0}
-]{1}{16}
-
-%% Chart %%
-% Title %
-\gantttitle[title label node/.append style={below left=0pt and -7pt}]{WEEK:\quad1}{1}
-\gantttitlelist{2,...,16}{1} \\
-
-% Elements %
-\ganttgroup[]{Implementation}{1}{10} \\
-\ganttbar{Phase 1}{1}{2} \\
-\ganttbar[]{Phase 2}{3}{4} \\
-\ganttbar[]{Evaluation}{6}{7} \\
-\ganttbar[bar/.append style={fill=unigrey}]{Buffer}{5}{5} \\
-
-\ganttgroup[]{Writing\footnotemark}{1}{13} \\
-\ganttbar[]{Related \& Fundamentals}{1}{3} \\
-\ganttbar[]{Approach \& Implementation}{4}{7} \\
-\ganttbar[]{Evaluation \& Conclusion}{8}{10} \\
-\ganttbar[bar/.append style={fill=unigrey}]{Buffer, Proofreading}{11}{13} \\
-\ganttbar[]{Corrections}{14}{15} \\
-
-\ganttgroup[]{Other}{5}{16} \\
-\ganttbar[]{Presentation Preparation}{15}{16} \\
-
-\end{ganttchart}
-
-\caption{Sketch of the Work Schedule for the thesis.}
-\label{fig:schedule}
-\end{figure}
-
-\footnotetext{The chapter 'Introduction' is not included since it will be written in parallel to other chapters, in small bits according to the progress of the thesis.}
-
-\newpage
-\printbibliography
-
-\newpage
-% Signatures and Delcaration %
-Hereby supervisor and student confirm that this proposal is the basis for the topic assignment of the described work.
-The timetable and topic description are accepted by both sides as laid out in this proposal.
-
-\vspace{6cm}
-
-\begin{center}
-     \begin{tabular}{l p{0.1\textwidth} r}
-       \cline{1-1} \cline{3-3}
-       \begin{minipage}[t]{0.4\textwidth}
-         \centering
-         Supervisor\\(Prof. Dr. Eyke H\"ullermeier)
-         \end{minipage}
-&
-         \begin{minipage}[t]{0.2\textwidth}
-         \end{minipage}
-&
-         \begin{minipage}[t]{0.4\textwidth}
-           \centering
-           Student\\(Helena Graf)
-         \end{minipage}
-     \end{tabular}
-\end{center}
-
-\end{document}
+\textbf{Chapter \ref{sec:fundamentals}} \\[0.2em]

### 2018-01-07 Writing/Thesis/content/chapter-related-work.tex
Add introduction, related + fundamentals parts

--- 2017-12-06 Writing/Proposal/Tex/paper.tex
@@
-\documentclass[12pt]{scrartcl}
+% !TEX root = ../my-thesis.tex
+%
+\chapter{Related Work}
+\label{sec:related}
 
-\usepackage[american]{babel}
-
-\usepackage{graphicx}
-
-\usepackage{paralist}
-\usepackage{csquotes}
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
-
-\usepackage[marginal]{footmisc}
-\usepackage{hyperref}
-\usepackage{pgfgantt}
-\usepackage{float}
-\usepackage[backend=biber,style=numeric-comp]{biblatex}
-\usepackage{tikz}
-\usepackage{xcolor}
-
-% Colour Definitions
-\definecolor{uniblue}{RGB}{000,032,091}
-\definecolor{unigrey}{RGB}{199,201,199}
-\definecolor{uniaccentblue}{RGB}{000,163,224}
-
-\addbibresource{literature3.bib}
-
-\usepackage{geometry}
-% \geometry{a4paper,body={5.8in,9in}}
-\geometry{a4paper}
-
-\usepackage{amsmath, amsfonts, amssymb}
-\usepackage{placeins}
-\usepackage{subcaption}
-
-\usepackage{setspace}
-
-\setlength{\parindent}{0pt}
-
-\renewcommand{\labelenumi}{\arabic{enumi}.} 
-\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
-\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumii}}
-
-\begin{document}
-
-\title{Ranking of Classification Algorithms in AutoML}
-\subtitle{A Comparison of Regression-Based Ranking and Preference Models
-\\\vspace{2em}Bachelor's Thesis Proposal \& Work Plan}
-
-\author{Helena Graf\\ 
-\small{matriculation number: 7011643}\\ 
-\small{hgraf@mail.upb.de}}
-\date{\today}
-
-\maketitle
-\vspace{2em}
-
-\begin{center}
-\small{Supervisors:}\\
-\large{Prof. Dr. Eyke H\"ullermeier}\\
-\large{Prof. Dr. Axel-Cyrille Ngonga Ngomo}
-\end{center}
-
-\newpage
-
-\section{Motivation}\label{sec:motivation}
-%start with why ML is becoming more important
-The potential of big data is evident, and an increasing amount of information is collected and available for analysis - but this potential is not utilized.
-In a white paper, the International Data Corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data only 3\% were tagged as to enable further processing, and only 0.5\% were analyzed \cite{gantz2012the}.
-A follow-up paper in 2017 projects that in 2025, 15\% of the estimated 163ZB of global data will be tagged, and approximately 3\% analyzed \cite{gantz2017data}.
-While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available.
-This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.\\
-
-One of the most prominent machine learning tasks is classification: A class is assigned to an instance, for example clients of a bank may be either deemed creditworthy or not, based on factors like other existing credits or the job of the client.
-But selecting a fitting classifier for a new data set is difficult, since algorithm performances can vary substantially among data sets, and it is not feasible to simply apply a large number of them to empirically find a good match.
-For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
-The predictive accuracy of the Random Forest\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
-On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}.
-So in each case, one would have picked a different algorithm in order to achieve the best results.
-In general, this means that for a different data set, a different algorithm might yield the best performance.\\
-
-Since there is no one best classifier for all data sets, it is likely that how well a classifier performs on a given data set is dependent on properties of the data set, at least to some degree.
-Combined with the need for automated machine learning, this calls for an approach that considers past performances of classifiers for data sets in relation to properties of these data sets to automatically suggest well-performing classifiers for a new problem.
-
-\section{Related Work}\label{sec:related_work}
 The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML).
@@
 \end{figure}
-
-\section{Goals}\label{sec:goals}
-The aim of this thesis is to test the assumption that given a new data set, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods.
-It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited meta-learning in this way.
-If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how meta-learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process.
-The aim presented consists of multiple goals, which can be divided into required and optional goals.
-
-\subsection{Required Goals}\label{subsec:required_goals}
-Based on the general objective of the thesis, several goals should be achieved:
-
-\begin{enumerate}
-	\item Implementing a tool with the following functionality:
-	\begin{enumerate}
-		\item A pre-processing phase in which the performances of the available set of classifiers is calculated for a set of data sets, a regression model is fit to each of the classifiers, and a preference-ranker is fit to the ranks of the algorithms which can be deduced from their performance values.
-		\item A method where the tool is given a data set and returns a ranking of classifiers for this data set.
-		\item The possibility to choose between regression-based and preference-based ranking.
-	\end{enumerate}
-	\item Evaluate the predictions of both the regression and preference-ranking variant of the implementation by comparing them against each other, an oracle that represents the best ranking according to actual algorithms performances, and a best-algorithm baseline.
-\end{enumerate}
-
-\newpage
-\subsection{Optional Goals}\label{subsec:optional_goals}
-If the required goals have been met in less time than originally allocated, and the initial results are promising, addressing additional goals may be considered.
-The following list suggests possible optional goals.
-However, they may be replaced if while working on the thesis it becomes clear that more appropriate expansions exist.
-
-\begin{enumerate}
-	\item Adding automatic optimization of regression and ranking models with the help of ML-Plan and jPL\footnotemark{ } respectively \cite{intelligent2017jpl}.
-	\item Extend the evaluation by comparing the tool with other AutoML solutions.
-	\item Extend the evaluation by evaluating against a more intelligent baseline.
-	\item Adding another layer to the search by including hyperparameters, possibly by means of iterative requests to the tool.
-	\item Adding runtime and/ or complexity prediciton to allow for combined predictions.
-\end{enumerate}
-\footnotetext{A framework for the evaluation of preference learners.}
-
-\section{Approach}\label{sec:approach}
-As described in Chapter \ref{sec:goals}, the goal is to implement an AutoML tool that returns a ranking of classification algorithms for a given data set based on past performances of the classifiers by using regression and ranking models and evaluating the results.
-The implementation of this tool will be done in Java 8.
-Since the aim is to ensure a basic functionality, preliminary algorithms are going to be used both for regression and ranking models.\\
-
-The first step therefore is to implement the pre-processing phase, which consist of computing the performances of classifiers on data sets.
-For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark.
-The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and algorithm runs.
-Since the results of the runs are available publicly on the website, some of the required data may be extracted instead of computed.
-OpenML.org provides the data sets in .ARFF format, and supplies a WEKA plug-in, which should ensure that these libraries work together smoothly.
-\\
-
-\footnotetext{Meta-classifiers and ensemble-classifiers will not be supported.}
-
-The next step is to add the functionality to fit preliminary regression models and a preference ranker to the performance data, based on properties of the data sets.
-This step also includes providing a method that can be given a data set and returns a ranking, based on the choice of ranking method either based on regression or a preference model.
-This method first needs to compute properties of the new data set.
-Then, for regression, it is going to use the preliminary regression model of each algorithm to get a predicted performance of each classifier for the new data set.
-These predictions are turned into a ranking.
-For the ranking model, the computed properties of the new data set can be fed to the model directly.\\
-
-For the evaluation, it is necessary to generate a baseline and an oracle.
-Both can be obtained from the data of the pre-processing phase.
-Due to all performances of classifiers being recorded on all data sets, one can obtain an optimal ranking of classifiers for each data set from that same table.
-The baseline which is going to be used is counting the number of data sets for which a classifier is the best option, and then ranking them from overall best performance (best choice for most data sets) to worst.
-This can be obtained from the table of the pre-processing phase as well.
-The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall rank correlation coefficient.
-
-\newpage
-\section{Preliminary Document Structure}\label{sec:doc-structure}
-The following structure will serve as an orientation during the writing process. While the chapters should remain the same, subsections may be added, removed or moved.
-
-\begin{enumerate}
-	\item Introduction
-	\item Fundamentals
-	\begin{enumerate}
-		\item Meta-Learning
-		\item Kendall Rank Correlation Coefficient
-		\item JPL
-		\item WEKA
-	\end{enumerate}
-	\item Approach
-	\item Implementation
-	\begin{enumerate} 
-		\item Regression-based Ranking
-		\begin{enumerate}
-			\item Preliminary Regression Algorithm
-			\item Automatic Algorithm Selection
-		\end{enumerate}
-		\item Preference Models
-		\begin{enumerate}
-			\item Preliminary Ranking Algorithm
-			\item Automatic Algorithm Selection
-		\end{enumerate}
-	\end{enumerate}
-	\item Evaluation
-	\begin{enumerate}
-		\item Computing the Accuracy of the Results
-		\item Assessment of the Accuracy
-	\end{enumerate}
-	\item Related Work
-		% Include RECIPE in final work also
-		%Auto-WEKA
-		%Auto-sklearn
-		% ML-Plan
-	\item Conclusion
-	\item Literature
-	\item Appendix
-\end{enumerate}
-
-\newpage
-\section{Schedule}\label{sec:schedule}
-The working time is going to be structured according to the schedule shown in Figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.
-
-\begin{figure}[H]
-% Gantt Chart of Schedule
-\begin{ganttchart}[
-%% Style Definitions %%
-% Canvas %
-x unit=0.6cm,
-y unit chart = 0.65cm,
-canvas/.append style={fill=none, draw=unigrey},
-hgrid style/.style={draw=black!25, line width=.75pt},
-vgrid={*1{draw=unigrey, line width=.75pt}},
-title/.style={draw=none, fill=none},
-% Title %
-title label font=\bfseries,
-title label node/.append style={below=0pt},
-include title in canvas=false,
-% Bar %
-bar height=.5,
-bar label node/.append style={align=left,text width=14em},
-bar/.append style={draw=none, fill=uniblue},
-% Group %
-group height=.2,
-   group peaks tip position=0,
-group label node/.append style={align=left,text width=15em},
-group/.append style={fill=black,opacity=0}
-]{1}{16}
-
-%% Chart %%
-% Title %
-\gantttitle[title label node/.append style={below left=0pt and -7pt}]{WEEK:\quad1}{1}
-\gantttitlelist{2,...,16}{1} \\
-
-% Elements %
-\ganttgroup[]{Implementation}{1}{10} \\
-\ganttbar{Phase 1}{1}{2} \\
-\ganttbar[]{Phase 2}{3}{4} \\
-\ganttbar[]{Evaluation}{6}{7} \\
-\ganttbar[bar/.append style={fill=unigrey}]{Buffer}{5}{5} \\
-
-\ganttgroup[]{Writing\footnotemark}{1}{13} \\
-\ganttbar[]{Related \& Fundamentals}{1}{3} \\
-\ganttbar[]{Approach \& Implementation}{4}{7} \\
-\ganttbar[]{Evaluation \& Conclusion}{8}{10} \\
-\ganttbar[bar/.append style={fill=unigrey}]{Buffer, Proofreading}{11}{13} \\
-\ganttbar[]{Corrections}{14}{15} \\
-
-\ganttgroup[]{Other}{5}{16} \\
-\ganttbar[]{Presentation Preparation}{15}{16} \\
-
-\end{ganttchart}
-
-\caption{Sketch of the Work Schedule for the thesis.}
-\label{fig:schedule}
-\end{figure}
-
-\footnotetext{The chapter 'Introduction' is not included since it will be written in parallel to other chapters, in small bits according to the progress of the thesis.}
-
-\newpage
-\printbibliography
-
-\newpage
-% Signatures and Delcaration %
-Hereby supervisor and student confirm that this proposal is the basis for the topic assignment of the described work.
-The timetable and topic description are accepted by both sides as laid out in this proposal.
-
-\vspace{6cm}
-
-\begin{center}
-     \begin{tabular}{l p{0.1\textwidth} r}
-       \cline{1-1} \cline{3-3}
-       \begin{minipage}[t]{0.4\textwidth}
-         \centering
-         Supervisor\\(Prof. Dr. Eyke H\"ullermeier)
-         \end{minipage}
-&
-         \begin{minipage}[t]{0.2\textwidth}
-         \end{minipage}
-&
-         \begin{minipage}[t]{0.4\textwidth}
-           \centering
-           Student\\(Helena Graf)
-         \end{minipage}
-     \end{tabular}
-\end{center}
-
-\end{document}

### 2018-01-07 Writing/Thesis/content/declaration.tex
Add introduction, related + fundamentals parts

% !TEX root = ../my-thesis.tex
%
%************************************************
% Declaration
%************************************************
\pdfbookmark[0]{Declaration}{Declaration}
\chapter*{Declaration}
\label{sec:declaration}
\thispagestyle{empty}
\vspace*{-10mm}

I hereby declare that I prepared this thesis independently and without illicit assistance and have not used any sources without declaration. Any statements that have been adopted literally or analogously have been identified as such. This thesis has not been submitted in the same or substantially similar version, not even in part, to another authrity for grading and has not been published elsewhere.

\vspace*{20mm}
{\usekomafont{chapter}Declaration (German)}\label{sec:abstract-diff} \\

Ich versichere, dass ich die Arbeit ohne fremde Hilfe und ohne Benutzung anderer als der angegebenen Quellen angefertigt habe und dass die Arbeit in gleicher oder ähnlicher Form noch keiner anderen Prüfungsbehörde vorgelegen hat und von dieser als Teil einer Prüfungsleistung angenommen worden ist. Alle Ausführungen, die wörtlich oder sinngemäß übernommen worden sind, sind als solche gekennzeichnet.

\bigskip

\noindent\textit{\thesisUniversityCity, \thesisDate}

\smallskip

\begin{flushright}
	\begin{minipage}{5cm}
		\rule{\textwidth}{1pt}
		\centering\thesisName
	\end{minipage}
\end{flushright}

%*****************************************
%*****************************************

### 2018-01-07 Writing/Thesis/main.tex
Add introduction, related + fundamentals parts

% **************************************************
% Document Class Definition
% **************************************************
\documentclass[%
    paper=A4,               % paper size --> A4 is default in Germany
    twoside=true,           % onesite or twoside printing
    openright,              % doublepage cleaning ends up right side
    parskip=full,           % spacing value / method for paragraphs
    chapterprefix=true,     % prefix for chapter marks
    11pt,                   % font size
    headings=normal,        % size of headings
    bibliography=totoc,     % include bib in toc
    listof=totoc,           % include listof entries in toc
    titlepage=on,           % own page for each title page
    captions=tableabove,    % display table captions above the float env
    draft=false,            % value for draft version
]{scrreprt}%

% **************************************************
% Setup YOUR thesis document in this file !
% **************************************************
\input{my-thesis-setup}

% **************************************************
% Document CONTENT
% **************************************************
\begin{document}

% --------------------------
% rename document parts
% --------------------------
%\renewcaptionname{ngerman}{\figurename}{Abb.}
%\renewcaptionname{ngerman}{\tablename}{Tab.}
\renewcaptionname{english}{\figurename}{Fig.}
\renewcaptionname{english}{\tablename}{Tab.}
\newtheorem{defn}{Definition}
% --------------------------
% Front matter
% --------------------------
\pagenumbering{roman}			% roman page numbing (invisible for empty page style)
\pagestyle{empty}				% no header or footers
\input{content/titlepages}		% INCLUDE: all titlepages
\cleardoublepage

\pagestyle{plain}				% display just page numbers
\input{content/abstract}		% INCLUDE: the abstracts (english and german)
\cleardoublepage
%
\input{content/acknowledgement} % INCLUDE: acknowledgement
\cleardoublepage
%
\setcounter{tocdepth}{2}		% define depth of toc
\tableofcontents				% display table of contents
\cleardoublepage

% --------------------------
% Body matter
% --------------------------
\pagenumbering{arabic}			% arabic page numbering
\setcounter{page}{1}			% set page counter
\pagestyle{maincontentstyle} 	% fancy header and footer

\input{content/chapter-introduction}   % INCLUDE: introduction
\input{content/chapter-fundamentals}   % INCLUDE: fundamentals
\input{content/chapter-approach}       % INCLUDE: approach
\input{content/chapter-implementation} % INCLUDE: implementation
\input{content/chapter-evaluation}     % INCLUDE: evaluation
\input{content/chapter-related-work}   % INCLUDE: related work
\input{content/chapter-conclusion}     % INCLUDE: conclusion

% --------------------------
% Back matter
% --------------------------
\appendix\cleardoublepage
\input{content/chapter-appendix}       % INCLUDE: appendix
%
{%
\setstretch{1.1}
\renewcommand{\bibfont}{\normalfont\small}
\setlength{\biblabelsep}{0pt}
\setlength{\bibitemsep}{0.5\baselineskip plus 0.5\baselineskip}
\printbibliography[nottype=online]
\printbibliography[heading=subbibliography,title={Webpages},type=online,prefixnumbers={@}]
}
\cleardoublepage

\listoffigures
\cleardoublepage

\listoftables
\cleardoublepage

\input{content/colophon}
\cleardoublepage

\input{content/declaration}
\clearpage
\newpage
\mbox{}

% **************************************************
% End of Document CONTENT
% **************************************************
\end{document}

### 2018-01-14 Writing/Thesis/content/chapter-fundamentals.tex
Write some more for thesis

@@
 \subsection{Classification and Regression}
+%TODO instance explained before here?
 In addition to falling into the category of supervised learning, the problem is a classification problem.
 The nature of the prediction is to assign one of the three classes, or labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
-Formally, this means that the output space $Y$ of the target function consist of a finite set of labels $(y_1,\dots,y_n)$, so in this case $Y=('iris-setosa','iris virginica', 'iris versicolor')$.
+Formally, this means that the output space $Y$ of the target function consist of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, so that each instance is associated with a label $y_i \in Y$, in this case $Y=\lbrace 'iris-setosa','iris virginica', 'iris versicolor' \rbrace $.
 
@@
 Preference Learning is a relatively new subfield of machine learning\cite{DBLP:books/daglib/0025729}.
-It is dedicated to the problem of learning how to rank, the precise definition of what this encompasses being defined by which specific task one is engaged in.
+It is dedicated to the problem of learning how to rank, the precise definition of what this encompasses being defined by the specific task.
 Out of the three main tasks of preference learning, namely label ranking, instance ranking and object ranking, label ranking is the relevant one in the context of this thesis.
@@
 \subsubsection{Ranking and Ordering}
+To clarify the meaning of ranking and ordering, we return to the gardening example.
+After spending some time studying the different flowers, the gardener has realized he prefers certain iris species to others.
+
+Ranking = Permutation of the actual labels!
+Ordering =
+
+A ranking for a set of items defines a strict total order
 
 % Gardener example ranking his favourite plants
+The ordering sorts the labels according to their given score.
+It thus may also implicitly be given by ordering the items themselves, as the labels are aliases for them.
+Therefore, an ordering for a set of labels $\lbrace 1\dots k\rbrace$ is a permutation $\pi$ of the labels where $\pi(i)$ is the
+
+It must be noted that the definitions given here are not transferable to the general case of a ranking or ordering problems, since a strict total order is not required in all contexts for either ranking or ordering.
 
@@
 		Species		& 	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris virginica}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris versicolor}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris setosa}	& 	\\ \hline
-		Labels		& [ & 1,									& 2,										& 3 									& ] \\
-		Scores		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
+		Label		& [ & 1,									& 2,										& 3 									& ] \\ 
+		Score		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
 		Ranking		& [ & 2,									& 3,										& 1 									& ] \\ 
@@
 % could be seen as a generalisation of classification
-Similar to classification, in label ranking there is a finite set of labels $Y=(y_1,\dots,y_n)$, but it is not the output space. Instead, the output space consists of rankings of these labels
+Similar to classification, in label ranking there is a finite set of labels $Y=\lbrace y_1,\dots,y_n \rbrace$, but it is not the output space.
+Instead, \citeauthor{DBLP:books/daglib/0025729} define the target function for label ranking as $X\rightarrow S_Y$ where the output space $S_Y$ contains all permutations over the set of labels $Y$ \cite{DBLP:books/daglib/0025729}.
+An instance $x \in X$ therefore is assigned a permutation $y_{\pi_x^i}$
+
+Although called label ranking actually label ordering!
 
@@
 % In theory explanation for Kendall's Tau B because ranking could be tied but not as a result of Label Ranking and unlikely for regression the implementation that is used calculates Tau b!
-\section{Implementation}
-\subsection{jPL}
-
-\subsection{WEKA}

### 2018-01-14 Writing/Thesis/content/chapter-implementation.tex
Write some more for thesis

@@
 \label{sec:implementation}
+
+\subsection{Frameworks used}
+% Weka for classifiers
+
+% Data sets from OpenML
+
+\subsection{jPL framework}
+The jPL framework is a java framework for the evaluation of preference learning algorithms.
+It implements several tasks from the context of preference learning, including label ranking.
+Furthermore, the framework introduces the Generic Preference Representation Format (GPRF) to store preference information.
+
+\subsection{WEKA}

### 2018-01-14 Writing/Thesis/content/chapter-introduction.tex
Write some more for thesis

@@
 
+This introduction emphasizes why there is a need for automation in machine learning, and how this thesis relates to that problem.
+
 \section{Motivation and Problem Statement}
 \label{sec:intro:motivation}
+% Need more automated analysis of data
 The potential of big data is evident, and an increasing amount of information is collected and available for analysis - but this potential is not utilized.
@@
 
+% Of ML, tasks, classification is important & classifier performances vary across data sets, so it is not easy to just pick one
 One of the most prominent machine learning tasks is classification: A class is assigned to an instance, for example clients of a bank may be either deemed creditworthy or not, based on factors like other existing credits or the job of the client.
@@
 
+% Together this means that classifier selection is area where one can automate -> area of problem is suggesting classifiers
 Since there is no one best classifier for all data sets, it is likely that how well a classifier performs on a given data set is dependent on properties of the data set, at least to some degree.
 Combined with the need for automated machine learning, this calls for an approach that considers past performances of classifiers for data sets in relation to properties of these data sets to automatically suggest well-performing classifiers for a new problem.
+
+% Therefore the goal is the development of a tool that does this
 
@@
 \label{sec:intro:structure}
+% These are sort of abstracts for each chapter
 
 \textbf{Chapter \ref{sec:fundamentals}} \\[0.2em]
+% Begin with fundamentals to give a brief overview of the field of ML relevant to this thesis
+%TODO measures of evaluation!!! 
+Firstly, relevant preliminaries are discussed. A brief overview of tasks from the field of machine learning which are relevant to this thesis is given.
+
+\textbf{Chapter \ref{sec:approach}} \\[0.2em]
+% Continue with description of the approach to the problem described in detail
+This chapter continues by describing the approach of this thesis in tackling the problem of suggesting classifies
+
+\textbf{Chapter \ref{sec:implementation}} \\[0.2em]
+% Go into detail of implementation
+Following the details of the approach the implementation thereof is presented.
+
+\textbf{Chapter \ref{sec:evaluation}} \\[0.2em]
+
+\textbf{Chapter \ref{sec:related}} \\[0.2em]
+
+\textbf{Chapter \ref{sec:conclusion}} \\[0.2em]
+The final chapter concludes the thesis and provides an outlook for possible future work.

### 2018-01-14 ranker/src/main/java/ranker/Main.java
More meta feature / data set get methods; adjust rankers

@@ -1,7 +1,11 @@
 package ranker;
 
+import java.io.BufferedReader;
 import java.io.File;
 import java.io.IOException;
+import java.nio.file.FileSystems;
+import java.nio.file.Files;
+import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.List;
 
@@ -11,22 +15,39 @@ import weka.core.converters.ArffSaver;
 public class Main {
 
 	public static void main(String[] args) throws Exception {
-
-//		BufferedReader reader = Files.newBufferedReader(Util.resultsPath.resolve("Perf").resolve("metafeatures.arff"),
-//				Util.charset);
-//		Instances instances = new Instances(reader);
-//		RandomForestRanker ranker = new RandomForestRanker();
-//		Util.testRanker(ranker, instances);
 		
-		List<Integer> datasets = Util.getDataSetsFromIndex();
-		Instances instances = Util.computeMetaFeatures(datasets);
-		ArffSaver saver = new ArffSaver();
-		saver.setInstances(instances);
-		try {
-			saver.setFile(new File(instances.relationName()));
-			saver.writeBatch();
-		} catch (IOException e) {
-			e.printStackTrace();
-		}
+//		List<Integer> datasets = Util.getDataSetsFromIndex();
+//		Instances instances1 = Util.getMetaFeaturesFromOpenML();
+//		ArffSaver saver = new ArffSaver();
+//		saver.setInstances(instances1);
+//		try {
+//			saver.setFile(new File(instances1.relationName() + ".arff"));
+//			saver.writeBatch();
+//		} catch (IOException e) {
+//			e.printStackTrace();
+//		}
+		
+		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("meta_computed.arff"),
+				Util.charset);
+		Instances instances = new Instances(reader);
+		Ranker ranker = new RandomForestRanker();
+		System.out.println(Util.testRanker(ranker, instances));
+		//ranker.buildRanker(instances);
+		
+//		ArrayList<Integer> dataIds = new ArrayList<Integer>();
+//		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("datasets_100_1000"));
+//		String line = null;
+//		while ((line=reader.readLine())!=null) {
+//			dataIds.add(Integer.parseInt(line));
+//		}
+//		Instances results = Util.computeMetaFeatures(dataIds);
[…]

### 2018-01-14 ranker/src/main/java/ranker/PreferenceRanker.java

@@ -14,6 +14,8 @@ import de.upb.cs.is.jpl.api.exception.algorithm.PredictionFailedException;
 import weka.classifiers.Classifier;
 import weka.core.Instance;
 import weka.core.Instances;
+import weka.filters.Filter;
+import weka.filters.unsupervised.attribute.ReplaceMissingValues;
 
 public abstract class PreferenceRanker extends Ranker {
 
@@ -43,19 +45,12 @@ public abstract class PreferenceRanker extends Ranker {
 		labelRankingInstance.setContextId(0);
 		labelRankingInstance.setTotalNumberOfLabels(labels.size());
 		Ranking ranking = learningModel.predict(labelRankingInstance);
-		System.out.println(ranking);
 		int[] rankingResult = ranking.getObjectList();
-		for (int i : rankingResult) {
-			System.out.println(i);
-		}
 		List<Classifier> result = new ArrayList<Classifier>();
 		for (int classifier : rankingResult) {
 			result.add(classifiersMap.get(reverseIndicesMap.get(classifier)));
 		}
 		int[] stuff = ranking.getOrderingForRanking();
-		for (int i : stuff) {
-			System.out.println(i);
-		}
 		return result;
 	}
 
@@ -65,8 +60,21 @@ public abstract class PreferenceRanker extends Ranker {
 		labels = new ArrayList<Integer>();
 		indicesMap = new HashMap<Integer, Integer>();
 		reverseIndicesMap = new HashMap<Integer, Integer>();
+		
+		// Ensure no missing vaules
+		ReplaceMissingValues filter = new ReplaceMissingValues();
+		filter.setInputFormat(data);
+		for (int i = 0; i < data.numInstances(); i++) {
+			filter.input(data.instance(i));
+		}
+		filter.batchFinished();
+		Instances newData = filter.getOutputFormat();
+		Instance processed;
+		while  ((processed=filter.output())!=null) {
+			newData.add(processed);
+		}
 
-		getClassifiersAndMetaFeatures(data);
+		getClassifiersAndMetaFeatures(newData);
 		for (int i = 0; i < classifierIndices.size(); i++) {
 			labels.add(i);
 			indicesMap.put(classifierIndices.get(i), i);
@@ -74,23 +82,19 @@ public abstract class PreferenceRanker extends Ranker {
 		}
 
 		// Convert data given to ranking information
-		data.forEach(instance -> {
+		newData.forEach(instance -> {
 			// Feature information
[…]

### 2018-01-14 ranker/src/main/java/ranker/Ranker.java

@@ -10,6 +10,8 @@ import weka.classifiers.AbstractClassifier;
 import weka.classifiers.Classifier;
 import weka.core.Instance;
 import weka.core.Instances;
+import weka.filters.Filter;
+import weka.filters.unsupervised.attribute.ReplaceMissingValues;
 
 public abstract class Ranker {
 	
@@ -75,7 +77,15 @@ public abstract class Ranker {
 		double[] instanceFeatureValues = new double[features.size()];
 		int featureIndex = 0;
 		for (int attributeIndex : features) {
-			instanceFeatureValues[featureIndex++]=instance.value(attributeIndex);
+			double value = instance.value(attributeIndex);
+			if (value != Double.NaN) {
+				instanceFeatureValues[featureIndex++]= value;				
+			} else {
+				// TODO remove if worked
+				instanceFeatureValues[featureIndex++]= value;
+				System.out.println("Found NaN");
+			}
+			
 		}
 		return instanceFeatureValues;
 	}

### 2018-01-14 ranker/src/main/java/ranker/Util.java

@@ -187,7 +187,16 @@ public class Util {
 		// Add meta features
 		for (int dataSetId : dids) {
 			Instance instance = new DenseInstance(attributes.size());
-			Map<String, Double> dataQualities = characterizer.characterize(getInstancesById(dataSetId));
+			Instances openMLData = null;
+			try {
+				openMLData = getInstancesById(dataSetId);
+			} catch (IOException e) {
+				// TODO logging maybe / outprint here
+				System.out.println("Couldn't get " + dataSetId);
+				continue;
+			}
+			
+			Map<String, Double> dataQualities = characterizer.characterize(openMLData);
 			dataQualities.forEach((dataQuality, value) -> {
 				if (value != null) {
 					instance.setValue(qualityIndices.get(dataQuality), value);
@@ -271,17 +280,21 @@ public class Util {
 				try {
 					BufferedReader reader = Files.newBufferedReader(file, charset);
 					String line = reader.readLine();
+					String fileName = file.getFileName().toString();
+					fileName = fileName.substring(0, fileName.length() - 4);
+					String[] parts = fileName.split("_");
+					String classifierName = parts[0];
+					int dataSetId = Integer.parseInt(parts[1]);
+					Instance instance = metaFeaturesForDataSets.get(dataSetId);
+					int attIndex = classifierIndices.get(classifierName);
+					double value;
 					if (line != null) {
-						String fileName = file.getFileName().toString();
-						fileName = fileName.substring(0, fileName.length() - 4);
-						String[] parts = fileName.split("_");
-						String classifierName = parts[0];
-						int dataSetId = Integer.parseInt(parts[1]);
-						Instance instance = metaFeaturesForDataSets.get(dataSetId);
-						int attIndex = classifierIndices.get(classifierName);
-						double value = Double.parseDouble(line);
-						instance.setValue(attIndex, value);
+						value = Double.parseDouble(line);
+					} else {
+						// TODO hack to avoid NaNs actually has to be worst value for performance measure used!
+						value = 0;
 					}
+					instance.setValue(attIndex, value);
 
 				} catch (IOException e) {
 					// TODO Auto-generated catch block
@@ -382,7 +395,8 @@ public class Util {
 		return dataset;
 	}
 
-	public static void getDataFromOpenML() throws Exception {
[…]

### 2018-01-14 ranker/src/main/java/rankerEvaluation/KendallRankCorrelation.java

@@ -26,7 +26,7 @@ public class KendallRankCorrelation implements RankerEvaluationMeasure {
 				try {
 					perfectRanking = perfectRanker.predictRankingforInstance(instance);
 					List<Classifier> ranking = ranker.predictRankingforInstance(instance);
-					correlation += calculateKendallRankCorrelation(perfectRanking, ranking);
+					correlation += calculateKendallRankCorrelation(ranking,perfectRanking);
 				} catch (Exception e) {
 					e.printStackTrace();
 					numInstancesCalculated--;

### 2018-01-14 ranker/src/main/java/rankerEvaluation/LeaveOneOut.java

@@ -4,6 +4,7 @@ import java.util.ArrayList;
 
 import ranker.Ranker;
 import weka.core.Attribute;
+import weka.core.Instance;
 import weka.core.Instances;
 
 public class LeaveOneOut implements RankerEstimationProcedure {
@@ -14,13 +15,13 @@ public class LeaveOneOut implements RankerEstimationProcedure {
 		double result = 0;
 		for (int i = 0; i < instances.numInstances(); i++) {
 			Instances train = new Instances(instances);
-			train.remove(i);
+			Instance remove = train.remove(i);
 			ArrayList<Attribute> attributes = new ArrayList<Attribute>();
 			for (int attribute = 0; attribute < instances.numAttributes(); attribute++) {
 				attributes.add(instances.attribute(attribute));
 			}
 			Instances test = new Instances("Test", attributes, 0);
-			test.add(instances.get(i));
+			test.add(remove);
 
 			result += evaluationProcedure.evaluate(ranker, train, test);
 		}

### 2018-02-04 ranker/src/main/java/ranker/Util.java
Refactoring / clean-up

@@ -1,86 +1,8 @@
 package ranker;
 
-import java.io.BufferedReader;
-import java.io.BufferedWriter;
-import java.io.File;
-import java.io.IOException;
 import java.nio.charset.Charset;
 import java.nio.file.FileSystems;
-import java.nio.file.Files;
 import java.nio.file.Path;
-import java.util.ArrayList;
-import java.util.HashMap;
-import java.util.List;
-import java.util.Map;
-import java.util.stream.Stream;
-
-import org.apache.commons.math3.stat.correlation.KendallsCorrelation;
-import org.openml.apiconnector.io.OpenmlConnector;
-import org.openml.apiconnector.xml.Data;
-import org.openml.apiconnector.xml.Data.DataSet;
-import org.openml.apiconnector.xml.DataFeature;
-import org.openml.apiconnector.xml.DataFeature.Feature;
-
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningModel;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.labelrankingbypairwisecomparison.LabelRankingByPairwiseComparisonLearningAlgorithm;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.labelrankingbypairwisecomparison.LabelRankingByPairwiseComparisonLearningModel;
-import de.upb.cs.is.jpl.api.dataset.defaultdataset.relative.Ranking;
-import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
-import de.upb.cs.is.jpl.api.exception.algorithm.PredictionFailedException;
-import de.upb.cs.is.jpl.api.exception.algorithm.TrainModelsFailedException;
-import openMLUtil.GlobalCharacterizer;
-import ranker.algorithms.Ranker;
-import rankerEvaluation.BestThreeLoss;
-import rankerEvaluation.KendallRankCorrelation;
-import rankerEvaluation.LeaveOneOut;
-import rankerEvaluation.Loss;
-import rankerEvaluation.PerformanceOrder;
-import rankerEvaluation.RankerEstimationProcedure;
[…]

### 2018-02-04 ranker/src/main/java/ranker/core/algorithms/BestAlgorithmRanker.java

@@ -1,4 +1,4 @@
-package ranker.algorithms;
+package ranker.core.algorithms;
 
 import java.util.ArrayList;
 import java.util.HashMap;

### 2018-02-04 ranker/src/main/java/ranker/core/algorithms/InstanceBasedLabelRankingRanker.java

@@ -1,4 +1,4 @@
-package ranker.algorithms;
+package ranker.core.algorithms;
 
 import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
 import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;

### 2018-02-04 ranker/src/main/java/ranker/core/algorithms/PerfectRanker.java

@@ -1,4 +1,4 @@
-package ranker.algorithms;
+package ranker.core.algorithms;
 
 import java.util.ArrayList;
 import java.util.List;

### 2018-02-04 ranker/src/main/java/ranker/core/evaluation/BestThreeLoss.java

@@ -1,4 +1,4 @@
-package rankerEvaluation;
+package ranker.core.evaluation;
 
 import java.util.ArrayList;
 import java.util.List;

### 2018-02-04 ranker/src/main/java/ranker/core/evaluation/LeaveOneOut.java

@@ -1,9 +1,9 @@
-package rankerEvaluation;
+package ranker.core.evaluation;
 
 import java.util.ArrayList;
 import java.util.List;
 
-import ranker.algorithms.Ranker;
+import ranker.core.algorithms.Ranker;
 import weka.core.Attribute;
 import weka.core.Instance;
 import weka.core.Instances;

### 2018-02-04 ranker/src/main/java/ranker/core/evaluation/PerformanceOrder.java

@@ -1,4 +1,4 @@
-package rankerEvaluation;
+package ranker.core.evaluation;
 
 public enum PerformanceOrder {
 	ASCENDING,DESCENDING;

### 2018-02-04 ranker/src/main/java/ranker/core/evaluation/RankerEstimationProcedure.java

@@ -1,12 +1,12 @@
-package rankerEvaluation;
+package ranker.core.evaluation;
 
 import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 
-import ranker.algorithms.PerfectRanker;
-import ranker.algorithms.Ranker;
+import ranker.core.algorithms.PerfectRanker;
+import ranker.core.algorithms.Ranker;
 import weka.classifiers.Classifier;
 import weka.core.Instance;
 import weka.core.Instances;

### 2018-02-04 ranker/src/main/java/ranker/core/evaluation/RootMeanSquaredError.java

@@ -1,4 +1,4 @@
-package rankerEvaluation;
+package ranker.core.evaluation;
 
 import java.util.List;
 
@@ -8,7 +8,7 @@ import weka.classifiers.Classifier;
  * Calculated the difference between the predicted performance value of the
  * learning algorithm and its actual value and thus fives information about how
  * well the Ranker has learned this model. Rankers evaluated with this class
- * need to be sub types of {@link ranker.algorithms.RegressionRanker}.
+ * need to be sub types of {@link ranker.core.algorithms.RegressionRanker}.
  * 
  * @author Helena Graf
  *

### 2018-02-04 ranker/src/main/java/ranker/core/metafeatures/DefaultAccuracy.java

@@ -1,4 +1,4 @@
-package openMLUtil;
+package ranker.core.metafeatures;
 
 import java.util.HashMap;
 import java.util.Map;

### 2018-02-04 ranker/src/main/java/ranker/core/metafeatures/GlobalCharacterizer.java

@@ -1,10 +1,13 @@
-package openMLUtil;
+package ranker.core.metafeatures;
 
 import java.util.ArrayList;
 import java.util.Arrays;
+import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 import java.util.TreeMap;
+
+import org.apache.commons.lang.time.StopWatch;
 
 import org.openml.webapplication.fantail.dc.Characterizer;
 import org.openml.webapplication.fantail.dc.landmarking.GenericLandmarker;
@@ -30,6 +33,8 @@ public class GlobalCharacterizer extends Characterizer {
 	private final String cpNB = "weka.classifiers.bayes.NaiveBayes";
 	private final String cpASC = "weka.classifiers.meta.AttributeSelectedClassifier";
 	private final String cpDS = "weka.classifiers.trees.DecisionStump";
+
+	private Map<String, Double> computationTimes = new HashMap<String, Double>();
 
 	public GlobalCharacterizer() throws Exception {
 		Characterizer[] characterizers = { new SimpleMetaFeatures(), // done before, but necessary for streams
@@ -85,16 +90,34 @@ public class GlobalCharacterizer extends Characterizer {
 		TreeMap<String, Double> metaFeatures = new TreeMap<String, Double>();
 		batchCharacterizers.forEach(characterizer -> {
 			 try {
+				 StopWatch watch = new StopWatch();
+				 watch.start();
 				 metaFeatures.putAll(characterizer.characterize(instances));
+				 watch.stop();
+				 computationTimes.put(characterizer.toString(), (double) watch.getTime());
 			 } catch (Exception e) {
+				 // Put NaN as result and computation time
 				 for (String metaFeature : characterizer.getIDs()) {
 					 metaFeatures.put(metaFeature, Double.NaN);
 				 }
+				 computationTimes.put(characterizer.toString(), Double.NaN);
 			 }
 		});
 		return metaFeatures;
 	}
 
+	public Map<String,Double> getMetaFeatureComputationTimes () {
+		return computationTimes;
+	}
+	
+	public List<String> getCharacterizerNames() {
+		List<String> result = new ArrayList<String>();
+		for (Characterizer chara : batchCharacterizers) {
+			result.add(chara.toString());
+		}
+		return result;
+	}
+
 }
 
-//TODO credit !
+// TODO credit !

### 2018-02-04 ranker/src/main/java/ranker/core/metafeatures/MetaFeatureHelper.java

@@ -1,0 +1,221 @@
+package ranker.core.metafeatures;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.IOException;
+import java.nio.file.FileSystems;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.stream.Stream;
+
+import org.openml.apiconnector.io.OpenmlConnector;
+
+import ranker.Util;
+import ranker.core.evaluation.EvaluationHelper;
+import ranker.util.openMLUtil.OpenMLHelper;
+import weka.core.Attribute;
+import weka.core.DenseInstance;
+import weka.core.Instance;
+import weka.core.Instances;
+
+public class MetaFeatureHelper {
+
+	/**
+	 * Computes all global meta features for all data sets in the given list. Adds a
+	 * feature for the data set id.
+	 * 
+	 * @param dataSetIds
+	 * @return
+	 * @throws Exception
+	 */
+	public static Instances computeMetaFeatures(List<Integer> dataSetIds) throws Exception {
+	
+		// Prepare List of Attributes for Instances
+		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
+	
+		// Qualities
+		GlobalCharacterizer characterizer = new GlobalCharacterizer();
+		String[] allDataQualities = characterizer.getIDs();
+		Map<String, Integer> qualityIndices = new HashMap<String, Integer>();
+		for (int i = 0; i < allDataQualities.length; i++) {
+			String dataQuality = allDataQualities[i];
+			qualityIndices.put(dataQuality, i);
+			attributes.add(new Attribute(dataQuality));
+		}
+	
+		// TODO isolate in class + clean up
+		HashMap<String, List<Double>> computationTimes = new HashMap<String, List<Double>>();
+		for (String chara : characterizer.getCharacterizerNames()) {
+			computationTimes.put(chara, new ArrayList<Double>());
+		}
+	
+		// Classifiers
+		Map<String, Integer> classifierIndices = new HashMap<String, Integer>();
+		for (int i = 0; i < EvaluationHelper.portfolio.length; i++) {
+			String classifierName = EvaluationHelper.portfolio[i].getClass().getName();
+			classifierIndices.put(classifierName, allDataQualities.length + i);
+			attributes.add(new Attribute(classifierName));
+		}
+	
+		// Prepare instances
[…]

### 2018-02-06 Writing/Thesis/content/chapter-approach.tex

@@
 
-\section{System Section 1}
-\label{sec:approach:sec1}
+Approach of ranking classifier implementations here realized by two concepts, regression-based and preference-based ranking, which will be explained in detail.
+Also predicting predictive accuracy here.
+Thus target function of the form $meta features^n \rightarrow classifiers^m$.
+
+% Theory of approach
+Since the aim is to generate a ranking of classification algorithms, first, performance values of a number of classifiers are recorded on a few data sets.
+Then, meta features are computed for each data set.
+This is for training the ranking model.
+A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently uing it to query the underlying model.
+
+EXAMPLE TABLE ALL DATA
+
+% How is the regression ranking done
+One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models.
+The idea is to use separate regression models to predict a performance value for each classifier, and to then derive an ordering from these predictions.
+This is done by splitting the data set compiled beforehand into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier.
+The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus a regression model can be trained on each of them.
+A regression model therefore tries to learn the target function $meta features \rightarrow classifier performance value$ for its respective classifier.
+Hence for a query instance, after computing the meta features, these are fed into each regression model.
+In a second step, the classifiers are ordered according to the predictions made by the models.
+
+EXAMPLE TABLE DERIVED DATA SETS and METAFEATURES -> PREDICTIONS -> COMBINED -> ORDERING
+
+% How is the preference ranking done
+The second ranking possibility considered here is using preference learning to predict a ranking.
+Each instance of the data set generated beforehand contains meta feature information for the considered data sets and performance values of classifiers This implies that the preference learning task at hand is label ranking.
+
+EXAMPLE TABLE CONVERTED INFORMATION
 

### 2018-02-06 Writing/Thesis/content/chapter-conclusion.tex

@@
-% !TEX root = ../my-thesis.tex
-%
+% Move from specific to general
+% Use existing literature for confirmation, contradiction, comparison
+% "Speak to introduction"
 \chapter{Conclusion}
@@
 
+% Introductory restatement of research problems, aims / reseach question -> remin of problem + purpose and how addressed
+
+% Summary of findings and limitations: what has been covered
+
+% Practical applications / limitations: assess value / relevance / implications
+
+% Recommendations for future work: this may not need to be a section on its own!
 \section{Future Work}
 \label{sec:conclusion:future}
+
+- deeper analysis of meta features, e.g. add some, remove some, consider trade-off time accuracy
+- better fitting of learning algorithms to meta data (more manual work, but of course consider danger of overfitting!
+- compare against other tools that rank r.g. the Jan van Rijn one
+- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)
+- hyperparameters neglected here, may include standard combinations in future work (or random ones)-> possible only if id by string
+- use this for regression
+- use this to try to predict other measures (e.g. time needed)

### 2018-02-06 ranker/src/main/java/ranker/Main.java
clean up

@@ -11,12 +11,23 @@ import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.List;
 
+import ranker.core.algorithms.BestAlgorithmRanker;
+import ranker.core.algorithms.InstanceBasedLabelRankingRanker;
+import ranker.core.algorithms.PairwiseComparisonRanker;
+import ranker.core.algorithms.PerfectRanker;
 import ranker.core.algorithms.RandomForestRanker;
+import ranker.core.algorithms.Ranker;
 import ranker.core.algorithms.RegressionRanker;
+import ranker.core.evaluation.EvaluationHelper;
 import ranker.core.evaluation.KendallRankCorrelation;
 import ranker.core.evaluation.LeaveOneOut;
 import ranker.core.evaluation.Loss;
 import ranker.core.evaluation.RankerEvaluationMeasure;
+import ranker.core.metafeatures.GlobalCharacterizer;
+import ranker.core.metafeatures.MetaFeatureHelper;
+import ranker.util.openMLUtil.OpenMLHelper;
+import ranker.util.wekaUtil.WekaHelper;
+import weka.classifiers.Classifier;
 import weka.classifiers.trees.RandomForest;
 import weka.core.Attribute;
 import weka.core.Instance;
@@ -27,9 +38,9 @@ public class Main {
 
 	public static void main(String[] args) throws Exception {
 
-//		List<Integer> datasets = Util.getDataSetsFromIndex();
+//		List<Integer> datasets = OpenMLHelper.getDataSetsFromIndex();
 //		// List<Integer> datasets = Arrays.asList(3,4,5);
-//		Instances instances1 = Util.computeMetaFeatures(datasets);
+//		Instances instances1 = MetaFeatureHelper.computeMetaFeatures(datasets);
 //		ArffSaver saver = new ArffSaver();
 //		saver.setInstances(instances1);
 //		try {
@@ -93,27 +104,22 @@ public class Main {
 		// writer.flush();
 		// writer.close();
 
-//		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("meta_computed.arff"),
-//				Util.charset);
-//
-//		Instances instances = new Instances(reader);
-//		List<Instance> test = instances.subList(1,100);
-//		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
-//		for (int attribute = 0; attribute < instances.numAttributes(); attribute++) {
-//			attributes.add(instances.attribute(attribute));
[…]

### 2018-02-06 ranker/src/main/java/ranker/Rankprediction.java

@@ -1,0 +1,46 @@
+package ranker;
+
+import java.util.List;
+import java.util.Map;
+
+import org.openml.webapplication.fantail.dc.Characterizer;
+
+import ranker.core.algorithms.Ranker;
+import weka.classifiers.Classifier;
+import weka.core.DenseInstance;
+import weka.core.Instance;
+import weka.core.Instances;
+
+public class Rankprediction {
+	
+	protected Instances metaData;
+	protected List<Integer> targetAttributes;
+	protected Characterizer characterizer;
+	protected Ranker ranker;
+	
+	public Rankprediction(Instances metaData, List<Integer> targetAttributes, Characterizer characterizer, Ranker ranker) throws Exception {
+		this.metaData = metaData;
+		this.targetAttributes = targetAttributes;
+		this.characterizer = characterizer;
+		this.ranker = ranker;
+		
+		ranker.buildRanker(metaData, targetAttributes);
+	}
+	
+	public List<Classifier> predictRanking (Instances instances) throws Exception {
+		// Get meta features for instance
+		Map<String,Double> metaFeatures = characterizer.characterize(instances);
+		
+		// Insert in the right order in instance
+		Instance queryInstance = new DenseInstance(metaData.numAttributes());
+		for (int i = 0; i < metaData.numAttributes(); i++) {
+			if (!targetAttributes.contains(i)) {
+				queryInstance.setValue(i, metaFeatures.get(metaData.attribute(i).name()));
+			}
+		}
+		
+		// Predict a ranking
+		return ranker.predictRankingforInstance(queryInstance);
+	}
+
+}

### 2018-02-06 ranker/src/main/java/ranker/core/algorithms/BestAlgorithmRanker.java

@@ -32,7 +32,7 @@ public class BestAlgorithmRanker extends PreferenceRanker {
 		List<Classifier> remaining = new ArrayList<Classifier>();
 		classifiersMap.values().forEach(classifier -> remaining.add(classifier));
 
-		// Find ranking
+		// Find #Classifiers many times the best classifier
 		for (int i = 0; i < targetAttributes.size(); i++) {
 			// Scores count how many times an algorithm is ranked first
 			HashMap<Classifier, Integer> scores = new HashMap<Classifier, Integer>();
@@ -43,13 +43,20 @@ public class BestAlgorithmRanker extends PreferenceRanker {
 				// Get ranking for instance
 				List<Classifier> ranking = oracle.predictRankingforInstance(data.get(j));
 
-				// Find first
+				// Find first (which algorithm is the first one in the ranking)
 				for (int k = 0; k < ranking.size(); k++) {
+					// First cannot be one that is already better
 					if (!bestRanking.contains(ranking.get(k))) {
 						// Increment score
-						int previousScore = scores.get(ranking.get(k));
-						int newScore = previousScore++;
-						scores.put(ranking.get(k), newScore);
+						for (Classifier cl : scores.keySet()) {
+							if (ranking.get(k).getClass().getName().equals(cl.getClass().getName())) {
+								int previousScore = scores.get(cl);
+								int newScore = previousScore++;
+								scores.put(ranking.get(k), newScore);
+								break;
+							}
+						}
+						// After found the first one, can stop
 						break;
 					}
 				}

### 2018-02-06 ranker/src/main/java/ranker/core/algorithms/InstanceBasedLabelRankingRanker.java

@@ -1,7 +1,16 @@
 package ranker.core.algorithms;
 
+import de.upb.cs.is.jpl.api.algorithm.baselearner.IBaselearnerAlgorithm;
+import de.upb.cs.is.jpl.api.algorithm.baselearner.classification.knearestneighbor.KNearestNeighborConfiguration;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingConfiguration;
 import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.bordacount.BordaCountConfiguration;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.bordacount.BordaCountLearningAlgorithm;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.kemenyyoung.KemenyYoungLearningAlgorithm;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.plackettluce.PlackettLuceConfiguration;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.plackettluce.PlackettLuceLearningAlgorithm;
 import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
+import de.upb.cs.is.jpl.api.math.RandomGenerator;
 
 /**
  * A ranker that uses an instance based label ranking learning algorithm to predict rankings.
@@ -13,8 +22,13 @@ public class InstanceBasedLabelRankingRanker extends PreferenceRanker {
 
 	@Override
 	protected void initialize() throws Exception {
+		RandomGenerator.initializeRNG(1234);
 		LabelRankingDataset dataset = convertToLabelRankingDataSet(data);
 		InstanceBasedLabelRankingLearningAlgorithm learningAlgorithm = new InstanceBasedLabelRankingLearningAlgorithm();
+		InstanceBasedLabelRankingConfiguration config = learningAlgorithm.getAlgorithmConfiguration();
+		config.setRankAggregationAlgorithm(new KemenyYoungLearningAlgorithm());
[…]

### 2018-02-06 ranker/src/main/java/ranker/core/algorithms/PairwiseComparisonRanker.java

@@ -1,7 +1,10 @@
 package ranker.core.algorithms;
 
+import de.upb.cs.is.jpl.api.algorithm.baselearner.regression.linear.LinearRegression;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.labelrankingbypairwisecomparison.LabelRankingByPairwiseComparisonConfiguration;
 import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.labelrankingbypairwisecomparison.LabelRankingByPairwiseComparisonLearningAlgorithm;
 import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
+import de.upb.cs.is.jpl.api.math.RandomGenerator;
 
 /**
  * A ranker that uses label ranking by pairwise comparison to predict rankings.
@@ -13,8 +16,11 @@ public class PairwiseComparisonRanker extends PreferenceRanker {
 
 	@Override
 	protected void initialize() throws Exception {
+		RandomGenerator.initializeRNG(1234);
 		LabelRankingDataset dataset = convertToLabelRankingDataSet(data);
 		LabelRankingByPairwiseComparisonLearningAlgorithm learningAlgorithm = new LabelRankingByPairwiseComparisonLearningAlgorithm();
+		LabelRankingByPairwiseComparisonConfiguration config = learningAlgorithm.getAlgorithmConfiguration();
+		//config.setBaseLearnerAlgorithm(new LinearRegression());
 		learningModel = learningAlgorithm.train(dataset);
 	}
 

### 2018-02-06 ranker/src/main/java/ranker/core/algorithms/REPTreeRanker.java

@@ -1,0 +1,15 @@
+package ranker.core.algorithms;
+import java.util.Map;
+
+import weka.classifiers.Classifier;
+import weka.core.Instances;
+
+public class REPTreeRanker extends RegressionRanker {
+
+	@Override
+	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
+		// TODO Auto-generated method stub
+		
+	}
+
+}

### 2018-02-06 ranker/src/main/java/ranker/core/algorithms/RandomForestRanker.java

@@ -24,5 +24,4 @@ public class RandomForestRanker extends RegressionRanker {
 			regressionModels.put(classifier, forest);
 		}
 	}
-
 }

### 2018-02-06 ranker/src/main/java/ranker/core/evaluation/EvaluationHelper.java

@@ -54,7 +54,7 @@ import weka.core.Instances;
 import weka.core.converters.ArffSaver;
 
 public class EvaluationHelper {
-	
+
 	/**
 	 * Path for saving the generated jobs
 	 */
@@ -79,7 +79,7 @@ public class EvaluationHelper {
 		RankerEstimationProcedure estim = new LeaveOneOut();
 		List<RankerEvaluationMeasure> measures = new ArrayList<RankerEvaluationMeasure>();
 		measures.add(new KendallRankCorrelation());
-		measures.add(new RootMeanSquaredError());
+		// measures.add(new RootMeanSquaredError());
 		Loss loss = new Loss();
 		loss.setPerformanceOrder(PerformanceOrder.ASCENDING);
 		measures.add(loss);
@@ -117,7 +117,7 @@ public class EvaluationHelper {
 	public static void generateJobs() throws IOException {
 		BufferedReader reader = Files.newBufferedReader(Util.dataSetIndexPath, Util.charset);
 		BufferedWriter writer = Files.newBufferedWriter(EvaluationHelper.jobsPath, Util.charset);
-	
+
 		String line = null;
 		while ((line = reader.readLine()) != null) {
 			for (Classifier classifier : EvaluationHelper.portfolio) {
@@ -128,7 +128,7 @@ public class EvaluationHelper {
 		reader.close();
 		writer.close();
 	}
-	
+
 	/**
 	 * Executes the given jobs which must have been generated before.
 	 * 
@@ -175,7 +175,8 @@ public class EvaluationHelper {
 	}
 
 	/**
-	 * Evaluates all classifiers on all data sets and saves results in a new data set (Features = Classifiers, Instances = data sets).
+	 * Evaluates all classifiers on all data sets and saves results in a new data
+	 * set (Features = Classifiers, Instances = data sets).
 	 * 
 	 * @param classifiers
 	 * @param datasets
@@ -185,8 +186,8 @@ public class EvaluationHelper {
 	 */
 	public static void generatePerformanceMeasures(List<Classifier> classifiers, List<Instances> datasets,
 			EvaluationMeasure evalM, EstimationProcedure estimProc, String filepath) {
-		//TODO add data set id
-	
+		// TODO add data set id
+
 		// Prepare table of results
 		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
 		for (int i = 0; i < datasets.size(); i++) {
[…]

### 2018-02-06 ranker/src/main/java/ranker/core/metafeatures/DefaultAccuracy.java

@@ -1,39 +1,0 @@
-package ranker.core.metafeatures;
-
-import java.util.HashMap;
-import java.util.Map;
-
-import org.openml.webapplication.fantail.dc.Characterizer;
-
-import weka.classifiers.Classifier;
-import weka.classifiers.Evaluation;
-import weka.classifiers.rules.ZeroR;
-import weka.core.Instances;
-
-public class DefaultAccuracy extends Characterizer {
-	
-	private String[] ids = {"DefaultAccuracy"};
-
-	@Override
-	public String[] getIDs() {
-		return ids;
-	}
-
-	@Override
-	public Map<String, Double> characterize(Instances instances) {
-		Classifier classifier = new ZeroR();
-		double result;
-		try {
-			classifier.buildClassifier(instances);
-			Evaluation eval = new Evaluation(instances);
-			eval.evaluateModel(classifier, instances);
-			result = eval.pctCorrect();
-		} catch (Exception e) {
-			result = 0;
-		}
-		HashMap<String,Double> results = new HashMap<String,Double>();
-		results.put(ids[0], result);
-		return results;
-	}
-
-}

### 2018-02-06 ranker/src/main/java/ranker/core/metafeatures/GlobalCharacterizer.java

@@ -65,7 +65,6 @@ public class GlobalCharacterizer extends Characterizer {
 					randomtreeOption));
 		}
 		batchCharacterizers.add(new Cardinality());
-		batchCharacterizers.add(new DefaultAccuracy());
 
 		List<String> metaFeatures = new ArrayList<String>();
 		for (Characterizer characterizer : batchCharacterizers) {

### 2018-02-06 ranker/src/main/java/ranker/core/metafeatures/MetaFeatureHelper.java

@@ -36,6 +36,9 @@ public class MetaFeatureHelper {
 	
 		// Prepare List of Attributes for Instances
 		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
+		
+		// Add the data set Id as an attribute
+		attributes.add(new Attribute("OpenML Data Set ID"));
 	
 		// Qualities
 		GlobalCharacterizer characterizer = new GlobalCharacterizer();
@@ -43,7 +46,7 @@ public class MetaFeatureHelper {
 		Map<String, Integer> qualityIndices = new HashMap<String, Integer>();
 		for (int i = 0; i < allDataQualities.length; i++) {
 			String dataQuality = allDataQualities[i];
-			qualityIndices.put(dataQuality, i);
+			qualityIndices.put(dataQuality, i+1);
 			attributes.add(new Attribute(dataQuality));
 		}
 	
@@ -57,17 +60,20 @@ public class MetaFeatureHelper {
 		Map<String, Integer> classifierIndices = new HashMap<String, Integer>();
 		for (int i = 0; i < EvaluationHelper.portfolio.length; i++) {
 			String classifierName = EvaluationHelper.portfolio[i].getClass().getName();
-			classifierIndices.put(classifierName, allDataQualities.length + i);
+			classifierIndices.put(classifierName, allDataQualities.length + 1 + i);
 			attributes.add(new Attribute(classifierName));
 		}
 	
 		// Prepare instances
-		Instances instances = new Instances("MetaDataOpenML_calculated_timed", attributes, 0);
+		Instances instances = new Instances("metaData_small_allPerformanceValues", attributes, 0);
 		HashMap<Integer, Instance> metaFeaturesForDataSets = new HashMap<Integer, Instance>();
 	
 		// Add meta features
 		for (int dataSetId : dataSetIds) {
 			Instance instance = new DenseInstance(attributes.size());
+			// Add data set id
+			instance.setValue(0, dataSetId);
+			
 			Instances openMLData = null;
 			try {
 				openMLData = OpenMLHelper.getInstancesById(dataSetId);
@@ -107,10 +113,12 @@ public class MetaFeatureHelper {
 						String classifierName = parts[0];
 						int dataSetId = Integer.parseInt(parts[1]);
 						if (dataSetIds.contains(dataSetId)) {
-							Instance instance = metaFeaturesForDataSets.get(dataSetId);
-							int attIndex = classifierIndices.get(classifierName);
-							double value = Double.parseDouble(line);
[…]

### 2018-02-06 ranker/src/main/java/ranker/util/wekaUtil/WekaHelper.java

@@ -1,5 +1,9 @@
 package ranker.util.wekaUtil;
 
+import java.util.ArrayList;
+import java.util.List;
+
+import weka.core.Attribute;
 import weka.core.Instance;
 import weka.core.Instances;
 import weka.filters.unsupervised.attribute.ReplaceMissingValues;
@@ -30,5 +34,16 @@ public class WekaHelper {
 			newData.add(processed);
 		}
 		return newData;
+	}
+	
+	public static Instances subSet(Instances instances, int fromIndex, int toIndex) {
+		List<Instance> test = instances.subList(fromIndex, toIndex);
+		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
+		for (int attribute = 0; attribute < instances.numAttributes(); attribute++) {
+			attributes.add(instances.attribute(attribute));
+		}
+		Instances testInst = new Instances(instances.relationName(), attributes, 0);
+		test.forEach(instance -> testInst.add(instance));
+		return testInst;
 	}
 }

### 2018-02-06 ranker/src/test/java/rankerTest/RankPredictionTest.java

@@ -1,0 +1,52 @@
+package rankerTest;
+
+import static org.junit.Assert.fail;
+
+import java.io.BufferedReader;
+import java.nio.file.FileSystems;
+import java.nio.file.Files;
+import java.util.ArrayList;
+import java.util.List;
+
+import org.junit.BeforeClass;
+import org.junit.Test;
+import org.openml.webapplication.fantail.dc.Characterizer;
+
+import ranker.Rankprediction;
+import ranker.Util;
+import ranker.core.algorithms.PerfectRanker;
+import ranker.core.algorithms.Ranker;
+import ranker.core.metafeatures.GlobalCharacterizer;
+import weka.core.Instances;
+
+public class RankPredictionTest {
+	
+	static Instances testInstances;
+	static List<Integer> targetAttributes;
+	static Characterizer characterizer;
+	static Ranker ranker;
+
+	@BeforeClass
+	public static void loadMetaData() throws Exception {
+		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("meta_computed.arff"),
+				Util.charset);
+		testInstances = new Instances(reader);
+		targetAttributes = new ArrayList<Integer>();
+		for (int i = 104; i < 131; i++) {
+			targetAttributes.add(i);
+		}
+		characterizer = new GlobalCharacterizer();
+		ranker = new PerfectRanker();
+	}
+
+	@Test
+	public void testCreation() {
+		try {
+			@SuppressWarnings("unused")
+			Rankprediction rankprediction = new Rankprediction(testInstances,targetAttributes,new GlobalCharacterizer(),ranker);
+		} catch (Exception e) {
+			e.printStackTrace();
+			fail("Could not generate a RankPrediction Object");
+		}
+	}
+}

### 2018-02-06 ranker/src/main/java/ranker/Main.java
Added timing of building rankers and CSV exports

@@ -104,18 +104,18 @@ public class Main {
 		// writer.flush();
 		// writer.close();
 
-		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues_noID.arff"),
+		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues.arff"),
 				Util.charset);
 
 		Instances instances = new Instances(reader);
 		Ranker ranker = new RandomForestRanker();
 		
 		List<Integer> targetAttributes = new ArrayList<Integer>();
-		for (int i = 104; i < 125; i++) {
+		for (int i = 104; i < 126; i++) {
 			targetAttributes.add(i);
 		}
 		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, WekaHelper.subSet(instances, 1, 50), targetAttributes));
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, WekaHelper.subSet(instances, 1, 4), targetAttributes));
 		//System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
 //		
 //		Rankprediction rankprediction = new Rankprediction(instances,targetAttributes,new GlobalCharacterizer(),ranker);

### 2018-02-06 ranker/src/main/java/ranker/Util.java

@@ -15,5 +15,6 @@ public class Util {
 	public static Path dataSetIndexPath = FileSystems.getDefault().getPath("datasets_100_1000");
 	public static Path resultsPath = FileSystems.getDefault().getPath("data");
 	public static Path cacheDirectory = FileSystems.getDefault().getPath("data");
-	
+	public static final String RANKER_BUILD_TIMES = "RankerBuildTimes";
+	public static final String DATA_ID = "DataId";
 }

### 2018-02-06 ranker/src/main/java/ranker/core/evaluation/LeaveOneOut.java

@@ -1,8 +1,19 @@
 package ranker.core.evaluation;
 
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.nio.file.FileSystems;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
 import java.util.ArrayList;
+import java.util.HashSet;
 import java.util.List;
+import java.util.Set;
 
+import ranker.Util;
 import ranker.core.algorithms.Ranker;
 import weka.core.Attribute;
 import weka.core.Instance;
@@ -19,32 +30,42 @@ import weka.core.Instances;
  */
 public class LeaveOneOut extends RankerEstimationProcedure {
 
+	private static final String CSV_SEPERATOR ="; ";
+	
 	@Override
 	public List<Double> estimate(Ranker ranker, List<RankerEvaluationMeasure> measures, Instances data,
 			List<Integer> targetAttributes) throws Exception {
 		// Initialize variables
 		for (RankerEvaluationMeasure measure : measures) {
-			detailedEvaluationResults.put(measure, new ArrayList<Double>());
+			detailedEvaluationResults.put(measure.getClass().getSimpleName(), new ArrayList<Double>());
 		}
+		detailedEvaluationResults.put(Util.DATA_ID, new ArrayList<>());
+		detailedEvaluationResults.put(Util.RANKER_BUILD_TIMES, new ArrayList<>());
 		
 		// Evaluate all instances separately
 		for (int i = 0; i < data.numInstances(); i++) {
 			Instances train = new Instances(data);
-			Instance remove = train.remove(i);
+			Instance instanceToTest = train.remove(i);
 			ArrayList<Attribute> attributes = new ArrayList<Attribute>();
-			for (int attribute = 0; attribute < data.numAttributes(); attribute++) {
-				attributes.add(data.attribute(attribute));
+			for (int j = 0; j < data.numAttributes(); j++) {
+				attributes.add(data.attribute(j));
 			}
 			Instances test = new Instances("Test", attributes, 0);
-			test.add(remove);
-
-			evaluateChunk(ranker, train, test, measures, targetAttributes);
+			test.add(instanceToTest);
+			detailedEvaluationResults.get(Util.DATA_ID).add((double) instanceToTest.value(0));
+			//remove DataIds, we do not want them as values for testing
[…]

### 2018-02-06 ranker/src/main/java/ranker/Main.java
add experiments

@@ -64,22 +64,22 @@ public class Main {
 		// ranker.predictRankingforInstance(instances.get(388));
 		// System.out.println(ranker.getEstimatesForRanking());
 
-		// ArrayList<Integer> dataIds = new ArrayList<Integer>();
-		// BufferedReader reader =
-		// Files.newBufferedReader(FileSystems.getDefault().getPath("datasets_100_1000"));
-		// String line = null;
-		// while ((line=reader.readLine())!=null) {
-		// dataIds.add(Integer.parseInt(line));
-		// }
-		// Instances results = Util.computeMetaFeatures(dataIds);
-		// ArffSaver saver = new ArffSaver();
-		// saver.setInstances(results);
-		// try {
-		// saver.setFile(new File("meta_computed.arff"));
-		// saver.writeBatch();
-		// } catch (IOException e) {
-		// e.printStackTrace();
-		// }
+		 ArrayList<Integer> dataIds = new ArrayList<Integer>();
+		 BufferedReader reader =
+		 Files.newBufferedReader(FileSystems.getDefault().getPath("datasets.txt"));
+		 String line = null;
+		 while ((line=reader.readLine())!=null) {
+		 dataIds.add(Integer.parseInt(line));
+		 }
+		 Instances results = MetaFeatureHelper.computeMetaFeatures(dataIds);
+		 ArffSaver saver = new ArffSaver();
+		 saver.setInstances(results);
+		 try {
+		 saver.setFile(new File("meta_computed.arff"));
+		 saver.writeBatch();
+		 } catch (IOException e) {
+		 e.printStackTrace();
+		 }
 
 		// Trying to save a .csv
 //		 Path path = FileSystems.getDefault().getPath("datatest.csv");
@@ -104,22 +104,31 @@ public class Main {
 		// writer.flush();
 		// writer.close();
 
-		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues_noID.arff"),
-				Util.charset);
-
-		Instances instances = new Instances(reader);
-		Ranker ranker = new RandomForestRanker();
-		
-		List<Integer> targetAttributes = new ArrayList<Integer>();
-		for (int i = 104; i < 125; i++) {
-			targetAttributes.add(i);
-		}
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, WekaHelper.subSet(instances, 1, 50), targetAttributes));
[…]

### 2018-02-06 ranker/src/main/java/ranker/Main.java
more Evaluation

@@ -12,9 +12,14 @@ import java.util.Arrays;
 import java.util.List;
 
 import ranker.core.algorithms.BestAlgorithmRanker;
+import ranker.core.algorithms.InstanceBasedLabelRankingKemenyYoung;
+import ranker.core.algorithms.InstanceBasedLabelRankingKemenyYoungSQRTN;
 import ranker.core.algorithms.InstanceBasedLabelRankingRanker;
+import ranker.core.algorithms.LinearRegressionRanker;
+import ranker.core.algorithms.M5PRanker;
 import ranker.core.algorithms.PairwiseComparisonRanker;
 import ranker.core.algorithms.PerfectRanker;
+import ranker.core.algorithms.REPTreeRanker;
 import ranker.core.algorithms.RandomForestRanker;
 import ranker.core.algorithms.Ranker;
 import ranker.core.algorithms.RegressionRanker;
@@ -128,14 +133,48 @@ public class Main {
 				Util.charset);
 
 		Instances instances = new Instances(reader);
-		Ranker ranker = new RandomForestRanker();
 		
 		List<Integer> targetAttributes = new ArrayList<Integer>();
 		for (int i = 104; i < 126; i++) {
 			targetAttributes.add(i);
 		}
 		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, WekaHelper.subSet(instances, 1, 4), targetAttributes));
+		Ranker ranker = new RandomForestRanker();
+		
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		
+		ranker = new M5PRanker();
+		
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		
+		ranker = new REPTreeRanker();
+		
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		
+		ranker = new LinearRegressionRanker();
+		
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		
+		ranker = new BestAlgorithmRanker();
+		
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		
+		ranker = new InstanceBasedLabelRankingRanker();
+		
+		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		
+		ranker = new InstanceBasedLabelRankingKemenyYoung();
[…]

### 2018-02-06 ranker/src/main/java/ranker/core/evaluation/EvaluationHelper.java

@@ -74,14 +74,26 @@ public class EvaluationHelper {
 	 */
 	public static List<Double> evaluateRanker(Ranker ranker, Instances instances, List<Integer> targetAttributes)
 			throws Exception {
-		// RegressionRanker ranker = new RegressionRanker();
-		// ranker.buildRanker(instances);
-		// ranker.predictRankingforInstance(instances.get(0)).forEach(action->System.out.println(action.getClass().getName()));
-		// TODO cases RegressionRanker: include RMSE
 		RankerEstimationProcedure estim = new LeaveOneOut();
 		List<RankerEvaluationMeasure> measures = new ArrayList<RankerEvaluationMeasure>();
 		measures.add(new KendallRankCorrelation());
-		// measures.add(new RootMeanSquaredError());
+		Loss loss = new Loss();
+		loss.setPerformanceOrder(PerformanceOrder.ASCENDING);
+		measures.add(loss);
+		BestThreeLoss bestLoss = new BestThreeLoss();
+		bestLoss.setPerformanceOrder(PerformanceOrder.ASCENDING);
+		measures.add(bestLoss);
+		List<Double> result = estim.estimate(ranker, measures, instances, targetAttributes);
+		System.out.println(estim.getDetailedEvaluationResults());
+		return result;
+	}
+	
+	public static List<Double> evaluateRegressionRanker(Ranker ranker, Instances instances, List<Integer> targetAttributes)
+			throws Exception {
+		RankerEstimationProcedure estim = new LeaveOneOut();
+		List<RankerEvaluationMeasure> measures = new ArrayList<RankerEvaluationMeasure>();
+		measures.add(new KendallRankCorrelation());
+		measures.add(new RootMeanSquaredError());
 		Loss loss = new Loss();
 		loss.setPerformanceOrder(PerformanceOrder.ASCENDING);
 		measures.add(loss);

### 2018-02-06 Writing/Thesis/content/chapter-approach.tex
more writing

@@
 This is for training the ranking model.
+This generates a table that contains all necessary informatino for training both types of rankers.
 A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently uing it to query the underlying model.
 
-EXAMPLE TABLE ALL DATA
+\begin{table}[h]
+\centering
+	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
+		%\hline
+		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
+		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ \hline
+		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ \hline
+		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ \hline
+		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
+	\end{tabularx}
+	\label{tab:table1}
+	\caption{This is a caption text.}
+\end{table}
 
@@
 The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus a regression model can be trained on each of them.
-A regression model therefore tries to learn the target function $meta features \rightarrow classifier performance value$ for its respective classifier.
-Hence for a query instance, after computing the meta features, these are fed into each regression model.
-In a second step, the classifiers are ordered according to the predictions made by the models.
+All regression models therefore try to learn the target function $meta features \rightarrow classifier performance value$ for their respective classifier.
+Hence for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
+In a second step, the classifiers are ordered according to the predictions.
 
-EXAMPLE TABLE DERIVED DATA SETS and METAFEATURES -> PREDICTIONS -> COMBINED -> ORDERING
+\begin{table}[h]
+\centering
+	\begin{tabularx}{\textwidth}{X | X | X | X}
+		%\hline
+		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
+		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ \hline
+		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ \hline
+		...				& ...	& ...				& ...					\\ \hline
+		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
+		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
+		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ \hline
+		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ \hline
+		...				& ...	& ...				& ...					\\ \hline
+		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
+	\end{tabularx}
+
+\vspace{1em}
+...
+\vspace{1em}
+
+	\begin{tabularx}{\textwidth}{X | X | X | X}
+		%\hline
+		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
+		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ \hline
+		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ \hline
+		...				& ...	& ...				& ...					\\ \hline
+		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
+	\end{tabularx}
+
+	\label{tab:table1}
+	\caption{This is a caption text.}
+\end{table}
 
 % How is the preference ranking done
-The second ranking possibility considered here is using preference learning to predict a ranking.
-Each instance of the data set generated beforehand contains meta feature information for the considered data sets and performance values of classifiers This implies that the preference learning task at hand is label ranking.
+The second possibility considered in this context is using preference learning to predict a ranking.
+Each instance of the data set generated beforehand contains meta feature information for the considered data set and performance values of all classifiers.
+Similarly to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values.
+This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking.
+In this case, there exists only one label ranking mode which is fed the computed meta data for a new data set and returns an ordering of classifiers.
+Thereby it attempts to learn the mapping from meta features to an ordering of classifiers directly.
 
-EXAMPLE TABLE CONVERTED INFORMATION
-
-\begin{figure}[htb]
-	\includegraphics[width=\textwidth]{gfx/Clean-Thesis-Figure}
-	\caption{Figure example: \textit{(a)} example part one, \textit{(c)} example part two; \textit{(c)} example part three}
-	\label{fig:system:example1}
-\end{figure}
+\begin{table}[h]
+\centering
+	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
+		%\hline
+		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
+		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ \hline
+		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ \hline
+		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\ \hline
+		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
+	\end{tabularx}
+	\label{tab:table1}
+	\caption{This is a ranking}
+\end{table}

### 2018-02-06 Writing/Thesis/content/chapter-conclusion.tex
more writing

--- 2018-01-07 Writing/Thesis/content/chapter-conclusion.tex
@@
-% !TEX root = ../my-thesis.tex
-%
+% Move from specific to general
+% Use existing literature for confirmation, contradiction, comparison
+% "Speak to introduction"
 \chapter{Conclusion}
 \label{sec:conclusion}
+% Introductory restatement of research problems, aims / reseach question -> remin of problem + purpose and how addressed
+In this thesis, the problem of predicting a ranking of classification algorithms for a new data set on the basis of meta features of the data set and past performances of the algorithms has been considered.
+Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed.
+The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking, and the evaluations of both against each other, a baseline and an oracle.
 
+% Summary of findings and limitations: what has been covered
+- Results -
+
+% Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
+On the basis of the results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
+A practical application of these findings may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
+However, some additional work may have to be done in extension to this thesis in order for a sensible integration.
+
+% Recommendations for future work
 \section{Future Work}
 \label{sec:conclusion:future}
+%- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)
+
+- use this to try to predict other measures (e.g. time needed)
+- look at the loss curve + loss-time (log) curve
+- further investigate the better solution
+- integrate solution into other auto ml solution if sensible regarding time contraints for that solution (and accuracy)
+-e.g. use A3R
+- or runtime could be predicted separately by nn based on meta data \cite{DBLP:journals/corr/abs-1709-07615}
+- adding feature pre-processing
+
+% Extension of the tool
+- better fitting of learning algorithms to meta data (more manual work, but of course consider danger of overfitting!
+
+% Extended evaluation
+- compare against other tools that rank r.g. the Jan van Rijn one
+- deeper analysis of meta features, e.g. add some, remove some, consider trade-off time accuracy
+
+% Use this for predicting different algorithms
+So far, the evaluation of the tool has been confined to predicting algorithms for classification.
+Since this has been relatively successful, it could be tested whether similar predictions can also be made for other machine learning tasks like regression or clustering.
+
+- hyperparameters neglected here, may include standard combinations in future work (or random ones)-> possible only if id by string
+- use this for regression
+
+an average baseline like used in speeding up algo select might be better

### 2018-02-06 Writing/Thesis/content/chapter-fundamentals.tex
more writing

@@
 
-This chapter lays out the fundamentals for Firstly,the
+The core topic of this thesis falls under the category of machine learning. Thus, firstly the concept of machine learning and the
 
@@
 
+% Algorithm selection problem
+
 \section{Evaluation}
@@
 To evaluate the quality of the prediction that the ranker will make, a statistic is needed to compare a predicted ranking with other rankings like a baseline or an optimal ranking.
+serves as indication of causal connection
 
@@
 % In theory explanation for Kendall's Tau B because ranking could be tied but not as a result of Label Ranking and unlikely for regression the implementation that is used calculates Tau b!
+
+\subsection{Loss}
+While kendall can serve as an indication how well t works (causal connection exists in the thing trying to proove / algorithm finds it) the disadvantage is that just from the correlation it is not clear what the user gains from following the advice represented by the ranking, i.e.
+how much worse is it when trying the best three and chossing the best than actually showing the best
+
+\subsection{Root Mean Square Error}

### 2018-02-06 Writing/Thesis/content/chapter-introduction.tex
Some writing
more writing

@@
-% !TEX root = ../my-thesis.tex
-%
+% Move from general to specific
 \chapter{Introduction}
 \label{sec:intro}
-
+%TODO does this introduction really follow the three-moves structure?
+%% Introduction to introduction
 This introduction emphasizes why there is a need for automation in machine learning, and how this thesis relates to that problem.
@@
 \label{sec:intro:motivation}
+%% Context
 % Need more automated analysis of data
@@
 While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available.
-This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.
+This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and the process is not accessible enough to non-experts.
+It thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.
 
@@
 But selecting a fitting classifier for a new data set is difficult, since algorithm performances can vary substantially among data sets, and it is not feasible to simply apply a large number of them to empirically find a good match.
-For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standart hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
+For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standard hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
 The predictive accuracy of the Random Forest\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
@@
 
-% Together this means that classifier selection is area where one can automate -> area of problem is suggesting classifiers
+%% Problem + Significance
 Since there is no one best classifier for all data sets, it is likely that how well a classifier performs on a given data set is dependent on properties of the data set, at least to some degree.
@@
 
-% Therefore the goal is the development of a tool that does this
+%% Problem + Significance
+% Together this means that classifier selection is area where one can automate -> area of problem is suggesting classifiers
+Since there is a need for automated machine learning and selecting a fitting classification algorithm for a new data set is an important but difficult task in the machine learning pipeline, facilitating this process by automatically suggesting well-performing classifiers for a new data set is a significant problem.
+A tool that efficiently predicts which algorithms are likely to perform well compared to their alternatives regarding a specific data set simplifies the process of selecting an algorithm for inexperienced users and experts alike.
+A user would send a request to the tool for their specific data set at hand and then evaluate highly ranked algorithms manually, choosing the one with the best performance.
+The advantage is that the user does not need to know characteristics of the classification algorithms or data set in order to achieve relatively good results in a short amount of time.
+A further speed-up and simplification could be achieved by embedding this tool in a solution that also takes care of the sampling of selected classifiers on the data set, for example existing solutions in the context of automated machine learning (auto-ml) context.
 
-\section{Results}
-\label{sec:intro:results}
+%% Response
+% Therefore the goal is testing the this assumption if possible by using regression algos and preference learning
+Thus, the aim of this thesis is to
+
+algorithm selection problem at heart but want ranking to allow the user iterative testing
+
+could work because regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}
 
@@
 \label{sec:intro:structure}
-% These are sort of abstracts for each chapter
+%% Roadmap
+The following paragraphs give an outline of the thesis structure by providing a brief summary of each chapter.
 
-\textbf{Chapter \ref{sec:fundamentals}} \\[0.2em]
+\textbf{Chapter \ref{sec:fundamentals} - \nameref{sec:fundamentals}} \\[0.2em]
 % Begin with fundamentals to give a brief overview of the field of ML relevant to this thesis
-%TODO measures of evaluation!!! 
-Firstly, relevant preliminaries are discussed. A brief overview of tasks from the field of machine learning which are relevant to this thesis is given.
+First, some preliminaries are discussed. A brief overview of tasks from the field of machine learning which are relevant to this thesis is given, and methods used for evaluation are explained.
 
-\textbf{Chapter \ref{sec:approach}} \\[0.2em]
+\textbf{Chapter \ref{sec:approach} - \nameref{sec:approach}} \\[0.2em]
 % Continue with description of the approach to the problem described in detail
-This chapter continues by describing the approach of this thesis in tackling the problem of suggesting classifies
+The next chapter continues by describing the approach of this thesis for ranking classification algorithms. The two different proposed methods are contrasted.
 
-\textbf{Chapter \ref{sec:implementation}} \\[0.2em]
+\textbf{Chapter \ref{sec:implementation} - \nameref{sec:implementation}} \\[0.2em]
 % Go into detail of implementation
-Following the details of the approach the implementation thereof is presented.
+Following the details of the approach, the implementation thereof is presented. Used software libraries are pointed out.
 
-\textbf{Chapter \ref{sec:evaluation}} \\[0.2em]
+% How the conducted experiments have been set up and discussion of results
+\textbf{Chapter \ref{sec:evaluation} - \nameref{sec:evaluation}} \\[0.2em]
+The evaluation of the different ranking implementations is described by first clarifying the experimental setup used for the evaluation, followed by a discussion of the results.
 
-\textbf{Chapter \ref{sec:related}} \\[0.2em]
+% Visit more work
+\textbf{Chapter \ref{sec:related} - \nameref{sec:related}} \\[0.2em]
+After the approach of this thesis has been laid out in detail, the scope is extended to related work in the area of auto-ml in general and ranking of learning algorithms more specifically.
+Differences and similarities in the approaches are discussed briefly.
 
-\textbf{Chapter \ref{sec:conclusion}} \\[0.2em]
-The final chapter concludes the thesis and provides an outlook for possible future work.
+\textbf{Chapter \ref{sec:conclusion} - \nameref{sec:conclusion}} \\[0.2em]
+% Conlude + future work
+In the last chapter, the results which have been achieved are revisited with the goals in mind. Finally, an outlook for possible future work extending more eval is provided.

### 2018-02-06 Writing/Thesis/content/chapter-related-work.tex
more writing

@@
-% !TEX root = ../my-thesis.tex
-%
 \chapter{Related Work}
 \label{sec:related}
+% Of course much work in this field and cannot possibly cover all of this so confined to closely related or well-known / state of the art
+The demand for aid in the process of selecting an algorithm has already led to the development of numerous solutions that automate machine-learning (AutoML).
+In the following sections, the workings of a few such tools that are related to this work are outlined briefly, loosely organized by their scope of operation.
+Each tool's usage of meta knowledge is discussed shortly.\\
 
-The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML).
-In the following paragraphs, three of such tools are outlined briefly.\\
+\section{Predicting Rankings}
+%% Ranking
 
+% Could do ranking by using meta-knowledge (avg ranking)
+One method of ranking algorithms called average-ranking utilizes meta-knowledge to suggest a ranking for a new data set.
+The meta-knowledge here consists of recording past performances of classifiers on data sets, and computing the average rank of each classifier over all data sets.
+Performance measures used are often related to the predictive accuracy of the classifier.
+
+% Could do ranking by evaluating on the spot (active testing)
+
+% Another interesting thing is that both of these could be improved by incorporating time
+% Speeding up algorithm selection
+\cite{DBLP:journals/ml/AbdulrahmanBRV18}
+
+\section{Algorithm and Hyperparameter Selection}
+%% CASH
+Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters are tools that in addition two selecting an algorithm also optimize its hyperparameters, which has been defined as 'the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}.
+Two widely used approaches of this kind are AUTO-WEKA and AUTO-SKLEARN.
+It has to be noted that thus these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.
+
+% Auto-WEKA
 Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
-It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka} to assist the large number of novice users of the software in selecting parameterized algorithms for their problems.
+It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parameterized algorithms for their problems.
 The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}.
@@
 This cycle is then repeated until the allocated time has run out.
-Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forests, which perform well on a large number of data sets, first.
+Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first.
 \\
@@
 
+\section{Constructing pipelines}
+%% Whole pipelines
+Before a classifier is evaluated on a data set, often a number of pre-processing steps are executed first.
+These could include selecting promising features and discarding other and normalizing the data.
+The 'sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a machine learning pipeline.
+Two tools which construct such complete pipelines for data sets are MP-Plan and the RECIPE framework.
+
 % ML-Plan
@@
 A best-first search algorithm in a modified variant is then used to find good solutions in this task network.
+For the actual implementation of the learning algorithms, WEKA is used.
 While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\
@@
 The figure is loosely adapted from \cite{wever2017automatic}.
-Nodes containing '...' represent an undefined amount of subtrees.
+Nodes containing '...' represent an undefined number of subtrees.
 \textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
@@
 \end{figure}
+
+% Recipe framework
+Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}.
+However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constraint the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}.
+This means that generated individuals representing complete pipelines can never be invalid.
+So for a new data set combined with a grammar that represents the valid pipelines, the tool first initializes the first generation according to the grammar.
+The fitness of individuals is then evaluated by mapping them to their respective implementations in the scikit-learn framework, and a new generation is created that takes this newly gained information into account.
+Evaluation by the authors indicates that the RECIPE framework is able to compete with AUTO-SKLEARN and a different evolutionary approach, although it does not incorporate meta-knowledge in the search.

### 2018-02-07 Writing/Thesis/content/chapter-evaluation.tex
Add introduction, related + fundamentals parts
Some writing
More writing

--- 2018-01-07 Writing/Thesis/content/chapter-conclusion.tex
@@
 %
-\chapter{Conclusion}
-\label{sec:conclusion}
+\chapter{Evaluation}
+\label{sec:evaluation}
 
-\section{Future Work}
-\label{sec:conclusion:future}
+\section{Experimental Setup}
+
+% Gathering data sets from OpenML
+
+% Generating base performance data
+
+% Oracle
+
+% Best Algo Performance
+Both variants compared against Best Algorithm baseline, which was implemented as a Ranker of type PreferenceRanker itself and evaluated the same way as the other PreferenceRankers.
+This baseline is computed iteratively by training an oracle on the same data set and then
+
+% Evaluation Measures used & computed
+
+% How find best version of preference and regression ranker
+
+\section{Results}
+
+% Results of Base Algorithms and full meta features
+% - scatter plot dataset -> best preferenceRanker, best regressionRanker, bestAlgorithmbaseline each Kendall
+
+% Results include the 4 evals on all sets, how long predictions took.
+Meta feature calc times sperately, but may give avg of comp+predict time each time meta feature values table in appendix with mean,min,max stdev
+
+% When removing probing
+
+% When removing expensive meta features
+
+% Results of optimized variants? full / no probing / no expensive
+
+% Insights about classifiers: place best ranking, min, max rank (optional) for each classif?
+% TODO replace by large data set
+\begin{table}[h]
+\centering
+	\begin{tabularx}{\textwidth}{X | X}
+		%\hline
+		Classifier		&	Number of Data Sets Placed First \\	\hline
+		Logistic			&	28								\\	\hline	
+		Naive Bayes			&	29								\\	\hline	
+		IBk		&	23								\\	\hline	
+		KStar			&	24								\\	\hline	
+		LMT		&	17								\\	\hline	
+		VotedPerceptron		&	16								\\	\hline	
+		ZeroR		&	14								\\	\hline	
+		J48			&	13								\\	\hline	
+		NaiveBayesMultinomial			&	6								\\	\hline	
+		RandomTree			&	2								\\	\hline	
+		SimpleLogistic			&	1								\\	\hline
+		DecisionStump			&	1								\\	\hline
+		MultilayerPerceptron			&	1								\\	\hline
+		RandomForest			&	1								\\	\hline
+		DecisionTable			&	1								\\	\hline
+		PART			&	1								\\	\hline
+		SGD			&	1								\\	\hline
+		BayesNet			&	1								\\	\hline
+		REPTree			&	1								\\	\hline
+		JRip			&	1								\\	\hline
+		SMO			&	313								\\	\hline
+		OneR			&	448								\\	\hline
+
+	\end{tabularx}
+	\label{tab:table1}
+	\caption{The ranking }
+\end{table}
+
+\pgfplotsset{width=\textwidth}
+\begin{tikzpicture}
+\begin{axis}
+\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
+\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
+\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
+\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
+\legend{IB Label KY, Best Algorithm}
+\end{axis}
+\end{tikzpicture}

### 2018-02-09 Writing/Thesis/content/chapter-evaluation.tex
More writing & some meta data calcs

@@
 \label{sec:evaluation}
+
+\section{Baseline and Oracle}
+% Workings of oracle
+In order to evaluate the implemented rankers, their outputs are compared to a perfect output generated by an oracle.
+The oracle is implemented as a ranker that, after having been trained on a meta data - performance data set returns correct rankings when queried for any instance of that data set.
+The correct ranking is implied by the performance values (highest first, as the measure used here is predictive accuracy), with ties being handled in a sequential manner, i.e.
+for the same performance values, the algorithm that was encountered first when constructing the ranking will be ranked before all others with the same value.
+
+% Evaluation Measures used & computed
+As a ranking returned by this oracle represents the ideal solution,
+
+% Baseline
+Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings.
+Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline.
+The baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the RMSE of predict performance values cannot bet computed.
+Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, and come as close as possible to the correct ranking.
 
@@
 % Generating base performance data
-
-% Oracle
-
-% Best Algo Performance
-Both variants compared against Best Algorithm baseline, which was implemented as a Ranker of type PreferenceRanker itself and evaluated the same way as the other PreferenceRankers.
-This baseline is computed iteratively by training an oracle on the same data set and then
-
-% Evaluation Measures used & computed
+Performance Values acquired with 5 times MCCV
 
@@
 % Insights about classifiers: place best ranking, min, max rank (optional) for each classif?
-% TODO replace by large data set
+
+\subsection{Accuracy}
+
+\begin{landscape}
+\begin{table}[h]
+\centering
+	\begin{tabularx}{23,7cm}{>{\hsize=3.4\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
+		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-13}
+							 			& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 		& Min	& Max		& Mean		& Stdv	\\ \hline
+		LinearRegression 				& -0.255 	& 0.896 		& 0.473	 	& 0.221 & 0 		& 86.667 	& 3.469	 	& 7.244 		& 0 		& 31.220 	& 1.267	 	& 3.011 	\\
+		M5P				 				& -0.29 		& 0.870 		& 0.470	 	& 0.219 & 0 		& 82.353 	& 3.78	 	& 6.535 		& 0 		& 82.353 	& 1.508	 	& 4.757 	\\	
+		RandomForest		 				& -0.281 	& 0.922 		& 0.495	 	& 0.228 & 0		& 60 		& 3.097 		& 5.745 		& 0 		& 34.634 	& 1.308	 	& 3.150 	\\	
+		REPTree			 				& -0.229 	& 0.896 		& 0.412		& 0.213 & 0 		& 82.353		& 4.829	 	& 7.948 		& 0		& 34.634 	& 1.759	 	& 3.515 	\\	
+		InstanceBased 					& -0.429 	& 0.870 		& 0.221	 	& 0.249 & 0 		& 82.353		& 5.401 		& 9.44 		& 0 		& 82.353 	& 3.62	 	& 8.540 	\\	
+		InstanceBased\footnotemark{}		& -0.429 	& 0.887 		& 0.340	 	& 0.252 & 0 		& 98.367 	& 5.437 		& 10.323 	& 0 		& 82.353 	& 3.294	 	& 8.367 	\\	
+		InstanceBased\footnotemark{}		& -0.429 	& 0.870 		& 0.335	 	& 0.249 & 0 		& 82.353 	& 5.382	 	& 9.402 		& 0 		& 82.353 	& 3.511	 	& 8.493 	\\	
+		PairwiseComparison 				& -0.870 	& 0.576		& 0.014	 	& 0.234 & 0 		& 97.822 	& 9.762	 	& 13.135 	& 0 		& 82.353 	& 4.001	 	& 8.600 	\\	
+		BestAlgorithm	 				& -0.437 	& 0.489 		& 0.057	 	& 0.159 & 0		& 82.353		& 6.480 		& 10.168 	& 0		& 82.353		& 3.420 		& 8.195 	\\							
+	\end{tabularx}
+	\label{tab:evaluationresults1}
+	\caption{Evaluation results with full meta data}
+\end{table}
+
+\addtocounter{footnote}{-2}
+\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
+\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
+\end{landscape}
+
+\tikzsetnextfilename{LossGraphics}
+\pgfplotsset{width=\textwidth}
+\begin{tikzpicture}
+\begin{axis}
+\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
+\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
+\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
+\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
+\legend{IB Label KY, Best Algorithm}
+\end{axis}
+\end{tikzpicture}
+
+\tikzsetnextfilename{BestThreeLossGraphics}
+\pgfplotsset{width=\textwidth}
+\begin{tikzpicture}
+\begin{axis}
+\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
+\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
+%\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
+%\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
+\legend{IB Label KY, Best Algorithm}
+\end{axis}
+\end{tikzpicture}
+
+\subsection{Time}
+\hspace{-1em}
+\begin{table}[h]
+	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
+		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
+										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
+		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 86.667 	& 3.469	 	& 7.244 	\\
+		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 82.353 	& 3.78	 	& 6.535	\\	
+		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 60 		& 3.097 		& 5.745	\\	
+		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 82.353		& 4.829	 	& 7.948	\\	
+		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 82.353		& 5.401 		& 9.44	\\	
+		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 98.367 	& 5.437 		& 10.323	\\	
+		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 82.353 	& 5.382	 	& 9.402	\\	
+		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 97.822 	& 9.762	 	& 13.135	\\	
+		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 82.353		& 6.480 		& 10.168	\\							
+	\end{tabularx}
+	\label{tab:evaluationresults1}
+	\caption{Build and Prediction Times of the Rankers in ms}
+\end{table}
+
+\addtocounter{footnote}{-2}
+\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
+\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
+
+\subsection{Further Insights}
+
+\begin{table}[h]
+	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
+		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} \\ \cline{2-5}
+										& Min		& Max		& Mean		& Stdv 	\\ \hline
+		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	\\
+		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	\\	
+		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	\\	
+		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\	
+		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	\\	
+		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	\\	
+		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	\\	
+		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	\\	
+		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23		\\							
+	\end{tabularx}
+	\label{tab:evaluationresults1}
+	\caption{Build and Prediction Times of the Rankers in ms}
+\end{table}
+
+% TODO replace by large data set??
 \begin{table}[h]
@@
 		OneR						&	448								\\	\hline																	
-
 	\end{tabularx}
 	\label{tab:table1}
-	\caption{The ranking }
+	\caption{The ranking of Classifiers returned by the Best Algorithm Baseline}
 \end{table}
-
-\pgfplotsset{width=\textwidth}
-\begin{tikzpicture}
-\begin{axis}
-\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
-\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
-\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
-\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
-\legend{IB Label KY, Best Algorithm}
-\end{axis}
-\end{tikzpicture}

### 2018-02-09 Writing/Thesis/content/chapter-evaluation.tex
more writing

@@
 		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\								
-		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	\\	
-		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	\\	
-		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	\\	
-		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	\\	
-		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23		\\							
 	\end{tabularx}
 	\label{tab:evaluationresults1}
-	\caption{Build and Prediction Times of the Rankers in ms}
+	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers}
 \end{table}

### 2018-02-09 ranker/src/main/java/ranker/Main.java
Add prediction times

@@ -139,42 +139,42 @@ public class Main {
 			targetAttributes.add(i);
 		}
 		
-		Ranker ranker = new RandomForestRanker();
+//		Ranker ranker = new RandomForestRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+//		
+//		ranker = new M5PRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+//		
+//		ranker = new REPTreeRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+//		
+//		ranker = new LinearRegressionRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+//		
+//		ranker = new BestAlgorithmRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
 		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
+		Ranker ranker = new InstanceBasedLabelRankingRanker();
 		
-		ranker = new M5PRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
-		ranker = new REPTreeRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
-		ranker = new LinearRegressionRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
-		ranker = new BestAlgorithmRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
-		ranker = new InstanceBasedLabelRankingRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
-		ranker = new InstanceBasedLabelRankingKemenyYoung();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
-		ranker = new InstanceBasedLabelRankingKemenyYoungSQRTN();
-		
-		System.out.println(EvaluationHelper.evaluateRanker(ranker, instances, targetAttributes));
-		
[…]

### 2018-02-09 ranker/src/main/java/ranker/Util.java

@@ -16,5 +16,6 @@ public class Util {
 	public static Path resultsPath = FileSystems.getDefault().getPath("data");
 	public static Path cacheDirectory = FileSystems.getDefault().getPath("data");
 	public static final String RANKER_BUILD_TIMES = "RankerBuildTimes";
+	public static final String RANKER_PREDICT_TIMES = "RankerPredictTimes";
 	public static final String DATA_ID = "DataId";
 }

### 2018-02-09 ranker/src/main/java/ranker/core/evaluation/LeaveOneOut.java

@@ -41,6 +41,7 @@ public class LeaveOneOut extends RankerEstimationProcedure {
 		}
 		detailedEvaluationResults.put(Util.DATA_ID, new ArrayList<>());
 		detailedEvaluationResults.put(Util.RANKER_BUILD_TIMES, new ArrayList<>());
+		detailedEvaluationResults.put(Util.RANKER_PREDICT_TIMES, new ArrayList<>());
 		
 		// Evaluate all instances separately
 		for (int i = 0; i < data.numInstances(); i++) {

### 2018-02-09 ranker/src/main/java/ranker/core/evaluation/RankerEstimationProcedure.java

@@ -87,13 +87,19 @@ public abstract class RankerEstimationProcedure {
 		watch.start();
 		ranker.buildRanker(train, targetAttributes);
 		watch.stop();
+		double buildTime = (double) watch.getTime();
 		perfectRanker.buildRanker(train, targetAttributes);
 
 		// Evaluate on each instance and get result from evaluationMeasure
 		for (Instance instance : test) {
 			try {
 				// Build, get results and add to lists
+				watch.reset();
+				watch.start();
 				List<Classifier> predictedRanking = ranker.predictRankingforInstance(instance);
+				watch.stop();
+				double predictTime = (double)watch.getTime();
+				detailedEvaluationResults.get(Util.RANKER_PREDICT_TIMES).add(predictTime);
 				List<Classifier> perfectRanking = perfectRanker.predictRankingforInstance(instance);
 				List<Double> estimatedValues = ranker.getEstimates();
 				List<Double> performanceMeasures = perfectRanker.getEstimates();
@@ -108,7 +114,6 @@ public abstract class RankerEstimationProcedure {
 					detailedEvaluationResults.get(measure.getClass().getSimpleName()).add(result);
 				}
 				//save time of ranker building
-				double buildTime = (double) watch.getTime();
 				detailedEvaluationResults.get(Util.RANKER_BUILD_TIMES).add(buildTime);
 			} catch (Exception e) {
 				throw(e);

### 2018-02-09 Writing/Thesis/content/chapter-fundamentals.tex

--- 2018-01-14 Writing/Thesis/content/chapter-fundamentals.tex
@@
 In this section, the aspects of the field of machine learning which are relevant for this thesis are going to be introduced briefly.
-The core of machine learning are learning algorithms, which are used to induce a general model from a set of data samples.
+The core of machine learning is learning algorithms, which are used to induce a general model from a set of data samples.
 The concept of machine learning will be explained here with the help of an example.
@@
 
+% Algorithm selection problem
+
 \section{Evaluation}
-
-\subsection{Classifier Evaluation}
 
@@
 
-As we have seen in example above, can also have same rank for items. In order to account for this, a second statistic, $T_B$ has been defined as
+As we have seen in example above, can also have same rank for items. In order to account for this, a second statistic, $T_B$ is defined as
 
@@
 % In theory explanation for Kendall's Tau B because ranking could be tied but not as a result of Label Ranking and unlikely for regression the implementation that is used calculates Tau b!
+
+\subsection{Loss}
+While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms.
+This difference can b expressed in measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.
+
+Additionally, the ranker recommends a ranking instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss.
+This is done here by computing a measure called best three loss, which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier among the considered set of classifiers.
+
+\subsection{Mann-Whitney U Test}
+too compare the ranking alternatives and to the basline to see if statistically significantly better.

### 2018-02-10 ranker/src/main/java/ranker/Main.java
refactor RMSE + add Mann-WhitneyU

@@ -129,32 +129,32 @@ public class Main {
 //		
 		//System.out.println(EvaluationHelper.evaluateRanker(ranker, WekaHelper.subSet(instances, 1, 50), targetAttributes));
 		
-		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues.arff"),
-				Util.charset);
-
-		Instances instances = new Instances(reader);
-		
-		List<Integer> targetAttributes = new ArrayList<Integer>();
-		for (int i = 104; i < 126; i++) {
-			targetAttributes.add(i);
-		}
-		
-		Ranker ranker = new RandomForestRanker();
-
-		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
-
-		
-		ranker = new M5PRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
-		
-		ranker = new REPTreeRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
-		
-		ranker = new LinearRegressionRanker();
-		
-		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
+//		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues.arff"),
+//				Util.charset);
+//
+//		Instances instances = new Instances(reader);
+//		
+//		List<Integer> targetAttributes = new ArrayList<Integer>();
+//		for (int i = 104; i < 126; i++) {
+//			targetAttributes.add(i);
+//		}
+//		
+//		Ranker ranker = new RandomForestRanker();
+//
+//		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
+//
+//		
+//		ranker = new M5PRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
+//		
+//		ranker = new REPTreeRanker();
+//		
+//		System.out.println(EvaluationHelper.evaluateRegressionRanker(ranker, instances, targetAttributes));
+//		
+//		ranker = new LinearRegressionRanker();
+//		
[…]

### 2018-02-10 ranker/src/main/java/ranker/core/evaluation/EvaluationHelper.java

@@ -11,6 +11,8 @@ import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.List;
 
+import org.apache.commons.math3.stat.inference.MannWhitneyUTest;
+
 import ranker.Util;
 import ranker.core.algorithms.Ranker;
 import ranker.util.openMLUtil.OpenMLHelper;
@@ -59,8 +61,6 @@ public class EvaluationHelper {
 	 * Path for saving the generated jobs
 	 */
 	public static Path jobsPath = FileSystems.getDefault().getPath("jobs.txt");
-	
-
 
 	/**
 	 * Evaluates all currently available measures for this type of ranker by means
@@ -87,13 +87,13 @@ public class EvaluationHelper {
 		System.out.println(estim.getDetailedEvaluationResults());
 		return result;
 	}
-	
-	public static List<Double> evaluateRegressionRanker(Ranker ranker, Instances instances, List<Integer> targetAttributes)
-			throws Exception {
+
+	public static List<Double> evaluateRegressionRanker(Ranker ranker, Instances instances,
+			List<Integer> targetAttributes) throws Exception {
 		RankerEstimationProcedure estim = new LeaveOneOut();
 		List<RankerEvaluationMeasure> measures = new ArrayList<RankerEvaluationMeasure>();
 		measures.add(new KendallRankCorrelation());
-		measures.add(new RootMeanSquaredError());
+		measures.add(new RootMeanSquareError());
 		Loss loss = new Loss();
 		loss.setPerformanceOrder(PerformanceOrder.ASCENDING);
 		measures.add(loss);
@@ -104,8 +104,6 @@ public class EvaluationHelper {
 		System.out.println(estim.getDetailedEvaluationResults());
 		return result;
 	}
-	
-
 
 	/**
 	 * Evaluates the predictive accuracy of the classifier on the data set by means
@@ -235,6 +233,66 @@ public class EvaluationHelper {
 			e.printStackTrace();
 		}
 
+	}
+
+	/**
+	 * For comparing whether one Ranker is significantly better regarding a measure
+	 * than the other; to be used with the .csv files when a ranker is generated.
+	 * 
+	 * @param firstFile Evaluation results of the first ranker
+	 * @param secondFile Evaluation results of the second ranker
+	 * @param measure The measure to compare
+	 * @return
+	 * @throws IOException
+	 */
+	public static double computeWhitneyU(Path firstFile, Path secondFile, String measure) throws IOException {
[…]

### 2018-02-10 ranker/src/main/java/ranker/core/evaluation/RootMeanSquareError.java

@@ -1,5 +1,6 @@
 package ranker.core.evaluation;
 
+import java.util.ArrayList;
 import java.util.List;
 
 import weka.classifiers.Classifier;
@@ -13,43 +14,59 @@ import weka.classifiers.Classifier;
  * @author Helena Graf
  *
  */
-public class RootMeanSquaredError extends RankerEvaluationMeasure {
+public class RootMeanSquareError extends RankerEvaluationMeasure {
 
 	@Override
 	public double evaluate(List<Classifier> predictedRanking, List<Classifier> perfectRanking, List<Double> estimates,
 			List<Double> performanceMeasures) {
 		System.out.print("RMSE ");
-		// Initialize result, catch NaNs
-		double result = 0;
-		int numCalculated = predictedRanking.size();
-		
+		List<Double> estimations = new ArrayList<Double>();
+		List<Double> actualValues = new ArrayList<Double>();
+
 		// Find corresponding classifier values and compare
 		for (int i = 0; i < predictedRanking.size(); i++) {
 			for (int j = 0; j < perfectRanking.size(); j++) {
 				if (predictedRanking.get(i).getClass().getName()
 						.equals(perfectRanking.get(j).getClass().getName())) {
-					// Have found position, now compare predicted value with actual Value
-					double difference = estimates.get(i) - performanceMeasures.get(j);
-					double squared =  Math.pow(difference, 2);
-
-					if (!Double.isNaN(squared)) {
-						result += squared;
-					} else {
-						numCalculated--;
-					}					
+					// Have found position, now remember value
+					estimations.add(estimates.get(i));
+					actualValues.add(performanceMeasures.get(j));
 					break;
 				}
 			}
 		}
 		
+
+		double result = computeRMSE(estimations, actualValues);
+		System.out.println(result);
+		return result;
+	}
+	
+	public double computeRMSE(List<Double> estimations, List<Double> actualValues) {
+		double result = 0;
+		int numCalculated = estimations.size();
+		
+		// Add squares of differences
+		for (int i = 0; i < estimations.size(); i++) {
+			double difference = estimations.get(i) - actualValues.get(i);
+			double squared = Math.pow(difference, 2);
+			if (!Double.isNaN(squared)) {
+				result += squared;
+			} else {
+				numCalculated--;
+			}	
+		}
+
+		// Divide by n
 		if (numCalculated == 0) {
 			result = Double.NaN;
 		} else {
[…]

### 2018-02-10 ranker/src/test/java/evluationTest/RootMeanSquareErrorTest.java

@@ -1,0 +1,37 @@
+package evluationTest;
+
+import static org.junit.Assert.assertEquals;
+
+import java.util.Arrays;
+import java.util.List;
+
+import org.junit.Test;
+
+import ranker.core.evaluation.RootMeanSquareError;
+
+public class RootMeanSquareErrorTest {
+	
+	@Test
+	public void testRMSE0() {
+		List<Double> estimates = Arrays.asList(1.0,2.0,3.0,4.0,5.0);
+		RootMeanSquareError rmse = new RootMeanSquareError();
+		assertEquals(0, rmse.computeRMSE(estimates, estimates),0.0001);
+	}
+	
+	@Test
+	public void testRMSE10() {
+		List<Double> estimates = Arrays.asList(100.0,100.0,100.0,100.0,100.0);
+		List<Double> actual = Arrays.asList(0.0,0.0,0.0,0.0,0.0);
+		RootMeanSquareError rmse = new RootMeanSquareError();
+		assertEquals(100, rmse.computeRMSE(estimates, actual),0.0001);
+	}
+	
+	@Test
+	public void testRMSEWorksWithNans() {
+		List<Double> estimates = Arrays.asList(100.0,100.0,Double.NaN,100.0,100.0);
+		List<Double> actual = Arrays.asList(0.0,0.0,0.0,0.0,0.0);
+		RootMeanSquareError rmse = new RootMeanSquareError();
+		assertEquals(100, rmse.computeRMSE(estimates, actual),0.0001);
+	}
+
+}

### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
more writing

@@
 	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
-		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} \\ \cline{2-5}
+		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Root Mean Square Error)} \\ \cline{2-5}
 										& Min		& Max		& Mean		& Stdv 	\\ \hline

### 2018-02-10 Writing/Thesis/content/chapter-conclusion.tex
more writing
More writing & some clean-up

@@
 Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed.
-The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking, and the evaluations of both against each other, a baseline and an oracle.
+The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking.
+Both have been evaluated extensively against a baseline and an oracle.
 
@@
 % Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
-On the basis of the results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
+On the basis of these results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
 A practical application of these findings may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
@@
 \label{sec:conclusion:future}
+% Has worked reasonably well -> extend evaluation
+
 %- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)

### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
More writing & some clean-up

--- 2018-02-09 Writing/Thesis/content/chapter-evaluation.tex
@@
 
+\hspace{-1em}
+\begin{table}[h]
+	\begin{tabularx}{1.1\textwidth}{>{\hsize=1.6\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X}
+		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7}
+										& Mann-Whitney U & P-Value & Mann-Whitney U	& P-Value & Mann-Whitney U & P-Value \\ \hline
+		LinearRegression 				& 186381.5 & 2.702E-109 & 126861.5 & 7.694E-12 & 129028.0 & 1.327E-13 \\
+		M5P				 				& 186236.0 & 6.230E-109 & 118828.5 & 1.840E-6 & 126379.5 & 1.821E-11 \\
+		RandomForest		 			& 187750.5 & 9.737E-113 & 128853.5 & 1.861E-13 & 129037.0 & 1.304E-13 \\
+		REPTree			 				& 181228.0 & 8.094E-97 & 111850.0 & 0.003 & 118793.0 & 1.926E-6 \\		
+		InstanceBased					& 142665.5 & 8.818E-28 & 109372.0 & 0.020 & 104279.0 & 0.311 \\
+		InstanceBased\footnotemark{}	& 166460.5 & 2.583E-65 & 111940.5 & 0.003 & 109211.0 & 0.022 \\
+		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
+		PairwiseComparison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
+	\end{tabularx}
+	\label{tab:evaluationresults1}
+	\caption{Significance of Results Regarding Kendall Rank Correlation Coefficient}
+\end{table}
+
+\addtocounter{footnote}{-2}
+\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
+\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
+
 \tikzsetnextfilename{LossGraphics}
@@
 	\label{tab:evaluationresults1}
-	\caption{Build and Prediction Times of the Rankers in ms}
+	\caption{Build and Prediction Times of the Rankers in ms (full meta data)}
 \end{table}
@@
 \begin{table}[h]
-	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
-		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} \\ \cline{2-5}
+	\begin{tabularx}{\textwidth}{>{\hsize=1.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
+		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Root Mean Square Error} \\ \cline{2-5}
 										& Min		& Max		& Mean		& Stdv 	\\ \hline
@@
 	\label{tab:evaluationresults1}
-	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers}
+	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers (full meta data)}
 \end{table}

### 2018-02-10 ranker/src/main/java/ranker/Main.java

@@ -23,6 +23,7 @@ import ranker.core.algorithms.REPTreeRanker;
 import ranker.core.algorithms.RandomForestRanker;
 import ranker.core.algorithms.Ranker;
 import ranker.core.algorithms.RegressionRanker;
+import ranker.core.evaluation.BestThreeLoss;
 import ranker.core.evaluation.EvaluationHelper;
 import ranker.core.evaluation.KendallRankCorrelation;
 import ranker.core.evaluation.LeaveOneOut;
@@ -183,13 +184,15 @@ public class Main {
 //		List<Classifier> classifs = rankprediction.predictRanking(OpenMLHelper.getInstancesById(2));
 //		classifs.forEach(elem -> System.out.println(elem.getClass().getSimpleName()));
 		
-		Path firstFile = FileSystems.getDefault().getPath("InstanceBasedLabelRankingKemenyYoungSQRTN_metaData_small_allPerformanceValues.csv");
-		Path secondFile = FileSystems.getDefault().getPath("InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv");
+		Path firstFile = FileSystems.getDefault().getPath("PairwiseComparisonRanker_metaData_small_allPerformanceValues.csv");
+		Path secondFile = FileSystems.getDefault().getPath("BestAlgorithmRanker_metaData_small_allPerformanceValues.csv");
 		String measure = new KendallRankCorrelation().getClass().getSimpleName();
-		System.out.println("\"" + measure + "\"");
+		System.out.print("& " + EvaluationHelper.computeWhitneyU(firstFile, secondFile, measure) + " ");
 		
-		System.out.println(EvaluationHelper.computeWhitneyU(firstFile, secondFile, measure));
+		measure = new Loss().getClass().getSimpleName();
+		System.out.print("& " + EvaluationHelper.computeWhitneyU(firstFile, secondFile, measure) + " ");
 
-		
+		measure = new BestThreeLoss().getClass().getSimpleName();
+		System.out.print("& " + EvaluationHelper.computeWhitneyU(firstFile, secondFile, measure) +" ");
 	}
 }

### 2018-02-10 ranker/src/main/java/ranker/core/evaluation/EvaluationHelper.java

@@ -12,6 +12,8 @@ import java.util.HashMap;
 import java.util.List;
 
 import org.apache.commons.math3.stat.inference.MannWhitneyUTest;
+import org.apache.commons.math3.stat.ranking.NaNStrategy;
+import org.apache.commons.math3.stat.ranking.TiesStrategy;
 
 import ranker.Util;
 import ranker.core.algorithms.Ranker;
@@ -25,27 +27,22 @@ import weka.classifiers.Classifier;
 import weka.classifiers.bayes.BayesNet;
 import weka.classifiers.bayes.NaiveBayes;
 import weka.classifiers.bayes.NaiveBayesMultinomial;
-import weka.classifiers.functions.GaussianProcesses;
-import weka.classifiers.functions.LinearRegression;
 import weka.classifiers.functions.Logistic;
 import weka.classifiers.functions.MultilayerPerceptron;
 import weka.classifiers.functions.SGD;
 import weka.classifiers.functions.SMO;
-import weka.classifiers.functions.SimpleLinearRegression;
 import weka.classifiers.functions.SimpleLogistic;
 import weka.classifiers.functions.VotedPerceptron;
 import weka.classifiers.lazy.IBk;
 import weka.classifiers.lazy.KStar;
 import weka.classifiers.rules.DecisionTable;
 import weka.classifiers.rules.JRip;
-import weka.classifiers.rules.M5Rules;
 import weka.classifiers.rules.OneR;
 import weka.classifiers.rules.PART;
 import weka.classifiers.rules.ZeroR;
 import weka.classifiers.trees.DecisionStump;
 import weka.classifiers.trees.J48;
 import weka.classifiers.trees.LMT;
-import weka.classifiers.trees.M5P;
 import weka.classifiers.trees.REPTree;
 import weka.classifiers.trees.RandomForest;
 import weka.classifiers.trees.RandomTree;
@@ -239,30 +236,33 @@ public class EvaluationHelper {
 	 * For comparing whether one Ranker is significantly better regarding a measure
 	 * than the other; to be used with the .csv files when a ranker is generated.
 	 * 
-	 * @param firstFile Evaluation results of the first ranker
-	 * @param secondFile Evaluation results of the second ranker
-	 * @param measure The measure to compare
+	 * @param firstFile
+	 *            Evaluation results of the first ranker
+	 * @param secondFile
+	 *            Evaluation results of the second ranker
+	 * @param measure
[…]

### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
add todonotes package and fixed layout of some tables

@@
 
-\hspace{-1em}
 \begin{table}[h]
-	\begin{tabularx}{1.1\textwidth}{>{\hsize=1.6\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X}
+\hspace{-1cm}
+	\begin{tabularx}{1.15\textwidth}{>{\hsize=1.4\hsize}X | >{\hsize=.84\hsize}X | >{\hsize=1.07\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X}
 		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7}
@@
 		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
-		PairwiseComparison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
+		PairwiseCom- parison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
 	\end{tabularx}

### 2018-02-10 Writing/Thesis/content/chapter-fundamentals.tex
add todonotes package and fixed layout of some tables

@@
 \begin{table}[h]
-	\begin{tabularx}{\textwidth}{X X X X X X}
+	\begin{tabularx}{\textwidth}{>{\hsize=1.1\hsize}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X  >{\hsize=1.7\hsize}X}
 		%\hline
-		Feature	& Sepal length	& Sepal width	& Petal length	& Petal width 	& Species			\\ \hline
+		Feature	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal width}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal width} 	& Species			\\ \hline
 				& 5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
@@
 
-Ranking = Permutation of the actual labels!
+Ranking = Permutation of the actual labels!\todo{fill}
 Ordering =

### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
added timings and removed todopackage

@@
 										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
-		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 86.667 	& 3.469	 	& 7.244 	\\
-		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 82.353 	& 3.78	 	& 6.535	\\	
-		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 60 		& 3.097 		& 5.745	\\	
-		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 82.353		& 4.829	 	& 7.948	\\	
-		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 82.353		& 5.401 		& 9.44	\\	
-		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 98.367 	& 5.437 		& 10.323	\\	
-		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 82.353 	& 5.382	 	& 9.402	\\	
-		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 97.822 	& 9.762	 	& 13.135	\\	
-		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 82.353		& 6.480 		& 10.168	\\							
+		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 1      	& 0	 	    & 0 	\\
+		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 16		 	& 0	 		& 1	\\	
+		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 16 		& 3	 		& 2	\\	
+		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 16			& 1	 		& 16	\\	
+		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 47			& 5 			& 8	\\	
+		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 19		 	& 1			& 3	\\	
+		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 16		 	& 1		 	& 2	\\	
+		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 0 			& 9.762	 	& 13.135	\\	
+		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 0			&  0 		& 0\\							
 	\end{tabularx}
@@
 
+%TODO add values for pairwise comparision}
 \addtocounter{footnote}{-2}

### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex
More writing

--- 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
@@
 Performance Values acquired with 5 times MCCV
+why decided to use these algorithms and not others
 
@@
 \section{Results}
+
+In the results mainly as so many data sets only taked about mean values but the full results with related to the specific data set id are included in supplementary material.
 
@@
 
-\subsection{Time}
+\subsection{Build and Prediction Times}
 \hspace{-1em}
@@
 	\label{tab:evaluationresults1}
-	\caption{Build and Prediction Times of the Rankers in ms (full meta data)}
+	\caption{Build and Prediction Times of the Rankers rounded to Full Milliseconds (Full Meta Data)}
 \end{table}

### 2018-02-11 Writing/Thesis/content/chapter-fundamentals.tex
added timings and removed todopackage
More writing

--- 2018-02-09 Writing/Thesis/content/chapter-fundamentals.tex
@@
 
-The core topic of this thesis falls under the category of machine learning. Thus, firstly the concept of machine learning and the
+The core topic of this thesis falls under the category of machine learning.
+Thus, first the concept of machine learning and the tasks related to the approach of this thesis are explained.
+Second, means used for evaluation of the approach are discussed.
 
@@
 More specifically, the focus lies on the three species iris versicolor, virginica and setosa.
-In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species.
-The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered the three) an unknown iris plant is.
+In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species, which is illustrated in Table \ref{tab:iris}.
+The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered three) an unknown iris plant is.
 The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation.
@@
 
-In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ that represents an ideal way of identifying iris species.
+In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ that represents an ideal way of identifying iris species \cite{abu2012learning}.
 $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant.
-The examples that the gardener recorded are samples $(x_1,y_1),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$.
+The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$.
 Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem.
-He then chooses a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees.
+They then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees.
 The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.
 
-%TODO include picture of the models etc + table + decision tree that is built
+%TODO include picture of the decision tree that is built & of the general ML-Model (from book)
 
@@
 Firstly, it falls in the category of supervised machine learning.
-Supervised learning is one of the three main learning paradigms of machine learning, together with reinforcement learning and unsupervised learning.
+Supervised learning is one of the three main learning paradigms of machine learning, together with reinforcement learning and unsupervised learning \cite{abu2012learning}.
 In the context of this thesis, the latter will be neglected as only supervised learning is used.
@@
 \subsection{Classification and Regression}
-%TODO instance explained before here?
 In addition to falling into the category of supervised learning, the problem is a classification problem.
 The nature of the prediction is to assign one of the three classes, or labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
-Formally, this means that the output space $Y$ of the target function consist of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, so that each instance is associated with a label $y_i \in Y$, in this case $Y=\lbrace 'iris-setosa','iris virginica', 'iris versicolor' \rbrace $.
+Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, so that each instance of the data set is associated with a label $y_i \in Y$, in this case $Y=\lbrace 'iris-setosa','iris virginica', 'iris versicolor' \rbrace $.
 
@@
 
+%TODO include a picture of the regression model mapping one of the width to height & say that this would be a linear model but others could be used
+
 \subsection{Preference Learning}
@@
 % Preference learning
-Preference Learning is a relatively new subfield of machine learning\cite{DBLP:books/daglib/0025729}.
-It is dedicated to the problem of learning how to rank, the precise definition of what this encompasses being defined by the specific task.
+Preference Learning is a relatively new subfield of machine learning \cite{DBLP:books/daglib/0025729}.
+It is dedicated to the problem of learning how to rank, the precise definition of what this encompasses being defined by the specific task one considers.
 Out of the three main tasks of preference learning, namely label ranking, instance ranking and object ranking, label ranking is the relevant one in the context of this thesis.
-But before going into to details of label ranking, it first has to be explained what is meant with a ranking in this context and how it is distinguished from the concept of an ordering.
+But before going into the details of label ranking, it first has to be explained what is meant with a ranking in this context and how it is distinguished from the concept of an ordering, as it is easily confused.
 
@@
 \subsubsection{Label Ranking}
-% could be seen as a generalisation of classification
 Similar to classification, in label ranking there is a finite set of labels $Y=\lbrace y_1,\dots,y_n \rbrace$, but it is not the output space.
-Instead, \citeauthor{DBLP:books/daglib/0025729} define the target function for label ranking as $X\rightarrow S_Y$ where the output space $S_Y$ contains all permutations over the set of labels $Y$ \cite{DBLP:books/daglib/0025729}.
+Instead, \citeauthor{DBLP:books/daglib/0025729} define the target function for label ranking as $f:X\rightarrow S_Y$ where the output space $S_Y$ contains all permutations over the set of labels $Y$ \cite{DBLP:books/daglib/0025729}.
 An instance $x \in X$ therefore is assigned a permutation $y_{\pi_x^i}$
@@
 % Context is meta learning -> what does that mean and what are the consequence
+Meta leThe previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets.
+In the context of meta learning, is 'possible to learn about the learning process
+itself, and in particular that a system could learn to profit from previous
+experience to generate additional knowledge that can simplify the automatic
+selection of efficient models summarizing the data' \cite{razdil2008metalearning}.
 
@@
 
+After having discussed the preliminaries that the theoretical approach of this thesis is built upon, the measures that will be used in the evaluation of the different methods are briefly reviewed.
+These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals if an advantage regarding one measure can be viewed as significant.
+
 \subsection{Kendall Rank Correlation Coefficient}
 % We need to evaluate the ranker quality somehow, ranker predicts rank, so need a 
-To evaluate the quality of the prediction that the ranker will make, a statistic is needed to compare a predicted ranking with other rankings like a baseline or an optimal ranking.
-serves as indication of causal connection
+To evaluate the quality of the prediction that a ranker will make, a statistic is needed to compare a predicted ranking with the correct ranking.
+For this, the Kendall Rank Correlation Coefficient will be used here, as it expresses the similarity of two rankings.
 
 % Definition of Kendall
-The Kendall Rank Correlation Coefficient is a measure of association between two rankings of the same items also known as Kendall's tau.
-For two independent variables $X$ and $Y$ and and observations of values $(x_1,...,x_m)$ for $X$ and $(y_1,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations.
+The Kendall Rank Correlation Coefficient, also known as Kendall's tau, is a measure of association between two rankings of the same items \cite{kendall1938new}.
+For two independent variables $X$ and $Y$ and and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations.
 If for two pairs $(x_i,y_i)$ and $(x_j,y_j)$ both $x_i < x_j$ and $y_i < y_j$ (or the opposite) holds, they are viewed as concordant.
@@
 
-$$T_A = \frac{n_c - n_d}{\sqrt{(n_0 - n_1 )(n_0 - n_2 )}},$$
+$$T_B = \frac{n_c - n_d}{\sqrt{(n_0 - n_1 )(n_0 - n_2 )}},$$
 with \\
@@
 
-% In theory explanation for Kendall's Tau B because ranking could be tied but not as a result of Label Ranking and unlikely for regression the implementation that is used calculates Tau b!
+Thus, the value of the tau (for both versions) lies in the interval $[-1,1]$, with 1 indicating a perfect agreement of rankings, -1 perfect disagreement, and 0 corresponding to no correlation.
+A high value is therefore desirable in this context, as it indicates that the prediction of the ranker agrees with the actual ranking of algorithms.
+
+%TODO include example ranking
 
@@
 While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms.
-This difference can b expressed in measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.
+This difference can be expressed in measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.
 
 Additionally, the ranker recommends a ranking instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss.
-This is done here by computing a measure called best three loss, which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier among the considered set of classifiers.
+This is done here by computing a measure called best three loss, which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier in the considered set of classifiers.
+
+%TODO include example loss calculatio
 
 \subsection{Mann-Whitney U Test}
-too compare the ranking alternatives and to the basline to see if statistically significantly better.
+%TODO describe & don't forget example
+The measures previously presented can indicate if one alternative is superior to another regarding that measure, but one cannot conclude from those results alone whether this advantage is significant.
+The question is whether the null-hypothesis that two distributions \cite{mann1947test}

### 2018-02-11 Writing/Thesis/content/chapter-fundamentals.tex

@@
 Ranking = Permutation of the actual labels!
+%TODO {fill}
 Ordering =

### 2018-02-11 Writing/Thesis/content/chapter-conclusion.tex
More writing

@@
 Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed.
-The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking.
+This problem has been addressed by implementing two different approaches, regression-based and preference-based ranking.
 Both have been evaluated extensively against a baseline and an oracle.
@@
 On the basis of these results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
-A practical application of these findings may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
+A practical application of these findings, apart from the direct use as a ranker, may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
 However, some additional work may have to be done in extension to this thesis in order for a sensible integration.
@@
 \label{sec:conclusion:future}
-% Has worked reasonably well -> extend evaluation
+% More evaluation - meta features
+As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression based approach using random forests, many possibilities for additional work arise.
+An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features.
+Different sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features.
 
-%- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)
-
-- use this to try to predict other measures (e.g. time needed)
-- look at the loss curve + loss-time (log) curve
-- further investigate the better solution
-- integrate solution into other auto ml solution if sensible regarding time contraints for that solution (and accuracy)
--e.g. use A3R
-- or runtime could be predicted separately by nn based on meta data \cite{DBLP:journals/corr/abs-1709-07615}
-- adding feature pre-processing
-
-% Extension of the tool
-- better fitting of learning algorithms to meta data (more manual work, but of course consider danger of overfitting!
-
-% Extended evaluation
-- compare against other tools that rank r.g. the Jan van Rijn one
-- deeper analysis of meta features, e.g. add some, remove some, consider trade-off time accuracy
+% More evaluation - loss - time & compare agains Jan van Rijn
+Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
+In this regard it would also be interesting  to implement the loss - and time - loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.
 
 % Use this for predicting different algorithms
-So far, the evaluation of the tool has been confined to predicting algorithms for classification.
-Since this has been relatively successful, it could be tested whether similar predictions can also be made for other machine learning tasks like regression or clustering.
+Additionally, so far the evaluation of the tool has been confined to predicting algorithms for classification.
+Since this has been relatively successful, it could be tested whether similar predictions can also be made for other machine learning tasks like regression or clustering with the same approach by extending the tool to handling these functions.
+Also, one could try to include a few parameterized versions of algorithms, as so far only one variant of each classifier with standard hyperparameters has been used.
 
-- hyperparameters neglected here, may include standard combinations in future work (or random ones)-> possible only if id by string
-- use this for regression
+% Use this to predict other measure
+In a similar manner to extending the algorithms for which a performance measure is predicted, one could use the tool to predict different performance measures.
+For this, the tool does not even need to be adapted, as it is agnostic to the semantics behind the measure it predicts, it only needs to be numeric.
+One possibility for this would be the prediction of build or prediction times of learning algorithms, or a measure that combines time and accuracy \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
 
-an average baseline like used in speeding up algo select might be better
+% Auto fitting
+Depending on the fact whether one is willing to trade-off longer build and prediction times, it would also be possible to fit more sophisticated regression models for the regression based approach.
+This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.
+
+% Additional baseline
+Last, it could be interesting to implement an additional baseline that averages ranks instead of counting how many times an algorithm is ranked first.
+This would help to determine if the surprising ranking returned by the best algorithm baseline (see Fig.
+\ref{tab:bestAlgorithmRanking}
+) still holds when using a different baseline. Naturally this new baseline then could also be used to re-evaluate the implemented ranking concepts.

### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex
More writing

@@
 \label{sec:evaluation}
+
+This chapter is dedicated to the evaluation of the proposed ranking approaches.
+First, the oracle and baseline against which the rankers are compared are explained.
+Second, the experimental setup, that is conditions under which the evaluation was conducted, is set forth.
+Last, results are presented and discussed.
 
@@
 % Evaluation Measures used & computed
-As a ranking returned by this oracle represents the ideal solution,
+As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{chapter:fundamentals}.
+These include the Kendall rank correlation coefficient, loss and best three loss.
+The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted.
+This is done by computing the root mean square error between the predicted and actual performance values.
+In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.
 
@@
 Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline.
-The baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the RMSE of predict performance values cannot bet computed.
-Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, and come as close as possible to the correct ranking.
+More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented.
+That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth.
+This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot bet computed.
+Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, which will be determined by calculating the Mann-Whitney U and determining whether its P-value.
 
@@
 % Gathering data sets from OpenML
+how many data sets from OpenML
 
@@
 Performance Values acquired with 5 times MCCV
+which (hyper)parameters where used
+which timeouts used
 why decided to use these algorithms and not others
@@
 
-\begin{landscape}
-\begin{table}[h]
-\centering
-	\begin{tabularx}{23,7cm}{>{\hsize=3.4\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
-		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-13}
-							 			& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 		& Min	& Max		& Mean		& Stdv	\\ \hline
-		LinearRegression 				& -0.255 	& 0.896 		& 0.473	 	& 0.221 & 0 		& 86.667 	& 3.469	 	& 7.244 		& 0 		& 31.220 	& 1.267	 	& 3.011 	\\
-		M5P				 				& -0.29 		& 0.870 		& 0.470	 	& 0.219 & 0 		& 82.353 	& 3.78	 	& 6.535 		& 0 		& 82.353 	& 1.508	 	& 4.757 	\\	
-		RandomForest		 				& -0.281 	& 0.922 		& 0.495	 	& 0.228 & 0		& 60 		& 3.097 		& 5.745 		& 0 		& 34.634 	& 1.308	 	& 3.150 	\\	
-		REPTree			 				& -0.229 	& 0.896 		& 0.412		& 0.213 & 0 		& 82.353		& 4.829	 	& 7.948 		& 0		& 34.634 	& 1.759	 	& 3.515 	\\	
-		InstanceBased 					& -0.429 	& 0.870 		& 0.221	 	& 0.249 & 0 		& 82.353		& 5.401 		& 9.44 		& 0 		& 82.353 	& 3.62	 	& 8.540 	\\	
-		InstanceBased\footnotemark{}		& -0.429 	& 0.887 		& 0.340	 	& 0.252 & 0 		& 98.367 	& 5.437 		& 10.323 	& 0 		& 82.353 	& 3.294	 	& 8.367 	\\	
-		InstanceBased\footnotemark{}		& -0.429 	& 0.870 		& 0.335	 	& 0.249 & 0 		& 82.353 	& 5.382	 	& 9.402 		& 0 		& 82.353 	& 3.511	 	& 8.493 	\\	
-		PairwiseComparison 				& -0.870 	& 0.576		& 0.014	 	& 0.234 & 0 		& 97.822 	& 9.762	 	& 13.135 	& 0 		& 82.353 	& 4.001	 	& 8.600 	\\	
-		BestAlgorithm	 				& -0.437 	& 0.489 		& 0.057	 	& 0.159 & 0		& 82.353		& 6.480 		& 10.168 	& 0		& 82.353		& 3.420 		& 8.195 	\\							
-	\end{tabularx}
-	\label{tab:evaluationresults1}
-	\caption{Evaluation results with full meta data}
-\end{table}
+\input{tables/evaluationResults}
+\ref{tab:evaluationResults}
 
-\addtocounter{footnote}{-2}
-\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
-\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
-\end{landscape}
+\input{tables/metaFeatureTimes}
+\ref{tab:metaFeatureTimes}
 
-\begin{table}[h]
-\hspace{-1cm}
-	\begin{tabularx}{1.15\textwidth}{>{\hsize=1.4\hsize}X | >{\hsize=.84\hsize}X | >{\hsize=1.07\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X}
-		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7}
-										& Mann-Whitney U & P-Value & Mann-Whitney U	& P-Value & Mann-Whitney U & P-Value \\ \hline
-		LinearRegression 				& 186381.5 & 2.702E-109 & 126861.5 & 7.694E-12 & 129028.0 & 1.327E-13 \\
-		M5P				 				& 186236.0 & 6.230E-109 & 118828.5 & 1.840E-6 & 126379.5 & 1.821E-11 \\
-		RandomForest		 			& 187750.5 & 9.737E-113 & 128853.5 & 1.861E-13 & 129037.0 & 1.304E-13 \\
-		REPTree			 				& 181228.0 & 8.094E-97 & 111850.0 & 0.003 & 118793.0 & 1.926E-6 \\		
-		InstanceBased					& 142665.5 & 8.818E-28 & 109372.0 & 0.020 & 104279.0 & 0.311 \\
-		InstanceBased\footnotemark{}	& 166460.5 & 2.583E-65 & 111940.5 & 0.003 & 109211.0 & 0.022 \\
-		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
-		PairwiseCom- parison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
-	\end{tabularx}
-	\label{tab:evaluationresults1}
-	\caption{Significance of Results Regarding Kendall Rank Correlation Coefficient}
-\end{table}
+\input{tables/significanceResults}
+\ref{tab:significanceResults}
 
@@
 \subsection{Build and Prediction Times}
-\hspace{-1em}
-\begin{table}[h]
-	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
-		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
-										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
-		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 1      	& 0	 	    & 0 	\\
-		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 16		 	& 0	 		& 1	\\	
-		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 16 		& 3	 		& 2	\\	
-		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 16			& 1	 		& 16	\\	
-		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 47			& 5 			& 8	\\	
-		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 19		 	& 1			& 3	\\	
-		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 16		 	& 1		 	& 2	\\	
-		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 0 			& 9.762	 	& 13.135	\\	
-		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 0			&  0 		& 0\\							
-	\end{tabularx}
-	\label{tab:evaluationresults1}
-	\caption{Build and Prediction Times of the Rankers rounded to Full Milliseconds (Full Meta Data)}
-\end{table}
 
-%TODO add values for pairwise comparision}
-\addtocounter{footnote}{-2}
-\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
-\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
+\input{tables/times}
+\ref{tab:times}
+%TODO add values for pairwise comparision in this table
 
@@
 
-\begin{table}[h]
-	\begin{tabularx}{\textwidth}{>{\hsize=1.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
-		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Root Mean Square Error} \\ \cline{2-5}
-										& Min		& Max		& Mean		& Stdv 	\\ \hline
-		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	\\
-		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	\\	
-		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	\\	
-		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\								
-	\end{tabularx}
-	\label{tab:evaluationresults1}
-	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers (full meta data)}
-\end{table}
+\input{tables/rootMeanSquareError}
+\ref{tab:rootMeanSquareError}
 
-% TODO replace by large data set??
-\begin{table}[h]
-\centering
-	\begin{tabularx}{\textwidth}{X | X}
-		%\hline
-		Classifier				&	Number of Data Sets Placed First \\	\hline
-		Logistic					&	28								\\	\hline	
-		Naive Bayes				&	29								\\	\hline	
-		IBk						&	23								\\	\hline	
-		KStar					&	24								\\	\hline	
-		LMT						&	17								\\	\hline	
-		VotedPerceptron			&	16								\\	\hline	
-		ZeroR					&	14								\\	\hline	
-		J48						&	13								\\	\hline	
-		NaiveBayesMultinomial	&	6								\\	\hline	
-		RandomTree				&	2								\\	\hline	
-		SimpleLogistic			&	1								\\	\hline
-		DecisionStump			&	1								\\	\hline
-		MultilayerPerceptron		&	1								\\	\hline
-		RandomForest				&	1								\\	\hline
-		DecisionTable			&	1								\\	\hline
-		PART						&	1								\\	\hline
-		SGD						&	1								\\	\hline
-		BayesNet					&	1								\\	\hline
-		REPTree					&	1								\\	\hline
-		JRip						&	1								\\	\hline
-		SMO						&	313								\\	\hline
-		OneR						&	448								\\	\hline																	
-	\end{tabularx}
-	\label{tab:table1}
-	\caption{The ranking of Classifiers returned by the Best Algorithm Baseline}
-\end{table}
+\input{tables/bestAlgorithmRanking}
+\ref{tab:bestAlgorithmRanking}

### 2018-02-11 Writing/Thesis/content/chapter-introduction.tex
add todonotes package and fixed layout of some tables
added timings and removed todopackage

@@
 \label{sec:intro}
-%TODO does this introduction really follow the three-moves structure?
 %% Introduction to introduction
-This introduction emphasizes why there is a need for automation in machine learning, and how this thesis relates to that problem.
+This introduction emphasizes why there is a need for automation in machine learning, and how this thesis relates to that problem in that it proposes two different approaches for ranking classification algorithms.
+Furthermore, an overview of the thesis structure is given.
 
@@
 Since there is no one best classifier for all data sets, it is likely that how well a classifier performs on a given data set is dependent on properties of the data set, at least to some degree.
-Combined with the need for automated machine learning, this calls for an approach that considers past performances of classifiers for data sets in relation to properties of these data sets to automatically suggest well-performing classifiers for a new problem.
+Combined with the need for automated machine learning and the importance but difficulty of selecting a fitting algorithm, this calls for an approach that considers past performances of classifiers for data sets in relation to properties of these data sets to automatically suggest well-performing classifiers for a new problem.
 
-%% Problem + Significance
-% Together this means that classifier selection is area where one can automate -> area of problem is suggesting classifiers
-Since there is a need for automated machine learning and selecting a fitting classification algorithm for a new data set is an important but difficult task in the machine learning pipeline, facilitating this process by automatically suggesting well-performing classifiers for a new data set is a significant problem.
+%% Response
+% Therefore the goal is testing the this assumption if possible by using regression algos and preference learning
+Thus, the aim of this thesis is the implementation and evaluation of two different approaches to ranking classification algorithms based on past-performances of the algorithms and according to properties of the data set.
+The two approaches include one regression-based approach that breaks down the problem of predicting a ranking into predicting a single performance value for each algorithm and then ranking them accordingly, and a preference based approach that is concerned with learning the rankings directly.
+Especially in the case of regression based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.
+
+% More Significance
 A tool that efficiently predicts which algorithms are likely to perform well compared to their alternatives regarding a specific data set simplifies the process of selecting an algorithm for inexperienced users and experts alike.
@@
 The advantage is that the user does not need to know characteristics of the classification algorithms or data set in order to achieve relatively good results in a short amount of time.
-A further speed-up and simplification could be achieved by embedding this tool in a solution that also takes care of the sampling of selected classifiers on the data set, for example existing solutions in the context of automated machine learning (auto-ml) context.
-
-%% Response
-% Therefore the goal is testing the this assumption if possible by using regression algos and preference learning
-Thus, the aim of this thesis is to
-
-algorithm selection problem at heart but want ranking to allow the user iterative testing
-
-could work because regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}
+A further speed-up and simplification could then possibly be achieved by embedding this tool in a solution that also takes care of the sampling of selected classifiers on the data set, for example existing solutions in the context of automated machine learning (auto-ml) context.
 

### 2018-02-11 Writing/Thesis/content/chapter-approach.tex
More writing & some meta data calcs
More writing
more writing

@@
 
+In this chapter the two alternatives which ar
+
+\section{Theory}
+
 Approach of ranking classifier implementations here realized by two concepts, regression-based and preference-based ranking, which will be explained in detail.
@@
 Thus target function of the form $meta features^n \rightarrow classifiers^m$.
+performance measure chosen predictive accuracy
 
@@
 This generates a table that contains all necessary informatino for training both types of rankers.
-A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently uing it to query the underlying model.
+A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently using it to query the underlying model.
 
@@
 \end{table}
+
+\section{Implementation}
+
+META FEATURES USED!
+
+for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before

### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex

@@
 \section{Experimental Setup}
+In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section where observed.
+This includes which classifiers and data sets where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.
 
-% Gathering data sets from OpenML
-how many data sets from OpenML
+% Which classifiers and data sets used
+The classifiers considered for a recommended ranking were the learning algorithms implemented in WEKA that are fit for classification, excluding meta and ensemble methods.
+The full list of the 22 classifiers can be gathered from Table \ref{tab:bestAlgorithmRanking}.
+They where all used in their default configurations as specified by WEKA.
 
-% Generating base performance data
-Performance Values acquired with 5 times MCCV
-which (hyper)parameters where used
-which timeouts used
-why decided to use these algorithms and not others
+datasets
+
+% How base performance data generated
+The performance data of the classifiers for the selected data sets was generated on [MACHINE DETAILS].
+[TIMEOUT AND HARDWARE ALLOCATION DETAILS].
+For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
+When a timeout occurred, the predictive accuracy was set to 0.
+
+% How rest of the evaluation carried out
+All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) and 12 GB RAM.
+It is notable that especially the time-related results are to be viewed in regard to this setup.
+No timeouts where used in this evaluation, and the rankers where evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values where recorded, they where trained with the meta data - performance examples for n - 1 data sets, and queried for the remaining data set.
+As n = 448 in this case, the full results are not included in the discussion of the results.
+They can, however, be found in the supplementary material, offering clues to how each ranker performed in the prediction of a ranking for each of the used data sets, identified by their ID on OpenML.
 
 % How find best version of preference and regression ranker
+Furthermore, four alternatives where selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem.
+For the regression based approach, the algorithms chosen where random forest, REPTree, M5P, and linear regression.
+For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA.
+As the preference based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives where generated by modifying the hyperparameters.
+The implemented alternatives are label ranking by pairwise comparison and instance based label ranking.
+As in early tests it became apparent that the instance based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used.
+For instance based label ranking, the default configuration, a configuration where the rank aggregation algorithm used by the label ranker was set to Kemeny-Young, and a configuration with Kemeny-Young rank aggregation and the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), set to the square root of the number of instances in the training data set.
+In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.
 

### 2018-02-11 Writing/Thesis/content/chapter-fundamentals.tex

@@
 
+original algorithms selection problem \cite{rice1976algorithm} can be viewed as a learning problem itself
+
 \subsection{Meta Learning}
@@
 
-After having discussed the preliminaries that the theoretical approach of this thesis is built upon, the measures that will be used in the evaluation of the different methods are briefly reviewed.
+After having discussed the preliminaries that the theoretical approach of this thesis is built upon, how a data set can be split into training and test data to estimate the performance of learning algorithms and the measures that will be used in the evaluation of the different ranking methods are briefly reviewed.
 These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals if an advantage regarding one measure can be viewed as significant.
+
+\subsection{Estimation Procedures}
+
+- estimation using cross validation (monte carloMCCV)
+
+- estimation using leave one out
 

### 2018-02-11 Writing/Thesis/content/chapter-introduction.tex

@@
 On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}.
-So in each case, one would have picked a different algorithm in order to achieve the best results.
+So in each case, one would have picked a different algorithm in order to achieve the best results, and this example just illustrates the choice between two algorithms - in reality, the of available algorithms is much larger.
 In general, this means that for a different data set, a different algorithm might yield the best performance.

### 2018-02-11 Writing/Thesis/content/chapter-related-work.tex

@@
 %% Ranking
+% Incorporating times
+In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifier \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
+They call this combined measure of accuracy and time A3R, and integrate it into to different ranking approaches.
 
-% Could do ranking by using meta-knowledge (avg ranking)
-One method of ranking algorithms called average-ranking utilizes meta-knowledge to suggest a ranking for a new data set.
-The meta-knowledge here consists of recording past performances of classifiers on data sets, and computing the average rank of each classifier over all data sets.
-Performance measures used are often related to the predictive accuracy of the classifier.
+% Rank aggregation A3R
+One of those two approaches is called average-ranking.
+It utilizes meta knowledge to suggest a ranking of classifiers for a new data sets, which in this case consist of recorded past performances of classifiers on data sets.
+That means this algorithms aggregates the performances of classifiers on all rankings once and then always recommends the same ranking.
+The new measures is integrated here by, instead of ordering only according to performance values, the classifiers are ordered according to the combined measure A3R.
 
-% Could do ranking by evaluating on the spot (active testing)
+% Active testing A3R
 
-% Another interesting thing is that both of these could be improved by incorporating time
-% Speeding up algorithm selection
-\cite{DBLP:journals/ml/AbdulrahmanBRV18}
+% Introduce loss curves and how the measure influences them
 
@@
 
+\tikzsetnextfilename{MLPlanTasks}
 \begin{figure}

### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex
more writing

@@
 In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section where observed.
-This includes which classifiers and data sets where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.
+This includes which classifiers, data sets and meta features where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.
 
-% Which classifiers and data sets used
-The classifiers considered for a recommended ranking were the learning algorithms implemented in WEKA that are fit for classification, excluding meta and ensemble methods.
+% Which classifiers 
+The classifiers considered in the rankings were the learning algorithms implemented in WEKA that are fit for classification, excluding meta and ensemble methods.
 The full list of the 22 classifiers can be gathered from Table \ref{tab:bestAlgorithmRanking}.
@@
 
-datasets
+% Which data sets
+Data sets for the analysis where gathered from OpenML.
+From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved and with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand where selected.
+Only data sets with a defined, nominal target feature that are in the .ARFF format and where not specifically designed for streaming analysis\footnotemark{} where considered, which resulted in a reduced selection of 812 instances.
+Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features where removed as well, leading to a final selection of 448 data sets.
+Even though evaluation was only carried out on the shorter list, both the list of 812 and 448 data sets are included in the supplementary material for completeness.
+
+\footnotetext{Data sets that contained the substring 'BNG' for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network\cite{van2014algorithm} for the sake of data stream analysis where not included in the evaluation.}
+
+% Which meta features
+As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used.
+Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew.
+Meta features where calculated with the help of an implementation provided by OpenML .Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
 
@@
 No timeouts where used in this evaluation, and the rankers where evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values where recorded, they where trained with the meta data - performance examples for n - 1 data sets, and queried for the remaining data set.
-As n = 448 in this case, the full results are not included in the discussion of the results.
+As n = 448 in this case, the detailed values for each data set are not included in the discussion of the results.
 They can, however, be found in the supplementary material, offering clues to how each ranker performed in the prediction of a ranking for each of the used data sets, identified by their ID on OpenML.

### 2018-02-12 Writing/Thesis/content/chapter-fundamentals.tex
even more writing

@@
 The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants.
-While this model will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.
+While this model (illustrated in Fig.
+\ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.
 
@@
 
-In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ that represents an ideal way of identifying iris species \cite{abu2012learning}.
+%\tikzsetnextfilename{DecisionTree}
+\begin{figure}
+\includegraphics[width=\textwidth]{gfx/placeholder_decisionTree}
+\caption{PLACEHOLDER: The decision tree constructed as a simple model in the gardening example to classify iris species}
+\label{fig:decision_tree}
+\end{figure}
+
+In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species.
 $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant.
@@
 
-%TODO include picture of the decision tree that is built & of the general ML-Model (from book)
+\begin{figure}
+\includegraphics[width=\textwidth]{gfx/placeholder_learning}
+\caption{PLACEHOLDER: The learning problem, adapted from \cite{abu2012learning}}
+\label{fig:learning_problem}
+\end{figure}
 
@@
 
+general measure predictive accuracy (e.g. go back to example gardener model is not perfect so miss classifies some instancs if want to know how good exactly, how find out?
+
 - estimation using cross validation (monte carloMCCV)

### 2018-02-12 ranker/src/main/java/ranker/core/algorithms/BestAlgorithmRanker.java
fix bug in best algorithm ranker

@@ -47,31 +47,51 @@ public class BestAlgorithmRanker extends PreferenceRanker {
 
 				// Find first (which algorithm is the first one in the ranking)
 				for (int k = 0; k < ranking.size(); k++) {
+
 					// First cannot be one that is already better
-					if (!bestRanking.contains(ranking.get(k))) {
-						// Increment score
-						for (Classifier cl : scores.keySet()) {
-							if (ranking.get(k).getClass().getName().equals(cl.getClass().getName())) {
-								int previousScore = scores.get(cl);
-								int newScore = previousScore + 1;
-								scores.put(ranking.get(k), newScore);
-								break;
-							}
+					boolean alreadyRanked = false;
+					for (Classifier bestClassifier : bestRanking) {
+						if (bestClassifier.getClass().getName().equals(ranking.get(k).getClass().getName())) {
+							alreadyRanked = true;
+							break;
 						}
-						// After found the first one, can stop
-						break;
 					}
+
+					if (alreadyRanked) {
+						continue;
+					}
+
+					// Increment score
+					for (Classifier cl : scores.keySet()) {
+						if (ranking.get(k).getClass().getName().equals(cl.getClass().getName())) {
+							int previousScore = scores.get(cl);
+							int newScore = previousScore + 1;
+							scores.put(cl, newScore);
+							break;
+						}
+					}
+					
+					// After found the first one, can stop
+					break;
 				}
 			}
 
 			// Find algorithm that is ranked first most often
 			Classifier bestClassifier = null;
 			int highScore = -1;
-			for (Classifier classifier : scores.keySet()) {
-				int score = scores.get(classifier);
-				if (score > highScore) {
-					bestClassifier = classifier;
-					highScore = score;
+
+			// Iterate over classifiers in order!
+			for (int attributeIndex : targetAttributes) {
+				for (Classifier classifier : scores.keySet()) {
+					if (classifier.getClass().getName()
+							.equals(classifiersMap.get(attributeIndex).getClass().getName())) {
+						int score = scores.get(classifier);
+						if (score > highScore) {
+							bestClassifier = classifier;
+							highScore = score;
+						}
+						break;
+					}
 				}
 			}
 
@@ -87,7 +107,7 @@ public class BestAlgorithmRanker extends PreferenceRanker {
 	public List<Classifier> predictRankingforInstance(Instance instance) {
 		return bestRanking;
 	}
-	
+
 	public List<Integer> getClassifierStats() {
 		return classifierStats;
 	}

### 2018-02-12 Writing/Thesis/content/chapter-approach.tex

@@
 
-META FEATURES USED!
+\subsection{Classifiers}
 
-for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before
+\subsection{Regression and Preference Learning}
+
+\subsection{Meta Features}
+META FEATURES USED! \cite{OpenML2013}
+
+\subsection{Other Used Implementations}
+for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before analysis
+apache commons implementation for Kendall Rank correlation as well
+JAICore implementation for stratified split of data set

### 2018-02-12 Writing/Thesis/content/chapter-conclusion.tex

@@
 
-% Summary of findings and limitations: what has been covered
-- Results -
+% Summary of findings and limitations: what has been covered LIMITATION: SMALL DATA SETS ESP!!
+The evaluation showed a significant advantage regarding the Kendall rank correlation for all tested methods in comparison to the best algorithm baseline, except instance based label ranking in the standard configuration and label ranking by pairwise comparison for the full meta data.
+However, regarding the practically possibly more important measure of best three loss, only the three regression based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage.
+When evaluating best three loss on reduced meta data that does not incorporate probing, although the evaluated data indicates a slight advantage of those same regression models over the baseline still, it is not statistically significant anymore.
+Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the best three loss and loss for both evaluation on the full and reduced meta data.
+Thus it can be included that a regression based approach seems to be generally more promising than the preference based approach, but is not better than the baseline regarding the best three loss when evalluated on the selected meta data without probing.
+
+One of the main limitations of the findings in this thesis is that the data sets used in the evaluation process where not very large, being limited to a maximum of 100 features and 1000 instances.
+Often, data sets can get much larger and the question whether this ranking approach would then still pose an efficient and, maybe even more importantly accurate enough solution for predicting classifiers remains.
 
@@
 An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features.
-Different sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features.
+Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features.
+Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting.
+One could consider adding the meta feature groups for DecisionStump with two folds, RandomTree with a depth of two with two folds, REPTree with a depth of two and two folds, and J48.0001 with two folds, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation times for the meta features in the mean, which seems to be reasonable.
+An effect on the time and quality of predictions for larger data sets would have to be examined still.
 
@@
 This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.
+Furthermore, the building and predictions for the regression models could be parallelized and evaluated on a cluster to simulate and test  the usage of the ranking tool in a productive environment.
 

### 2018-02-12 Writing/Thesis/content/chapter-evaluation.tex

@@
 These include the Kendall rank correlation coefficient, loss and best three loss.
+For all three measures, it is computed if any advantages or disadvantages one solutions has is significant, by means of the Mann-Whitney U.
 The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted.
@@
 Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew.
-Meta features where calculated with the help of an implementation provided by OpenML .Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
+Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
 
@@
 
-In the results mainly as so many data sets only taked about mean values but the full results with related to the specific data set id are included in supplementary material.
-
-% Results of Base Algorithms and full meta features
-% - scatter plot dataset -> best preferenceRanker, best regressionRanker, bestAlgorithmbaseline each Kendall
-
-% Results include the 4 evals on all sets, how long predictions took.
-Meta feature calc times sperately, but may give avg of comp+predict time each time meta feature values table in appendix with mean,min,max stdev
-
-% When removing probing
-
-% When removing expensive meta features
-
-% Results of optimized variants? full / no probing / no expensive
-
-% Insights about classifiers: place best ranking, min, max rank (optional) for each classif?
+In the following subsections, results of the evaluation are discussed in detail.
+First, the quality of the predictions of the rankers is examined.
+Then, the times required for building the rankers and for predictions made as well as for the calculation of the meta features is reviewed.
+Last, additional insights gathered during the evaluation are pointed out.
 
 \subsection{Accuracy}
+
+- on the full meta data set, all approaches except for instance based with kemeny young and pairwise comparison
 
@@
 
-\input{tables/metaFeatureTimes}
-\ref{tab:metaFeatureTimes}
-
 \input{tables/significanceResults}
@@
 
-\addtocounter{footnote}{-2}
-\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
-\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
+\tikzsetnextfilename{LossGraphics}
+\begin{figure}
+\pgfplotsset{width=.5\textwidth}
+\begin{tikzpicture}
+\begin{axis}[ylabel={BestThreeLoss}, xlabel={Data Set}]
+\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
+\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
+\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
+\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
+\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
+\end{axis}
+\end{tikzpicture}%
+~%
+%
+%\begin{tikzpicture}
+%\begin{axis}[ymin=-5, ymax=25,ylabel={BestThreeLoss}, xlabel={Data Set}]
+%\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
+%\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
+%\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
+%\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
+%\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
+%\end{axis}
+%\end{tikzpicture}
+\caption{The Best Three Loss for the Best Algorithm Baseline and the Random Forest Ranker (Full Meta Data)}
+\label{fig:lossGraphics}
+\end{figure}
 
-\tikzsetnextfilename{LossGraphics}
-\pgfplotsset{width=\textwidth}
-\begin{tikzpicture}
-\begin{axis}
-\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
-\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
-\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
-\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
-\legend{IB Label KY, Best Algorithm}
-\end{axis}
-\end{tikzpicture}
+\subsection{Computation Times}
 
-\tikzsetnextfilename{BestThreeLossGraphics}
-\pgfplotsset{width=\textwidth}
-\begin{tikzpicture}
-\begin{axis}
-\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
-\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
-%\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
-%\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
-\legend{IB Label KY, Best Algorithm}
-\end{axis}
-\end{tikzpicture}
-
-\subsection{Build and Prediction Times}
+Because the ranking itself is implemented as a means of speeding up the process of algorithm selection, the time it takes to rank is not negligible.
+The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}.
+Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible anyways.
+The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves.
+However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker likewise.
+The Random Forest ranker, for example, is the ranker with the highest build time, and also with the rankings of the generally highest quality.
+But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds.
+Furthermore, while the build times are higher, these are not as important due to the fact that each model only needs to be trained once.
+Although in a real-world scenario, calculation times for meta features also have to be taken into account when ranking, which therefore will be discussed in the following paragraph.
 
 \input{tables/times}
-\ref{tab:times}
-%TODO add values for pairwise comparision in this table
+
+Table \ref{tab:metaFeatureTimes} shows the times required For the full meta features, on average approximately 135 milliseconds would be added to the prediction times 3 milliseconds whithout probing
+
+\input{tables/metaFeatureTimes}
 
@@
 
+Further insights to be noted are the accuracy of predictions of performance values for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline.
+The accuracy of the predictions achieved by the regression based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively.
+The first thing that attracts attention in this table is the absurdly high values for Linear Regression and M5P, however, these are all caused by the very high maximum value on one data set with id 685.
+If these extreme maxima remain out of consideration for Linear Regression and M5P (the other algorithms do not have this problem) more reasonable values are obtained.
+For M5P, on the full meta data the new maximum is 311.526, mean 8.127 and standard deviation 18.407; on the reduced meta data it is a maximum of 474.692, mean 15.444 and standard deviation 27.433.
+For Linear Regression, on the full meta data the new maximum is 142.996, mean 9.281 and standard deviation 8.438; on the reduced meta data it is a maximum of 131.456, mean 14.351 and standard deviation 10.299.
+However, these values are still worse than the ones obtained for the Random Forest and REPTree variants.
+It comes as little surprise that the Random Forest Ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful.
+
 \input{tables/rootMeanSquareError}
-\ref{tab:rootMeanSquareError}
+
+The second interesting thing to consider is the ranking which is created by the best algorithm baseline.
+This ranking constitutes meta-knowledge about the learning process itself in that it shows which algorithms are generally a good choice for many data sets.
+This ranking is depicted in Table \ref{tab:bestAlgorithmRanking}.
+The table is to be read top to bottom; of the 22 algorithms, the algorithm in the ith row is placed first on most data sets when compared to the next 22-i algorithms.
+The associated number represents the number of data sets on which the algorithm was placed first.
+It is, however, not a particularly surprising result, as for example the placement of Random Forest as the first algorithm was to be expected.
+Random Forest is a learning algorithm that is known to often deliver good performances, which was proven again in the results discussed previously - out of the reviewed ranking approaches, Random Forest was the best choice.
 
 \input{tables/bestAlgorithmRanking}
-\ref{tab:bestAlgorithmRanking}

### 2018-02-12 Writing/Thesis/content/chapter-related-work.tex

@@
 They call this combined measure of accuracy and time A3R, and integrate it into to different ranking approaches.
+In both cases, this lead to a better mean interval loss, which is a measure that expresses the mean loss experienced in respect to the time that has been allowed for the construction of the ranking.
 
@@
 % Active testing A3R
-
-% Introduce loss curves and how the measure influences them
+The second approach does not initially use meta knowledge and is called active testing.
+Active testing is a strategy that 'intelligently select the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
+Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set.
+The authors aim to improve this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation, incorporating time in the estimations made by the strategy which previously only compared accuracy values.
 

### 2018-02-12 Writing/Thesis/content/chapter-conclusion.tex
more writing

@@
 Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the best three loss and loss for both evaluation on the full and reduced meta data.
-Thus it can be included that a regression based approach seems to be generally more promising than the preference based approach, but is not better than the baseline regarding the best three loss when evalluated on the selected meta data without probing.
+Thus it can be included that a regression based approach seems to be generally more promising than a preference based approach, but is not better than the baseline regarding the best three loss when evaluated on the selected meta data without probing.
+Out of the regression based variants, random forest seems to be the most promising one.
 
-One of the main limitations of the findings in this thesis is that the data sets used in the evaluation process where not very large, being limited to a maximum of 100 features and 1000 instances.
-Often, data sets can get much larger and the question whether this ranking approach would then still pose an efficient and, maybe even more importantly accurate enough solution for predicting classifiers remains.
+The main limitation of the findings in this thesis is that the data sets used in the evaluation process where not very large, being limited to a maximum of 100 features and 1000 instances.
+Often, data sets can get much larger and the question whether this ranking approach would then still pose an efficient regarding calculation of meta features and prediction times and, maybe even more importantly, an accurate enough solution for predicting classifiers remains.
 
 % Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
-On the basis of these results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
+On the basis of these results, it can be concluded that a there is an indication of a connection between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
 A practical application of these findings, apart from the direct use as a ranker, may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
@@
 For this, the tool does not even need to be adapted, as it is agnostic to the semantics behind the measure it predicts, it only needs to be numeric.
-One possibility for this would be the prediction of build or prediction times of learning algorithms, or a measure that combines time and accuracy \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
+One possibility for this would be the prediction of build or prediction times of learning algorithms, or a measure that combines time and accuracy like A3R \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
 
@@
 Last, it could be interesting to implement an additional baseline that averages ranks instead of counting how many times an algorithm is ranked first.
-This would help to determine if the surprising ranking returned by the best algorithm baseline (see Fig.
+This would help to determine if the ranking returned by the best algorithm baseline (see Fig.
 \ref{tab:bestAlgorithmRanking}

### 2018-02-12 Writing/Thesis/content/chapter-evaluation.tex
more writing

@@
 These include the Kendall rank correlation coefficient, loss and best three loss.
-For all three measures, it is computed if any advantages or disadvantages one solutions has is significant, by means of the Mann-Whitney U.
+For all three measures, it is computed if any advantage or disadvantage one solutions has is significant, by means of the Mann-Whitney U and its P-value.
 The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted.
@@
 This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot bet computed.
-Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, which will be determined by calculating the Mann-Whitney U and determining whether its P-value.
+Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline.
 
@@
 Data sets for the analysis where gathered from OpenML.
-From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved and with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand where selected.
-Only data sets with a defined, nominal target feature that are in the .ARFF format and where not specifically designed for streaming analysis\footnotemark{} where considered, which resulted in a reduced selection of 812 instances.
+From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand where selected.
+Only data sets with a defined, nominal target feature that are in the .ARFF format which where not specifically designed for streaming analysis\footnotemark{} where considered, which resulted in a reduced selection of 812 instances.
 Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features where removed as well, leading to a final selection of 448 data sets.
@@
 
-\footnotetext{Data sets that contained the substring 'BNG' for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network\cite{van2014algorithm} for the sake of data stream analysis where not included in the evaluation.}
+\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis where not included in the evaluation.}
 
@@
 Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew.
-Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
+Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.
+Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
+Since the meta data also includes probing, which is generally an expensive operation and furthermore does not aid in proving the point of a connection of properties of a data set and the performance of classifiers, additionally to the full meta features all evaluation measures where computed without using those meta features that use probing.
 
@@
 % How rest of the evaluation carried out
-All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) and 12 GB RAM.
+All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) with 12 GB RAM.
 It is notable that especially the time-related results are to be viewed in regard to this setup.
@@
 
-- on the full meta data set, all approaches except for instance based with kemeny young and pairwise comparison
+When looking at the results depicted in Table \ref{tab:evaluationResults}, it must first be noted that positive findings regarding the Kendall rank correlation can be reported.
+For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults} which shows the results of the significance tests, with random forest having the highest correlation of 0.495.
+In contrast, the two approaches that did not overtake the baseline, instance based label ranking in the default configuration and label ranking by pairwise comparison, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches.
+Regarding loss, only linear regression and random forest show a significant advantage, with all label ranking approaches except for instance based label ranking having a significant disadvantage in contrast.
+Moving on to best three loss, the picture largely remains the same, except that surprisingly, REPTree now also has a significant advantage over the baseline.
+The lowest value here is achieved by random forest with a best three loss of 1.308, in comparison to 2.440 for the best algorithm baseline.
+These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual best three loss values on the data sets.
+
+Compared to the evaluation on the full set of meta data, the results on the reduced set without out probing are less distinctive.
+For the Kendall Rank correlation, linear regression, M5P and random forest are significantly better than the baseline, and for label ranking, both of the instance based approaches with non-default parameters as well, while the other label ranking approaches are significantly worse than the baseline.
+In total, random forest is still the best alternative with a correlation of 0.439, slightly worse than the correlation achieved on the full meta data.
+For both loss measures however, while the disadvantages of the label ranking approaches remain, none of the eight alternatives achieves a significantly better loss or best three loss than the baseline anymore.
+
+Summarizing the observed results, in general, a regression based approach shows an indication to be stronger than a preference based approach.
+Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often.
 
@@
 The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}.
-Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible anyways.
+Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible.
 The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves.
-However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker likewise.
+However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker.
 The Random Forest ranker, for example, is the ranker with the highest build time, and also with the rankings of the generally highest quality.
@@
 
-Table \ref{tab:metaFeatureTimes} shows the times required For the full meta features, on average approximately 135 milliseconds would be added to the prediction times 3 milliseconds whithout probing
+Table \ref{tab:metaFeatureTimes} shows the times required for the computation of groups of meta features as discussed in chapter \ref{sec:approach}.
+As can be taken from the table, the computation of the full meta features takes approximately 135 milliseconds on average, while the simple meta features without probing add approximately 3 milliseconds to the prediction times on average.
+Regarding these computation times it is also notable that among the probing meta feature groups, some are considerably more expensive than others, so that in the future it might be sensible to consider only light probing with probing meta feature groups that are not as expensive.
 
@@
 It comes as little surprise that the Random Forest Ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful.
+The usefulness is dependent on the task these predictions would be used for an whether if requires very accurate predictions of performance values.
 

### 2018-02-12 Writing/Thesis/content/chapter-related-work.tex
more writing

@@
 % Incorporating times
-In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifier \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
-They call this combined measure of accuracy and time A3R, and integrate it into to different ranking approaches.
-In both cases, this lead to a better mean interval loss, which is a measure that expresses the mean loss experienced in respect to the time that has been allowed for the construction of the ranking.
+In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifiers \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
+They call this combined measure of accuracy and time A3R, and integrate it into two different ranking approaches.
+In both cases, the authors find that this leads to a better mean interval loss, which is a measure that expresses the mean loss experienced in respect to the time that has been allowed for the construction of the ranking, that is time taken to evaluate top-ranked classifiers.
 

### 2018-02-13 Writing/Thesis/content/chapter-approach.tex
more writing
more writing + adding some picture

@@
 
-In this chapter the two alternatives which ar
+In this chapter the two alternatives to tackle the problem of ranking classification algorithms regarding properties of the data set based on past performance values are described in detail.
+First, the theoretical approach is presented.
+Then, implementation details are discussed.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=1]{gfx/regression_models.pdf}
+\caption{A model of the regression based ranker}
+\label{fig:regression_ranker_model}
+\end{figure}
+
 % How is the preference ranking done
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
+\caption{A model of the preference based ranker}
+\label{fig:preference_ranker_model}
+\end{figure}
+
 \section{Implementation}
@@
 JAICore implementation for stratified split of data set
+
+\subsection{Frameworks used}
+% Weka for classifiers
+
+% Data sets from OpenML
+
+\subsection{jPL framework}
+The jPL framework is a java framework for the evaluation of preference learning algorithms.
+It implements several tasks from the context of preference learning, including label ranking.
+Furthermore, the framework introduces the Generic Preference Representation Format (GPRF) to store preference information.
+
+\subsection{WEKA}
+
+% openml Webapp for metaFeature implementation except default accuracy
+
+\section{Generating Performance Values}
+Performance values generated by
+
+\section{Stuff}
+
+Rankers trained with data set of the following form, so each ranking algorithm can derive its on performance

### 2018-02-13 Writing/Thesis/content/chapter-approach.tex
table and figure overhaul

--- 2018-02-11 Writing/Thesis/content/chapter-approach.tex
@@
 		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
-		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ \hline
-		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ \hline
-		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ \hline
+		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
+		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
+		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
 		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
 	\end{tabularx}
-	\label{tab:table1}
+	\label{tab:performanceValues}
 	\caption{This is a caption text.}
@@
 
+\subsection{Regression Based Ranking}
 % How is the regression ranking done
@@
 \centering
-	\begin{tabularx}{\textwidth}{X | X | X | X}
+\resizebox{\textwidth}{!}{%
+	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
 		%\hline
 		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
-		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ \hline
-		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ \hline
-		...				& ...	& ...				& ...					\\ \hline
+		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
+		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
+		...				& ...	& ...				& ...					\\ 
 		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
 		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
-		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ \hline
-		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ \hline
-		...				& ...	& ...				& ...					\\ \hline
+		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
+		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
+		...				& ...	& ...				& ...					\\ 
 		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
 	\end{tabularx}
-
+}	
 \vspace{1em}
@@
 \vspace{1em}	
-
-	\begin{tabularx}{\textwidth}{X | X | X | X}
+\resizebox{\textwidth}{!}{%
+	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
 		%\hline
 		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
-		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ \hline
-		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ \hline
-		...				& ...	& ...				& ...					\\ \hline
+		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
+		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
+		...				& ...	& ...				& ...					\\ 
 		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
 	\end{tabularx}
-
-	\label{tab:table1}
+}
+	\label{tab:regressionTables}
 	\caption{This is a caption text.}
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=1]{gfx/regression_models.pdf}
+\caption{A model of the regression based ranker}
+\label{fig:regression_ranker_model}
+\end{figure}
+
+\subsection{Preference Based Ranking}
 % How is the preference ranking done
@@
 		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
-		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ \hline
-		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ \hline
-		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\ \hline
+		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
+		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\
+		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\
 		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
 	\end{tabularx}
-	\label{tab:table1}
+	\label{tab:preferenceTable}
 	\caption{This is a ranking}
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
+\caption{A model of the preference based ranker}
+\label{fig:preference_ranker_model}
+\end{figure}
+
 \section{Implementation}
+% regression based model - weka used
 
-META FEATURES USED!
+% preference learning
+The jPL framework is a java framework for the evaluation of preference learning algorithms. It implements several tasks from the context of preference learning, including label ranking.
 
-for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before
+% meta features - openML webapp
+\cite{OpenML2013}
+% Which meta features
+As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used.
+Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew.
+Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.
+Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
+Since the meta data also includes probing, which is generally an expensive operation and furthermore does not aid in proving the point of a connection of properties of a data set and the performance of classifiers, additionally to the full meta features all evaluation measures where computed without using those meta features that use probing.

### 2018-02-13 Writing/Thesis/content/chapter-evaluation.tex
table and figure overhaul

@@
-% !TEX root = ../my-thesis.tex
-%
 \chapter{Evaluation}
@@
 % Evaluation Measures used & computed
-As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{chapter:fundamentals}.
+As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}.
 These include the Kendall rank correlation coefficient, loss and best three loss.
@@
 
-% Which meta features
-As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used.
-Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew.
-Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.
-Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
-Since the meta data also includes probing, which is generally an expensive operation and furthermore does not aid in proving the point of a connection of properties of a data set and the performance of classifiers, additionally to the full meta features all evaluation measures where computed without using those meta features that use probing.
+% How base performance data generated
+The performance data of the classifiers for the selected data sets was generated on a linux cluster, each node consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 16GB RAM with usage of up to 150 nodes.
+There was a timeout of eight hours set for the computation of a single performance value of a classifier on a data set.
+For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
+When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.
 
-% How base performance data generated
-The performance data of the classifiers for the selected data sets was generated on [MACHINE DETAILS].
-[TIMEOUT AND HARDWARE ALLOCATION DETAILS].
-For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
-When a timeout occurred, the predictive accuracy was set to 0.
+%TODO integrate DONT FORGET META FEAUTRES (WHY EVERYTHING X2??)
+for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before analysis
+apache commons implementation for Kendall Rank correlation as well
+JAICore implementation for stratified split of data set
 
@@
 \input{tables/evaluationResults}
-\ref{tab:evaluationResults}
 
 \input{tables/significanceResults}
-\ref{tab:significanceResults}
 
@@
 \begin{figure}
-\pgfplotsset{width=.5\textwidth}
+%\pgfplotsset{width=\textwidth}
+\resizebox{\textwidth}{!}{%
 \begin{tikzpicture}
-\begin{axis}[ylabel={BestThreeLoss}, xlabel={Data Set}]
+\begin{axis}[
+	title=regular scale,
+	height=\textwidth,
+	width=\textwidth,
+	ylabel={BestThreeLoss}, 
+	xlabel={Data Set},
+]
 \addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
@@
 \addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
+\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
 \legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
@@
 %
-%\begin{tikzpicture}
-%\begin{axis}[ymin=-5, ymax=25,ylabel={BestThreeLoss}, xlabel={Data Set}]
-%\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
-%\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
-%\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
-%\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
-%\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
-%\end{axis}
-%\end{tikzpicture}
-\caption{The Best Three Loss for the Best Algorithm Baseline and the Random Forest Ranker (Full Meta Data)}
+\begin{tikzpicture}
+\begin{axis}[
+	title=log scale (base 2),
+	height=\textwidth,
+	width=\textwidth,
+	ylabel={BestThreeLoss}, 
+	xlabel={Data Set},
+	ymode=log,
+	log basis y={2}
+]
+\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
+\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
+\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
+\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
+\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
+\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
+\end{axis}
+\end{tikzpicture}
+}
+\caption{The Best Three Loss for the Best Algorithm Baseline and Random Forest Ranker (Full Meta Data)}
 \label{fig:lossGraphics}

### 2018-02-13 Writing/Thesis/content/chapter-fundamentals.tex
more writing
table and figure overhaul

@@
-% !TEX root = ../my-thesis.tex
-%
 \chapter{Fundamentals}
@@
 \begin{table}[h]
-	\begin{tabularx}{\textwidth}{>{\hsize=1.1\hsize}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X  >{\hsize=1.7\hsize}X}
+	\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | X}
 		%\hline
-		Feature	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal width}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal width} 	& Species			\\ \hline
-				& 5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
-				& 5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
-				& 5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
-				& 5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
-				& 6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
-				& 5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
-				& 7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
-				& 5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
-				& 6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
+		\multicolumn{1}{X}{Sepal length}	& \multicolumn{1}{X}{Sepal width}	& \multicolumn{1}{X}{Petal length}	& \multicolumn{1}{X}{Petal width} & Species			\\ \hline
+				5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
+				5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
+				5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
+				5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
+				6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
+				5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
+				7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
+				5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
+				6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
 	\end{tabularx}
+	\caption{The information the gardener in the example could have gathered; this is an excerpt from the well known iris data set \cite{iris}}
 	\label{tab:iris}
-	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context).
-The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
 \end{table}
@@
 	\end{tabularx}
-	\label{tab:ranking_vs_ordering}
 	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context).
 The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
+	\label{tab:ranking_vs_ordering}
 \end{table}
@@
 experience to generate additional knowledge that can simplify the automatic
-selection of efficient models summarizing the data' \cite{razdil2008metalearning}.
+selection of efficient models summarizing the data' \cite{brazdil2008metalearning}.
 

### 2018-02-13 Writing/Thesis/content/chapter-related-work.tex
more writing + adding some picture
table and figure overhaul

@@
 
-\tikzsetnextfilename{MLPlanTasks}
+%\tikzsetnextfilename{MLPlanTasks}
 \begin{figure}
-\tikzset{edge from parent/.style={draw,->}}
-\begin{tikzpicture}[sibling distance=10em,
-  every node/.style = {shape=rectangle, rounded corners,
-    draw, align=center}]]
-  \node {\textcolor{uniblue}{classify}}
-    child { node {...} }
-    child { node {\textcolor{uniblue}{classifyWithNN}}
-    child { node {...} }
-      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
-        child { node {...} }
-        child { node {...} 
-          child { node {...}  }
-          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } } } }
-    };
-\end{tikzpicture}
-\caption{An example for how the complex task 'classify' might be broken down by ML-Plan.
-The figure is loosely adapted from \cite{wever2017automatic}.
-Nodes containing '...' represent an undefined number of subtrees.
-\textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
+\centering
+%\tikzset{edge from parent/.style={draw,->}}
+%\begin{tikzpicture}[sibling distance=10em,
+%  every node/.style = {shape=rectangle, rounded corners,
+%    draw, align=center}]]
+%  \node {\textcolor{uniblue}{classify}}
+%    child { node {...} }
+%    child { node {\textcolor{uniblue}{classifyWithNN}}
+%    child { node {...} }
+%      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
+%        child { node {...} }
+%        child { node {...} 
+%          child { node {...}  }
+%          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } %} } }
+%    };
+%\end{tikzpicture}
+\includegraphics[width=.8\textwidth]{gfx/MLPlan.pdf}
+\caption{An example for how the complex task 'classify' might be broken down by ML-Plan, adapted from \cite{wever2017automatic}. Nodes containing '...' represent an undefined number of subtrees.}
 \label{fig:mltree}

### 2018-02-14 ranker/src/main/java/ranker/Main.java
add toString for GlobalCharacterizer

@@ -44,17 +44,17 @@ public class Main {
 
 	public static void main(String[] args) throws Exception {
 
-//		List<Integer> datasets = OpenMLHelper.getDataSetsFromIndex();
-//		// List<Integer> datasets = Arrays.asList(3,4,5);
-//		Instances instances1 = MetaFeatureHelper.computeMetaFeatures(datasets);
-//		ArffSaver saver = new ArffSaver();
-//		saver.setInstances(instances1);
-//		try {
-//			saver.setFile(new File(instances1.relationName() + ".arff"));
-//			saver.writeBatch();
-//		} catch (IOException e) {
-//			e.printStackTrace();
-//		}
+		// List<Integer> datasets = OpenMLHelper.getDataSetsFromIndex();
+		// // List<Integer> datasets = Arrays.asList(3,4,5);
+		// Instances instances1 = MetaFeatureHelper.computeMetaFeatures(datasets);
+		// ArffSaver saver = new ArffSaver();
+		// saver.setInstances(instances1);
+		// try {
+		// saver.setFile(new File(instances1.relationName() + ".arff"));
+		// saver.writeBatch();
+		// } catch (IOException e) {
+		// e.printStackTrace();
+		// }
 
 		// BufferedReader reader =
 		// Files.newBufferedReader(FileSystems.getDefault().getPath("meta_computed.arff"),
@@ -88,8 +88,8 @@ public class Main {
 		// }
 
 		// Trying to save a .csv
-//		 Path path = FileSystems.getDefault().getPath("datatest.csv");
-//		 BufferedWriter writer = Files.newBufferedWriter(path, Util.charset);
+		// Path path = FileSystems.getDefault().getPath("datatest.csv");
+		// BufferedWriter writer = Files.newBufferedWriter(path, Util.charset);
 		//
 		// writer.write("1");
 		// writer.write(seperator);
@@ -110,89 +110,186 @@ public class Main {
 		// writer.flush();
 		// writer.close();
 
-//		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues_noID.arff"),
-//				Util.charset);
-//
-//		Instances instances = new Instances(reader);
-//		BestAlgorithmRanker ranker = new BestAlgorithmRanker();
-//		
-//		List<Integer> targetAttributes = new ArrayList<Integer>();
-//		for (int i = 103; i < 125; i++) {
-//			targetAttributes.add(i);
-//		}
-//		
[…]

### 2018-02-14 ranker/src/main/java/ranker/core/metafeatures/GlobalCharacterizer.java

@@ -116,6 +116,23 @@ public class GlobalCharacterizer extends Characterizer {
 		}
 		return result;
 	}
+	
+	@Override
+	public String toString() {
+		StringBuilder builder = new StringBuilder();
+		
+		for (Characterizer characterizer : batchCharacterizers) {
+			builder.append(characterizer.toString());
+			builder.append(System.lineSeparator());
+			String[] ids = characterizer.getIDs();
+			for (String id : ids) {
+				builder.append(id + ",");
+			}
+			builder.append(System.lineSeparator());
+		}
+		
+		return builder.toString();
+	}
 
 }
 

### 2018-02-14 Writing/Thesis/content/chapter-appendix.tex
more writing
more table and figure overhaul

@@
 %
-\chapter{Example Appendix}
+\chapter{Appendix}
 \label{sec:appendix}
 
-\section{Appendix Section 1}
-\label{sec:appendix:sec1}
+\begin{table}[h]
+\centering
+	\begin{tabularx}{\textwidth}{X}
+	\multicolumn{1}{>{\centering\arraybackslash}X}{Meta Feature Group} \\
+	\hline \hline
+	\multicolumn{1}{>{\centering\arraybackslash}X}{NominalAttDistinctValues} \\ \hline
+	MaxNominalAttDistinctValues, MinNominalAttDistinctValues, MeanNominalAttDistinctValues, StdvNominalAttDistinctValues \\ \hline
+	\multicolumn{1}{>{\centering\arraybackslash}X}{SimpleMetaFeatures} \\ \hline
+	NumberOfInstances, NumberOfFeatures, NumberOfClasses, Dimensionality, NumberOfInstancesWithMissingValues, NumberOfMissingValues, PercentageOfInstancesWithMissingValues, PercentageOfMissingValues, NumberOfNumericFeatures, NumberOfSymbolicFeatures, NumberOfBinaryFeatures, PercentageOfNumericFeatures, PercentageOfSymbolicFeatures, PercentageOfBinaryFeatures, MajorityClassSize, MinorityClassSize, MajorityClassPercentage, MinorityClassPercentage, AutoCorrelation \\ \hline
+	\multicolumn{1}{>{\centering\arraybackslash}X}{Cardinality} \\ \hline
+	MeanCardinalityOfNumericAttributes, StdevCardinalityOfNumericAttributes, MinCardinalityOfNumericAttributes, MaxCardinalityOfNumericAttributes, MeanCardinalityOfNominalAttributes, StdevCardinalityOfNominalAttributes, MinCardinalityOfNominalAttributes, MaxCardinalityOfNominalAttributes, CardinalityAtTwo, CardinalityAtThree, CardinalityAtFour \\ \hline
+	\multicolumn{1}{>{\centering\arraybackslash}X}{Statistical} \\ \hline
+	MeanMeansOfNumericAtts, MeanStdDevOfNumericAtts, MeanKurtosisOfNumericAtts, MeanSkewnessOfNumericAtts, MinMeansOfNumericAtts, MinStdDevOfNumericAtts, MinKurtosisOfNumericAtts, MinSkewnessOfNumericAtts, MaxMeansOfNumericAtts, MaxStdDevOfNumericAtts, MaxKurtosisOfNumericAtts, MaxSkewnessOfNumericAtts, Quartile1MeansOfNumericAtts, Quartile1StdDevOfNumericAtts, Quartile1KurtosisOfNumericAtts, Quartile1SkewnessOfNumericAtts, Quartile2MeansOfNumericAtts, Quartile2StdDevOfNumericAtts, Quartile2KurtosisOfNumericAtts, Quartile2SkewnessOfNumericAtts, Quartile3MeansOfNumericAtts, Quartile3StdDevOfNumericAtts, Quartile3KurtosisOfNumericAtts, Quartile3SkewnessOfNumericAtts \\ \hline
+	\multicolumn{1}{>{\centering\arraybackslash}X}{Landmarkers\footnotemark{}} \\ \hline
+	DecisionStump, RandomTreeDepth1, RandomTreeDepth2, RandomTreeDepth3, REPTreeDepth1, REPTreeDepth2, REPTreeDepth3, J48.001., J48.0001., J48.00001., NaiveBayes, kNN1N, CfsSubsetEval kNN1N, CfsSubsetEval NaiveBayes, CfsSubsetEval DecisionStump \\
+	\end{tabularx}
+	\label{tab:metaFeatureDetails}
+	\caption{The meta features computed by each meta feature group. More details can be found on \href{www.openml.org}{www.openml.org}.}
+\end{table}
 
-\begin{table}[h]
-	\begin{tabularx}{\textwidth}{X | X | X}
-		%\hline
-		Alpha		& Beta			& Gamma			\\ \hline
-		0			& 1				& 2				\\ \hline
-		3			& 4				& 5				\\ %\hline
-	\end{tabularx}
-	\label{tab:table1}
-	\caption{This is a caption text.}
-\end{table}
+\footnotetext{Each landmarker represents its own group of meta features consisting of AUC, ErrRate and Kappa. All are computed with 2-fold crossvalidation.}

### 2018-02-14 Writing/Thesis/content/chapter-approach.tex
more table and figure overhaul

@@
 	\label{tab:performanceValues}
-	\caption{This is a caption text.}
+	\caption{Training data for the rankers.}
 \end{table}
@@
 	\label{tab:regressionTables}
-	\caption{This is a caption text.}
+	\caption{How the regression ranker processes the training data.}
 \end{table}
@@
 \includegraphics[scale=1]{gfx/regression_models.pdf}
-\caption{A model of the regression based ranker}
+\caption{An overview of how a regression based ranker constructs a ranking.}
 \label{fig:regression_ranker_model}
@@
 	\label{tab:preferenceTable}
-	\caption{This is a ranking}
+	\caption{How the preference ranker processes the training data.}
 \end{table}
@@
 \includegraphics[scale=1]{gfx/label_ranking_model.pdf}
-\caption{A model of the preference based ranker}
+\caption{An overview of how a preference based ranker constructs a ranking.}
 \label{fig:preference_ranker_model}

### 2018-02-14 Writing/Thesis/content/chapter-fundamentals.tex
more table and figure overhaul

@@
 The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants.
-While this model (illustrated in Fig.
-\ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.
+While this model (illustrated in Figure \ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.
 
@@
 	\end{tabularx}
-	\caption{The information the gardener in the example could have gathered; this is an excerpt from the well known iris data set \cite{iris}}
+	\caption{Features of different iris plants. This is an excerpt from the well known iris data set \cite{iris}}
 	\label{tab:iris}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{gfx/placeholder_decisionTree}
-\caption{PLACEHOLDER: The decision tree constructed as a simple model in the gardening example to classify iris species}
+\centering
+\includegraphics[scale=.75]{gfx/decision_tree.pdf}
+\caption{The decision tree constructed as a simple model  to classify iris plants in the gardening example.}
 \label{fig:decision_tree}
@@
 The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.
+An overview of this learning problem is provided in Figure \ref{fig:learning_problem}.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{gfx/placeholder_learning}
-\caption{PLACEHOLDER: The learning problem, adapted from \cite{abu2012learning}}
+\centering
+\includegraphics[width=\textwidth]{gfx/machine_learning.pdf}
+\caption{The learning problem, adapted from \cite{abu2012learning}.}
 \label{fig:learning_problem}
@@
 	\end{tabularx}
-	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context).
-The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
+	\caption{Ranking and ordering in direct comparison.}
 	\label{tab:ranking_vs_ordering}

### 2018-02-14 Writing/Thesis/content/abstract.tex
more writing
more table and figure overhaul
First draft

@@
 
-Should abstract be included?
+Although the amount of data available worldwide is increasing, the portion of analyzed data remains low.
+This problem is caused by a lack of experts in the field that are able to carry out an analysis, and the difficulty of the analysis for non-experts.
+Especially for the task of classification, there are many algorithms with variing performance values from data set to data set - there does not exist one best algorithm, which one can always recommend.
+One response to this problem is automated machine learning.
+Therefore, in this thesis, to approaches to construct a ranking of classification algorithms for a new data set, based on properties of that data set,are presented and compared.
+The first of the two alternatives works on the basis of regression models; one regression model predicts a performance value for each classifier, from which then a ranking is constructed.
+In contrast, the second, preference based model directly learns and returns rankings.
+In the evaluation it became clear that the regression based alternative is superior to the preference based approach; the best evaluated regression model, based on the random forest algorithm, achieved values of up to 0.495 for Kendall's rank correlation coefficient and a peformance loss of 1.308 percent on average.
+However, the tested preference models are superior at least to the baseline in some scenarios.
+Therefore the conlucion can be drawn that at least certain properties of data sets are connected to performance values of classification algorithms, which can be exploited by regression and preference models, although the regression approach is superior to the preference alternative within the scope of the conducted evaluation.
 
 \vspace*{20mm}
+\newpage
 
-{\usekomafont{chapter}Abstract (different language)}\label{sec:abstract-diff} \\
+{\usekomafont{chapter}Abstract (German)}\label{sec:abstract-german} \\
 
-Und falls ja, dann zweisprachig?
+% Motivation
+Die weltweit verfügbare Menge an Daten steigt immer weiter an, und doch bleibt der Anteil der tatsächlich analysierten Daten gering.
+Dieses Problem entsteht, da nicht genug Experten verfügbar sind, um diese Analyse auszuführen, und es für Laien schwierig ist, das richtige Verfahren auszuwählen.
+Besonders im Bereich der Klassifikation gibt es viele Algorithmen, deren Performanz jedoch von Datensatz zu Datensatz variieren kann - es gibt also keinen einen besten Algorithmus, der immer eine gute Wahl darstellt.
+Eine Antwort auf diese Problem ist automatisiertes Machine Learning.
+Daher werden in dieser Arbeit zwei verschiedene Ansätze, welche für einen neuen Datensatz ein Ranking von Klassifizierungsalgorithmen aufgrund von Eigenschaften des Datensatzes vorhersagt, vorgestellt und miteinander verglichen.
+Der erste der beiden Ansätze arbeitet auf Grundlage von Regressionsmodellen; ein Ranking wird hier konstruiert indem ein einzelnes Regressionsmodell für jeden Klassifizierungsalgorithmus einen Performanzwert vorhersagt, auf deren basierend dann das Ranking erstellt wird.
+Der zweite Ansatz beschäftigt sich mit Präferenzmodellen, welche direkt Rankings lernen und zurückgeben.
+In der Evaluation stellte sich heraus, dass der Regressionsansatz dem Präferenzmodell überlegen ist; das beste der getesteten Regressionsmodelle, basierend auf dem Random Forest Algorithmus, erreicht einen Wert von Kendalls Tau von bis zu 0,495 und Performanzverlustwerte von durchschnittlich nur 1,308 Prozentpunkten.
+Jedoch sind auch manche der getesten Präferenzmodelle in einigen Punkten wenigstens der zum Vergleich benutzten Baseline überlegen.
+Daher kann die Schlussfolgerung gezogen werden, dass wenigstens einige der benutzen Eigenschaften der Datensätze mit den Performanzwerten der Klassifizierungsalgorithmen zusammenhängen, und dieser Zusammenhang durch Regressionsmodelle sowohl als auch Präferenzmodelle ausgenutzt werden kann, wobei jedoch der Regressionsansatz letzterem im Rahmen der durchgeführten Evaluation überlegen ist.

### 2018-02-14 Writing/Thesis/content/chapter-approach.tex
First draft

@@
 
-In this chapter the two alternatives to tackle the problem of ranking classification algorithms regarding properties of the data set based on past performance values are described in detail.
+In this chapter the two alternatives considered in this thesis to tackle the problem of ranking classification algorithms regarding properties of the data set.
 First, the theoretical approach is presented.
@@
 
-Approach of ranking classifier implementations here realized by two concepts, regression-based and preference-based ranking, which will be explained in detail.
-Also predicting predictive accuracy here.
-Thus target function of the form $meta features^n \rightarrow classifiers^m$.
-performance measure chosen predictive accuracy
-
-% Theory of approach
-Since the aim is to generate a ranking of classification algorithms, first, performance values of a number of classifiers are recorded on a few data sets.
-Then, meta features are computed for each data set.
-This is for training the ranking model.
-This generates a table that contains all necessary informatino for training both types of rankers.
-A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently using it to query the underlying model.
+In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set.
+This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed.
+The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and n data sets.
+This approach to ranking is realized here, as pointed out before, in a regression based and preference based approach, which are explained in detail in the following sections.
 
@@
 The idea is to use separate regression models to predict a performance value for each classifier, and to then derive an ordering from these predictions.
-This is done by splitting the data set compiled beforehand into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier.
+This is done by splitting the data set compiled beforehand (see Tab.
+\ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}.
 The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus a regression model can be trained on each of them.
-All regression models therefore try to learn the target function $meta features \rightarrow classifier performance value$ for their respective classifier.
+All regression models therefore try to learn the target function metafeatures$\rightarrow$performance value for their respective classifier.
 Hence for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
 In a second step, the classifiers are ordered according to the predictions.
+This process the ranker passes through for making a prediction is presented in Figure \ref{fig:regression_ranker_model}.
 
@@
 }
+	\caption{How the regression ranker processes the training data.}
 	\label{tab:regressionTables}
-	\caption{How the regression ranker processes the training data.}
 \end{table}
@@
 The second possibility considered in this context is using preference learning to predict a ranking.
-Each instance of the data set generated beforehand contains meta feature information for the considered data set and performance values of all classifiers.
-Similarly to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values.
+Each instance of the data set generated beforehand (see Fig \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers.
+Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set.
 This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking.
-In this case, there exists only one label ranking mode which is fed the computed meta data for a new data set and returns an ordering of classifiers.
+In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}.
 Thereby it attempts to learn the mapping from meta features to an ordering of classifiers directly.
@@
 \centering
-	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
+	\begin{tabularx}{\textwidth}{X | X | X | X | X}
 		%\hline
-		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
-		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
-		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\
-		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\
-		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
+		MF 1				& MF 2				& ... 	& MF n				& Ranking 	\\ \hline
+		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $r_1$		\\ 
+		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $r_2$		\\
+		...				& ...				& ...	& ...				& ...		\\
+		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_m$		 
 	\end{tabularx}
@@
 \section{Implementation}
-% regression based model - weka used
-
-% preference learning
-The jPL framework is a java framework for the evaluation of preference learning algorithms. It implements several tasks from the context of preference learning, including label ranking.
-
-% meta features - openML webapp
-\cite{OpenML2013}
-% Which meta features
-As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used.
-Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew.
-Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.
-Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.
-Since the meta data also includes probing, which is generally an expensive operation and furthermore does not aid in proving the point of a connection of properties of a data set and the performance of classifiers, additionally to the full meta features all evaluation measures where computed without using those meta features that use probing.
+In general, all implementations for the approach are carried out in Java, particularly Java 8.
+However, some additional packages where used, which are pointed out briefly.
+For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}.
+Regarding the preference algorithms, the jPL framework was used \cite{intelligent2017jpl}.
+The jPL framework is a java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information.
+The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets.
+Thus the meta features where calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; The full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.

### 2018-02-14 Writing/Thesis/content/chapter-evaluation.tex
more table and figure overhaul
First draft

@@
 For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
+The stratified split was generated with the help of JAICore, 'A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing].
 When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.
-
-%TODO integrate DONT FORGET META FEAUTRES (WHY EVERYTHING X2??)
-for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before analysis
-apache commons implementation for Kendall Rank correlation as well
-JAICore implementation for stratified split of data set
 
@@
 They can, however, be found in the supplementary material, offering clues to how each ranker performed in the prediction of a ranking for each of the used data sets, identified by their ID on OpenML.
+Furthermore, the evaluation was carried out twice for all measures: once with the full meta data used, and one time using only the meta features not generated by landmarkers, that is the ones that require probing to be carried out for a new data set.
+
+% Implementation of measures
+For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations where used.
+Regarding the Mann-Whitney U, the strategy for ties as set to averaging, and the NaNs where set to be removed before the analysis was started.
 
@@
 
-Compared to the evaluation on the full set of meta data, the results on the reduced set without out probing are less distinctive.
+As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other.
+From Table \ref{tab:evaluationResults} it is clear that the regression rankers are superior to the preference rankers, and this advantage is significant, as the weakest of the regression rankers, REPTree, is still significantly better than the strongest label ranking approach, instance based label ranking with Kemeny-Young rank aggregation ($p \approx 4.305E-6$).
+Out of the four regression rankers, three approaches are furthermore significantly better than REPTree.
+
+Compared to the evaluation on the full set of meta data, the results on the reduced set without probing are less distinctive.
 For the Kendall Rank correlation, linear regression, M5P and random forest are significantly better than the baseline, and for label ranking, both of the instance based approaches with non-default parameters as well, while the other label ranking approaches are significantly worse than the baseline.
@@
 
+With reduced meta data, out of the alternatives that pose a significant advantage compared to the baseline, only random forest is significantly better than all other approaches, the others are not significantly different.
+With loss and best three loss, no such statement can be made.
+
 Summarizing the observed results, in general, a regression based approach shows an indication to be stronger than a preference based approach.
-Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often.
+Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often A surprising result is that the label ranking approaches achieve very similar results with or without meta data.
 
@@
 }
-\caption{The Best Three Loss for the Best Algorithm Baseline and Random Forest Ranker (Full Meta Data)}
+\caption{The best three loss for the baseline compared to the random forest ranker (full meta data).}
 \label{fig:lossGraphics}

### 2018-02-14 Writing/Thesis/content/chapter-fundamentals.tex
First draft

@@
 After spending some time studying the different flowers, the gardener has realized he prefers certain iris species to others.
-
-Ranking = Permutation of the actual labels!
-%TODO {fill}
-Ordering =
-
-A ranking for a set of items defines a strict total order
-
-% Gardener example ranking his favourite plants
-The ordering sorts the labels according to their given score.
-It thus may also implicitly be given by ordering the items themselves, as the labels are aliases for them.
-Therefore, an ordering for a set of labels $\lbrace 1\dots k\rbrace$ is a permutation $\pi$ of the labels where $\pi(i)$ is the
-
-It must be noted that the definitions given here are not transferable to the general case of a ranking or ordering problems, since a strict total order is not required in all contexts for either ranking or ordering.
+He expresses his preference for a plant in a score, and labels all the plants in no particular order (see Fig.
+\ref{tab:ranking_vs_ordering}).
+An \textit{ordering} then is the result of simply ordering the labels in decreasing order of their respective score.
+It thus can also be given implicitly by just ordering the original classes, the flower names, as such being a permuation of the labels.
+A ranking, on the other hand, assigns a fixed position to each label; for instance the rank of 'iris virginica' will always be in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering.
+Therefore the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.
+It is notable that these can be the same, and are easily convertible.
+However, in the remainder of this thesis mostly the term ranking is used to identify both ranking and ordering interchangeably, especially as usually only the term 'ranking' is used.
 
@@
 
-The values in table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.
-
 \subsubsection{Label Ranking}
@@
 Instead, \citeauthor{DBLP:books/daglib/0025729} define the target function for label ranking as $f:X\rightarrow S_Y$ where the output space $S_Y$ contains all permutations over the set of labels $Y$ \cite{DBLP:books/daglib/0025729}.
-An instance $x \in X$ therefore is assigned a permutation $y_{\pi_x^i}$
-
-Although called label ranking actually label ordering!
-
-original algorithms selection problem \cite{rice1976algorithm} can be viewed as a learning problem itself
+To come back to the topic of rankings and orderings, it becomes clear now that even though it is called label ranking, the labels are actually ordered.
+An example of label ranking could be, to stay in the domain of gardening, to learn the preferences of different gardeners towards iris plants.
+A label ranking data set used to learn this connection could, for example, map the favourite colour and height of a gardener to a ranking of the three iris plants.
 
@@
 % Context is meta learning -> what does that mean and what are the consequence
-Meta leThe previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets.
-In the context of meta learning, is 'possible to learn about the learning process
-itself, and in particular that a system could learn to profit from previous
-experience to generate additional knowledge that can simplify the automatic
-selection of efficient models summarizing the data' \cite{brazdil2008metalearning}.
+The previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets.
+In the context of meta learning regarding machine learning, it is researched whether it is 'possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data' \cite{brazdil2008metalearning}.
+That is, the original algorithm selection problem \cite{rice1976algorithm} is viewed as a learning problem itself that is to be tackled.
 
-% Algorithm selection problem
+The approach of this thesis clearly falls under that category, as it is trying to learn whether a connection exists beween properties of a data set, that is its meta features, and the performance values of certain classification algorithms, and how well it can be exploited by regression and preference models respetively, if it exists.
+The benefit from meta learning in the conext of machine learning is that learning how properties of data sets influence the learning process of the classifiers could save much work; Often, much work is put into the fitting of an algorithm to a specific data set, but it is not transferred to other poblems that may be of the same nature.
 
@@
 
-general measure predictive accuracy (e.g. go back to example gardener model is not perfect so miss classifies some instancs if want to know how good exactly, how find out?
+To find out how well a classifier performs, it first needs to be decided which measure consider.
+There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set.
+But since using the whole data set to train a classifier, that is build a model, would skew the analysis - the classifier has already 'seen' these examples - a method for dividing data sets into train and test sets is needed.
 
-- estimation using cross validation (monte carloMCCV)
+A popular approach is using a stratified split, for example splitting the data into 70\% test and 30\% training data, with the important aspect that both sub sets have equal (or at least very similar) ratios of classes [Reference Missing].
+The learning algorithm is then trained with one part of the data (usually the larger), and its performance tested on the other.
+To get more stable results, often the process is repeated: The data is divided in k folds, k times, the learning algorithm is trained on k-1 folds, and tested on the left out subset.
+Results are averaged.
+This process is then called k-fold (stratified) cross validation [Reference Missing].
+A variant of this is Monte Carlo crossvalidation, where after each time the algorithm has been trained and evaluated, a new split is computed [Reference Missing].
+This especially causes the fact that the number of folds does not dictate the ratio of the split; one could for example have 5-folds Mone Carlo crossvalidation with a 70\%/30\% train/test split.
 
-- estimation using leave one out
+An alternative to using a stratified split is using a method called leave-one-out.
+This method essentially is, for a data set with n instances, n-fold crossvalidation (not stratified, naturally).
+This means that the algorithm is trained on n-1 instances and evaluated on the instance that has been left out.
 
@@
 
-%TODO include example ranking
-
 \subsection{Loss}
@@
 
-%TODO include example loss calculatio
-
 \subsection{Mann-Whitney U Test}
-%TODO describe & don't forget example
-The measures previously presented can indicate if one alternative is superior to another regarding that measure, but one cannot conclude from those results alone whether this advantage is significant.
-The question is whether the null-hypothesis that two distributions \cite{mann1947test}
+The measures previously presented can indicate if one of the ranking alternatives is superior to another regarding that measure, but one cannot conclude from those results alone whether this advantage is significant.
+The question here is whether the null-hypothesis that two distributions belong to the same population can be rejected.
+This can be determined with the help of the Mann-Whitney U, a non-parametric hypthesis test \cite{mann1947test}.
+The Mann-Whitney U is computed by, for two distributions one wants to analyze, counting how many times each value frome one distribution is lower than another value from the other distribution.
+If the U is very high (or low, depending on the hypothesis), the null hypothesis can be rejected.
+Whether this significance level is reached is expressed by the p-value: for a p-value below 0.05, The null hypothesis can be rejected.
+Therefore, if two distributions, for example regarding the loss values of two ranking approaches, suggest that one is superior to the other, and the p-value for the Mann-Whitney U is <= 0.05, this suggests that the difference is statistically significant.

### 2018-02-15 Writing/Thesis/content/abstract.tex
Updated abstract

@@
 Although the amount of data available worldwide is increasing, the portion of analyzed data remains low.
-This problem is caused by a lack of experts in the field that are able to carry out an analysis, and the difficulty of the analysis for non-experts.
-Especially for the task of classification, there are many algorithms with variing performance values from data set to data set - there does not exist one best algorithm, which one can always recommend.
-One response to this problem is automated machine learning.
-Therefore, in this thesis, to approaches to construct a ranking of classification algorithms for a new data set, based on properties of that data set,are presented and compared.
-The first of the two alternatives works on the basis of regression models; one regression model predicts a performance value for each classifier, from which then a ranking is constructed.
-In contrast, the second, preference based model directly learns and returns rankings.
-In the evaluation it became clear that the regression based alternative is superior to the preference based approach; the best evaluated regression model, based on the random forest algorithm, achieved values of up to 0.495 for Kendall's rank correlation coefficient and a peformance loss of 1.308 percent on average.
-However, the tested preference models are superior at least to the baseline in some scenarios.
-Therefore the conlucion can be drawn that at least certain properties of data sets are connected to performance values of classification algorithms, which can be exploited by regression and preference models, although the regression approach is superior to the preference alternative within the scope of the conducted evaluation.
+This problem is likely caused by a lack of experts in the field that are able to carry out an analysis effectively, as it is a difficult task for a layperson.
+Especially regarding the challenge of classification there exist many algorithms with varying performances from data set to data set - there is no one best algorithm that can always be recommended.
+One response to this problem is automated machine learning (AutoML): tools that recommend a learning algorithm for a new data set that they estimate to perform best on this particular data set.
+Current AutoML approaches, however, often search for a fitting algorithm without explicitly taking into account how properties of the data set in question might influence the performances of classifiers.
+For the most part, they also suggest a single algorithm only.
+In comparison to the recommendation of a ranking of classifiers this has the disadvantage that no alternatives to the suggested algorithm are presented, which, due to a certain inaccuracy of the prediction, may have an equal or even better performance than the first suggestion regarding the examined data set.
+The problem considered in this thesis is thus the construction of a ranking of classification algorithms in relation to properties of a data set.
+Two different approaches that aim to solve this problem are presented and compared.
+The first alternative works on the basis of regression models: one regression model for each classifier predicts a performance value for that classifier.
+On the basis of the predicted performance values, a ranking then is constructed.
+In contrast, for the second approach, a preference-based model directly learns and returns rankings.
+In the evaluation of the two alternatives, it became apparent that the regression-based alternative is superior to the preference-based approach.
+However, the tested preference models also achieved a significant advantage compared to the static baseline used in the evaluation, at least in certain scenarios.
 

### 2018-02-15 Writing/Thesis/content/chapter-related-work.tex
working on tables + reworking related work chapter

@@
 % Of course much work in this field and cannot possibly cover all of this so confined to closely related or well-known / state of the art
-The demand for aid in the process of selecting an algorithm has already led to the development of numerous solutions that automate machine-learning (AutoML).
-In the following sections, the workings of a few such tools that are related to this work are outlined briefly, loosely organized by their scope of operation.
-Each tool's usage of meta knowledge is discussed shortly.\\
+The demand for aid in the process of selecting an algorithm has already led to the development of a number of solutions that automate machine-learning (AutoML).
+In the following sections, the functionality of a few such tools that are related to this work are outlined briefly, organized by their scope of operation.
+Each tool's usage of meta knowledge is discussed shortly.
 
@@
 They call this combined measure of accuracy and time A3R, and integrate it into two different ranking approaches.
-In both cases, the authors find that this leads to a better mean interval loss, which is a measure that expresses the mean loss experienced in respect to the time that has been allowed for the construction of the ranking, that is time taken to evaluate top-ranked classifiers.
+In both cases, the authors find that this leads to a better mean interval loss, which is a measure that expresses the mean loss experienced with respect to the time that has been allowed for the construction of the ranking, that is the time taken to evaluate top-ranked classifiers.
 
@@
 One of those two approaches is called average-ranking.
-It utilizes meta knowledge to suggest a ranking of classifiers for a new data sets, which in this case consist of recorded past performances of classifiers on data sets.
-That means this algorithms aggregates the performances of classifiers on all rankings once and then always recommends the same ranking.
-The new measures is integrated here by, instead of ordering only according to performance values, the classifiers are ordered according to the combined measure A3R.
+It utilizes meta knowledge to suggest a ranking of classifiers for a new data set, which in this case consists of recorded past performances of classifiers on a number of data sets, meaning this algorithm aggregates the performances of classifiers across all data sets once and then always recommends the same ranking.
+The new measure is integrated here by, instead of ordering only according to performance values, ordering classifiers according to the combined measure A3R.
 
@@
 The second approach does not initially use meta knowledge and is called active testing.
-Active testing is a strategy that 'intelligently select the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
+Active testing is a strategy that 'intelligently selects the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
 Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set.
-The authors aim to improve this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation, incorporating time in the estimations made by the strategy which previously only compared accuracy values.
+The authors improved this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation variant, incorporating time in the estimations made by the strategy which previously only compared accuracy values.
 
@@
 %% CASH
-Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters are tools that in addition two selecting an algorithm also optimize its hyperparameters, which has been defined as 'the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}.
-Two widely used approaches of this kind are AUTO-WEKA and AUTO-SKLEARN.
+Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally also optimizing the classifier's hyperparameters, which has been defined as 'the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}.
+Two widely used approaches of this kind are Auto-WEKA and AUTO-SKLEARN.
 It has to be noted that thus these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.
@@
 Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}.
-It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parameterized algorithms for their problems.
+It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parametrized algorithms for their problems.
 The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}.
@@
 This cycle is then repeated until the allocated time has run out.
-Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first.
+Auto-WEKA exploits hard-coded meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first.
 \\
@@
 Before a classifier is evaluated on a data set, often a number of pre-processing steps are executed first.
-These could include selecting promising features and discarding other and normalizing the data.
+This includes, for example, selecting promising features and discarding others, and normalizing the data.
 The 'sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a machine learning pipeline.
-Two tools which construct such complete pipelines for data sets are MP-Plan and the RECIPE framework.
+Two tools which construct such complete pipelines for data sets are ML-Plan and the RECIPE framework.
 
@@
 ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}.
-This is achieved by viewing machine-learning as a task, building a hierarchical task network out of those tasks, and then searching for a solution in the induced tree structure.
+This is achieved by viewing machine-learning as a task, building a hierarchical task network out of the resulting subtasks, and then searching for a solution in the induced tree structure.
 In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks.
 An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'.
-The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed.
+The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'train NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed.
 A best-first search algorithm in a modified variant is then used to find good solutions in this task network.
 For the actual implementation of the learning algorithms, WEKA is used.
-While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\
+Like Auto-WEKA, ML-Plan uses hard-coded meta-knowledge by using a fixed orders as to which classifiers are tried first.
+However, the authors find that their results exceed those achieved by Auto-WEKA.\\
 
@@
 Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}.
-However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constraint the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}.
+However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constrain the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}.
 This means that generated individuals representing complete pipelines can never be invalid.

### 2018-02-15 Writing/Thesis/content/chapter-conclusion.tex
re-worked conclusion chapter

@@
 In this thesis, the problem of predicting a ranking of classification algorithms for a new data set on the basis of meta features of the data set and past performances of the algorithms has been considered.
-Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed.
+Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is relevant due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed.
 This problem has been addressed by implementing two different approaches, regression-based and preference-based ranking.
@@
 % Summary of findings and limitations: what has been covered LIMITATION: SMALL DATA SETS ESP!!
-The evaluation showed a significant advantage regarding the Kendall rank correlation for all tested methods in comparison to the best algorithm baseline, except instance based label ranking in the standard configuration and label ranking by pairwise comparison for the full meta data.
+The evaluation showed a significant advantage regarding Kendall's rank correlation coefficient for all tested methods in comparison to the best algorithm baseline, except instance based label ranking in the standard configuration and label ranking by pairwise comparison for the full meta data.
 However, regarding the practically possibly more important measure of best three loss, only the three regression based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage.
@@
 Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the best three loss and loss for both evaluation on the full and reduced meta data.
-Thus it can be included that a regression based approach seems to be generally more promising than a preference based approach, but is not better than the baseline regarding the best three loss when evaluated on the selected meta data without probing.
-Out of the regression based variants, random forest seems to be the most promising one.
+Thus it can be concluded that in general, a regression-based approach seems to be more promising than a preference-based approach, but is not better than the baseline regarding the best three loss when evaluated on the selected meta data without probing.
+Out of the regression-based variants, random forest seems to be the most promising one.
 
-The main limitation of the findings in this thesis is that the data sets used in the evaluation process where not very large, being limited to a maximum of 100 features and 1000 instances.
-Often, data sets can get much larger and the question whether this ranking approach would then still pose an efficient regarding calculation of meta features and prediction times and, maybe even more importantly, an accurate enough solution for predicting classifiers remains.
+The main limitation of these findings is that the data sets used in the evaluation process were not very large, being limited to a maximum of 100 features and 1000 instances.
+Often, data sets can get much larger and the question whether this ranking approach would then still pose an efficient solution regarding the calculation of meta features and the resulting prediction times and, maybe even more importantly, an accurate enough solution for predicting classifiers, remains.
 
 % Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
-On the basis of these results, it can be concluded that a there is an indication of a connection between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
-A practical application of these findings, apart from the direct use as a ranker, may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
-However, some additional work may have to be done in extension to this thesis in order for a sensible integration.
+On the basis of these results, it can be concluded that there is an indication of a connection between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms.
+A practical application of these findings, apart from the direct use as a ranker, may be to incorporate the implementation or parts of it in another AutoML tool as a search heuristic, similar to how some AutoML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}.
+However, some additional work may have to be done in extension to this thesis for such an integration to be sensible.
 
@@
 % More evaluation - meta features
-As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression based approach using random forests, many possibilities for additional work arise.
+As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise.
 An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features.
@@
 Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting.
-One could consider adding the meta feature groups for DecisionStump with two folds, RandomTree with a depth of two with two folds, REPTree with a depth of two and two folds, and J48.0001 with two folds, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation times for the meta features in the mean, which seems to be reasonable.
+One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seemss reasonable.
 An effect on the time and quality of predictions for larger data sets would have to be examined still.
@@
 Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
-In this regard it would also be interesting  to implement the loss - and time - loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.
+In this regard it would also be interesting  to implement the loss- and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.
 
@@
 % Auto fitting
-Depending on the fact whether one is willing to trade-off longer build and prediction times, it would also be possible to fit more sophisticated regression models for the regression based approach.
+Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuarcy, it would also be possible to fit more sophisticated regression models for the regression based approach.
 This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.
-Furthermore, the building and predictions for the regression models could be parallelized and evaluated on a cluster to simulate and test  the usage of the ranking tool in a productive environment.
 
@@
 This would help to determine if the ranking returned by the best algorithm baseline (see Fig.
-\ref{tab:bestAlgorithmRanking}
-) still holds when using a different baseline. Naturally this new baseline then could also be used to re-evaluate the implemented ranking concepts.
+\ref{tab:bestAlgorithmRanking}) still holds when using a different baseline.
+Naturally, this new baseline then could also be used to re-evaluate the implemented ranking concepts.

### 2018-02-16 Writing/Thesis/content/chapter-evaluation.tex
more re-working

@@
 As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}.
-These include the Kendall rank correlation coefficient, loss and best three loss.
-For all three measures, it is computed if any advantage or disadvantage one solutions has is significant, by means of the Mann-Whitney U and its P-value.
+These include the Kendall rank correlation coefficient, performance loss and best three loss regarding classifier performance.
+For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U.
 The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted.
@@
 This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot bet computed.
-Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline.
+Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.
 
 \section{Experimental Setup}
-In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section where observed.
-This includes which classifiers, data sets and meta features where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.
+In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section were observed.
+This includes which classifiers and data sets were chosen, and what the specifications of the machines the evaluation was executed on were.
+It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations where used.
 
@@
 The full list of the 22 classifiers can be gathered from Table \ref{tab:bestAlgorithmRanking}.
-They where all used in their default configurations as specified by WEKA.
+They were all used in their default configurations as specified by WEKA.
 
 % Which data sets
-Data sets for the analysis where gathered from OpenML.
-From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand where selected.
-Only data sets with a defined, nominal target feature that are in the .ARFF format which where not specifically designed for streaming analysis\footnotemark{} where considered, which resulted in a reduced selection of 812 instances.
-Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features where removed as well, leading to a final selection of 448 data sets.
+Data sets for the analysis were gathered from OpenML.
+From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand were selected.
+Only data sets in the .ARFF format with a defined, nominal target feature which were not specifically designed for streaming analysis\footnotemark{} were considered, which resulted in a reduced selection of 812 instances.
+Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features were removed as well, leading to a final selection of 448 data sets.
 Even though evaluation was only carried out on the shorter list, both the list of 812 and 448 data sets are included in the supplementary material for completeness.
@@
 % How base performance data generated
-The performance data of the classifiers for the selected data sets was generated on a linux cluster, each node consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 16GB RAM with usage of up to 150 nodes.
-There was a timeout of eight hours set for the computation of a single performance value of a classifier on a data set.
+The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM.
+For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours.
+Up 150 of such processes were executed in parallel.
 For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
@@
 % How rest of the evaluation carried out
-All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) with 12 GB RAM.
+All other experiments were carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) with 12 GB RAM.
 It is notable that especially the time-related results are to be viewed in regard to this setup.
-No timeouts where used in this evaluation, and the rankers where evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values where recorded, they where trained with the meta data - performance examples for n - 1 data sets, and queried for the remaining data set.
+No timeouts were used in this evaluation, and the rankers were evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values were recorded, they were trained with the meta data - performance examples for n - 1 data sets, and queried for the left-out data set.
 As n = 448 in this case, the detailed values for each data set are not included in the discussion of the results.
@@
 % Implementation of measures
-For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations where used.
-Regarding the Mann-Whitney U, the strategy for ties as set to averaging, and the NaNs where set to be removed before the analysis was started.
+For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used [REFERENCE MISSING].
+Regarding the Mann-Whitney U, the strategy for ties as set to averaging, and the NaNs were set to be removed before the analysis was started.
 
 % How find best version of preference and regression ranker
-Furthermore, four alternatives where selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem.
-For the regression based approach, the algorithms chosen where random forest, REPTree, M5P, and linear regression.
+Furthermore, four alternatives were selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem.
+For the regression based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression.
 For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA.
-As the preference based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives where generated by modifying the hyperparameters.
-The implemented alternatives are label ranking by pairwise comparison and instance based label ranking.
-As in early tests it became apparent that the instance based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used.
-For instance based label ranking, the default configuration, a configuration where the rank aggregation algorithm used by the label ranker was set to Kemeny-Young, and a configuration with Kemeny-Young rank aggregation and the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), set to the square root of the number of instances in the training data set.
+As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters.
+The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking.
+As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used.
+For instance-based label ranking, the default configuration, a configuration where the rank aggregation algorithm used by the label ranker was set to Kemeny-Young, and a configuration with Kemeny-Young rank aggregation and the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), set to the square root of the number of instances in the training data set.
+All of the described rankers are included in an overview in Table \ref{tab:methods}.
 In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.
+
+\begin{table}
+\resizebox{\textwidth}{!}{%
+\begin{tabularx}{1.25\textwidth}{>{\hsize=.4\hsize}X | >{\hsize=1.6\hsize}X}
+	Ranker				& Configuration \\ \hline\hline
+	LinearRegression		& Linear regression with S:0, R:1.0E-8, num-decimal-places:4 \\ \hline
+	M5P					& M5 model trees with M:4 \\ \hline
+	RandomForest			& Random forest with P:100, I:100, num-slots:1, K:0, M:1.0, V:0.001, S:1 \\ \hline
+	REPTree				& REPT tree with M:2, V:0.001, N:3, S:1, L:1, I: 0.0 \\ \hline \hline	
+	InstanceBased		& Instance-based label ranking with rankaggregation: Placket-Luce (norm tolerance: 1E-9, max iterations: 1000, log likelihood tolerance: 1E-5), baselearner: kNN (k: 10) \\ \hline
+	InstanceBased		& Instance-based label ranking with rankaggregation: Kemeny-Young, baselearner: kNN (k: 10) \\ \hline
+	InstanceBased		& Instance-based label ranking with rankaggregation: Kemeny-Young, baselearner: kNN (k:$\sqrt{\text{number of instances}}$) \\ \hline
+	PairwiseComparison 	& Label ranking by pairwise comparison with baselearner: logistic regression (learning rate: 0.001), gradient step: adam (beta1: 0.99, beta2: 0.999, epsilon: 10E-8) \\
+\end{tabularx}
+}
+\caption{An overview over the different base algorithms used in the evaluated rankers.}
+\label{tab:methods}
+\end{table}
 
@@
 
-When looking at the results depicted in Table \ref{tab:evaluationResults}, it must first be noted that positive findings regarding the Kendall rank correlation can be reported.
+Table \ref{tab:evaluationResults} shows the results of the evaluation, with the best mean values and significant differences emphasized as described in the caption of the table.
+When looking at these results, it must first be noted that positive findings regarding the Kendall rank correlation can be reported.
 For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults} which shows the results of the significance tests, with random forest having the highest correlation of 0.495.
 In contrast, the two approaches that did not overtake the baseline, instance based label ranking in the default configuration and label ranking by pairwise comparison, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches.
-Regarding loss, only linear regression and random forest show a significant advantage, with all label ranking approaches except for instance based label ranking having a significant disadvantage in contrast.
+Regarding performance loss, only linear regression and random forest show a significant advantage, with all label ranking approaches except for instance based label ranking having a significant disadvantage in contrast.
 Moving on to best three loss, the picture largely remains the same, except that surprisingly, REPTree now also has a significant advantage over the baseline.
@@
 Summarizing the observed results, in general, a regression based approach shows an indication to be stronger than a preference based approach.
-Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often A surprising result is that the label ranking approaches achieve very similar results with or without meta data.
+Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often.
+A surprising result is that the label ranking approaches achieve very similar results with or without probing.
 
@@
 
-Table \ref{tab:metaFeatureTimes} shows the times required for the computation of groups of meta features as discussed in chapter \ref{sec:approach}.
+Table \ref{tab:metaFeatureTimes} shows the times required for the computation of groups of meta features as discussed in Chapter \ref{sec:approach}.
 As can be taken from the table, the computation of the full meta features takes approximately 135 milliseconds on average, while the simple meta features without probing add approximately 3 milliseconds to the prediction times on average.
@@
 
-Further insights to be noted are the accuracy of predictions of performance values for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline.
+Further insights to be noted are the accuracies predicted for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline.
 The accuracy of the predictions achieved by the regression based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively.
@@
 It comes as little surprise that the Random Forest Ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful.
-The usefulness is dependent on the task these predictions would be used for an whether if requires very accurate predictions of performance values.
+The usefulness is dependent on the task these predictions would be used for and whether it requires very accurate predictions of performance values.
 
@@
 This ranking is depicted in Table \ref{tab:bestAlgorithmRanking}.
-The table is to be read top to bottom; of the 22 algorithms, the algorithm in the ith row is placed first on most data sets when compared to the next 22-i algorithms.
+The table is to be read top to bottom; of the 22 algorithms, the algorithm in the i-th row is placed first on most data sets when compared to the next 22-i algorithms.
 The associated number represents the number of data sets on which the algorithm was placed first.

### 2018-02-17 Writing/Thesis/content/abstract.tex
Some more corrections (writing)

@@
 Die weltweit verfügbare Menge an Daten steigt immer weiter an, und doch bleibt der Anteil der tatsächlich analysierten Daten gering.
-Dieses Problem entsteht, da nicht genug Experten verfügbar sind, um diese Analyse auszuführen, und es für Laien schwierig ist, das richtige Verfahren auszuwählen.
+Dieses Problem entsteht sehr wahrscheinlich, da nicht genug Experten verfügbar sind, um diese Analyse auszuführen, und es für Laien schwierig ist, das richtige Verfahren auszuwählen.
 Besonders im Bereich der Klassifikation gibt es viele Algorithmen, deren Performanz jedoch von Datensatz zu Datensatz variieren kann - es gibt also keinen einen besten Algorithmus, der immer eine gute Wahl darstellt.
-Eine Antwort auf diese Problem ist automatisiertes Machine Learning.
+Eine Antwort auf diese Problem ist automatisiertes Machine Learning: Werkzeuge, für einen neuen Datensatz einen Lernalgorithmus, von dem sie schätzen dass dieser bezüglich dessen die besten Vorraussagen treffen kann, vorschlagen.
+Aktuelle Ansätze dieser Art führen diese Suche oft aus, ohne explizit zu berücksichtigen wie Eigenschaften des Datensatzes die Performanz von Klassifizierungsalgorithmen beeinflussen.
+Außerdem schlagen sie meist nur einen einzelnen Algorithmus vor, was den Nachteil hat, dass keine Alternativen zu dem vorgeschlagenen Algorithmus verfügbar sind, welche aufgrund der Ungenauigkeit von Vorhersagen möglicherweise eine gleicherwertige oder sogar bessere Vorhersagegenauigkeit auf diesem Datensatz haben.
 Daher werden in dieser Arbeit zwei verschiedene Ansätze, welche für einen neuen Datensatz ein Ranking von Klassifizierungsalgorithmen aufgrund von Eigenschaften des Datensatzes vorhersagt, vorgestellt und miteinander verglichen.
@@
 Der zweite Ansatz beschäftigt sich mit Präferenzmodellen, welche direkt Rankings lernen und zurückgeben.
-In der Evaluation stellte sich heraus, dass der Regressionsansatz dem Präferenzmodell überlegen ist; das beste der getesteten Regressionsmodelle, basierend auf dem Random Forest Algorithmus, erreicht einen Wert von Kendalls Tau von bis zu 0,495 und Performanzverlustwerte von durchschnittlich nur 1,308 Prozentpunkten.
+In der Evaluation stellte sich heraus, dass der Regressionsansatz dem Präferenzmodell überlegen ist.
 Jedoch sind auch manche der getesten Präferenzmodelle in einigen Punkten wenigstens der zum Vergleich benutzten Baseline überlegen.
-Daher kann die Schlussfolgerung gezogen werden, dass wenigstens einige der benutzen Eigenschaften der Datensätze mit den Performanzwerten der Klassifizierungsalgorithmen zusammenhängen, und dieser Zusammenhang durch Regressionsmodelle sowohl als auch Präferenzmodelle ausgenutzt werden kann, wobei jedoch der Regressionsansatz letzterem im Rahmen der durchgeführten Evaluation überlegen ist.

### 2018-02-17 Writing/Thesis/content/chapter-approach.tex
Some more corrections (writing)

@@
 
-In this chapter the two alternatives considered in this thesis to tackle the problem of ranking classification algorithms regarding properties of the data set.
+In this chapter, the two alternatives considered in this thesis to tackle the problem of ranking classification algorithms regarding properties of a data set are explained.
 First, the theoretical approach is presented.
@@
 	\end{tabularx}
+	\caption{Training data for the rankers.}
 	\label{tab:performanceValues}
-	\caption{Training data for the rankers.}
 \end{table}
@@
 One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models.
-The idea is to use separate regression models to predict a performance value for each classifier, and to then derive an ordering from these predictions.
+The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions.
 This is done by splitting the data set compiled beforehand (see Tab.
 \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}.
-The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus a regression model can be trained on each of them.
-All regression models therefore try to learn the target function metafeatures$\rightarrow$performance value for their respective classifier.
-Hence for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
+The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them.
+All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier.
+Hence, for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
 In a second step, the classifiers are ordered according to the predictions.
-This process the ranker passes through for making a prediction is presented in Figure \ref{fig:regression_ranker_model}.
+This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.
 
@@
 }
+	\label{tab:regressionTables}
 	\caption{How the regression ranker processes the training data.}
-	\label{tab:regressionTables}
 \end{table}
@@
 In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}.
-Thereby it attempts to learn the mapping from meta features to an ordering of classifiers directly.
+Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.
 
@@
 In general, all implementations for the approach are carried out in Java, particularly Java 8.
-However, some additional packages where used, which are pointed out briefly.
+However, some additional packages were used, which are pointed out briefly.
 For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}.
 Regarding the preference algorithms, the jPL framework was used \cite{intelligent2017jpl}.
-The jPL framework is a java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information.
+The jPL framework is a Java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information.
 The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets.
-Thus the meta features where calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; The full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.
+Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; The full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.

### 2018-02-17 Writing/Thesis/content/chapter-fundamentals.tex
Some more corrections (writing)

@@
 \centering
-\includegraphics[width=\textwidth]{gfx/machine_learning.pdf}
+\includegraphics[width=\textwidth]{gfx/machine_learning.png}
 \caption{The learning problem, adapted from \cite{abu2012learning}.}
@@
 In addition to falling into the category of supervised learning, the problem is a classification problem.
-The nature of the prediction is to assign one of the three classes, or labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
+The nature of the prediction is to assign one of the three classes, also called labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
 Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, so that each instance of the data set is associated with a label $y_i \in Y$, in this case $Y=\lbrace 'iris-setosa','iris virginica', 'iris versicolor' \rbrace $.
 
-Apart from classification, another important category of machine learning problems is regression problems.
+Apart from classification, another important category of machine learning problems are regression problems.
 In the case of regression, the output space of the target function is no longer finite, but instead consist of real numbers.
@@
 Likewise, they would have to observe a number of plants to gather feature values together with the expected target value, which instead of the species would then be the height of the plant in centimeters, that is $Y=\mathbb{R}$.
-
-%TODO include a picture of the regression model mapping one of the width to height & say that this would be a linear model but others could be used
 
@@
 A ranking, on the other hand, assigns a fixed position to each label; for instance the rank of 'iris virginica' will always be in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering.
-Therefore the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.
+Therefore, the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.
 It is notable that these can be the same, and are easily convertible.
@@
 An example of label ranking could be, to stay in the domain of gardening, to learn the preferences of different gardeners towards iris plants.
-A label ranking data set used to learn this connection could, for example, map the favourite colour and height of a gardener to a ranking of the three iris plants.
+A label ranking data set used to learn this connection could, for example, map the favorite color and height of a gardener to a ranking of the three iris plants.
 
@@
 
-The approach of this thesis clearly falls under that category, as it is trying to learn whether a connection exists beween properties of a data set, that is its meta features, and the performance values of certain classification algorithms, and how well it can be exploited by regression and preference models respetively, if it exists.
-The benefit from meta learning in the conext of machine learning is that learning how properties of data sets influence the learning process of the classifiers could save much work; Often, much work is put into the fitting of an algorithm to a specific data set, but it is not transferred to other poblems that may be of the same nature.
+The approach of this thesis clearly falls under that category, as it is trying to learn whether a connection exists between properties of a data set, that is its meta features, and the performance values of certain classification algorithms, and how well it can be exploited by regression and preference models respectively, if it exists.
+The benefit from meta learning in the context of machine learning is that learning how properties of data sets influence the learning process of the classifiers could save much work; often, much work is put into the fitting of an algorithm to a specific data set, but it is not transferred to other problems that may be of the same nature.
 
@@
 After having discussed the preliminaries that the theoretical approach of this thesis is built upon, how a data set can be split into training and test data to estimate the performance of learning algorithms and the measures that will be used in the evaluation of the different ranking methods are briefly reviewed.
-These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals if an advantage regarding one measure can be viewed as significant.
+These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals whether an advantage regarding one measure can be viewed as significant.
 
@@
 
-To find out how well a classifier performs, it first needs to be decided which measure consider.
+To find out how well a classifier performs, it first needs to be decided which measure to consider.
 There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set.
@@
 
-A popular approach is using a stratified split, for example splitting the data into 70\% test and 30\% training data, with the important aspect that both sub sets have equal (or at least very similar) ratios of classes [Reference Missing].
+A popular approach is using a stratified split, for example splitting the data into 70\% training and 30\% test data, with the important aspect that both subsets have equal (or at least very similar) ratios of classes [Reference Missing].
 The learning algorithm is then trained with one part of the data (usually the larger), and its performance tested on the other.
@@
 Results are averaged.
-This process is then called k-fold (stratified) cross validation [Reference Missing].
-A variant of this is Monte Carlo crossvalidation, where after each time the algorithm has been trained and evaluated, a new split is computed [Reference Missing].
-This especially causes the fact that the number of folds does not dictate the ratio of the split; one could for example have 5-folds Mone Carlo crossvalidation with a 70\%/30\% train/test split.
+This process is then called k-fold (stratified) cross-validation [Reference Missing].
+A variant of this is Monte Carlo cross-validation, where after each time the algorithm has been trained and evaluated, a new split is randomly computed [Reference Missing].
+This especially causes the fact that the number of folds does not dictate the ratio of the split; one could for example have 5-folds Monte Carlo cross-validation with a 70\%/30\% train/test split.
 
 An alternative to using a stratified split is using a method called leave-one-out.
-This method essentially is, for a data set with n instances, n-fold crossvalidation (not stratified, naturally).
+This method essentially is, for a data set with n instances, n-fold cross-validation (not stratified, naturally).
 This means that the algorithm is trained on n-1 instances and evaluated on the instance that has been left out.
@@
 The Kendall Rank Correlation Coefficient, also known as Kendall's tau, is a measure of association between two rankings of the same items \cite{kendall1938new}.
-For two independent variables $X$ and $Y$ and and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations.
+For two independent variables $X$ and $Y$ and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations.
 If for two pairs $(x_i,y_i)$ and $(x_j,y_j)$ both $x_i < x_j$ and $y_i < y_j$ (or the opposite) holds, they are viewed as concordant.
@@
 $n_d$, the number of discordant pairs, and \\
-$n_0 = n * (n + 1) / 2$.
+$n_0 = n * (n - 1) / 2$.
 
-As we have seen in example above, can also have same rank for items. In order to account for this, a second statistic, $T_B$ is defined as
+To account for ties in the rankings, a second statistic, $T_B$ is defined as
 
@@
 While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms.
-This difference can be expressed in measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.
+This difference can be expressed in a measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.
 
@@
 This can be determined with the help of the Mann-Whitney U, a non-parametric hypthesis test \cite{mann1947test}.
-The Mann-Whitney U is computed by, for two distributions one wants to analyze, counting how many times each value frome one distribution is lower than another value from the other distribution.
+The Mann-Whitney U is computed by, for two distributions one wants to analyze, counting how many times each value from one distribution is lower than another value from the other distribution.
 If the U is very high (or low, depending on the hypothesis), the null hypothesis can be rejected.
-Whether this significance level is reached is expressed by the p-value: for a p-value below 0.05, The null hypothesis can be rejected.
+Whether this significance level is reached is expressed by the p-value: for a p-value below 0.05, the null hypothesis can be rejected.
 Therefore, if two distributions, for example regarding the loss values of two ranking approaches, suggest that one is superior to the other, and the p-value for the Mann-Whitney U is <= 0.05, this suggests that the difference is statistically significant.

### 2018-02-17 Writing/Thesis/content/chapter-introduction.tex
table and figure overhaul
Some more corrections (writing)

--- 2018-02-11 Writing/Thesis/content/chapter-introduction.tex
@@
 \label{sec:intro}
-%% Introduction to introduction
-This introduction emphasizes why there is a need for automation in machine learning, and how this thesis relates to that problem in that it proposes two different approaches for ranking classification algorithms.
-Furthermore, an overview of the thesis structure is given.
 
-\section{Motivation and Problem Statement}
-\label{sec:intro:motivation}
 %% Context
@@
 On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}.
-So in each case, one would have picked a different algorithm in order to achieve the best results.
+So in each case, one would have picked a different algorithm in order to achieve the best results, and this example just illustrates the choice between two algorithms - in reality, the number of available algorithms is much larger.
 In general, this means that for a different data set, a different algorithm might yield the best performance.
 
+\section{Problem Statement}
+\label{sec:intro:problem}
 %% Problem + Significance
-Since there is no one best classifier for all data sets, it is likely that how well a classifier performs on a given data set is dependent on properties of the data set, at least to some degree.
-Combined with the need for automated machine learning and the importance but difficulty of selecting a fitting algorithm, this calls for an approach that considers past performances of classifiers for data sets in relation to properties of these data sets to automatically suggest well-performing classifiers for a new problem.
+Since there is no one best classifier for all data sets, it can be concluded that how well a classifier performs on a given data set is dependent on certain properties of the data set.
+Combined with the need for automated machine learning and the importance but difficulty of selecting a fitting classification algorithm, this calls for an approach that properties of data sets to automatically suggest well-performing classifiers for a new problem.
 
@@
 Especially in the case of regression based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.
-
-% More Significance
-A tool that efficiently predicts which algorithms are likely to perform well compared to their alternatives regarding a specific data set simplifies the process of selecting an algorithm for inexperienced users and experts alike.
-A user would send a request to the tool for their specific data set at hand and then evaluate highly ranked algorithms manually, choosing the one with the best performance.
-The advantage is that the user does not need to know characteristics of the classification algorithms or data set in order to achieve relatively good results in a short amount of time.
-A further speed-up and simplification could then possibly be achieved by embedding this tool in a solution that also takes care of the sampling of selected classifiers on the data set, for example existing solutions in the context of automated machine learning (auto-ml) context.
 
@@
 % Continue with description of the approach to the problem described in detail
-The next chapter continues by describing the approach of this thesis for ranking classification algorithms. The two different proposed methods are contrasted.
-
-\textbf{Chapter \ref{sec:implementation} - \nameref{sec:implementation}} \\[0.2em]
-% Go into detail of implementation
-Following the details of the approach, the implementation thereof is presented. Used software libraries are pointed out.
+The next chapter continues by describing the approach of this thesis for ranking classification algorithms.
+The two different proposed methods are contrasted.
+Following the details of the approach, the implementation thereof is presented.
+Used software libraries are pointed out.
 
@@
 \textbf{Chapter \ref{sec:related} - \nameref{sec:related}} \\[0.2em]
-After the approach of this thesis has been laid out in detail, the scope is extended to related work in the area of auto-ml in general and ranking of learning algorithms more specifically.
+After the approach of this thesis has been laid out in detail, the scope is extended to related work in the area of AutoML in general and ranking of learning algorithms more specifically.
 Differences and similarities in the approaches are discussed briefly.
@@
 % Conlude + future work
-In the last chapter, the results which have been achieved are revisited with the goals in mind. Finally, an outlook for possible future work extending more eval is provided.
+In the last chapter, the results which have been achieved are revisited with the goals in mind, and future work is outlined.

### 2018-02-17 ranker/src/main/java/ranker/Main.java

@@ -159,27 +159,27 @@ public class Main {
 		// stats.get(i));
 		// }
 		//
-		// reader =
-		// Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues_noProbing.arff"),
-		// Util.charset);
-		//
-		// instances = new Instances(reader);
-		//
-		// targetAttributes = new ArrayList<Integer>();
-		// for (int i = 59; i < 81; i++) {
-		// targetAttributes.add(i);
-		// }
-		//
-		// ranker = new BestAlgorithmRanker();
+		 BufferedReader reader =
+		 Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues_noProbing.arff"),
+		 Util.charset);
+		
+		 Instances instances = new Instances(reader);
+		
+		 List<Integer> targetAttributes = new ArrayList<Integer>();
+		 for (int i = 59; i < 81; i++) {
+		 targetAttributes.add(i);
+		 }
+		
+		 BestAlgorithmRanker ranker = new BestAlgorithmRanker();
 
-		// ranker.buildRanker(instances, targetAttributes);
-		// ranking = ranker.predictRankingforInstance(instances.get(0));
-		// stats = ranker.getClassifierStats();
-		// System.out.println("---------------------------------------------------------------------");
-		// for (int i = 0; i < ranking.size(); i++) {
-		// System.out.println(ranking.get(i).getClass().getSimpleName() + " " +
-		// stats.get(i));
-		// }
+		 ranker.buildRanker(instances, targetAttributes);
+		 List<Classifier> ranking = ranker.predictRankingforInstance(instances.get(0));
+		 List<Integer> stats = ranker.getClassifierStats();
+		 System.out.println("---------------------------------------------------------------------");
+		 for (int i = 0; i < ranking.size(); i++) {
+		 System.out.println(ranking.get(i).getClass().getSimpleName() + " " +
+		 stats.get(i));
+		 }
 
 		// System.out.println(EvaluationHelper.evaluateRanker(ranker, instances,
 		// targetAttributes));
@@ -248,9 +248,13 @@ public class Main {
 		// System.out.print("& " + EvaluationHelper.computeWhitneyU(firstFile,
 		// secondFile, measure) +" ");
 		
-		//evaluateAllRankersOnAllDataSets();
+//		evaluateAllRankersOnAllDataSets();
 		
[…]

### 2018-03-09 Writing/Thesis/content/abstract.tex
integrate first part of comments

--- 2018-02-14 Writing/Thesis/content/abstract.tex
@@
-% !TEX root = ../my-thesis.tex
-%
 \pdfbookmark[0]{Abstract}{Abstract}
@@
 
-Although the amount of data available worldwide is increasing, the portion of analyzed data remains low.
-This problem is caused by a lack of experts in the field that are able to carry out an analysis, and the difficulty of the analysis for non-experts.
-Especially for the task of classification, there are many algorithms with variing performance values from data set to data set - there does not exist one best algorithm, which one can always recommend.
-One response to this problem is automated machine learning.
-Therefore, in this thesis, to approaches to construct a ranking of classification algorithms for a new data set, based on properties of that data set,are presented and compared.
-The first of the two alternatives works on the basis of regression models; one regression model predicts a performance value for each classifier, from which then a ranking is constructed.
-In contrast, the second, preference based model directly learns and returns rankings.
-In the evaluation it became clear that the regression based alternative is superior to the preference based approach; the best evaluated regression model, based on the random forest algorithm, achieved values of up to 0.495 for Kendall's rank correlation coefficient and a peformance loss of 1.308 percent on average.
-However, the tested preference models are superior at least to the baseline in some scenarios.
-Therefore the conlucion can be drawn that at least certain properties of data sets are connected to performance values of classification algorithms, which can be exploited by regression and preference models, although the regression approach is superior to the preference alternative within the scope of the conducted evaluation.
+As the demand for machine learning functionality increases dramatically, automated machine learning (AutoML) aims to (partially) automate the creation of machine learning applications.
+Current AutoML approaches, however, often search for a fitting learning algorithm for a new data set without explicitly considering how properties of the data set might influence algorithm performances.
+Furthermore, in comparison to recommending a ranking of learning algorithms, this has the disadvantage that no alternatives are presented.
+Due to a certain inaccuracy of the prediction, these may have an equal or even better performance than the first suggestion regarding the examined data set.
+
+In this thesis, the problem of predicting a ranking of classification algorithms based on properties of a data set is considered.
+To this end, two approaches are presented and compared.
+The first uses regression models to predict the accuracy of each classifier on a new data set, and then constructs a ranking from these predictions.
+Alternatively, a preference-based model directly learns and returns rankings.
+In an experimental study, it is shown that the regression-based approach performs superiorly to the preference-based alternative.
+However, the latter still outperforms a static ranking based on how often a classifier has performed best on previously considered data sets.
 
@@
 
-% Motivation
-Die weltweit verfügbare Menge an Daten steigt immer weiter an, und doch bleibt der Anteil der tatsächlich analysierten Daten gering.
-Dieses Problem entsteht, da nicht genug Experten verfügbar sind, um diese Analyse auszuführen, und es für Laien schwierig ist, das richtige Verfahren auszuwählen.
-Besonders im Bereich der Klassifikation gibt es viele Algorithmen, deren Performanz jedoch von Datensatz zu Datensatz variieren kann - es gibt also keinen einen besten Algorithmus, der immer eine gute Wahl darstellt.
-Eine Antwort auf diese Problem ist automatisiertes Machine Learning.
-Daher werden in dieser Arbeit zwei verschiedene Ansätze, welche für einen neuen Datensatz ein Ranking von Klassifizierungsalgorithmen aufgrund von Eigenschaften des Datensatzes vorhersagt, vorgestellt und miteinander verglichen.
-Der erste der beiden Ansätze arbeitet auf Grundlage von Regressionsmodellen; ein Ranking wird hier konstruiert indem ein einzelnes Regressionsmodell für jeden Klassifizierungsalgorithmus einen Performanzwert vorhersagt, auf deren basierend dann das Ranking erstellt wird.
-Der zweite Ansatz beschäftigt sich mit Präferenzmodellen, welche direkt Rankings lernen und zurückgeben.
-In der Evaluation stellte sich heraus, dass der Regressionsansatz dem Präferenzmodell überlegen ist; das beste der getesteten Regressionsmodelle, basierend auf dem Random Forest Algorithmus, erreicht einen Wert von Kendalls Tau von bis zu 0,495 und Performanzverlustwerte von durchschnittlich nur 1,308 Prozentpunkten.
-Jedoch sind auch manche der getesten Präferenzmodelle in einigen Punkten wenigstens der zum Vergleich benutzten Baseline überlegen.
-Daher kann die Schlussfolgerung gezogen werden, dass wenigstens einige der benutzen Eigenschaften der Datensätze mit den Performanzwerten der Klassifizierungsalgorithmen zusammenhängen, und dieser Zusammenhang durch Regressionsmodelle sowohl als auch Präferenzmodelle ausgenutzt werden kann, wobei jedoch der Regressionsansatz letzterem im Rahmen der durchgeführten Evaluation überlegen ist.
+Da die Nachfrage nach Funktionalität im Bereich des maschinellen Lernens dramatisch ansteigt, hat automatisiertes maschinelles Lernen (AutoML) das Ziel, die Erstellung von Anwendungen im Kontext des maschinellen Lernens (teilweise) zu automatisieren.
+Aktuelle Ansätze dieser Art suchen jedoch oft nach einem Lernalgorithmus für einen neuen Datensatz, ohne explizit zu berücksichtigen, wie Eigenschaften des Datensatzes die Performanz der Algorithmen beeinflussen können.
+Außerdem hat dies im Vergleich zu dem Vorschlag eines Rankings von Lernalgorithmen den Nachteil, dass keine Alternativen präsentiert werden.
+Diese können allerdings, aufgrund der Ungenauigkeit der Vorhersagen, gleichwertig oder sogar bessere Genauigkeiten auf diesem Datensatz haben.
+
+In dieser Arbeit wird das Problem betrachtet, ein Ranking von Klassifizierungsalgorithmen basierend auf den Eigenschaften eines Datensatzes zu erstellen.
+Dafür werden zwei Ansätze vorgestellt und verglichen.
+Der erste benutzt Regressionsmodelle,  um die Genauigkeit jedes Klassifizierers für den neuen Datensatz vorherzusagen, und erzeugt dann basierend auf den Vorhersagen ein Ranking.
+Alternativ lernt ein Präferenzmodell direkt Rankings und gibt sie zurück.
+In einer experimentellen Studie wird gezeigt, dass der regressionsbasierte Ansatz eine bessere Performanz aufweist als die präferenzbasierte Alternative.
+Allerdings ist letztere noch einem statischen Ranking überlegen, welches darauf basiert, wie oft ein Klassifizierer die beste Performanz auf zuvor betrachteten Datensätzen hatte.

### 2018-03-09 Writing/Thesis/content/chapter-approach.tex
integrate first part of comments

@@
 This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed.
-The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and n data sets.
+The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets.
 This approach to ranking is realized here, as pointed out before, in a regression based and preference based approach, which are explained in detail in the following sections.
@@
 		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
-		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
+		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2n}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
 	\end{tabularx}
@@
 All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier.
-Hence, for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
+Hence, for a query instance, a new data set, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
 In a second step, the classifiers are ordered according to the predictions.
@@
 }
+	\caption{How the regression ranker processes the training data. Performance data for each classifier are in a separate table, which are then used to train separate regression models.}
 	\label{tab:regressionTables}
-	\caption{How the regression ranker processes the training data.}
 \end{table}
@@
 The second possibility considered in this context is using preference learning to predict a ranking.
-Each instance of the data set generated beforehand (see Fig \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers.
+Each instance of the data set generated beforehand (see Tab.
+\ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers.
 Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set.
@@
 	\label{tab:preferenceTable}
-	\caption{How the preference ranker processes the training data.}
+	\caption{How the preference ranker processes the training data. The ranker is trained with a table containing meta features and a ranking of classifiers for each data set.}
 \end{table}

### 2018-03-09 Writing/Thesis/content/chapter-conclusion.tex
integrate first part of comments

@@
 Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
-In this regard it would also be interesting  to implement the loss- and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.
+In this regard it would also be interesting to implement the loss and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.
 
@@
 Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuarcy, it would also be possible to fit more sophisticated regression models for the regression based approach.
-This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.
+This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools like AUTOWEKA \cite{thornton2013auto} or AUTO-SKLEARN \cite{feurer2015efficient}, or even using a whole pipeline prediction tool, for example ML-Plan \cite{wever2017automatic} or the RECIPE framework \cite{DBLP:conf/eurogp/SaPOP17}.
 

### 2018-03-09 Writing/Thesis/content/chapter-evaluation.tex
integrate first part of comments

@@
 In order to evaluate the implemented rankers, their outputs are compared to a perfect output generated by an oracle.
-The oracle is implemented as a ranker that, after having been trained on a meta data - performance data set returns correct rankings when queried for any instance of that data set.
+The oracle is implemented as a ranker that, after having been trained on a meta data-performance data set, returns correct rankings when queried for any instance of that data set.
 The correct ranking is implied by the performance values (highest first, as the measure used here is predictive accuracy), with ties being handled in a sequential manner, i.e.
@@
 Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings.
-Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline.
+Therefore, a ranker that is agnostic to the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline.
 More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented.
 That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth.
-This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot bet computed.
-Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.
+This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot be computed.
+Ideally, rankings returned by the preference and regression based rankers should then be statistically significantly better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.
 
@@
 This includes which classifiers and data sets were chosen, and what the specifications of the machines the evaluation was executed on were.
-It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations where used.
+It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations were used.
 
@@
 
-\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis where not included in the evaluation.}
+\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis were not included in the evaluation.}
 
@@
 For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours.
-Up 150 of such processes were executed in parallel.
+Up to 150 of such processes were executed in parallel.
 For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
-The stratified split was generated with the help of JAICore, 'A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing].
+The stratified split was generated with the help of JAICore, \textquotesingle A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning\textquotesingle [Reference Missing].
 When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.
@@
 For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used [REFERENCE MISSING].
-Regarding the Mann-Whitney U, the strategy for ties as set to averaging, and the NaNs were set to be removed before the analysis was started.
+Regarding the Mann-Whitney U, the strategy for ties was set to averaging, and the NaNs were set to be removed before the analysis was started.
 
@@
 As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used.
-For instance-based label ranking, the default configuration, a configuration where the rank aggregation algorithm used by the label ranker was set to Kemeny-Young, and a configuration with Kemeny-Young rank aggregation and the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), set to the square root of the number of instances in the training data set.
+For instance-based label ranking, three different configurations were evaluated, the default configurations and two custom ones.
+For the first customization, the rank aggregation algorithm used by the label ranker was set to Kemeny-Young.
+For the second customization, additionally, the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), was set to the square root of the number of instances in the training data set.
 All of the described rankers are included in an overview in Table \ref{tab:methods}.
@@
 However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker.
-The Random Forest ranker, for example, is the ranker with the highest build time, and also with the rankings of the generally highest quality.
+The Random Forest ranker, for example, is the ranker with the highest build time (apart from Pairwise Comparison), and also with the rankings of the generally highest quality.
 But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds.

### 2018-03-09 Writing/Thesis/content/chapter-fundamentals.tex
integrate first part of comments

@@
 
-The core topic of this thesis falls under the category of machine learning.
-Thus, first the concept of machine learning and the tasks related to the approach of this thesis are explained.
+The core topic of this thesis falls into the category of machine learning.
+Hence, first the concept of machine learning and the tasks related to the approach of this thesis are explained.
 Second, means used for evaluation of the approach are discussed.
@@
 \section{Machine Learning}
-In this section, the aspects of the field of machine learning which are relevant for this thesis are going to be introduced briefly.
 The core of machine learning is learning algorithms, which are used to induce a general model from a set of data samples.
-The concept of machine learning will be explained here with the help of an example.
+The concept of machine learning is explained here with the help of an example.
 % Further what happens exactly here
@@
 More specifically, the focus lies on the three species iris versicolor, virginica and setosa.
-In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species, which is illustrated in Table \ref{tab:iris}.
+In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals of which they know the species, which is illustrated in Table \ref{tab:iris}.
 The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered three) an unknown iris plant is.
 The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation.
-They observe that all iris setosa plants from his sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species.
+They observe that all iris setosa plants from the sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species.
 The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants.
-While this model (illustrated in Figure \ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.
+While this model (illustrated in Figure \ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener settles with the approximation they have found.
 
@@
 	\end{tabularx}
-	\caption{Features of different iris plants. This is an excerpt from the well known iris data set \cite{iris}}
+	\caption{Features of different iris plants. This is an excerpt from the well-known iris data set \cite{iris}}
 	\label{tab:iris}
@@
 The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$.
-Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem.
-They then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees.
+These tuples form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem.
+The gardener then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees.
 The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.
@@
 Firstly, it falls in the category of supervised machine learning.
-Supervised learning is one of the three main learning paradigms of machine learning, together with reinforcement learning and unsupervised learning \cite{abu2012learning}.
+Supervised learning is one of the three main learning paradigms of machine learning, besides reinforcement learning and unsupervised learning \cite{abu2012learning}.
 In the context of this thesis, the latter will be neglected as only supervised learning is used.
@@
 In addition to falling into the category of supervised learning, the problem is a classification problem.
-The nature of the prediction is to assign one of the three classes, also called labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
-Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, so that each instance of the data set is associated with a label $y_i \in Y$, in this case $Y=\lbrace 'iris-setosa','iris virginica', 'iris versicolor' \rbrace $.
+The nature of the prediction in the example is to assign one of the three classes, also called labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
+Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, such that each instance of the data set is associated with a label $y_i \in Y$.
+In this case $Y=\lbrace '$\textit{iris setosa}$'$,$'$\textit{iris virginica}$'$, $'$\textit{iris versicolor}$' \rbrace $.
 
@@
 In the case of regression, the output space of the target function is no longer finite, but instead consist of real numbers.
-To reconsider the gardening example, the gardener could want to predict the height of a plant on the basis of the same features as used above.
+To reconsider the gardening example, the gardener might want to predict the height of a plant on the basis of the same features as used above.
 Likewise, they would have to observe a number of plants to gather feature values together with the expected target value, which instead of the species would then be the height of the plant in centimeters, that is $Y=\mathbb{R}$.
@@
 To clarify the meaning of ranking and ordering, we return to the gardening example.
-After spending some time studying the different flowers, the gardener has realized he prefers certain iris species to others.
-He expresses his preference for a plant in a score, and labels all the plants in no particular order (see Fig.
+After spending some time studying the different flowers, the gardener has realized they prefer certain iris species to others.
+He expresses his preference for a plant in a score, and labels all the plants in no particular order (see Tab.
 \ref{tab:ranking_vs_ordering}).
 An \textit{ordering} then is the result of simply ordering the labels in decreasing order of their respective score.
-It thus can also be given implicitly by just ordering the original classes, the flower names, as such being a permuation of the labels.
-A ranking, on the other hand, assigns a fixed position to each label; for instance the rank of 'iris virginica' will always be in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering.
+It thus can also be given implicitly by just ordering the original classes, the flower names, as such being a permutation of the labels.
+A \textit{ranking}, on the other hand, assigns a fixed position to each label; for instance the rank of 'iris virginica' will always be represented by the number in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering.
 Therefore, the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.
@@
 To come back to the topic of rankings and orderings, it becomes clear now that even though it is called label ranking, the labels are actually ordered.
-An example of label ranking could be, to stay in the domain of gardening, to learn the preferences of different gardeners towards iris plants.
+An example of label ranking could be, staying in the domain of gardening, to learn the preferences of different gardeners towards iris plants.
 A label ranking data set used to learn this connection could, for example, map the favorite color and height of a gardener to a ranking of the three iris plants.
@@
 The previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets.
-In the context of meta learning regarding machine learning, it is researched whether it is 'possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data' \cite{brazdil2008metalearning}.
+In the context of meta learning regarding machine learning, it is researched whether it is \textquotesingle possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data\textquotesingle \cite{brazdil2008metalearning}.
 That is, the original algorithm selection problem \cite{rice1976algorithm} is viewed as a learning problem itself that is to be tackled.
@@
 The approach of this thesis clearly falls under that category, as it is trying to learn whether a connection exists between properties of a data set, that is its meta features, and the performance values of certain classification algorithms, and how well it can be exploited by regression and preference models respectively, if it exists.
-The benefit from meta learning in the context of machine learning is that learning how properties of data sets influence the learning process of the classifiers could save much work; often, much work is put into the fitting of an algorithm to a specific data set, but it is not transferred to other problems that may be of the same nature.
+The benefit from meta learning in the context of machine learning is that learning how properties of data sets influence the learning process of the classifiers could save much work.
+Often, a large effort is put into the fitting of an algorithm to a specific data set, but this knowledge is not transferred to other problems that may be of the same nature.
 
@@
 
-After having discussed the preliminaries that the theoretical approach of this thesis is built upon, how a data set can be split into training and test data to estimate the performance of learning algorithms and the measures that will be used in the evaluation of the different ranking methods are briefly reviewed.
+After having discussed the preliminaries that the theoretical approach of this thesis is built upon, techniques used for evaluation are briefly reviewed.
+This includes the used methodology of splitting a data set into training and test data to estimate the performance of learning algorithms, and the measures that will be used in the evaluation of the different ranking methods.
 These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals whether an advantage regarding one measure can be viewed as significant.
@@
 There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set.
-But since using the whole data set to train a classifier, that is build a model, would skew the analysis - the classifier has already 'seen' these examples - a method for dividing data sets into train and test sets is needed.
+But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already 'seen' these examples - a method for dividing data sets into train and test sets is needed.
 
 A popular approach is using a stratified split, for example splitting the data into 70\% training and 30\% test data, with the important aspect that both subsets have equal (or at least very similar) ratios of classes [Reference Missing].
-The learning algorithm is then trained with one part of the data (usually the larger), and its performance tested on the other.
-To get more stable results, often the process is repeated: The data is divided in k folds, k times, the learning algorithm is trained on k-1 folds, and tested on the left out subset.
+The learning algorithm is then trained with one part of the data (usually the larger one), and its performance tested on the other.
+To get more stable results, often the process is repeated: The data is divided in k folds.
+Then, the learning algorithm is repeatedly trained on k-1 folds, k times, and tested on the left out subset each repetition.
 Results are averaged.
-This process is then called k-fold (stratified) cross-validation [Reference Missing].
+This process is called k-fold (stratified) cross-validation [Reference Missing].
 A variant of this is Monte Carlo cross-validation, where after each time the algorithm has been trained and evaluated, a new split is randomly computed [Reference Missing].
@@
 % We need to evaluate the ranker quality somehow, ranker predicts rank, so need a 
-To evaluate the quality of the prediction that a ranker will make, a statistic is needed to compare a predicted ranking with the correct ranking.
+To evaluate the quality of the prediction that a ranker produces, a statistic is needed to compare a predicted ranking with the correct ranking.
 For this, the Kendall Rank Correlation Coefficient will be used here, as it expresses the similarity of two rankings.
@@
 The Kendall Rank Correlation Coefficient, also known as Kendall's tau, is a measure of association between two rankings of the same items \cite{kendall1938new}.
-For two independent variables $X$ and $Y$ and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations.
+For two independent random variables $X$ and $Y$ and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations.
 If for two pairs $(x_i,y_i)$ and $(x_j,y_j)$ both $x_i < x_j$ and $y_i < y_j$ (or the opposite) holds, they are viewed as concordant.
@@
 $n_1=\sum_i{t_i(t_i-1)/2}$, \\
-$n_1=\sum_j{t_j(t_j-1)/2}$, \\
+$n_2=\sum_j{t_j(t_j-1)/2}$, \\
 $t_i,$ the number of ties observed for X in the ith position of the ranking \\
@@
 \subsection{Loss}
-While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms.
-This difference can be expressed in a measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.
+While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms compared to the performance of the actually best algorithm.
+This difference can be expressed in a measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the performance of the first recommended algorithm.
 

### 2018-03-09 Writing/Thesis/content/chapter-introduction.tex
integrate first part of comments

@@
 For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standard hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}.
-The predictive accuracy of the Random Forest\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
+The predictive accuracy of the Random Forest\footnote{With standard hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value.
 On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}.
@@
 Since there is no one best classifier for all data sets, it can be concluded that how well a classifier performs on a given data set is dependent on certain properties of the data set.
-Combined with the need for automated machine learning and the importance but difficulty of selecting a fitting classification algorithm, this calls for an approach that properties of data sets to automatically suggest well-performing classifiers for a new problem.
+Combined with the need for automated machine learning and the importance but difficulty of selecting a fitting classification algorithm, this calls for an approach that exploits properties of data sets to automatically suggest well-performing classifiers for a new problem.
 
@@
 Especially in the case of regression based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.
+
+\section{Objectives}
+\label{sec:intro:objectives}
+
+The thesis has two main goals.
+The first is to investigate the question whether it is possible to learn rankings of classification algorithms based on certain properties of data sets.
+This question is explored to the extent of empirically determining whether one of the proposed approaches has an advantage over a static baseline that does not use these properties for the prediction of a ranking.
+Furthermore, it is assessed how well both approaches perform in comparison to the correct ranking of classifiers for a data set.
+The second main goal is to compare the two different approaches among each other.
+
+In order to conduct this evaluation, an implementation of the two approaches is needed.
+A third goal is thus the development of an AutoML-tool that, after a pre-processing phase, returns a ranking of classifiers for a given data set, using either regression- or preference models for the prediction.
+The pre-processing phase constitutes of recording classifier performances on a number of data sets together with properties of the data sets to serve as training data, and training the regression models or preference model respectively.
 
@@
 % Continue with description of the approach to the problem described in detail
-The next chapter continues by describing the approach of this thesis for ranking classification algorithms.
+The next chapter follows up by describing the approach of this thesis for ranking classification algorithms.
 The two different proposed methods are contrasted.
 Following the details of the approach, the implementation thereof is presented.
-Used software libraries are pointed out.
 
@@
 % Conlude + future work
-In the last chapter, the results which have been achieved are revisited with the goals in mind, and future work is outlined.
+In the last chapter, the results which have been achieved are revisited with the goals in mind. Lastly, future work is outlined.

### 2018-03-09 Writing/Thesis/content/chapter-related-work.tex
integrate first part of comments

@@
 \section{Predicting Rankings}
+\label{sec:related:rankings}
 %% Ranking
@@
 The second approach does not initially use meta knowledge and is called active testing.
-Active testing is a strategy that 'intelligently selects the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
+Active testing is a strategy that \textquotesingle intelligently selects the most useful tests\textquotesingle \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
 Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set.
@@
 \section{Algorithm and Hyperparameter Selection}
+\label{sec:related:cash}
 %% CASH
-Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally also optimizing the classifier's hyperparameters, which has been defined as 'the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}.
+Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally optimizing the classifier's hyperparameters, which has been defined as \textquotesingle the combined algorithm selection and hyperparameter optimization problem (short: CASH)\textquotesingle \cite{thornton2013auto}.
 Two widely used approaches of this kind are Auto-WEKA and AUTO-SKLEARN.
@@
 An input data set is first preprocessed by means of feature selection.
-Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}.
+Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to \textquotesingle iterate [...] between fitting models and using them to make choices about which configurations to investigate\textquotesingle  \cite{hutter2011sequential}.
 In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model.
@@
 \section{Constructing pipelines}
+\label{sec:related:pipelines}
 %% Whole pipelines
@@
 This includes, for example, selecting promising features and discarding others, and normalizing the data.
-The 'sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a machine learning pipeline.
+The \textquotesingle sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories\textquotesingle \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a classification pipeline.
 Two tools which construct such complete pipelines for data sets are ML-Plan and the RECIPE framework.
@@
 
-%\tikzsetnextfilename{MLPlanTasks}
 \begin{figure}
 \centering
-%\tikzset{edge from parent/.style={draw,->}}
-%\begin{tikzpicture}[sibling distance=10em,
-%  every node/.style = {shape=rectangle, rounded corners,
-%    draw, align=center}]]
-%  \node {\textcolor{uniblue}{classify}}
-%    child { node {...} }
-%    child { node {\textcolor{uniblue}{classifyWithNN}}
-%    child { node {...} }
-%      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
-%        child { node {...} }
-%        child { node {...} 
-%          child { node {...}  }
-%          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } %} } }
-%    };
-%\end{tikzpicture}
 \includegraphics[width=.8\textwidth]{gfx/MLPlan.pdf}
-\caption{An example for how the complex task 'classify' might be broken down by ML-Plan, adapted from \cite{wever2017automatic}. Nodes containing '...' represent an undefined number of subtrees.}
+\caption{An example for how the complex task \textquotesingle classify\textquotesingle might be broken down by ML-Plan, adapted from \cite{wever2017automatic}.
+Nodes containing \textquotesingle ...\textquotesingle represent an undefined number of subtrees.}
 \label{fig:mltree}
@@
 Evaluation by the authors indicates that the RECIPE framework is able to compete with AUTO-SKLEARN and a different evolutionary approach, although it does not incorporate meta-knowledge in the search.
+It is notable that another evolutionary approach, Tree-based Pipeline Optimization Tool (TPOT) \cite{olson2016automating} exists, although in comparison to the RECIPE framework, it can generate individuals that represent invalid pipelines.

### 2018-03-12 Writing/Thesis/content/abstract.tex
integrate comments part three

@@
 As the demand for machine learning functionality increases dramatically, automated machine learning (AutoML) aims to (partially) automate the creation of machine learning applications.
-Current AutoML approaches, however, often search for a fitting learning algorithm for a new data set without explicitly considering how properties of the data set might influence algorithm performances.
+Current AutoML approaches, however, often search for a single fitting learning algorithm for a new data set without explicitly considering how properties of the data set influence algorithm performances.
 Furthermore, in comparison to recommending a ranking of learning algorithms, this has the disadvantage that no alternatives are presented.
@@
 Da die Nachfrage nach Funktionalität im Bereich des maschinellen Lernens dramatisch ansteigt, hat automatisiertes maschinelles Lernen (AutoML) das Ziel, die Erstellung von Anwendungen im Kontext des maschinellen Lernens (teilweise) zu automatisieren.
-Aktuelle Ansätze dieser Art suchen jedoch oft nach einem Lernalgorithmus für einen neuen Datensatz, ohne explizit zu berücksichtigen, wie Eigenschaften des Datensatzes die Performanz der Algorithmen beeinflussen können.
+Aktuelle Ansätze dieser Art suchen jedoch oft nach einem Lern-algorithmus für einen neuen Datensatz, ohne explizit zu berücksichtigen, wie Eigenschaften des Datensatzes die Performanz der Algorithmen beeinflussen können.
 Außerdem hat dies im Vergleich zu dem Vorschlag eines Rankings von Lernalgorithmen den Nachteil, dass keine Alternativen präsentiert werden.

### 2018-03-12 Writing/Thesis/content/chapter-approach.tex
integrate comments part three

@@
 The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets.
-This approach to ranking is realized here, as pointed out before, in a regression based and preference based approach, which are explained in detail in the following sections.
+This approach to ranking is realized here, as pointed out before, in a regression-based and preference-based approach, which are explained in detail in the following sections.
 
@@
 		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
-		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2n}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
+		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{m1}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
 	\end{tabularx}
@@
 
-\subsection{Regression Based Ranking}
+\subsection{Regression-Based Ranking}
 % How is the regression ranking done
@@
 All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier.
-Hence, for a query instance, a new data set, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved.
+Hence, for a query instance, here represented by a new data set, the first step is to compute the meta features.
+Afterwards, these are fed into each regression model and the predicted performance value for each classifier is saved.
 In a second step, the classifiers are ordered according to the predictions.
@@
 \vspace{1em}
-...
+$\vdots$
 \vspace{1em}	
@@
 \includegraphics[scale=1]{gfx/regression_models.pdf}
-\caption{An overview of how a regression based ranker constructs a ranking.}
+\caption{An overview of how a regression-based ranker constructs a ranking.}
 \label{fig:regression_ranker_model}
@@
 
-\subsection{Preference Based Ranking}
+\subsection{Preference-Based Ranking}
 % How is the preference ranking done
@@
 \includegraphics[scale=1]{gfx/label_ranking_model.pdf}
-\caption{An overview of how a preference based ranker constructs a ranking.}
+\caption{An overview of how a preference-based ranker constructs a ranking.}
 \label{fig:preference_ranker_model}
@@
 The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets.
-Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; The full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.
+Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; the full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.

### 2018-03-12 Writing/Thesis/content/chapter-conclusion.tex
integrate comments part three

@@
 Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting.
-One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seemss reasonable.
+One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable.
 An effect on the time and quality of predictions for larger data sets would have to be examined still.
@@
 % More evaluation - loss - time & compare agains Jan van Rijn
-Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
+Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example with the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}.
 In this regard it would also be interesting to implement the loss and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.

### 2018-03-12 Writing/Thesis/content/chapter-evaluation.tex
integrate comments part three

@@
 For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U.
-The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted.
+The regression-based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted.
 This is done by computing the root mean square error between the predicted and actual performance values.
@@
 Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings.
-Therefore, a ranker that is agnostic to the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline.
+Therefore, a ranker that is agnostic to the meta features of a query data set, meaning that it will always return the same ranking for any data set, is used as a baseline.
 More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented.
@@
 In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section were observed.
-This includes which classifiers and data sets were chosen, and what the specifications of the machines the evaluation was executed on were.
+This includes which classifiers and data sets were chosen, and the specifications of the machines the evaluation was executed on.
 It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations were used.
@@
 Data sets for the analysis were gathered from OpenML.
-From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand were selected.
+From all data sets considered as `active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand were selected.
 Only data sets in the .ARFF format with a defined, nominal target feature which were not specifically designed for streaming analysis\footnotemark{} were considered, which resulted in a reduced selection of 812 instances.
@@
 
-\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis were not included in the evaluation.}
+\footnotetext{Data sets that contained the substring `BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis were not included in the evaluation.}
 
@@
 For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
-The stratified split was generated with the help of JAICore, \textquotesingle A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning\textquotesingle [Reference Missing].
+The stratified split was generated with the help of JAICore, `A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing].
 When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.
@@
 % How find best version of preference and regression ranker
-Furthermore, four alternatives were selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem.
-For the regression based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression.
+Furthermore, four alternatives were selected for a regression-based and preference-based alternative each, to get a general idea of how well the respective approach might be suited for the problem.
+For the regression-based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression.
 For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA.
@@
 Then, the times required for building the rankers and for predictions made as well as for the calculation of the meta features is reviewed.
-Last, additional insights gathered during the evaluation are pointed out.
+At last, additional insights gathered during the evaluation are pointed out.
 
@@
 
-Summarizing the observed results, in general, a regression based approach shows an indication to be stronger than a preference based approach.
+Summarizing the observed results, in general, a regression-based approach shows an indication to be stronger than a preference-based approach.
 Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often.

### 2018-03-12 Writing/Thesis/content/chapter-fundamentals.tex
integrate comments part three

@@
 	\end{tabularx}
-	\caption{Features of different iris plants. This is an excerpt from the well-known iris data set \cite{iris}}
+	\caption{Features of different iris plants. This is an excerpt from the well-known iris data set \cite{iris}.}
 	\label{tab:iris}
@@
 In addition to falling into the category of supervised learning, the problem is a classification problem.
-The nature of the prediction in the example is to assign one of the three classes, also called labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant.
+The nature of the prediction in the example is to assign one of the three classes, also called labels, `iris setosa', `iris virginica' and `iris versicolor' to a new plant.
 Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, such that each instance of the data set is associated with a label $y_i \in Y$.
-In this case $Y=\lbrace '$\textit{iris setosa}$'$,$'$\textit{iris virginica}$'$, $'$\textit{iris versicolor}$' \rbrace $.
+In this case, the output space is defined as $Y=\lbrace '$\textit{iris setosa}$'$,$'$\textit{iris virginica}$'$, $'$\textit{iris versicolor}$' \rbrace $.
 
@@
 After spending some time studying the different flowers, the gardener has realized they prefer certain iris species to others.
-He expresses his preference for a plant in a score, and labels all the plants in no particular order (see Tab.
+They express their preference for a plant in a score, and labels all the plants in no particular order (see Tab.
 \ref{tab:ranking_vs_ordering}).
@@
 It thus can also be given implicitly by just ordering the original classes, the flower names, as such being a permutation of the labels.
-A \textit{ranking}, on the other hand, assigns a fixed position to each label; for instance the rank of 'iris virginica' will always be represented by the number in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering.
+A \textit{ranking}, on the other hand, assigns a fixed position to each label; for instance the rank of `iris virginica' will always be represented by the number in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering.
 Therefore, the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$.
 It is notable that these can be the same, and are easily convertible.
-However, in the remainder of this thesis mostly the term ranking is used to identify both ranking and ordering interchangeably, especially as usually only the term 'ranking' is used.
+However, in the remainder of this thesis mostly the term ranking is used to identify both ranking and ordering interchangeably, especially as usually only the term `ranking' is used.
 
@@
 The previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets.
-In the context of meta learning regarding machine learning, it is researched whether it is \textquotesingle possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data\textquotesingle \cite{brazdil2008metalearning}.
+In the context of meta learning regarding machine learning, it is researched whether it is `possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data' \cite{brazdil2008metalearning}.
 That is, the original algorithm selection problem \cite{rice1976algorithm} is viewed as a learning problem itself that is to be tackled.
@@
 There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set.
-But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already 'seen' these examples - a method for dividing data sets into train and test sets is needed.
+But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already `seen' these examples - a method for dividing data sets into train and test sets is needed.
 
@@
 $n_1=\sum_i{t_i(t_i-1)/2}$, \\
-$n_2=\sum_j{t_j(t_j-1)/2}$, \\
+$n_2=\sum_j{u_j(u_j-1)/2}$, \\
 $t_i,$ the number of ties observed for X in the ith position of the ranking \\
-$u_j,$ the number of ties observed for Y in the ith position of the ranking
+$u_j,$ the number of ties observed for Y in the jth position of the ranking
 
-Thus, the value of the tau (for both versions) lies in the interval $[-1,1]$, with 1 indicating a perfect agreement of rankings, -1 perfect disagreement, and 0 corresponding to no correlation.
+Thus, the value of the tau (for both versions) lies in the interval $[-1,1]$, with 1 indicating a perfect agreement of rankings, -1 for a perfect disagreement, and 0 corresponding to no correlation.
 A high value is therefore desirable in this context, as it indicates that the prediction of the ranker agrees with the actual ranking of algorithms.
@@
 This difference can be expressed in a measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the performance of the first recommended algorithm.
+Therefore, the loss in performance $L$ a user experiences on a data set when following a ranker's recommendation by choosing the first algorithm in the returned ranking can be expressed as
 
-Additionally, the ranker recommends a ranking instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss.
-This is done here by computing a measure called best three loss, which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier in the considered set of classifiers.
+$$L=|p_{\textit{best}}-p_{\textit{first}}|$$
+with \\
+$p_{\textit{best}}$, the performance of the best algorithm on the data set, \\
+$p_{\textit{first}}$, the  performance of the first recommended algorithm on the data set.
+
+Taking the absolute value of the difference is necessary here, since the `best' performance value of a classifier does not always need to be the largest value.
+When choosing the error rate of a classifier on a data set as the performance value, for example, the best possible value is 0, and in general, all classifiers besides the best one will have an equal or higher performance value.
+When choosing the percentage of correctly classified instances, though, the opposite is true, but the loss always needs to be non-negative.
+This is ensured by the taking the absolute value of the difference.
+
+However, the ranker recommends a \textit{ranking} instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss.
+This is done here by computing a measure called best three loss (B3L), which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier in the considered set of classifiers.
+Similar to the definition above, the loss in performance a user experiences on a data set when following a ranker's recommendation by choosing the best of the first three recommended algorithms can be expressed as
+
+$$\textit{B3L}=|p_{\textit{best}}-\textit{max}(p_{\textit{first}}, p_{\textit{second}}, p_{\textit{third}})|$$
+with \\
+$p_{\textit{best}}$, $p_{\textit{first}}$ as above, \\
+$p_{\textit{second}}$, the performance of the second recommended algorithm on the data set. \\
+$p_{\textit{third}}$, the performance of the third recommended algorithm on the data set.
+
+It is notable that this definition is only valid if the `best' performance value is the largest possible value, as for example is the case for the percentage of correctly classified instances, as explained above.
+When choosing a measure like the error rate, where the lowest value is the best value, the maximum in the equation needs to be substituted by a minimum, since the best of the first three recommended algorithms then is the one with the \textit{lowest} performance value.
+
+To demonstrate how the loss measures work, we return to the gardener example from the previous sections.
+Previously, the gardener has just chosen a tree-based model (see Fig.
+\ref{fig:decision_tree}) and hoped that this was a good approximation.
+But they conclude that the error rate of this model is too high, and a better approximation is needed.
+So instead, they now choose to use an AutoML tool that will return a ranking of classification algorithms for their data set of flowers, a ranker.
+The ranker has four available algorithms $A_1$, $A_2$, $A_3$ and $A_4$, and has produced the ranking depicted in Tab.
+\ref{tab:lossTable}.
+When the gardener follows this recommendation, the loss $L$ experienced is $L=|0.1-0.3|=0.2$, and $\textit{B3L}=|0.1-\textit{min}(0.3,0.1,0.4)|=0$.
+So by trying the best three recommended algorithms, the gardener finds the best of the four available algorithms.
+But the example also shows, that the loss is always viewed only regarding the algorithms that are contained in the ranking, not all available algorithms - the algorithms $A_1$ to $A_4$ are only compared among each other and not, for example, with the tree model constructed earlier.
+
+\begin{table}
+\begin{tabularx}{\textwidth}{X | X | X | X | X}
+			& $A_1$	& $A_2$	& $A_3$	& $A_4$ \\\hline
+error rate	& 0.1	& 0.7	& 0.3	& 0.4	\\
+rank			& 2		& 4		& 1		& 3	
+\end{tabularx}
+\caption{An exam.}
+\label{tab:lossTable}
+\end{table}
 

### 2018-03-12 Writing/Thesis/content/chapter-related-work.tex
integrate comments part three

@@
 The second approach does not initially use meta knowledge and is called active testing.
-Active testing is a strategy that \textquotesingle intelligently selects the most useful tests\textquotesingle \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
+Active testing is a strategy that `intelligently selects the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets.
 Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set.
@@
 %% CASH
-Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally optimizing the classifier's hyperparameters, which has been defined as \textquotesingle the combined algorithm selection and hyperparameter optimization problem (short: CASH)\textquotesingle \cite{thornton2013auto}.
+Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally optimizing the classifier's hyperparameters, which has been defined as `the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}.
 Two widely used approaches of this kind are Auto-WEKA and AUTO-SKLEARN.
-It has to be noted that thus these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.
+It has to be noted that these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.
 
@@
 An input data set is first preprocessed by means of feature selection.
-Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to \textquotesingle iterate [...] between fitting models and using them to make choices about which configurations to investigate\textquotesingle  \cite{hutter2011sequential}.
+Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to `iterate [...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}.
 In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model.
@@
 This includes, for example, selecting promising features and discarding others, and normalizing the data.
-The \textquotesingle sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories\textquotesingle \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a classification pipeline.
+The `sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a classification pipeline.
 Two tools which construct such complete pipelines for data sets are ML-Plan and the RECIPE framework.
@@
 In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks.
-An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'.
-The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'train NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed.
+An example of this might be `classify' as the root node, with an intermediate node on some level that contains the tasks `build NN', `train NN' and `predict from NN'.
+The complex task `build NN' would then further be decomposed, and could lead to a leaf node with n tasks `Add layer', `train NN' and `predict from NN', which are all primitive tasks that do not need to be further decomposed.
 A best-first search algorithm in a modified variant is then used to find good solutions in this task network.
@@
 \includegraphics[width=.8\textwidth]{gfx/MLPlan.pdf}
-\caption{An example for how the complex task \textquotesingle classify\textquotesingle might be broken down by ML-Plan, adapted from \cite{wever2017automatic}.
-Nodes containing \textquotesingle ...\textquotesingle represent an undefined number of subtrees.}
+\caption{An example for how the complex task `classify' might be broken down by ML-Plan, adapted from \cite{wever2017automatic}. Nodes containing `...' represent an undefined number of subtrees.}
 \label{fig:mltree}
@@
 Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}.
-However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constrain the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}.
+However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which `is used to generate the initial population, as well as to constrain the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}.
 This means that generated individuals representing complete pipelines can never be invalid.

### 2018-03-12 Writing/Thesis/content/chapter-conclusion.tex
integrate comments part four

@@
 % Summary of findings and limitations: what has been covered LIMITATION: SMALL DATA SETS ESP!!
-The evaluation showed a significant advantage regarding Kendall's rank correlation coefficient for all tested methods in comparison to the best algorithm baseline, except instance based label ranking in the standard configuration and label ranking by pairwise comparison for the full meta data.
-However, regarding the practically possibly more important measure of best three loss, only the three regression based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage.
-When evaluating best three loss on reduced meta data that does not incorporate probing, although the evaluated data indicates a slight advantage of those same regression models over the baseline still, it is not statistically significant anymore.
-Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the best three loss and loss for both evaluation on the full and reduced meta data.
-Thus it can be concluded that in general, a regression-based approach seems to be more promising than a preference-based approach, but is not better than the baseline regarding the best three loss when evaluated on the selected meta data without probing.
-Out of the regression-based variants, random forest seems to be the most promising one.
+The evaluation showed a significant advantage regarding Kendall's rank correlation coefficient for all tested methods in comparison to the best algorithm baseline, with the exception of the InstanceBased ranker in the standard configuration and the PairwiseComparison ranker for the full meta data.
+However, regarding the practically possibly more important measure of B3L, only the three regression-based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage.
+When evaluating B3L on reduced meta data that does not incorporate probing, although the evaluated data indicates a slight advantage of those same regression models over the baseline still, it is not statistically significant anymore.
+Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the B3L and loss for both evaluation on the full and reduced meta data.
+Thus it can be concluded that in general, a regression-based approach seems to be more promising than a preference-based approach, but is not better than the baseline regarding the B3L when evaluated on the selected meta data without probing.
+Furthermore, since the regression-based approach shows an advantage over the preference-based approach in respect to the problem considered in this thesis, one can conclude, that here, the preference-based approach generalizes too much.
+The additional information available to the regression-based models, the performance values of classifiers, seems to pose an advantage over the abstraction of only considering rankings of classifiers in this case.
+Out of the regression-based variants, the RandomForest ranker seems to be the most promising one.
 
@@
 Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features.
-Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting.
+Since the significant advantage of any approach was lost regarding B3L when moving from the full meta data to the reduced meta data without probing, this might be especially interesting.
 One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable.
@@
 % Auto fitting
-Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuarcy, it would also be possible to fit more sophisticated regression models for the regression based approach.
+Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuracy, it would also be possible to fit more sophisticated regression models for the regression based approach.
 This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools like AUTOWEKA \cite{thornton2013auto} or AUTO-SKLEARN \cite{feurer2015efficient}, or even using a whole pipeline prediction tool, for example ML-Plan \cite{wever2017automatic} or the RECIPE framework \cite{DBLP:conf/eurogp/SaPOP17}.

### 2018-03-12 Writing/Thesis/content/chapter-evaluation.tex
integrate comments part four

@@
 As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}.
-These include the Kendall rank correlation coefficient, performance loss and best three loss regarding classifier performance.
+These include the Kendall rank correlation coefficient, performance loss and B3L regarding classifier performance.
+The measure chosen for the performance values here is the \textit{predictive accuracy} of a classifier, meaning the number of correctly classified instances in a data set.
 For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U.
@@
 In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.
+They are referenced by the names in Table \ref{tab:methods} to avoid confusion between the ranker and the learning algorithm it is based on.
 
@@
 
-Table \ref{tab:evaluationResults} shows the results of the evaluation, with the best mean values and significant differences emphasized as described in the caption of the table.
+Table \ref{tab:evaluationResults} shows the results of the evaluation regarding the accuracy of returned rankings, with the best mean values and significant differences emphasized as described in the caption of the table.
 When looking at these results, it must first be noted that positive findings regarding the Kendall rank correlation can be reported.
-For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults} which shows the results of the significance tests, with random forest having the highest correlation of 0.495.
-In contrast, the two approaches that did not overtake the baseline, instance based label ranking in the default configuration and label ranking by pairwise comparison, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches.
-Regarding performance loss, only linear regression and random forest show a significant advantage, with all label ranking approaches except for instance based label ranking having a significant disadvantage in contrast.
-Moving on to best three loss, the picture largely remains the same, except that surprisingly, REPTree now also has a significant advantage over the baseline.
-The lowest value here is achieved by random forest with a best three loss of 1.308, in comparison to 2.440 for the best algorithm baseline.
-These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual best three loss values on the data sets.
+For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults}, which shows the results of the significance tests according to the p-value for the Mann-Whitney U.
+Of all rankers, RandomForest has the highest rank correlation with a value of 0.495.
+In contrast, the two approaches that did not overtake the baseline, the InstanceBased ranker in the default configuration and the PairwiseComparison ranker, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches.
+Especially the latter approach has a very low rank correlation, that with a mean value of 0.014 shows almost no correlation with the correct ranking.
+Regarding performance loss, only the LinearRegression and RandomForest ranker show a significant advantage, with all label ranking approaches except for the InstanceBased ranker with Kemeny-Young rank aggregation having a significant disadvantage in contrast.
+Here, an advantage of the regression-based approach in general is indicated, although the best value with a loss of 3.097 (achieved by the RandomForest ranker) is still fairly high, depending on the data set one considers.
+Moving on to B3L, the picture largely remains the same, except that surprisingly, the REPTree ranker now also has a significant advantage over the baseline.
+The lowest value here again is achieved by the RandomForest ranker with a mean B3L of 1.308, in comparison to 2.440 for the best algorithm baseline.
+These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual B3L values on the data sets.
 
 As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other.
-From Table \ref{tab:evaluationResults} it is clear that the regression rankers are superior to the preference rankers, and this advantage is significant, as the weakest of the regression rankers, REPTree, is still significantly better than the strongest label ranking approach, instance based label ranking with Kemeny-Young rank aggregation ($p \approx 4.305E-6$).
-Out of the four regression rankers, three approaches are furthermore significantly better than REPTree.
+From Table \ref{tab:evaluationResults} it is clear that the regression-based rankers are superior to the preference-based rankers, and this advantage is significant, as the weakest of the regression rankers, the REPTree ranker, is still significantly better than the strongest label ranking approach, the InstanceBased ranker with Kemeny-Young rank aggregation ($p \approx 4.305E-6$).
+Out of the four regression rankers, three approaches are furthermore significantly better than the REPTree ranker.
 
 Compared to the evaluation on the full set of meta data, the results on the reduced set without probing are less distinctive.
-For the Kendall Rank correlation, linear regression, M5P and random forest are significantly better than the baseline, and for label ranking, both of the instance based approaches with non-default parameters as well, while the other label ranking approaches are significantly worse than the baseline.
-In total, random forest is still the best alternative with a correlation of 0.439, slightly worse than the correlation achieved on the full meta data.
-For both loss measures however, while the disadvantages of the label ranking approaches remain, none of the eight alternatives achieves a significantly better loss or best three loss than the baseline anymore.
+For the Kendall Rank correlation, the LinearRegression, M5P and RandomForest rankers are significantly better than the baseline, and for label ranking, both of the InstanceBased approaches with non-default parameters as well, while the other label ranking approaches are significantly worse than the baseline.
+In total, the RandomForest ranker is still the best alternative with a correlation of 0.439, slightly worse than the correlation achieved on the full meta data.
+For both loss measures however, while the disadvantages of the label ranking approaches remain, none of the eight alternatives achieves a significantly better loss or B3L than the baseline anymore.
 
-With reduced meta data, out of the alternatives that pose a significant advantage compared to the baseline, only random forest is significantly better than all other approaches, the others are not significantly different.
-With loss and best three loss, no such statement can be made.
+Again, the different approaches can be compared among each other.
+With reduced meta data, out of the alternatives that pose a significant advantage compared to the baseline, only the RandomForest ranker is significantly better than all other approaches, the others are not significantly different.
+With loss and B3L, no such statement can be made.
+
+Further interesting points can be observed.
+First, in Table \ref{tab:evaluationResults} one can see that for the loss and B3L, often, rankers have a similar values.
+Second, the performance of the preference-based rankers does not differ very much, whether full meta data or reduced meta data was used in the evaluation.
+While, for example, Kendall's Rank correlation for the LinearRegression ranker is 0.473 for full meta data, it is noticeably lower for reduced meta data with a value of 0.350.
+On the other hand, the correlation coefficient for the InstanceBased rankers in all configurations does not change at all when removing meta features that involve probing.
 
@@
 	width=\textwidth,
-	ylabel={BestThreeLoss}, 
+	ylabel={B3L}, 
 	xlabel={Data Set},
@@
 }
-\caption{The best three loss for the baseline compared to the random forest ranker (full meta data).}
+\caption{The B3L for the baseline compared to the random forest ranker (full meta data).}
 \label{fig:lossGraphics}
@@
 The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves.
-However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker.
-The Random Forest ranker, for example, is the ranker with the highest build time (apart from Pairwise Comparison), and also with the rankings of the generally highest quality.
+However, it is notable that while the PairwiseComparison ranker was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker.
+The RandomForest ranker, for example, is the ranker with the highest build time (apart from the PairwiseComparison ranker), and also with the rankings of the generally highest quality.
 But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds.
@@
 Further insights to be noted are the accuracies predicted for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline.
-The accuracy of the predictions achieved by the regression based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively.
-The first thing that attracts attention in this table is the absurdly high values for Linear Regression and M5P, however, these are all caused by the very high maximum value on one data set with id 685.
-If these extreme maxima remain out of consideration for Linear Regression and M5P (the other algorithms do not have this problem) more reasonable values are obtained.
-For M5P, on the full meta data the new maximum is 311.526, mean 8.127 and standard deviation 18.407; on the reduced meta data it is a maximum of 474.692, mean 15.444 and standard deviation 27.433.
-For Linear Regression, on the full meta data the new maximum is 142.996, mean 9.281 and standard deviation 8.438; on the reduced meta data it is a maximum of 131.456, mean 14.351 and standard deviation 10.299.
-However, these values are still worse than the ones obtained for the Random Forest and REPTree variants.
-It comes as little surprise that the Random Forest Ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful.
-The usefulness is dependent on the task these predictions would be used for and whether it requires very accurate predictions of performance values.
+The accuracy of the predictions achieved by the regression-based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively.
+The first thing that attracts attention in this table is the absurdly high values for the LinearRegression and M5P rankers, however, these are all caused by the very high maximum value on one data set with id 685 on OpenML.
+If these extreme maxima remain out of consideration for the LinearRegression and M5P ranker (the other algorithms do not have this problem) more reasonable values are obtained.
+For the M5P ranker, on the full meta data the new maximum is 311.526, mean 8.127 and standard deviation 18.407; on the reduced meta data it is a maximum of 474.692, mean 15.444 and standard deviation 27.433.
+For the LinearRegression ranker, on the full meta data the new maximum is 142.996, mean 9.281 and standard deviation 8.438; on the reduced meta data it is a maximum of 131.456, mean 14.351 and standard deviation 10.299.
+However, these values are still worse than the ones obtained for the RandomForest and REPTree variants.
+It comes as little surprise that the RandomForest ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful.
+This is especially the case, since in addition to a relatively high mean, the standard deviation is rather high as well in all observed variants.
+The usefulness of the tool to predict performance values is therefore dependent on the task these predictions would be utilized for and whether it requires very accurate predictions of performance values.
+On the other hand, judging by the fact that the regression-based approach shows to be superior to the preference-based approach, these imperfect predictions seem still seem to be accurate enough to result in a rather good ranking.
 
@@
 The associated number represents the number of data sets on which the algorithm was placed first.
-It is, however, not a particularly surprising result, as for example the placement of Random Forest as the first algorithm was to be expected.
-Random Forest is a learning algorithm that is known to often deliver good performances, which was proven again in the results discussed previously - out of the reviewed ranking approaches, Random Forest was the best choice.
+It is, however, not a particularly surprising result, as for example the placement of random forest as the first algorithm, and ZeroR in the lower ranks was to be expected.
+Random forest is a learning algorithm that is known to often deliver good performances, which was proven again in the results discussed previously - out of the reviewed ranking approaches, the RandomForest ranker was the best choice.
+On the other hand, ZeroR is a simple classifier often used as a baseline, that predicts a static value based on the majority class (or average numeric value of the target feature) \cite{devasena2011effectiveness}.
 

### 2018-03-14 Writing/Thesis/content/chapter-approach.tex
integrate comments part five

@@
 The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets.
-This approach to ranking is realized here, as pointed out before, in a regression-based and preference-based approach, which are explained in detail in the following sections.
+This approach to ranking is realized here, as pointed out before, in a regression-based and preference-based variant, which are explained in detail and compared briefly in the following sections.
 
@@
 The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions.
-This is done by splitting the data set compiled beforehand (see Tab.
+The training of the ranker is done by splitting the data set compiled beforehand (see Tab.
 \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}.
-The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them.
+The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model is trained on each of them.
 All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier.
-Hence, for a query instance, here represented by a new data set, the first step is to compute the meta features.
+After the regression models have been trained for each classifiers, the training of the ranker is finished.
+For a query instance, here represented by a new data set, the first step is to compute the meta features.
 Afterwards, these are fed into each regression model and the predicted performance value for each classifier is saved.
@@
 \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers.
-Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set.
+The performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set, similar to the prediction step of the regression alternative, which is the first step of building the ranker.
 This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking.
-In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}.
+In this case, in contrast to the regression-based approach, there exists only one model, a label ranking model.
+To complete the training of the ranker, this model is built with the training data that has been converted to a label ranking data set in the previous step.
+To make predictions, the computed meta data for a new data set is fed to this model, which consequently returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}.
 Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.
@@
 
+\subsection{Comparison}
+
+While both of the ranking approaches above are used for the same purpose of ranking classification algorithms, they differ in some aspects that are interesting to point out.
+First, they theoretically do not require the same kind of training data.
+While the preference ranker only needs rankings, the regression ranker requires the exact performance data of all considered classifiers on the data sets.
+Although here it does not make a difference, since the performance values are computed anyways as the regression ranker utilizes them, in cases where only rankings of classifiers for a data set are known or performance values are estimated in a way that is biased, but has the same bias for all classifiers, so that the ranking is not influenced, this may be an advantage.
+Furthermore this leads to the curios case that training examples for the regression ranker are not directly samples from the target function the ranker learns.
+The target function for the regression ranker (as for the preference ranker) maps meta features of a data set to a ranking.
+However, for the regression ranker, the training examples have to include the actual performance values, meaning that they are of the form (\textit{meta features}, \textit{performance values}).
+
+Also, the approaches behave differently regarding the addition (or deletion) of a data set or classifier.
+If a classifier is added, for the regression-based approach, a regression model needs to be added to the ranker.
+Therefore, performance values for the classifier for the data set would need to be available or have to be computed anew.
+For the preference-based approach, however, the whole label ranking model, therefore the whole ranker, would need to be trained again, as for every data set, the ranking of classifiers has changed.
+Here a regression ranker conceptually has an advantage.
+The deletion of a classifier is much simpler: for the regression-based ranker, one regression model has to be deleted, which does not affect the other models, and in the case of the preference ranker, in the rankings produced by the label ranking model the unwanted classifier can just be removed from the rankings.
+
+For the addition of a data set, the situation is unfavorable for both rankers.
+Since a new training example would be added to each regression model, they all need to be trained again on the now extended training data.
+For the preference ranker, likewise a new training example is added to the training data, and a new model has to be trained.
+The same is the case for the deletion of a data set.
+
+Regarding training and prediction, conceptually, the preference ranker has the advantage that it both only needs to build one model and to have one model make a prediction for a new data set.
+On the other hand, the regression ranker needs to build as many models as there are classifiers in consideration, and also have as many models predict a performance value for their respective classifiers, which then also have to be turned into a ranking.
+In general, this indicates a better scalability of the preference-based approach regarding the number of classifiers (unless they are to be added dynamically) and data sets, although of course this also depends on the specific algorithms used.
+
 \section{Implementation}
-In general, all implementations for the approach are carried out in Java, particularly Java 8.
-However, some additional packages were used, which are pointed out briefly.
+
+The implementation of the rankers themselves is relatively straightforward with the theory of the previous sections in mind.
+However, since the goals for his thesis includes the development of an AutoML tool that returns a ranking of classification algorithms when given a data sets, the scope of the implementation goes beyond the ranking algorithms, including also pre-processing steps and means of evaluation for the rankers, relevant parts of the implementation are described in the following paragraphs; it is notable that all implementations were carried out in Java, particularly Java 8.
+
+As mentioned before, the implementations of the ranking approaches are relatively close to the theory and will therefore not be described in detail, except for a few notable parts.
+First, since the tool relies on external libraries for the learning algorithms, these need to be pointed out.
 For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}.
@@
 The jPL framework is a Java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information.
+
+Furthermore, so far, the descriptions of the `performance measure' used for the classifiers, that is the measure according to which the classifiers are ranked, for example the error rate or predictive accuracy, have been kept non-specific.
+Likewise, although the measure used in the evaluation in this thesis is predictive accuracy, the implementation has been kept general to allow any measure to be used with the rankers, as long as it is numeric.
+
+Another fact worth mentioning regarding the implementation of the rankers is that both the regression-based approach and the preference-based approach are implemented in a way that abstract superclasses handle the data set conversions and other necessary tasks, so that it is very easy to add a new ranker implementation.
+For example, to create a new ranker that uses random forest as a regression model for each classifier, it is only necessary to override a method called \texttt{buildRegressionModels} which has the classifiers mapped to the training data necessary for the regression model of each classifier as a parameter and is responsible for the generation of the regression models.
+How this method is implemented in the case of random forest is illustrated in Figure \ref{lst:randomForest}.
+Here we can see that the regression model that has been acquired by training on the provided data is saved together with the classifier for which it predicts performance values.
+Later, this model is used to predict the performance value of that specific classifier.
+
+\begin{figure}
+\begin{lstlisting}
+@Override
+protected void buildRegressionModels
+			(Map  Classifier, Instances> train) 
+			throws Exception {
+	regressionModels = new HashMap<Classifier,Classifier>();
+	for (Classifier classifier : train.keySet()) {
+		RandomForest forest = new RandomForest();
+		forest.buildClassifier(train.get(classifier));
+		regressionModels.put(classifier, forest);
+	}
+}
+\end{lstlisting}
+\caption{A source code excerpt for a ranker based on the random forest algorithm.}
+\label{lst:randomForest}
+\end{figure}
+
+Last, while the computation of the meta features is included in the workflow of a ranker in the theoretical explanations of the previous sections, meta features are calculated separately in the implementation since it is a repeating task, to speed up the evaluation of classifiers.
 The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets.
 Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; the full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.
+Like the choice which classifier and performance measure to use, the choice of which meta features to be used in the implementation can be changed flexibly.
+
+In addition to this ranking functionality, methods for the evaluation of both classifiers and rankers are implemented.
+Although WEKA offers capabilities for the evaluation of classifiers, additional functionality had to be added, as for example the desired estimation procedure of stratified Monte Carlo cross-validation was not supported by WEKA at the time of the implementation.
+Furthermore, since for the evaluation of the rankers (to build the table depicted in Tab.
+\ref{tab:performanceValues}), many classifiers had to be evaluated on a large number of data sets, an efficient way to execute this task was needed.
+This was realized by enabling the tool to take a number of jobs, consisting of classifiers and data sets, as command-line parameters, which enables execution for example on a data mining cluster.
+For the evaluation of rankers, the functionality needed to be built without the help of existing frameworks, and was realized in a similar way to the implemented evaluation of WEKA classifiers.
+It was also implemented such that after a ranker has been trained once, it can be evaluated regarding a number of different measures, to speed up the evaluation process.
+
+Apart from the functionality described above, the implementation includes some useful recurring functions from the context of handling data sets and classifiers in the context of WEKA and OpenML.
+To give a general idea how the tool is structured, an overview of the package structure is given in Fig.
+\ref.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{gfx/Package_Structure.png}
+\caption{An overview of the package structure of the tool.}
+\label{fig:package_overview}
+\end{figure}

### 2018-03-14 Writing/Thesis/content/chapter-evaluation.tex
integrate comments part five

@@
 Especially the latter approach has a very low rank correlation, that with a mean value of 0.014 shows almost no correlation with the correct ranking.
-Regarding performance loss, only the LinearRegression and RandomForest ranker show a significant advantage, with all label ranking approaches except for the InstanceBased ranker with Kemeny-Young rank aggregation having a significant disadvantage in contrast.
+
+Regarding performance loss, meaning much worse the performance of the first recommended algorithm is in comparison to the actual best algorithm on the data set, as defined in Chapter \ref{sec:fundamentals}, only the LinearRegression and RandomForest ranker show a significant advantage, with all label ranking approaches except for the InstanceBased ranker with Kemeny-Young rank aggregation having a significant disadvantage in contrast.
 Here, an advantage of the regression-based approach in general is indicated, although the best value with a loss of 3.097 (achieved by the RandomForest ranker) is still fairly high, depending on the data set one considers.
+
 Moving on to B3L, the picture largely remains the same, except that surprisingly, the REPTree ranker now also has a significant advantage over the baseline.
-The lowest value here again is achieved by the RandomForest ranker with a mean B3L of 1.308, in comparison to 2.440 for the best algorithm baseline.
+The lowest value here is achieved by the inearRegression ranker with a mean B3L of 1.267, in comparison to 2.440 for the best algorithm baseline.
 These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual B3L values on the data sets.
+In this figure, we can observe that, for a large number of data sets, the B3L is actually 0, namely 206 data sets for the BestAlgorithm ranker and 248 for the RandomForest ranker, which corresponds to 46\% and 55\% of the 448 data sets used in the evaluation.
+The main portion of the remaining data points is situated between 0.25 and 8 for the RandomForestRanker, and 0.5 and 16 for the BestAlgorithm ranker, with few exceptions.
 
 As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other.
-From Table \ref{tab:evaluationResults} it is clear that the regression-based rankers are superior to the preference-based rankers, and this advantage is significant, as the weakest of the regression rankers, the REPTree ranker, is still significantly better than the strongest label ranking approach, the InstanceBased ranker with Kemeny-Young rank aggregation ($p \approx 4.305E-6$).
+From Table \ref{tab:evaluationResults} it is clear that the regression-based rankers are superior to the preference-based rankers, and this advantage is significant, as the weakest of the regression rankers, the REPTree ranker, is still significantly better than the strongest label ranking approach, the InstanceBased ranker with Kemeny-Young rank aggregation, as indicated by a p-value of 4.305E-6.
 Out of the four regression rankers, three approaches are furthermore significantly better than the REPTree ranker.
@@
 \addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
-\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
 \legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
@@
 Table \ref{tab:metaFeatureTimes} shows the times required for the computation of groups of meta features as discussed in Chapter \ref{sec:approach}.
-As can be taken from the table, the computation of the full meta features takes approximately 135 milliseconds on average, while the simple meta features without probing add approximately 3 milliseconds to the prediction times on average.
+As can be taken from the table, the computation of the full meta features takes approximately 135 milliseconds on average, while the simple meta features without probing add approximately 3 milliseconds to the prediction times on average, which is already a difference of factor 45, which is quite large especially considering the fact that only light data sets, restricted in the number of features and instances, were used.
+To emphasize this difference, the meta features were calculated for the popular MNIST data set \cite{mnist}, which contains pictures of handwritten digits in a 28 by 28 pixel resolution, resulting in 784 features, plus the target feature.
+The data set contains 70.000 different pictures.
+For the computation of the full set of meta features, 4 hours and 51 minutes were needed, out of which only 24 seconds were needed for the reduced set of meta features, a difference of factor 735.
 Regarding these computation times it is also notable that among the probing meta feature groups, some are considerably more expensive than others, so that in the future it might be sensible to consider only light probing with probing meta feature groups that are not as expensive.

### 2018-03-14 Writing/Thesis/content/chapter-fundamentals.tex
integrate comments part five

@@
 In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species.
-$X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant.
+$X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, or the target feature of the data set, here the species of iris plant.
 The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$.
 These tuples form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem.
-The gardener then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees.
+The gardener then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees, and in general contains candidate formulas considered by the learning algorithm.
 The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.
@@
 There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set.
-But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already `seen' these examples - a method for dividing data sets into train and test sets is needed.
+But since using the whole data set to train a classifier (build a model) and consequently test it, would skew the analysis - the classifier has already `seen' these examples - a method for dividing data sets into train and test sets is needed.
 
@@
 This means that the algorithm is trained on n-1 instances and evaluated on the instance that has been left out.
+Since this method is executed n times on a data set with n instances, whereas for example 10-fold (stratified) cross-validation is always only executed ten times, it is computationally more expensive.
+This is especially the case for larger data sets, because generally, the time for training a classifier is increased with the number of training examples.
+However, as the number of training examples increases, the estimated accuracy of the classifier approaches the accuracy that it would achieve on the entire population (assuming that the samples are independent and not biased), making it desirable to have as many training examples as possible.
+Therefore, leave-one-out tends to be less biased than the (usually more negatively biased) variant of using k-fold cross-validation with a relatively small k \cite{kohavi1995study}.
+On the other hand, this leads to a higher variance of the estimates.
+So apart from considering the computational expense when choosing k, one has to think about the bias-variance trade-off.
 
@@
 A high value is therefore desirable in this context, as it indicates that the prediction of the ranker agrees with the actual ranking of algorithms.
+
+For illustration, once again the gardener example is used.
+Previously, the gardener has expressed their preference for the three different iris species of iris plants with the ranking [2,3,1] (see Tab \ref{tab:ranking_vs_ordering}).
+Suppose a different gardener instead has the preferences [3,2,1], and one wants to know to what degree they agree.
+To compute the Kendall rank correlation coefficient, first, the first position of both rankings would be the compared with the second positions, that is (2,3) with (3,2).
+This pair is discordant.
+The next pair, (2,3), (1,1), is concordant, and the last pair, (3,2), (1,1) is concordant as well.
+As there are no ties, this results in a correlation of $\frac{2-1}{3}=\frac{1}{3}$, indicating a slight agreement.
 
@@
 \begin{tabularx}{\textwidth}{X | X | X | X | X}
-			& $A_1$	& $A_2$	& $A_3$	& $A_4$ \\\hline
-error rate	& 0.1	& 0.7	& 0.3	& 0.4	\\
-rank			& 2		& 4		& 1		& 3	
+Algorithm	& $A_1$	& $A_2$	& $A_3$	& $A_4$ \\\hline
+Error Rate	& 0.1	& 0.7	& 0.3	& 0.4	\\
+Rank			& 2		& 4		& 1		& 3	
 \end{tabularx}

### 2018-03-14 ranker/src/main/java/ranker/Main.java
forgot to push some code

@@ -12,17 +12,17 @@ import java.util.Arrays;
 import java.util.List;
 
 import ranker.core.algorithms.BestAlgorithmRanker;
-import ranker.core.algorithms.InstanceBasedLabelRankingKemenyYoung;
-import ranker.core.algorithms.InstanceBasedLabelRankingKemenyYoungSQRTN;
-import ranker.core.algorithms.InstanceBasedLabelRankingRanker;
-import ranker.core.algorithms.LinearRegressionRanker;
-import ranker.core.algorithms.M5PRanker;
-import ranker.core.algorithms.PairwiseComparisonRanker;
 import ranker.core.algorithms.PerfectRanker;
-import ranker.core.algorithms.REPTreeRanker;
-import ranker.core.algorithms.RandomForestRanker;
 import ranker.core.algorithms.Ranker;
-import ranker.core.algorithms.RegressionRanker;
+import ranker.core.algorithms.preference.InstanceBasedLabelRankingKemenyYoung;
+import ranker.core.algorithms.preference.InstanceBasedLabelRankingKemenyYoungSQRTN;
+import ranker.core.algorithms.preference.InstanceBasedLabelRankingRanker;
+import ranker.core.algorithms.preference.PairwiseComparisonRanker;
+import ranker.core.algorithms.regression.LinearRegressionRanker;
+import ranker.core.algorithms.regression.M5PRanker;
+import ranker.core.algorithms.regression.REPTreeRanker;
+import ranker.core.algorithms.regression.RandomForestRanker;
+import ranker.core.algorithms.regression.RegressionRanker;
 import ranker.core.evaluation.BestThreeLoss;
 import ranker.core.evaluation.EvaluationHelper;
 import ranker.core.evaluation.KendallRankCorrelation;
@@ -31,8 +31,9 @@ import ranker.core.evaluation.Loss;
 import ranker.core.evaluation.RankerEvaluationMeasure;
 import ranker.core.metafeatures.GlobalCharacterizer;
 import ranker.core.metafeatures.MetaFeatureHelper;
+import ranker.core.metafeatures.NoProbingCharacterizer;
 import ranker.util.openMLUtil.OpenMLHelper;
-import ranker.util.wekaUtil.WekaHelper;
+import ranker.util.wekaUtil.WEKAHelper;
 import weka.classifiers.Classifier;
 import weka.classifiers.trees.RandomForest;
 import weka.core.Attribute;
@@ -159,28 +160,26 @@ public class Main {
 		// stats.get(i));
 		// }
 		//
[…]

### 2018-03-14 ranker/src/main/java/ranker/Rankprediction.java

@@ -11,13 +11,27 @@ import weka.core.DenseInstance;
 import weka.core.Instance;
 import weka.core.Instances;
 
+/**
+ * @author Helena Graf
+ *
+ */
 public class Rankprediction {
 	
+	/**
+	 * Instances holding the meta data
+	 */
 	protected Instances metaData;
 	protected List<Integer> targetAttributes;
 	protected Characterizer characterizer;
 	protected Ranker ranker;
 	
+	/**
+	 * @param metaData
+	 * @param targetAttributes
+	 * @param characterizer
+	 * @param ranker
+	 * @throws Exception
+	 */
 	public Rankprediction(Instances metaData, List<Integer> targetAttributes, Characterizer characterizer, Ranker ranker) throws Exception {
 		this.metaData = metaData;
 		this.targetAttributes = targetAttributes;
@@ -27,11 +41,17 @@ public class Rankprediction {
 		ranker.buildRanker(metaData, targetAttributes);
 	}
 	
+	/**
+	 * @param instances
+	 * @return
+	 * @throws Exception
+	 */
 	public List<Classifier> predictRanking (Instances instances) throws Exception {
 		// Get meta features for instance
 		Map<String,Double> metaFeatures = characterizer.characterize(instances);
 		
 		// Insert in the right order in instance
+		// TODO extract in class
 		Instance queryInstance = new DenseInstance(metaData.numAttributes());
 		for (int i = 0; i < metaData.numAttributes(); i++) {
 			if (!targetAttributes.contains(i)) {

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/BestAlgorithmRanker.java

@@ -4,6 +4,7 @@ import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.List;
 
+import ranker.core.algorithms.preference.PreferenceRanker;
 import weka.classifiers.Classifier;
 import weka.core.Instance;
 

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/InstanceBasedLabelRankingKemenyYoung.java

@@ -1,21 +1,0 @@
-package ranker.core.algorithms;
-
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingConfiguration;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.kemenyyoung.KemenyYoungLearningAlgorithm;
-import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
-import de.upb.cs.is.jpl.api.math.RandomGenerator;
-
-public class InstanceBasedLabelRankingKemenyYoung extends PreferenceRanker {
-
-	@Override
-	protected void initialize() throws Exception {
-		RandomGenerator.initializeRNG(1234);
-		LabelRankingDataset dataset = convertToLabelRankingDataSet(data);
-		InstanceBasedLabelRankingLearningAlgorithm learningAlgorithm = new InstanceBasedLabelRankingLearningAlgorithm();
-		InstanceBasedLabelRankingConfiguration config = learningAlgorithm.getAlgorithmConfiguration();
-		config.setRankAggregationAlgorithm(new KemenyYoungLearningAlgorithm());
-		learningModel = learningAlgorithm.train(dataset);
-	}
-
-}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/InstanceBasedLabelRankingKemenyYoungSQRTN.java

@@ -1,24 +1,0 @@
-package ranker.core.algorithms;
-
-import de.upb.cs.is.jpl.api.algorithm.baselearner.classification.knearestneighbor.KNearestNeighborConfiguration;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingConfiguration;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
-import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.kemenyyoung.KemenyYoungLearningAlgorithm;
-import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
-import de.upb.cs.is.jpl.api.math.RandomGenerator;
-
-public class InstanceBasedLabelRankingKemenyYoungSQRTN extends PreferenceRanker {
-	
-	@Override
-	protected void initialize() throws Exception {
-		RandomGenerator.initializeRNG(1234);
-		LabelRankingDataset dataset = convertToLabelRankingDataSet(data);
-		InstanceBasedLabelRankingLearningAlgorithm learningAlgorithm = new InstanceBasedLabelRankingLearningAlgorithm();
-		InstanceBasedLabelRankingConfiguration config = learningAlgorithm.getAlgorithmConfiguration();
-		config.setRankAggregationAlgorithm(new KemenyYoungLearningAlgorithm());
-		KNearestNeighborConfiguration baseConfig = (KNearestNeighborConfiguration) config.getBaseLearnerAlgorithm().getAlgorithmConfiguration();
-		baseConfig.setNumberOfNeighbors((int)Math.floor(Math.sqrt(dataset.getNumberOfInstances())));
-		learningModel = learningAlgorithm.train(dataset);
-	}
-
-}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/LinearRegressionRanker.java

@@ -1,22 +1,0 @@
-package ranker.core.algorithms;
-
-import java.util.HashMap;
-import java.util.Map;
-
-import weka.classifiers.Classifier;
-import weka.classifiers.functions.LinearRegression;
-import weka.core.Instances;
-
-public class LinearRegressionRanker extends RegressionRanker {
-
-	@Override
-	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
-		regressionModels = new HashMap<Classifier,Classifier>();
-		for (Classifier classifier : train.keySet()) {
-			LinearRegression lineReg = new LinearRegression();
-			lineReg.buildClassifier(train.get(classifier));
-			regressionModels.put(classifier, lineReg);
-		}
-	}
-
-}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/M5PRanker.java

@@ -1,21 +1,0 @@
-package ranker.core.algorithms;
-
-import java.util.HashMap;
-import java.util.Map;
-
-import weka.classifiers.Classifier;
-import weka.classifiers.trees.M5P;
-import weka.core.Instances;
-
-public class M5PRanker extends RegressionRanker {
-
-	@Override
-	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
-		regressionModels = new HashMap<Classifier,Classifier>();
-		for (Classifier classifier : train.keySet()) {
-			M5P m5p = new M5P();
-			m5p.buildClassifier(train.get(classifier));
-			regressionModels.put(classifier, m5p);
-		}
-	}
-}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/PerfectRanker.java

@@ -5,6 +5,7 @@ import java.util.List;
 
 import de.upb.cs.is.jpl.api.dataset.defaultdataset.relative.Ranking;
 import de.upb.cs.is.jpl.api.exception.algorithm.PredictionFailedException;
+import ranker.core.algorithms.preference.PreferenceRanker;
 import weka.classifiers.Classifier;
 import weka.core.Instance;
 

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/PerformanceOrder.java

@@ -1,4 +1,4 @@
-package ranker.core.evaluation;
+package ranker.core.algorithms;
 
 public enum PerformanceOrder {
 	ASCENDING,DESCENDING;

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/REPTreeRanker.java

@@ -1,22 +1,0 @@
-package ranker.core.algorithms;
-import java.util.HashMap;
-import java.util.Map;
-
-import weka.classifiers.Classifier;
-import weka.classifiers.trees.REPTree;
-import weka.classifiers.trees.RandomForest;
-import weka.core.Instances;
-
-public class REPTreeRanker extends RegressionRanker {
-
-	@Override
-	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
-		regressionModels = new HashMap<Classifier,Classifier>();
-		for (Classifier classifier : train.keySet()) {
-			REPTree repTree = new REPTree();
-			repTree.buildClassifier(train.get(classifier));
-			regressionModels.put(classifier, repTree);
-		}
-	}
-
-}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/package-info.java

@@ -1,0 +1,8 @@
+/**
+ * Provides different algorithms for ranking learning algorithms according to
+ * meta data.
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.core.algorithms;

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/preference/InstanceBasedLabelRankingKemenyYoung.java

@@ -1,0 +1,21 @@
+package ranker.core.algorithms.preference;
+
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingConfiguration;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.kemenyyoung.KemenyYoungLearningAlgorithm;
+import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
+import de.upb.cs.is.jpl.api.math.RandomGenerator;
+
+public class InstanceBasedLabelRankingKemenyYoung extends PreferenceRanker {
+
+	@Override
+	protected void initialize() throws Exception {
+		RandomGenerator.initializeRNG(1234);
+		LabelRankingDataset dataset = convertToLabelRankingDataSet(data);
+		InstanceBasedLabelRankingLearningAlgorithm learningAlgorithm = new InstanceBasedLabelRankingLearningAlgorithm();
+		InstanceBasedLabelRankingConfiguration config = learningAlgorithm.getAlgorithmConfiguration();
+		config.setRankAggregationAlgorithm(new KemenyYoungLearningAlgorithm());
+		learningModel = learningAlgorithm.train(dataset);
+	}
+
+}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/preference/InstanceBasedLabelRankingKemenyYoungSQRTN.java

@@ -1,0 +1,24 @@
+package ranker.core.algorithms.preference;
+
+import de.upb.cs.is.jpl.api.algorithm.baselearner.classification.knearestneighbor.KNearestNeighborConfiguration;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingConfiguration;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
+import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.rankaggregation.kemenyyoung.KemenyYoungLearningAlgorithm;
+import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
+import de.upb.cs.is.jpl.api.math.RandomGenerator;
+
+public class InstanceBasedLabelRankingKemenyYoungSQRTN extends PreferenceRanker {
+	
+	@Override
+	protected void initialize() throws Exception {
+		RandomGenerator.initializeRNG(1234);
+		LabelRankingDataset dataset = convertToLabelRankingDataSet(data);
+		InstanceBasedLabelRankingLearningAlgorithm learningAlgorithm = new InstanceBasedLabelRankingLearningAlgorithm();
+		InstanceBasedLabelRankingConfiguration config = learningAlgorithm.getAlgorithmConfiguration();
+		config.setRankAggregationAlgorithm(new KemenyYoungLearningAlgorithm());
+		KNearestNeighborConfiguration baseConfig = (KNearestNeighborConfiguration) config.getBaseLearnerAlgorithm().getAlgorithmConfiguration();
+		baseConfig.setNumberOfNeighbors((int)Math.floor(Math.sqrt(dataset.getNumberOfInstances())));
+		learningModel = learningAlgorithm.train(dataset);
+	}
+
+}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/preference/InstanceBasedLabelRankingRanker.java

@@ -1,4 +1,4 @@
-package ranker.core.algorithms;
+package ranker.core.algorithms.preference;
 
 import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.instancebasedlabelranking.InstanceBasedLabelRankingLearningAlgorithm;
 import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/preference/PairwiseComparisonRanker.java

@@ -1,4 +1,4 @@
-package ranker.core.algorithms;
+package ranker.core.algorithms.preference;
 
 import de.upb.cs.is.jpl.api.algorithm.baselearner.regression.linear.LinearRegression;
 import de.upb.cs.is.jpl.api.algorithm.learningalgorithm.labelranking.labelrankingbypairwisecomparison.LabelRankingByPairwiseComparisonConfiguration;

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/preference/PreferenceRanker.java

@@ -1,4 +1,4 @@
-package ranker.core.algorithms;
+package ranker.core.algorithms.preference;
 
 import java.util.ArrayList;
 import java.util.HashMap;
@@ -10,7 +10,8 @@ import de.upb.cs.is.jpl.api.dataset.defaultdataset.relative.Ranking;
 import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingDataset;
 import de.upb.cs.is.jpl.api.dataset.labelranking.LabelRankingInstance;
 import de.upb.cs.is.jpl.api.exception.algorithm.PredictionFailedException;
-import ranker.util.wekaUtil.WekaHelper;
+import ranker.core.algorithms.Ranker;
+import ranker.util.wekaUtil.WEKAHelper;
 import weka.classifiers.Classifier;
 import weka.core.Instance;
 import weka.core.Instances;
@@ -91,7 +92,7 @@ public abstract class PreferenceRanker extends Ranker {
 
 	protected LabelRankingDataset convertToLabelRankingDataSet(Instances data) throws Exception {
 		// Replace missing values as preference algorithm can't deal with those
-		Instances newData = WekaHelper.replaceMissingValues(data);
+		Instances newData = WEKAHelper.replaceMissingValues(data);
 
 		initializeLabels();
 

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/preference/package-info.java

@@ -1,0 +1,8 @@
+/**
+ * Contains rankers that predict rankings of learning algorithms on the basis of
+ * preference learning (label ranking).
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.core.algorithms.preference;

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/regression/LinearRegressionRanker.java

@@ -1,0 +1,22 @@
+package ranker.core.algorithms.regression;
+
+import java.util.HashMap;
+import java.util.Map;
+
+import weka.classifiers.Classifier;
+import weka.classifiers.functions.LinearRegression;
+import weka.core.Instances;
+
+public class LinearRegressionRanker extends RegressionRanker {
+
+	@Override
+	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
+		regressionModels = new HashMap<Classifier,Classifier>();
+		for (Classifier classifier : train.keySet()) {
+			LinearRegression lineReg = new LinearRegression();
+			lineReg.buildClassifier(train.get(classifier));
+			regressionModels.put(classifier, lineReg);
+		}
+	}
+
+}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/regression/M5PRanker.java

@@ -1,0 +1,21 @@
+package ranker.core.algorithms.regression;
+
+import java.util.HashMap;
+import java.util.Map;
+
+import weka.classifiers.Classifier;
+import weka.classifiers.trees.M5P;
+import weka.core.Instances;
+
+public class M5PRanker extends RegressionRanker {
+
+	@Override
+	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
+		regressionModels = new HashMap<Classifier,Classifier>();
+		for (Classifier classifier : train.keySet()) {
+			M5P m5p = new M5P();
+			m5p.buildClassifier(train.get(classifier));
+			regressionModels.put(classifier, m5p);
+		}
+	}
+}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/regression/REPTreeRanker.java

@@ -1,27 +1,22 @@
-package ranker.core.algorithms;
-
+package ranker.core.algorithms.regression;
 import java.util.HashMap;
 import java.util.Map;
 
 import weka.classifiers.Classifier;
+import weka.classifiers.trees.REPTree;
 import weka.classifiers.trees.RandomForest;
 import weka.core.Instances;
 
-/**
- * A ranker that uses random forests for predicting rankings.
- * 
- * @author Helena Graf
- *
- */
-public class RandomForestRanker extends RegressionRanker {
+public class REPTreeRanker extends RegressionRanker {
 
 	@Override
 	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
 		regressionModels = new HashMap<Classifier,Classifier>();
 		for (Classifier classifier : train.keySet()) {
-			RandomForest forest = new RandomForest();
-			forest.buildClassifier(train.get(classifier));
-			regressionModels.put(classifier, forest);
+			REPTree repTree = new REPTree();
+			repTree.buildClassifier(train.get(classifier));
+			regressionModels.put(classifier, repTree);
 		}
 	}
+
 }

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/regression/RandomForestRanker.java

@@ -1,0 +1,27 @@
+package ranker.core.algorithms.regression;
+
+import java.util.HashMap;
+import java.util.Map;
+
+import weka.classifiers.Classifier;
+import weka.classifiers.trees.RandomForest;
+import weka.core.Instances;
+
+/**
+ * A ranker that uses random forests for predicting rankings.
+ * 
+ * @author Helena Graf
+ *
+ */
+public class RandomForestRanker extends RegressionRanker {
+
+	@Override
+	protected void buildRegressionModels(Map<Classifier, Instances> train) throws Exception {
+		regressionModels = new HashMap<Classifier,Classifier>();
+		for (Classifier classifier : train.keySet()) {
+			RandomForest forest = new RandomForest();
+			forest.buildClassifier(train.get(classifier));
+			regressionModels.put(classifier, forest);
+		}
+	}
+}

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/regression/RegressionRanker.java

@@ -1,4 +1,4 @@
-package ranker.core.algorithms;
+package ranker.core.algorithms.regression;
 
 import java.util.ArrayList;
 import java.util.HashMap;
@@ -6,6 +6,7 @@ import java.util.List;
 import java.util.Map;
 import java.util.TreeMap;
 
+import ranker.core.algorithms.Ranker;
 import weka.classifiers.Classifier;
 import weka.core.Attribute;
 import weka.core.DenseInstance;
@@ -15,18 +16,17 @@ import weka.core.Instances;
 public abstract class RegressionRanker extends Ranker {
 
 	/**
-	 * Maps that contains a regression model for each classifier
-	 * (classifier -> regression model)
+	 * Maps learning algorithms to their regression models.
 	 */
 	protected Map<Classifier, Classifier> regressionModels;
 
 	/**
-	 * Map that contains a training data set for each regression model.
+	 * Maps regression models to their training data.
 	 */
-	protected HashMap<Classifier, Instances> map;
-	
+	protected HashMap<Classifier, Instances> trainingData;
+
 	/**
-	 * List with estimates of learning algorithm performances for last predicted
+	 * Contains estimates of learning algorithm performances for the last predicted
 	 * ranking.
 	 */
 	protected List<Double> estimates;
@@ -47,7 +47,7 @@ public abstract class RegressionRanker extends Ranker {
 		// Calculate results
 		for (Classifier classifier : regressionModels.keySet()) {
 			Instance newInstance = new DenseInstance(newFeatures.length, newFeatures);
-			newInstance.setDataset(map.get(classifier));
+			newInstance.setDataset(trainingData.get(classifier));
 			double result = regressionModels.get(classifier).classifyInstance(newInstance);
 			if (predictions.containsKey(result)) {
 				predictions.get(result).add(classifier);
@@ -83,8 +83,7 @@ public abstract class RegressionRanker extends Ranker {
 
 	@Override
 	protected void initialize() throws Exception {
-		// Initialize variable
-		map = new HashMap<Classifier, Instances>();
+		trainingData = new HashMap<Classifier, Instances>();
 
 		// Get all attributes
 		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
@@ -95,8 +94,8 @@ public abstract class RegressionRanker extends Ranker {
 
 		// Create new Instances for each target attribute
 		for (int i : targetAttributes) {
[…]

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/regression/package-info.java

@@ -1,0 +1,8 @@
+/**
+ * Contains rankers that predict rankings of learning algorithms on the basis of
+ * regression models.
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.core.algorithms.regression;

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/BestThreeLoss.java

@@ -3,6 +3,7 @@ package ranker.core.evaluation;
 import java.util.ArrayList;
 import java.util.List;
 
+import ranker.core.algorithms.PerformanceOrder;
 import weka.classifiers.Classifier;
 
 public class BestThreeLoss extends RankerEvaluationMeasure {

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/EvaluationHelper.java

@@ -16,6 +16,7 @@ import org.apache.commons.math3.stat.ranking.NaNStrategy;
 import org.apache.commons.math3.stat.ranking.TiesStrategy;
 
 import ranker.Util;
+import ranker.core.algorithms.PerformanceOrder;
 import ranker.core.algorithms.Ranker;
 import ranker.util.openMLUtil.OpenMLHelper;
 import ranker.util.wekaUtil.EstimationProcedure;

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/Loss.java

@@ -2,6 +2,7 @@ package ranker.core.evaluation;
 
 import java.util.List;
 
+import ranker.core.algorithms.PerformanceOrder;
 import weka.classifiers.Classifier;
 
 public class Loss extends RankerEvaluationMeasure {

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/RootMeanSquareError.java

@@ -9,7 +9,7 @@ import weka.classifiers.Classifier;
  * Calculated the difference between the predicted performance value of the
  * learning algorithm and its actual value and thus fives information about how
  * well the Ranker has learned this model. Rankers evaluated with this class
- * need to be sub types of {@link ranker.core.algorithms.RegressionRanker}.
+ * need to be sub types of {@link ranker.core.algorithms.regression.RegressionRanker}.
  * 
  * @author Helena Graf
  *

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/package-info.java

@@ -1,0 +1,7 @@
+/**
+ * Provides means of evaluating the performance of Rankers.
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.core.evaluation;

### 2018-03-14 ranker/src/main/java/ranker/core/metafeatures/GlobalCharacterizer.java

@@ -11,22 +11,21 @@ import org.apache.commons.lang.time.StopWatch;
 
 import org.openml.webapplication.fantail.dc.Characterizer;
 import org.openml.webapplication.fantail.dc.landmarking.GenericLandmarker;
-import org.openml.webapplication.fantail.dc.statistical.AttributeEntropy;
 import org.openml.webapplication.fantail.dc.statistical.Cardinality;
 import org.openml.webapplication.fantail.dc.statistical.NominalAttDistinctValues;
 import org.openml.webapplication.fantail.dc.statistical.SimpleMetaFeatures;
 import org.openml.webapplication.fantail.dc.statistical.Statistical;
-import org.openml.webapplication.features.GlobalMetafeatures;
-
 import weka.core.Instances;
 import weka.core.Utils;
 
+/**
+ * Characterizer that applies a number of Characterizers to a data set. Uses
+ * probing.
+ * 
+ * @author Helena Graf
+ *
+ */
 public class GlobalCharacterizer extends Characterizer {
-
-	private String[] ids;
-	private List<Characterizer> characterizers;
-
-	private ArrayList<Characterizer> batchCharacterizers;
 
 	private final String preprocessingPrefix = "-E \"weka.attributeSelection.CfsSubsetEval -P 1 -E 1\" -S \"weka.attributeSelection.BestFirst -D 1 -N 5\" -W ";
 	private final String cp1NN = "weka.classifiers.lazy.IBk";
@@ -34,94 +33,66 @@ public class GlobalCharacterizer extends Characterizer {
 	private final String cpASC = "weka.classifiers.meta.AttributeSelectedClassifier";
 	private final String cpDS = "weka.classifiers.trees.DecisionStump";
 
-	private Map<String, Double> computationTimes = new HashMap<String, Double>();
+	/**
+	 * The names of all the meta features that are computed by this characterizer
+	 */
+	protected String[] ids;
 
+	/**
+	 * The list of characterizers used in the computation of meta features
+	 */
+	protected ArrayList<Characterizer> characterizers;
+
+	/**
+	 * The names of the characterizers used
+	 */
+	protected Map<Characterizer, String> characterizerNames;
+
+	/**
+	 * The time it took to compute the meta features for each characterizer by name
+	 */
+	protected Map<String, Double> computationTimes = new HashMap<String, Double>();
+
[…]

### 2018-03-14 ranker/src/main/java/ranker/core/metafeatures/NoProbingCharacterizer.java

@@ -2,116 +2,39 @@ package ranker.core.metafeatures;
 
 import java.util.ArrayList;
 import java.util.Arrays;
-import java.util.HashMap;
-import java.util.List;
-import java.util.Map;
-import java.util.TreeMap;
 
-import org.apache.commons.lang.time.StopWatch;
 import org.openml.webapplication.fantail.dc.Characterizer;
-import org.openml.webapplication.fantail.dc.landmarking.GenericLandmarker;
 import org.openml.webapplication.fantail.dc.statistical.Cardinality;
 import org.openml.webapplication.fantail.dc.statistical.NominalAttDistinctValues;
 import org.openml.webapplication.fantail.dc.statistical.SimpleMetaFeatures;
 import org.openml.webapplication.fantail.dc.statistical.Statistical;
 
-import weka.core.Instances;
-import weka.core.Utils;
+/**
+ * A Characterizer that applies several characterizers to a data set, but does
+ * not use any probing.
+ * 
+ * @author Helena Graf
+ *
+ */
+public class NoProbingCharacterizer extends GlobalCharacterizer {
 
-public class NoProbingCharacterizer extends Characterizer {
-
-	private String[] ids;
-	private List<Characterizer> characterizers;
-
-	private ArrayList<Characterizer> batchCharacterizers;
-
-	private final String preprocessingPrefix = "-E \"weka.attributeSelection.CfsSubsetEval -P 1 -E 1\" -S \"weka.attributeSelection.BestFirst -D 1 -N 5\" -W ";
-	private final String cp1NN = "weka.classifiers.lazy.IBk";
-	private final String cpNB = "weka.classifiers.bayes.NaiveBayes";
-	private final String cpASC = "weka.classifiers.meta.AttributeSelectedClassifier";
-	private final String cpDS = "weka.classifiers.trees.DecisionStump";
-
-	private Map<String, Double> computationTimes = new HashMap<String, Double>();
-
+	/**
+	 * Constructs a new NoProbingCharacterizer. Construction is the same as for the
+	 * {@link ranker.core.metafeatures.GlobalCharacterizer}, except that only Characterizers that do not use probing
+	 * are initialized.
+	 * 
+	 * @throws Exception
+	 */
 	public NoProbingCharacterizer() throws Exception {
[…]

### 2018-03-14 ranker/src/main/java/ranker/core/metafeatures/package-info.java

@@ -1,0 +1,7 @@
+/**
+ * Provides means of computing meta features for a data set.
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.core.metafeatures;

### 2018-03-14 ranker/src/main/java/ranker/util/openMLUtil/OpenMLHelper.java

@@ -23,6 +23,10 @@ import weka.core.Attribute;
 import weka.core.Instances;
 import weka.core.converters.ConverterUtils.DataSource;
 
+/**
+ * @author Helena Graf
+ *
+ */
 public class OpenMLHelper {
 
 	/**

### 2018-03-14 ranker/src/main/java/ranker/util/openMLUtil/package-info.java

@@ -1,0 +1,7 @@
+/**
+ * Aids in getting data sets fom OpenML.
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.util.openMLUtil;

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/EstimationProcedure.java

@@ -5,7 +5,7 @@ import weka.core.Instances;
 
 /**
  * Estimation procedure interface. Represents a way of measuring the performance
- * of a classifier on a given data set, e.g. by using 10-fold-Crossvaliation. 
+ * of a classifier on a given data set, e.g. by using 10-fold cross-validation. 
  * 
  * @author Helena Graf
  *
@@ -14,20 +14,20 @@ import weka.core.Instances;
 public interface EstimationProcedure {
 	/**
 	 * Estimates the performance of the classifier on the data set according to the
-	 * evaluation measure given. Examples of estimation procedures are 33% Holdout
-	 * Set or 10-fold-Crossvalidation.
+	 * evaluation measure given. Examples of estimation procedures are 33% hold-out
+	 * set or 10-fold cross-validation.
 	 * 
 	 * @param classifier
 	 *            The classifier to be used for estimation.
 	 * @param evaluationMeasure
 	 *            The measure according to which the performance of the classifier
 	 *            is evaluated.
-	 * @param dataset
+	 * @param dataSet
 	 *            The data set on which the performance of the classifier is
 	 *            estimated.
-	 * @return The performance of the classifier on the dataset.
+	 * @return The performance of the classifier on the datas et.
 	 * @throws Exception
 	 */
-	public double estimate(Classifier classifier, EvaluationMeasure evaluationMeasure, Instances dataset)
+	public double estimate(Classifier classifier, EvaluationMeasure evaluationMeasure, Instances dataSet)
 			throws Exception;
 }

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/PredictiveAccuary.java

@@ -5,7 +5,7 @@ import weka.classifiers.evaluation.Evaluation;
 import weka.core.Instances;
 
 /**
- * Computes the predictive accuary of a classifier. 
+ * Computes the predictive accuracy of a classifier. 
  * 
  * @author Helena Graf
  *

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/StratifiedMCCV.java

@@ -8,7 +8,7 @@ import weka.classifiers.Classifier;
 import weka.core.Instances;
 
 /**
- * Measuring the performance of a classifier on a given data set by means of Monte Carlo Crossvalidation.
+ * Measures the performance of a classifier on a given data set by means of Monte Carlo Crossvalidation.
  * 
  * @author Helena Graf
  *
@@ -18,7 +18,7 @@ public class StratifiedMCCV implements EstimationProcedure {
 	final private double holdout;
 
 	/**
-	 * Construct a StratifiedMCCV estimation procedure.
+	 * Construct a StratifiedMCCV estimation procedure with the specified number of repetitions and size of hold-out set.
 	 * 
 	 * @param times How many times the procedure is to be repeated (results averaged).
 	 * @param holdout The size of the holdout set.
@@ -29,14 +29,19 @@ public class StratifiedMCCV implements EstimationProcedure {
 	}
 
 	@Override
-	public double estimate(Classifier classifier, EvaluationMeasure evaluationMeasure, Instances dataset)
+	public double estimate(Classifier classifier, EvaluationMeasure evaluationMeasure, Instances dataSet)
 			throws Exception {
 		double result = 0;
+		
+		// Split data set and evaluate classifier
 		for (int i = 0; i < times; i++) {
-			List<Instances> splits = WekaUtil.getStratifiedSplit(dataset, new Random(i), 1 - holdout);
+			List<Instances> splits = WekaUtil.getStratifiedSplit(dataSet, new Random(i), 1 - holdout);
 			result += evaluationMeasure.evaluate(classifier, splits.get(0), splits.get(1));
 		}
+		
+		// Average results
 		result /= times;
+		
 		return result;
 	}
 

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/WEKAHelper.java

@@ -1,0 +1,76 @@
+package ranker.util.wekaUtil;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import weka.core.Attribute;
+import weka.core.Instance;
+import weka.core.Instances;
+import weka.filters.unsupervised.attribute.ReplaceMissingValues;
+
+/**
+ * A collection of recurring tasks regarding WEKA.
+ * 
+ * @author Helena Graf
+ *
+ */
+public class WEKAHelper {
+
+	/**
+	 * Replaces missing values in the Instances object with the
+	 * {@link weka.filters.unsupervised.attribute.ReplaceMissingValues} filter.
+	 * Returns new Instances object without missing values.
+	 * 
+	 * @param instances
+	 *            Instances with missing values
+	 * @return New Instances without missing values
+	 * @throws Exception
+	 *             If
+	 *             {@link weka.filters.unsupervised.attribute.ReplaceMissingValues#setInputFormat(Instances)}
+	 *             causes an Exception
+	 */
+	public static Instances replaceMissingValues(Instances instances) throws Exception {
+		// Initialize filter
+		ReplaceMissingValues filter = new ReplaceMissingValues();
+		filter.setInputFormat(instances);
+
+		// Process all instances
+		for (int i = 0; i < instances.numInstances(); i++) {
+			filter.input(instances.instance(i));
+		}
+		filter.batchFinished();
+
+		// Create new Instances object
+		Instances filteredInstances = filter.getOutputFormat();
+		Instance processed;
+		while ((processed = filter.output()) != null) {
+			filteredInstances.add(processed);
+		}
+
+		return filteredInstances;
+	}
+
+	/**
+	 * Creates a new Instances object containing only the instances within and
+	 * including the specified bounds. The new Instances is created as a shallow
+	 * copy, it is only a view of the instances in the original object.
+	 * 
+	 * @param instances
+	 *            The Instances from which the subset is created
+	 * @param fromIndex
+	 *            The lower bound
+	 * @param toIndex
+	 *            The upper bound
+	 * @return A subset of the given Instances
+	 */
+	public static Instances subSet(Instances instances, int fromIndex, int toIndex) {
+		List<Instance> subList = instances.subList(fromIndex, toIndex);
+		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
+		for (int attribute = 0; attribute < instances.numAttributes(); attribute++) {
[…]

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/WekaHelper.java

@@ -1,49 +1,0 @@
-package ranker.util.wekaUtil;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import weka.core.Attribute;
-import weka.core.Instance;
-import weka.core.Instances;
-import weka.filters.unsupervised.attribute.ReplaceMissingValues;
-
-public class WekaHelper {
-	
-	/**
-	 * Replaces missing values in the Instances object given with the
-	 * {@link weka.filters.unsupervised.attribute.ReplaceMissingValues} filter.
-	 * Returns new Instances object without missing values.
-	 * 
-	 * @param data
-	 * @return
-	 * @throws Exception
-	 */
-	public static Instances replaceMissingValues(Instances data) throws Exception {
-		// Ensure no missing vaules
-		// TODO extract method
-		ReplaceMissingValues filter = new ReplaceMissingValues();
-		filter.setInputFormat(data);
-		for (int i = 0; i < data.numInstances(); i++) {
-			filter.input(data.instance(i));
-		}
-		filter.batchFinished();
-		Instances newData = filter.getOutputFormat();
-		Instance processed;
-		while ((processed = filter.output()) != null) {
-			newData.add(processed);
-		}
-		return newData;
-	}
-	
-	public static Instances subSet(Instances instances, int fromIndex, int toIndex) {
-		List<Instance> test = instances.subList(fromIndex, toIndex);
-		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
-		for (int attribute = 0; attribute < instances.numAttributes(); attribute++) {
-			attributes.add(instances.attribute(attribute));
-		}
-		Instances testInst = new Instances(instances.relationName(), attributes, 0);
-		test.forEach(instance -> testInst.add(instance));
-		return testInst;
-	}
-}

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/package-info.java

@@ -1,0 +1,8 @@
+/**
+ * Provides classes for the evaluation of WEKA classifiers and other useful
+ * functions from the WEKA context.
+ * 
+ * @author Helena Graf
+ *
+ */
+package ranker.util.wekaUtil;

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/RankerEstimationProcedure.java
some cleanup

@@ -5,7 +5,7 @@ import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 
-import org.apache.commons.lang.time.StopWatch;
+import org.apache.commons.lang3.time.StopWatch;
 
 import ranker.core.algorithms.PerfectRanker;
 import ranker.core.algorithms.Ranker;

### 2018-03-14 ranker/src/main/java/ranker/core/metafeatures/GlobalCharacterizer.java

@@ -7,7 +7,7 @@ import java.util.List;
 import java.util.Map;
 import java.util.TreeMap;
 
-import org.apache.commons.lang.time.StopWatch;
+import org.apache.commons.lang3.time.StopWatch;
 
 import org.openml.webapplication.fantail.dc.Characterizer;
 import org.openml.webapplication.fantail.dc.landmarking.GenericLandmarker;

### 2018-03-14 ranker/src/test/java/rankerTest/RankPredictionTest.java

@@ -28,7 +28,7 @@ public class RankPredictionTest {
 
 	@BeforeClass
 	public static void loadMetaData() throws Exception {
-		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("meta_computed.arff"),
+		BufferedReader reader = Files.newBufferedReader(FileSystems.getDefault().getPath("metaData_small_allPerformanceValues.arff"),
 				Util.charset);
 		testInstances = new Instances(reader);
 		targetAttributes = new ArrayList<Integer>();

### 2018-03-14 ranker/src/main/java/ranker/Rankprediction.java
more minor cleanup

@@ -51,7 +51,6 @@ public class Rankprediction {
 		Map<String,Double> metaFeatures = characterizer.characterize(instances);
 		
 		// Insert in the right order in instance
-		// TODO extract in class
 		Instance queryInstance = new DenseInstance(metaData.numAttributes());
 		for (int i = 0; i < metaData.numAttributes(); i++) {
 			if (!targetAttributes.contains(i)) {

### 2018-03-14 ranker/src/main/java/ranker/core/algorithms/Ranker.java

@@ -38,7 +38,7 @@ public abstract class Ranker {
 	 * @param data
 	 *            The training data
 	 * @param targetAttributes
-	 *            TODO
+	 *            The target attributes
 	 */
 	public void buildRanker(Instances data, List<Integer> targetAttributes) throws Exception {
 		// Check for sensible input

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/EvaluationHelper.java

@@ -198,8 +198,6 @@ public class EvaluationHelper {
 	 */
 	public static void generatePerformanceMeasures(List<Classifier> classifiers, List<Instances> datasets,
 			EvaluationMeasure evalM, EstimationProcedure estimProc, String filepath) {
-		// TODO add data set id
-
 		// Prepare table of results
 		ArrayList<Attribute> attributes = new ArrayList<Attribute>();
 		for (int i = 0; i < datasets.size(); i++) {

### 2018-03-14 ranker/src/main/java/ranker/core/evaluation/LeaveOneOut.java

@@ -101,7 +101,6 @@ public class LeaveOneOut extends RankerEstimationProcedure {
 			writer.flush();
 			writer.close();
 		} catch (IOException e) {
-			// TODO Auto-generated catch block
 			e.printStackTrace();
 		}
 	}

### 2018-03-14 ranker/src/main/java/ranker/core/metafeatures/MetaFeatureHelper.java

@@ -50,7 +50,6 @@ public class MetaFeatureHelper {
 			attributes.add(new Attribute(dataQuality));
 		}
 	
-		// TODO isolate in class + clean up
 		HashMap<String, List<Double>> computationTimes = new HashMap<String, List<Double>>();
 		for (String chara : characterizer.getCharacterizerNames()) {
 			computationTimes.put(chara, new ArrayList<Double>());
@@ -78,14 +77,12 @@ public class MetaFeatureHelper {
 			try {
 				openMLData = OpenMLHelper.getInstancesById(dataSetId);
 			} catch (IOException e) {
-				// TODO logging maybe / outprint here
 				System.out.println("Couldn't get " + dataSetId);
 				continue;
 			}
 	
 			Map<String, Double> dataQualities = characterizer.characterize(openMLData);
 	
-			// TODO remove/ disable
 			Map<String, Double> times = characterizer.getMetaFeatureComputationTimes();
 			System.out.println(times);
 			for (String metaFeature : times.keySet()) {
@@ -123,13 +120,11 @@ public class MetaFeatureHelper {
 					}
 	
 				} catch (IOException e) {
-					// TODO Auto-generated catch block
 					e.printStackTrace();
 				}
 			});
 		}
 		
-		//TODO make this more efficient
 		BufferedWriter writer = Files.newBufferedWriter(FileSystems.getDefault().getPath("MetaStats_new.txt"), Util.charset);
 		for (String chara : computationTimes.keySet()) {
 			List<Double> values = computationTimes.get(chara);
@@ -141,7 +136,6 @@ public class MetaFeatureHelper {
 					writer.write(value + ";");
 					writer.newLine();
 				} catch (IOException e) {
-					// TODO Auto-generated catch block
 					e.printStackTrace();
 				}
 			});
@@ -209,14 +203,11 @@ public class MetaFeatureHelper {
 					if (line != null) {
 						value = Double.parseDouble(line);
 					} else {
-						// TODO hack to avoid NaNs actually has to be worst value for performance
-						// measure used!
 						value = 0;
 					}
 					instance.setValue(attIndex, value);
 	
 				} catch (IOException e) {
-					// TODO Auto-generated catch block
 					e.printStackTrace();
 				}
 			});

### 2018-03-14 ranker/src/main/java/ranker/util/openMLUtil/OpenMLHelper.java

@@ -74,8 +74,6 @@ public class OpenMLHelper {
 	 * @throws Exception
 	 */
 	public static void createDataSetIndex(int maxNumFeatures, int maxNumInstances) throws Exception {
-		// TODO more elaborate filters maybe?
-		
 		// For statistics
 		int unfiltered;
 		int filteredBNG = 0;

### 2018-03-14 ranker/src/main/java/ranker/util/wekaUtil/WEKAHelper.java

@@ -1,11 +1,14 @@
 package ranker.util.wekaUtil;
 
+import java.io.File;
+import java.io.IOException;
 import java.util.ArrayList;
 import java.util.List;
 
 import weka.core.Attribute;
 import weka.core.Instance;
 import weka.core.Instances;
+import weka.core.converters.ArffSaver;
 import weka.filters.unsupervised.attribute.ReplaceMissingValues;
 
 /**
@@ -72,5 +75,19 @@ public class WEKAHelper {
 		Instances subSet = new Instances(instances.relationName(), attributes, instances.numInstances());
 		subList.forEach(instance -> subSet.add(instance));
 		return subSet;
+	}
+
+	/**
+	 * Takes an Instances object and saves it in the .arff format with the filename
+	 * as the relation name.
+	 * 
+	 * @param instances
+	 * @throws IOException
+	 */
+	public static void saveAsArff(Instances instances) throws IOException {
+		ArffSaver saver = new ArffSaver();
+		saver.setInstances(instances);
+		saver.setFile(new File(instances.relationName()));
+		saver.writeBatch();
 	}
 }

### 2018-03-14 Writing/Thesis/content/chapter-fundamentals.tex
Final version

@@
 
-A popular approach is using a stratified split, for example splitting the data into 70\% training and 30\% test data, with the important aspect that both subsets have equal (or at least very similar) ratios of classes [Reference Missing].
+A popular approach is using a stratified split, for example splitting the data into 70\% training and 30\% test data, with the important aspect that both subsets have equal (or at least very similar) ratios of classes \cite{kohavi1995study}.
 The learning algorithm is then trained with one part of the data (usually the larger one), and its performance tested on the other.
@@
 Results are averaged.
-This process is called k-fold (stratified) cross-validation [Reference Missing].
-A variant of this is Monte Carlo cross-validation, where after each time the algorithm has been trained and evaluated, a new split is randomly computed [Reference Missing].
+This process is called k-fold (stratified) cross-validation \cite{kohavi1995study}.
+A variant of this is Monte Carlo cross-validation, where after each time the algorithm has been trained and evaluated, a new split is randomly computed \cite{xu2001monte}.
 This especially causes the fact that the number of folds does not dictate the ratio of the split; one could for example have 5-folds Monte Carlo cross-validation with a 70\%/30\% train/test split.
@@
 Other cases are not considered.
-The simplest version of the statistic, called $T_A$ is then defined as
+The simplest version of the statistic, called $T_A$ \cite{Kendall2} is then defined as
 
@@
 
-To account for ties in the rankings, a second statistic, $T_B$ is defined as
+To account for ties in the rankings, a second statistic, $T_B$ \cite{Kendall2} is defined as
 

### 2018-03-14 Writing/Thesis/Tex/content/acknowledgement.tex
Create Presentation

\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\chapter*{Acknowledgement}
\label{sec:acknowledgement}
\vspace*{-10mm}

I would like to thank Prof. Dr. Hüllermeier for trusting me with this topic, and for his useful feedback on the matter. A very special gratitude goes out to Marcel Wever and Felix Mohr, without whose helpful insights and encouragement this thesis could not have been completed. Thank you for your explanations when I was struggling, and for pointing me in the right direction when I ran the risk of losing focus. My sincere thanks also goes to the proofreaders, who meticulously corrected my spelling and pointed out weak explanations. Last but not least, I am grateful for my family and friends for always supporting me and believing in me, and reminding me that I, too, need some sleep once in a while.

### 2018-03-14 Writing/Thesis/Tex/content/chapter-conclusion.tex
Create Presentation

--- 2018-03-12 Writing/Thesis/content/chapter-conclusion.tex
@@
 Since the significant advantage of any approach was lost regarding B3L when moving from the full meta data to the reduced meta data without probing, this might be especially interesting.
-One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable.
-An effect on the time and quality of predictions for larger data sets would have to be examined still.
+One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable, and even on the large MNIST data set only represented 8.5 minutes out of a computation time of almost five hours for the full set of meta features.
+An effect on the time required for and quality of predictions for other larger data sets would have to be examined still.
 

### 2018-03-14 Writing/Thesis/Tex/content/chapter-evaluation.tex
Create Presentation

--- 2018-03-14 Writing/Thesis/content/chapter-evaluation.tex
@@
 For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data.
-The stratified split was generated with the help of JAICore, `A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing].
+The stratified split was generated with the help of JAICore, `A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' \cite{jaicore}.
 When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.
@@
 % Implementation of measures
-For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used [REFERENCE MISSING].
+For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used \cite{apache}.
 Regarding the Mann-Whitney U, the strategy for ties was set to averaging, and the NaNs were set to be removed before the analysis was started.

### 2018-03-14 Writing/Thesis/Tex/content/chapter-introduction.tex
Create Presentation

--- 2018-03-09 Writing/Thesis/content/chapter-introduction.tex
@@
 In a white paper, the International Data Corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data only 3\% were tagged as to enable further processing, and only 0.5\% were analyzed \cite{gantz2012the}.
-A follow-up paper in 2017 projects that in 2025, 15\% of the estimated 163ZB of global data will be tagged, and approximately 3\% analyzed \cite{gantz2017data}.
+A follow-up paper in 2017 projects that in 2025, 15\% of the estimated 163 ZB of global data will be tagged, and approximately 3\% analyzed \cite{gantz2017data}.
 While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available.
@@
 The two approaches include one regression-based approach that breaks down the problem of predicting a ranking into predicting a single performance value for each algorithm and then ranking them accordingly, and a preference based approach that is concerned with learning the rankings directly.
-Especially in the case of regression based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.
+Especially in the case of regression-based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.
 
@@
 In order to conduct this evaluation, an implementation of the two approaches is needed.
-A third goal is thus the development of an AutoML-tool that, after a pre-processing phase, returns a ranking of classifiers for a given data set, using either regression- or preference models for the prediction.
+A third goal is thus the development of an AutoML-tool that, after a pre-processing phase, returns a ranking of classifiers for a given data set, using either regression or preference models for the prediction.
 The pre-processing phase constitutes of recording classifier performances on a number of data sets together with properties of the data sets to serve as training data, and training the regression models or preference model respectively.
